### 2017-06-11 Article/MIRSVM_corrected.tex
Initial commit

%\begin{filecontents*}{MIRSVM.eps}
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
\RequirePackage{fix-cm}
\documentclass[smallcondensed]{svjour3}                 
\smartqed  
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath,amssymb,mathtools,float,times,bm,tikz,proof,tabularx,capt-of,natbib}
\usepackage{graphicx,amsfonts,array,url,algorithm,algorithmicx,algpseudocode,booktabs}
\usepackage[flushleft]{threeparttable}
\usepackage[top=1in,bottom=1in,right=1in,left=1in]{geometry}
\usepackage{tikz-cd,adjustbox}
\usetikzlibrary{shapes.geometric,arrows,automata,positioning}
\usepackage{setspace}
\let\Algorithm\algorithm
\renewcommand\algorithm[1][]{\Algorithm[#1]\setstretch{1}}

\newcommand{\iitem}{\item[-]}
\newcommand{\set}[1]{{\left\{#1\right\}}} 
\newcommand{\norm}[1]{{||#1||}} 
\newcommand{\st}{{\,|\,}} 
\newcommand{\reals}{{\mathbb R}}
\newcommand{\ints}{{\mathbb Z}}
\newcommand{\spa}[1]{\mathcal{#1}}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\overfullrule=5pt

\journalname{Machine Learning}

\begin{document}

\tikzstyle{decision} = [diamond, draw, text centered, inner sep=3pt]
\tikzstyle{block} = [rectangle, draw, fill=gray!20,text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{arrow} = [thick,->,>=stealth]

\title{MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives}

\author{Gabriella Melki \and
        Alberto Cano			\and
        Sebasti\'an Ventura
}

\institute{Gabriella Melki \at
			Virginia Commonwealth University, 401 W. Main St. E2264, Richmond, VA 23284\\
            \email{melkiga@vcu.edu}          
           \and
           Alberto Cano \at
           	Virginia Commonwealth University, 401 W. Main St. E4251, Richmond, VA 23284\\
            \email{acano@vcu.edu}
           \and
           Sebasti\'an Ventura \at
            University of C\'{o}rdoba, ``Albert Einstein Building'', 3rd floor, 14071 C\'{o}rdoba, Spain\\
            \email{sventura@uco.es}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
\textit{Multiple-instance learning} (MIL) is a generalization of \textit{supervised learning}, where samples are represented by labeled bags, each containing sets of instances. The individual labels of the samples within a bag are unknown, and labels are assigned based on a multi-instance assumption. One of the major complexities associated with this type of learning is the ambiguous relationship between a bag's label and the instances it contains. This paper proposes a novel support vector machine (SVM) multiple-instance formulation and presents an algorithm with a bag-representative selector that trains the SVM based on bag-level information, named MIRSVM. The contribution is able to identify instances that highly impact classification, i.e. bag-representatives, for both positive and negative bags, while finding the optimal class separation hyperplane. Unlike other multi-instance SVM methods, this approach eliminates possible class imbalance issues by allowing both positive and negative bags to have at most one representative, while highlighting the instances that contribute most to the classification model. The experimental study evaluates and compares the performance of this proposal against $10$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis. The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as this proposal's overall superior performance against other multi-instance SVM models. 
\keywords{Machine learning \and multiple-instance learning \and support vector machines \and bag-level multi-instance classification \and bag-representative selection}
\end{abstract}

\section{Introduction}\label{intro}
In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns that exist between training samples and their class label. \textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008,Wei2016155}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.

The difference between MIL and traditional learning is the nature of the data samples. In the traditional setting, each sample is represented by a single feature vector that has its own class label. In multi-instance learning, a sample is considered to be a \textit{bag} that contains multiple instances, and is associated with a single label. The individual labels of the samples within a bag, referred to as \textit{instances}, are unknown, and labels are assigned based on a multi-instance assumption, or hypothesis. Introduced by~\cite{Dietterich1997}, the standard MI assumption states that a bag is labeled as positive if and only if it contains at least one positive instance. More recently, other MI hypotheses and frameworks have been proposed by~\cite{Foulds2010} to encompass a wider range of applications with multi-instance data.

One of the major complexities associated with multi-instance learning is the ambiguity of the relationship between a bag label and instances within the bag~\citep{Alpaydin2015}. This stems from the standard MIL assumption, where the underlying distribution among instances within positive bags is unknown. All that is known is that at least one instance has a positive label within a positive bag. There have been different attempts to overcome this complexity. One approach involves ``flattenning" the MIL datasets, meaning samples contained in positive bags each adopt a positive label, allowing the use of classical supervised learning techniques~\citep{Ray2005}. This approach assumes that positive bags contain a significant number of positive samples, which may not be the case, causing the classifier to mislabel negative instances within the bag, decreasing the power of the resulting MIL model.

To overcome this, a different MIL approach was proposed, where subsets of instances are selected from positive bags for classifier training~\citep{Maron1998,Zhang2001}. One drawback of this type of method is that the resulting training datasets become imbalanced towards positive instances by significantly decreasing the number of negative instances. The performance of these methods deteriorates when more instances are selected as subsets than needed~\citep{Carbonneau2016,Faria2017196,Vanwinckelen2016}. Our proposal aims to deal with this drawback by minimizing class imbalance. This is achieved by optimally selecting bag-representatives from both classes using Support Vector Machines.

Support Vector Machines (SVMs) represent a set of supervised, linear and nonlinear, classification and regression methods that have theoretical foundations on Vapnik-Chervonenkis (VC) theory~\citep{Huang2006,Schoelkopf2002}. SVM models are similar to other machine learning algorithms and techniques, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, which makes them a useful data mining tool for various real-world applications.

To address the limitations presented by MIL algorithms, this paper proposes a novel support vector machine formulation with a bag-representative selector, called Multiple-Instance Representative Support Vector Machine (MIRSVM). SVMs are known to perform well when data is limited, therefore combining them with a bag-representative selector aims to remedy class imbalance caused by limited positive bags, without assuming their internal distributions. The algorithm selects bag-representatives iteratively according to the standard MI assumption, ensuring known information, such as the negative bag labels, are fully utilized during the training process. The optimal separating hyperplane between bags is then found with respect to the bag-representatives using a Gaussian kernel and a quadratic programming solver. The optimal set of representatives is found when they have stopped changing from one iteration to the next. The algorithm does not assume any distribution of the instances and is not affected by the number of samples within a bag, making it applicable to a variety of contexts. The key contributions of this work include,
\begin{itemize}
\iitem Reformulating the traditional primal L$1$-SVM problem to optimize over bags, rather than instances, ensuring all the information contained within each bag is utilized during training, while defining bag representative selector criteria.

\iitem Deriving the dual multi-instance SVM problem, with the Karush-Kuhn-Tucker necessary and sufficient conditions for optimality. The dual is maximized with respect to the Lagrange multipliers and provides insightful information about the resulting sparse model. The dual formulation is kernelized with a Gaussian radial basis function, which calculates the distances between bag representatives.

\iitem Devising a unique bag-representative selector method that makes no presumptions about the underlying distributions of the instances within each bag, while maintaining the default MIL assumption. This approach eliminates the issue of class imbalance caused by techniques such as flattening or subsetting positive instances from each bag. The key feature of MIRSVM is its ability to identify instances (support vectors) within positive and negative bags that highly impact the model.
\end{itemize}

This work is organized as follows. First, the notation used throughout the paper is provided, the MIL problem is formalized, and recent multiple-instance learning methods, traditional support vector machines, and state-of-the-art multi-instance SVM methods are reviewed in Section~\ref{sec:background}. The primal L$1$-SVM is formulated with respect to optimizing over bags, the dual formulation is then derived, along with the conditions for optimality, and the proposed algorithm, MIRSVM, is listed and described in Section~\ref{sec:contribution}. Section~\ref{sec:experiments} presents the experimental environment, including results from various metrics, run-time, and non-parametric statistical analysis over $15$ benchmark MI datasets compared with $10$ state-of-the-art algorithms. Finally, Section~\ref{sec:conclusion} presents the conclusions of this contribution.

\section{Background}\label{sec:background}
This section defines the notation that will be used throughout the paper, and reviews related works on multi-instance learning, traditional support vector machines, and multi-instance support vector machines.

\subsection{Notation}\label{subsec:notation}
Let $\mathcal{D}$ be a training dataset of $n$ bags. Let $\bm{Y} \in \mathcal{D}$ be a vector of $n$ labels corresponding to each bag, having a domain of $\bm{Y} \in \set{-1,\,+1}^n$. Let $\bm{X} \in \mathcal{D}$ be a matrix consisting of $d$ input variables and $m$ instances, having a domain of $\bm{X} \in \mathbb{R}^{m \times d}$. Let $\bm B$ be the set of bags which contain a number of instances, sometimes of different size, and usually non-overlapping, such as $\bm{B}_I = \{\bm x_{1}, \ldots, \bm x_{|\bm B_I|}\}$ for index set $I \subseteq \set{1,\ldots,n}$, where $|\bm B_I|$ is the number of instances in bag $I$. Using the training dataset $\mathcal{D} = \{(\bm B_1,Y_1), \ldots, (\bm B_n,Y_n)\}$, the goal is to learn a model $f : \bm{X} \times Y$, that assigns a label, $Y_I \in \set{-1,\,+1}$, for each input bag $\bm{B}_I$. The model will then be used to predict the labels of new, unlabeled, and unseen input bags. Table~\ref{tab:Notation} provides a summary of the notation used in this paper.
\begin{table}
\caption{Summary of notation used throughout the paper}\label{tab:Notation}
\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}l}
\hline\noalign{\smallskip}
Definition & Notation\\ 
\noalign{\smallskip}\hline\noalign{\smallskip}
Number of Bags & $n$ \\
Number of Instances & $m$ \\
Number of Input Attributes & $d$ \\
Set of Bags & $\bm B = \set{\bm B_1,\, \ldots,\, \bm B_n}$ \\
Bag Index Set & $I \in \ints_+^n$ \\
Input Space & $\bm{X} \in \mathbb{R}^{m \times d}$ \\
Bag $I$ & $\bm B_I = \set{\bm x_i \st \forall i \in I}$ \\
Input Instance $i$ from Bag $I$ & $\bm{x}_i = (x_{1}, \ldots, x_{d}),\, i \in I$ \\
Bag Labels & $\bm{Y} \in \{-1,\,1\}^n$ \\
Individual Instance Label $i$ & $y_i \in \set{-1,+1}$ \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Full Multi-Instance Training Dataset & $\mathcal{D} = \{(\bm B_1,Y_1), \ldots, (\bm B_n,Y_n)\}$ \\
Full Single-Instance Training Dataset & $\mathcal{S} = \{(\bm x_1,y_1), \ldots, (\bm x_m,y_m)\} $\\
\noalign{\smallskip}\hline
\end{tabularx}
\end{table}

\subsection{Multiple-Instance Learning}\label{subsec:mil}
In traditional binary classification problems, the goal is to learn a model that maps input samples to labels, $f: \reals^{m \times d} \rightarrow Y^m \in \set{-1,\,+1}$. Multiple instance learning generalizes this framework and makes weaker assumptions about sample labeling. In the MIL case, samples are called \textit{bags} and each bag contains one or more input instances. Each bag is assigned a label, unlike traditional classification problems, where individual samples are assigned a label. Input instances, $\set{\bm x_1,\, \bm x_2,\, \ldots,\, \bm x_m}$, are grouped into bags with unique identifiers, $\bm B = \set{\bm B_1,\, \bm B_2,\, \ldots,\, \bm B_n \st \bm B_I = \set{\bm x_i \st \forall i \in I}}$, $\forall I \in \set{1, \ldots, n}$ and assigned a label, $Y_I$. An example representation of an MI dataset is shown in Figure~\ref{fig:mirep}.

In MIL, the goal is to train a classifier that predicts the label of an unseen bag, $f(\bm B_{n+1}) \rightarrow Y_{n+1}$~\citep{Amores2013}. In order to build a classifier without any knowledge of the individual training instance labels,~\cite{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the domain of drug-activity prediction, shown in Equation~\ref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
\begin{equation}
\centering \label{eqn:stas}
 Y_I = \begin{cases}
			+1 & \text{if }\exists\, y_i = +1,\, \forall i \in I \\
			-1 & \text{otherwise}.
		  \end{cases}
\end{equation}

This implies that individual instance labels $y_i$ exist, but are not known during training. Equation~\ref{eqn:stas} can also be rewritten as Equation~\ref{eqn:stasmax} for simplicity:
\begin{equation}
\centering \label{eqn:stasmax}
Y_I = \text{argmax}_{\forall i \in I}\,\,\, y_i.
\end{equation}

In addition to the SMI assumption, alternative MI assumptions have been proposed to date~\citep{Foulds2010}. A recent review describing the taxonomy of multi-instance classification was presented by~\cite{Amores2013}. The review presents various methods and algorithms used in literature which are categorized based on their approach to handling the MI input space. Instance-based classifiers that fall under the \textit{instance-space paradigm}, aim to separate instances in positive bags from those in negative ones. Bag-level classifiers (\textit{bag-space paradigm}) treat each bag as a whole entity, implicitly extracting information from each bag in order to accurately predict their labels. Methods that fall under the \textit{embedded-space paradigm} map the input bags to a single feature vector that explicitly encapsulates all the relevant information contained within each bag.

Instance-based methods that follow the SMI assumption attempt to identify desirable instance properties that make a bag positive. One traditional method in this category is the Axis-Parallel Rectangle (APR)~\citep{Dietterich1997}, which trains a model that assigns a positive label to an instance if it belongs to an axis-parallel rectangle in feature space, and assigns a negative label otherwise. The APR is optimized by maximizing the number of positive bags in the training set containing at least one instance in the APR, while concurrently maximizing the number of negative bags that do not contain any instance in the APR. Another similar method is the Diverse Density (DD)~\citep{Maron1998} framework which is maximized for instances in feature space that are near at least one instance in a positive bag and far from all instances in negative bags. In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\cite{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\cite{Auer2004} present a boosting approach~\citep{Schapire19981651} that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall). This approach is similar to that of APR and DD, except that~\cite{Auer2004} propose computing optimal balls per positive bags. A major challenge affecting these methods is that the distributions of the positive and negative bags affect their performance. Methods based on the DD metric~\citep{Chen2004,Chen2006,Carbonneau2016,Zhang2001} assume the positive instances form a cluster, which may not be the case. Alternatively~\cite{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited. 
\begin{figure*}
\centering
\begin{tabular}{|c|ccccc|c|}
\hline
$\bm B$ & $F_1$ & $F_2$ & $F_3$ & \ldots & $F_d$ & $Y$ \\        
\hline
    	  & 0.1 & 0.8 & 2.5 & \ldots & 0.8 &    \\        
    $B_1$ 	  & 0.2 & 2.0 & 5.5 & \ldots & 3.0 & POS \\
    	  & 0.1 & ?   & 4.5 & \ldots & 0.1 &    \\
\hline
    	  & 1.5 & 4.0 & 0.8 & \ldots & 0.1 &    \\
    	  & 0.8 & 0.4 & 2.9 & \ldots & 1.1 &    \\
    $B_2$	  & 2.3 & 0.2 & 4.0 & \ldots & 5.5 & NEG \\
    	  & 6.7 & 5.0 & ?   & \ldots & 0.5 &    \\
    	  & 0.1 & 4.0 & 8.7 & \ldots & 3.3 &    \\
\hline
  \end{tabular}
  \caption{Example of multi-instance data representation. The figure shows a sample binary MI dataset with $2$ bags, identified as $B_1$ and $B_2$. The bags each contain differing number of instances, each with $d$ dimension, and are assigned positive and negative labels indicated by column $Y$. Missing instance feature values are denoted by a question mark.}%
  \label{fig:mirep}%
\end{figure*}

Some methods in literature~\citep{Ray2005,Viola2005}, such as Simple-MI~\citep{Dong2006}, transform the MI dataset to a traditional instance-level dataset. Simple-MI represents each bag with the mean vector of the instances within it. This approach was evaluated by~\cite{Bunescu2007} and they proposed mapping each bag to a max-min vector, a concatenation of the features with the highest and lowest values. The major disadvantage of these types of approaches is that they assume the distribution the instances in positive bags is positive, when it may not be.

An extension of traditional single-instance $k$-nearest neighbors method (KNN) was proposed by~\cite{Wang2000} to be applied to the bag-level, named CitationKNN. This method uses a distance function between bags in order to determine bag similarities. Not only are the set of closest bags to a single bag  considered, but also how many bags is the single bag closest to. A voting scheme is then used to determine the bag class labels.~\cite{Xu2011} proposed a multi-instance Decision-Based Neural Network (MI-DBNN), a probabilistic variant of the traditional DBNN, which is a neural network with a modular structure~\citep{Herrera2016}.

~\cite{Blockeel2005} introduced the Multi-Instance Tree Inducer (MITI), based on the standard MI assumption, which uses decision trees as a heuristic to solve the MI problem. This approach aims to identify whether an instance within a bag is truly positive and eliminate false positives within the same bag. The disadvantage of this approach stems from removing instances considered as false positives from partially grown trees without updating the existing tree structure.~\cite{Bjerring2011} then enhanced this approach by creating the method Multi-Instance Rule Induction (MIRI). The algorithm aims to eliminate any possibility of a suboptimal split because the tree is discarded and regrown. Other popular methods include MIBoost~\citep{Hall2009}, MIWrapper~\citep{Hall2009}, and Two-Level Classifier (TLC)~\citep{Wang2014}.

For most of the methods described above, implicit or explicit assumptions have been made about the distribution of the data. Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}. The proposed method, MIRSVM, is a general method that uses support vector machines to design a MIL model without making prior assumptions about the data. Classifiers of this type are known to provide better generalization capabilities and performance, as well as sparser models.

\subsection{Support Vector Machines}\label{subsec:svms}
Most classical machine learning techniques require knowledge of the data distribution in order to learn accurate models~\citep{Alabdulmohsin2016215,Suzumura20171}. This is a serious restriction because, in most cases, the distribution of the data is unknown. Another disadvantage of these methods stems from high dimensional, sparse datasets, which are very common in real-world applications~\citep{durrant2015random}. Small sample size also poses problems of model reliability, especially when coupled with high dimensional feature spaces. SVMs represent learning techniques that have been introduced under the \textit{structural risk minimization} (SRM) framework and VC theory~\citep{Kecman2001}. Rather than optimizing over L1 or L2 norms and classification error, SVMs perform SRM~\citep{Shalev2014}, minimizing the expected probability of classification error, resulting in a generalized model without making assumptions about the data distribution~\citep{Cortes1995}.

SVMs are a particularly useful for learning linear predictors in high dimensional feature spaces, which is a computationally complex learning problem. In the context of classification, this problem is approached by searching for the optimal \textit{maximal margin} of separability between classes. A training set $\mathcal{D}$ is \textit{linearly separable} if a halfspace exists, $(\bm{w},b)$, such that $y_i = \text{sign }(\langle \bm{w},\bm{x}_i\rangle+b), \forall i \in \{1,\ldots,m\}$, where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, and $b \in \reals$ is a bias term. All halfspaces, defined as $d(\bm{x}_i) = \langle \bm{w},\bm{x}_i\rangle + b$, satisfying $y_i \left(\langle \bm{w},\bm{x}_i\rangle + b\right) > 0,\,\, \forall i \in \{1,\ldots,m\}$, have no error. This hard constraint is associated with the \textit{Hard-Margin SVM}. No feasible solution exists for the Hard-Margin SVM problem if the dataset is non-linearly separable, which is the case for most datasets. To overcome this,~\cite{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:
\begin{subequations} 
\label{eq:primalsvm}
\begin{alignat}{2}
\min\limits_{\bm w,b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{m}\sum_{i=1}^m \xi_i \tag{\ref{eq:primalsvm}} \\ 
\text{s.t.}& {\,\,} y_i(\langle\bm{w},\bm{x}_i\rangle + b) \geq 1 - \xi_i,\,\, \forall i \in \{1,\ldots,m\}  \\
{} & {\,\,} \xi_i \geq 0,\,\, \forall i \in \{1,\ldots,m\},
\end{alignat}
\end{subequations} 
where $C \in \reals$ is the penalty parameter that controls the trade-off between margin maximization and classification error minimization, penalizing large norms and errors. The slack variable $\bm \xi \in \reals^m$ allows for optimizing over sample errors. The resulting hyperplane is called \textit{soft-margin hyperplane}. Although the Soft-SVM learns an optimal hyperplane, if the training data set is not linearly separable, the classifier learned may not have a good generalization capability~\citep{Nocedal2006}. Generalization and linear separability can be enhanced by mapping the original input space to a higher dimensional dot-product space by using a kernel function shown in Equation~\ref{eqn:kerneltrick}:
\begin{equation}
\spa{K}\left(\bm{x}_i,\bm{x}_j\right) = \langle \phi\left(\bm{x}_i\right),\,\phi\left(\bm{x}_j\right)\rangle,
\label{eqn:kerneltrick}
\end{equation}
where $\phi\left(\cdot\right)$ represents a function mapping from the original feature space to a higher dimensional space. This kernel mapping is particularly helpful when solving the dual SVM optimization problem shown in Equation~\eqref{eq:dualsvm}. Rather than calculating the inner product of two mapped vectors, their corresponding \textit{scalar} kernel value can be used. 
\begin{subequations}
\label{eq:dualsvm}
\begin{alignat}{2}
\max\limits_{\bm \alpha} &\,\,\,\, \frac{1}{2}\sum_{i,j=1}^m{\alpha_i \alpha_jy_iy_j\spa{K}\left(\bm{x}_i,\bm{x}_j\right)} - \sum_{i=1}^m \alpha_i \tag{\ref{eq:dualsvm}} \\ 
\text{s.t.} &\,\,\,\, \sum_{i=1}^m \alpha_iy_i = 0,  \\
&\,\,\,\, 0 \leq \alpha_i \leq \frac{C}{m},\,\, \forall i \in \{1,\ldots,m\}. 
\end{alignat}
\end{subequations}

A traditional and widely used method of solving the L1-SVM problem is the \textit{Sequential Minimal Optimization} (SMO) technique proposed by~\cite{Platt1998}. It is an iterative procedure that divides the SVM dual problem into a series of sub-problems, which are then solved analytically by finding the optimal $\bm \alpha$ values that satisfy the Karush-Kuhn-Tucker (KKT) conditions~\citep{Boyd2004}. Although SMO is guaranteed to converge, heuristics are used to choose $\bm \alpha$ values in order to accelerate the convergence rate. This is a critical step because the convergence speed of the SMO algorithm is highly dependent on the dataset size, as well as the SVM hyperparameters~\citep{Schoelkopf2002}. \textit{Iterative Single Data Algorithm} (ISDA)~\citep{Huang2006,Kecman2016} is a more recent and efficient approach for solving the L2-SVM problem, shown to be faster than the SMO algorithm and equal in terms of accuracy~\citep{Kecman2015,Kecman2014}. It iteratively updates the objective function by working on one data point at a time, using coordinate descent to find the optimal objective function value. Other methods for solving the SVM problem include \textit{Quadratic Programming} solvers, such as the interior point method. These types of algorithms find the true optimal objective function value at the trade-off of having a relatively slower run-time.

\subsection{Multiple-Instance Support Vector Machines}
The MI adaptation of the SVM presents two contexts for solving the problem: the instance-level and the bag-level. The first tries to identify instances, either all within a bag or just key instances, that help find the optimal separating hyperplane between positive and negative bags. The latter uses kernels defined over whole bags to optimize the margin~\citep{Doran201479}.

\cite{Andrews2002} proposed a mixed-integer quadratic program that solves the MI problem at an instance-level, using a support vector machine, named MISVM, that can be solved heuristically. Rather than maximizing the margin of separability between instances of different classes, this instance-based method maximizes the margin between bags. It tries to identify the key instance from each positive bag that makes the bag positive by assuming it has the highest margin value~\citep{Herrera2016}. Instances from positive bags are selected as bag-representatives, and the algorithm iteratively creates a classifier that separates those representatives from all instances from the negative bags. Using bag-representatives from one class and all instances from the other is an example of an approach that combines rules from the SMI assumption and the collective assumption. A disadvantage of this approach stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\cite{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which does not discard the negative instances of the positive bags. It rather tries to identify the instances within positive bags that are negative and utilize them in the construction of the negative margin. The main disadvantage of these approaches is that they create an imbalanced class problem that favors the negative class, resulting in a biased classifier.

\cite{Yang2006} presented an instance-based SVM that uses an asymmetric loss function that follows the SMI assumption. The idea behind this loss function is that positive and negative misclassification costs are different. A false negative instance in a positive bag might not cause an error on the bag label, but a false positive instance within a negative bag would lead to a misclassification error. The algorithm ensures all negative instances are correctly classified while minimizing false positives.

One of the first bag-level approaches to the multi-instance SVM problem was proposed by~\cite{Smola2002}, who defined a bag-level kernel. A bag-level kernel determines the similarity between two bags in a higher dimensional space and using such a kernel with the standard SVM problem, the margin can be optimized over bag classes without any modification to the SVM problem.~\cite{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance, without affecting the angles between vectors in the transformed space. Bag level kernels transform the bags into a single-instance representation which enables standard SVMs to be directly applied to multi-instance data~\citep{Herrera2016}.

%In the following section our contribution, MIRSVM, will be introduced, which modifies the traditional SVM optimization problem to accommodate multi-instance datasets, optimizes over representatives chosen per positive and negative bags, and is solved iteratively using a quadratic programming solver.

\section{Multiple-Instance Representative SVM}\label{sec:contribution}
MIRSVM is based on the idea of selecting representative instances from both positive and negative bags which are used to find an unbiased, optimal separating hyperplane. A representative is iteratively chosen from each bag, and a new hyperplane is formed according to the representatives until they converge. Based on the SMI hypothesis, only one instance in a bag is required to be positive for the bag to adopt a positive label. Due to the unknown distribution of instances within positive bags, MIRSVM is designed to give preference to negative bags during training, because their distribution is known, i.e. all instances are guaranteed to be negative. This is evident during the representative selection process, by taking the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$. In other words, the most positive sample is chosen from each positive bag and the least negative sample is chosen from each negative bag (samples with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags. Equation~\eqref{eq:primalmirsvm} presents the primal MIRSVM optimization problem:
\begin{subequations} 
\label{eq:primalmirsvm}
\begin{alignat}{2}
\min\limits_{\bm w, b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{n}\sum_I \xi_I, \tag{\ref{eq:primalmirsvm}}\\ 
\text{s.t.}& {\,\,} y_I(\langle\bm{w},\bm{x}_{s_I}\rangle + b) \geq 1 - \xi_I,\, \forall I \in \set{1,\ldots,n}  \label{eq:primalmirsvm1}\\
{} & {\,\,} \xi_I \geq 0,\, \forall I \in \set{1,\ldots,n}, 
\end{alignat}
\end{subequations} 
where $\bm S_I$ is a set of the bag representatives' indices and $\bm x_{s_I}$ is the sample representative of bag $\bm B_I$. Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance. Solving the optimization problem given in Equation~\eqref{eq:primalmirsvm} using a quadratic programming solver is a computationally expensive task due to the number of constraints, which scales by the number of bags $n$, as well as the calculation of the inner product between two $d$-dimensional vectors in constraint~\eqref{eq:primalmirsvm1}. The proposed solution for these problems was deriving and solving the dual of the optimization problem given by Equation~\eqref{eq:primalmirsvm}.

The dual can be found by first forming the primal Lagrangian given by Equation~\ref{eqn:svmlagrangian}, where $\bm{\alpha}$ and $\bm{\beta}$ are the non-negative Lagrange multipliers.
\begin{equation}
\centering
\resizebox{.9\textwidth}{!}{$
\begin{aligned}
\label{eqn:svmlagrangian}
\mathcal{L}\left(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}\right) = \frac{1}{2}\sum_{j=1}^d w_j^2  + \frac{C}{n}\sum_I \xi_I - \sum_I{\beta_I \xi_I} - \sum_I{\alpha_I\left(y_I\left(\sum_{j=1}^d w_j \bm x_{s_Ij} + b\right) -1 + \xi_I\right)}
\end{aligned}$}
\end{equation}
The following Karush-Kuhn-Tucker (KKT)~\citep{Boyd2004} conditions must be satisfied:
\begin{align*}
&\frac{\partial\mathcal{L}}{\partial w_j} = 0, \,\forall j \in \{1,\ldots,d\} \\
&\frac{\partial\mathcal{L}}{\partial b} = 0     \\
&\frac{\partial\mathcal{L}}{\partial\xi_I} = 0,\,\forall I \in \set{1,\ldots,n}\\
&\alpha_I\left(y_I(\langle\bm{w},\bm{x}_{s_I}\rangle + b)-1+\xi_{I}\right) = 0,\, \forall I \in \set{1,\ldots,n}\\
&\beta_I\xi_I = 0, \forall I \in \set{1,\ldots,n} \\
&\alpha_I \geq 0,\, \beta_I \geq 0,\, \xi_I \geq 0,\, \forall I \in \set{1,\ldots,n}
\end{align*}
At optimality, $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$ and the following conditions are met:
\begin{align}
&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,y_I\,\bm x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
&\frac{\partial\mathcal{L}}{\partial b}: \sum_I{\alpha_Iy_I} = 0,\label{eqn:optcond2}\\
&\frac{\partial\mathcal{L}}{\partial\xi_I}: \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}\label{eqn:optcond3}
\end{align}
By substituting Equations~\ref{eqn:optcond1},~\ref{eqn:optcond2}, and~\ref{eqn:optcond3} into the Lagrangian in~\ref{eqn:svmlagrangian}, the following dual problem, $q(\bm \alpha, \bm \beta)$, is obtained:
\begin{align*}
q(\bm \alpha, \bm \beta) &= \underset{\bm w, b, \bm \xi}{\text{ inf }} \frac{1}{2} \sum_I \sum_{K \in I} \sum_{j=1}^d \alpha_I \alpha_K y_I y_K  x_{s_I j} x_{s_K j} + \sum_I \xi_I \left( \alpha_I + \beta_I \right) - \sum_I \xi_I \left( \alpha_I + \beta_I \right) \\
{} & - \sum_I \sum_{K\in I} \sum_{j=1}^d \alpha_I \alpha_K y_I y_K  x_{s_I j} x_{s_K j} - \sum_I \alpha_I y_I b  + \sum_I \alpha_I.
\end{align*}

At optimality, $\sum_I{\alpha_Iy_I} = 0$, so the term with $b$ can be removed. The terms with $\bm \xi$ can also be removed because they negate each other. The resulting function is now with respect to the dual variables, so the infimum can be dropped. The dual MIRSVM formulation then becomes:
\begin{subequations} 
\label{eq:dualmirsvm1}
\begin{alignat}{2}
\max\limits_{\bm \alpha,\bm \beta}& \sum_I \alpha_I -\frac{1}{2}\sum_I \sum_{K\in I} \sum_{j=1}^d \alpha_I \alpha_K y_I y_K  x_{s_I j} x_{s_K j} \tag{\ref{eq:dualmirsvm1}}\\
\text{s.t.}&  \sum_I{\alpha_Iy_I} = 0\, \\
{} & \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}   \label{eq:implicit1}\\
{} & \alpha_I \geq 0,\, \forall I \in \set{1,\ldots,n}  \label{eq:implicit2} \\
{} & \beta_I \geq 0,\, \forall I \in \set{1,\ldots,n}  \label{eq:implicit3}
\end{alignat}
\end{subequations} 
where $s_I$ is computed for each bag, as shown in Equation~\eqref{eq:si}:
\begin{equation}
\label{eq:si}
\centering
s_I = \underset{i \in I}{\text{argmax}}(\sum_{K\in I} \sum_{j=1}^d \alpha_K y_K x_{s_K j} x_{ij} + b),\, \forall I \in \set{1,\ldots,n}.
\end{equation}

The implicit constraints~\eqref{eq:implicit1} through~\eqref{eq:implicit3} imply three possible cases for the $\alpha_I$ values:
\begin{itemize}
\item[1.] If $\alpha_I = 0$, then $\beta_I = C/n$ and $\xi_I = 0$, implying the instance is correctly classified and outside the margin. 
\item[2.] If $0 \leq \alpha_I \leq C/n$, then $\beta_I > 0$ and $\xi_I = 0$, indicating that the instance sits on the margin boundary, i.e. is an \textit{unbounded support vector}.
\item[3.] If $\alpha_I = C/n$, then $\beta_I = 0$ and there is no restriction for $\xi_I \geq 0$. This also indicates that the instance is a support vector that is \textit{unbounded}. If $0 \leq \xi_I < 1$, then the instance is correctly classified, and is misclassified otherwise. 
\end{itemize}

We then kernelize the dual function by replacing the inner product of the samples in feature space with their corresponding kernel values, $\spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right)$. The dual function is now written as:
\begin{subequations} 
\label{eq:dualmirsvm}
\begin{alignat}{2}
\max\limits_{\bm \alpha}& \sum_I \alpha_I - \frac{1}{2}\sum_I \sum_{K\in I} \alpha_I \alpha_K y_I y_K  \spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right) \tag{\ref{eq:dualmirsvm}}\\
\text{s.t.}&  \sum_I{\alpha_Iy_I} = 0\,  \\
{} & 0 \leq \alpha_I \leq \frac{C}{n},\, \forall I \in \set{1,\ldots,n}.
\end{alignat}
\end{subequations}

One of the biggest advantages of the dual SVM formulation is the sparseness of the resulting model. This is because support vectors, instances that have their corresponding $\alpha_I \neq 0$, are only considered when forming the decision boundary. MIRSVM uses a Gaussian RBF kernel, given by Equation~\eqref{eq:gaussiankernel}, where $\sigma$ is the Gaussian shape parameter.
\begin{equation}
\label{eq:gaussiankernel}
\centering
\mathcal{K}(\bm x_i, \bm x_j) = e^{-\frac{\norm{x_i - x_j}^2}{2\sigma^2}}
\end{equation}
\begin{figure}[tpb]
\centering
\small
\label{fig:mirsvm}
\begin{minipage}{\textwidth}
\adjustbox{scale=0.901}{
\begin{tikzpicture}[%
    node distance=4cm,
    on grid,
    auto
  ]
\node[block](A) {Initialize $\bm S$ randomly};
\node(B)[block, right of=A, text width=6em] {Train SVM using QP solver over $\bm S$, set $\bm S_{old} = \bm S$};
\draw[arrow] (A) -- (B);
\node(C)[block, right of=B,text width=6.3em] {Find optimal representatives, $\bm S$, for the current hyper-plane};
\draw[arrow] (B) -- (C);
\node(D) [decision,right of=C,fill=gray!55,text width=2cm]{while $\bm S$ has not changed, $\bm S \neq \bm S_{old}$};
\draw[arrow] (C) -- (D);
\node(E) [block,right of=D]{return $\bm \alpha,\, b, \bm S$};
\draw[arrow] (D) -- node {yes} (E);
\draw[arrow] (D.north) --+(0,0.1cm) -| (B.north) node[below,pos=0.25] {no} ;
\end{tikzpicture}}
\caption{MIRSVM Flow Diagram. This figure represents a summary of the steps performed by the MIRSVM algorithm. The representatives are first randomly initialized and continuously updated according to the current hyper-plane, which is found using a quadratic programming (QP) solver. Upon completion, the model is returned along with the optimal bag-representatives.}
\end{minipage}
\begin{algorithm}[H]
\caption{Multi-Instance Representative SVM (MIRSVM)}
\label{alg:mirsvm} 
\begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\Require Training dataset $\mathcal{D}$, SVM Parameters $C$ and $\sigma$
\Ensure  SVM model parameters $\bm \alpha$ and $b$, Bag Representative IDs $\bm S$
\State $\bm S_{old} \leftarrow \bm -\infty$
\For {$I \in \set{1,\ldots,n}$}
\State $S_I \leftarrow \text{ rand}\left(|\bm B_I|,1,1\right)$ \Comment{Assign each bag a random instance}
\EndFor
\State $\bm X_S \leftarrow \bm X(\bm S),\,Y_S \leftarrow Y(\bm S)$ \Comment{Initialize the representative dataset}
\While {$\bm S \neq \bm S_{old}$}
\State $\bm S_{old} \leftarrow \bm S$
\State $\bm G \leftarrow (Y_S \times Y_S) \bm \cdot \mathcal{K}\left( \bm X_S,\,\bm X_S,\,\sigma\right)$ \Comment{Build Graham matrix}
\State $\bm \alpha \leftarrow \text{ quadprog}\left(\bm G, \bm{-1}^n, Y_S, \bm 0^n, \bm 0^n, \bm C^n\right)$ \Comment{Solve QP Problem}
\State $\bm{sv} \leftarrow \text{find}\left(0 < \bm \alpha \leq C \right)$ \Comment{Get the support vector indices}
\State $n_{sv} \leftarrow \text{count}\left(0 < \bm \alpha \leq C \right)$ \Comment{Get the number of support vectors}
\State $b \leftarrow \frac{1}{n_{sv}}\sum_{i=1}^{n_{sv}} \left(Y_{\bm sv} - \bm G_{\bm sv}*\left(\bm{\alpha_{\bm sv}} \cdot Y_{\bm sv}\right)\right)$ \Comment{Calculate the bias term}
\For {$I \in \set{1,\ldots,n}$} 
\State $\bm G_I \leftarrow (Y_I \times Y_S) \bm \cdot \mathcal{K}\left( \bm B_I,\,\bm X_S,\,\sigma\right)$
\State $\bm S_I \leftarrow \text{argmax}_{i \in I}\left(\bm G_I*\bm{\alpha} + b \right)$ \tab\tab[0.62cm]\Comment{Select optimal bag-representatives using SMI assumption}
\EndFor
\State $\bm X_S \leftarrow \bm X(\bm S),\,Y_S \leftarrow Y(\bm S)$ \Comment{Re-set the representative dataset}
\EndWhile 
\end{algorithmic} 
\end{algorithm}
\begin{algorithm}[H]
\caption{MIRSVM Prediction}
\label{alg:mirsvmtest} 
\begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\Require Testing dataset $\mathcal{D^\prime}$ with $n^\prime$ bags, Representatives $\bm S$, Classifier $\bm \alpha$ and $b$, SVM Parameter $\sigma$
\Ensure Classifier output $\bm O$
\For {$I \in \set{1,\ldots,n^\prime}$}
\State $\bm G_I \leftarrow (Y_I \times Y_S) \bm \cdot \mathcal{K}\left( \bm B_I,\,\bm X_S,\,\sigma\right)$
\State $\bm O_I \leftarrow \text{sign}(\text{max}\left(\bm G_I*\bm{\alpha} + b \right))$
\EndFor 
\end{algorithmic} 
\end{algorithm}
\end{figure}

To evaluate the output vector, $\bm o_I$, of bag $I$ using the kernel, the following equation is used~\citep{Huang2006},
\begin{align}
\bm o = \spa{K}(\bm B_I,\bm X_S)*(\bm\alpha \cdot Y_S) + b
\end{align}
where $\bm B_I$ are the instances of bag $I$, $\bm X_S$ are the optimal bag representatives, and $Y_S$ are the representative bag labels. The bias term $b$ is calculated as shown in Equation~\ref{eqn:bias}, where $\bm{sv}$ is the vector of support vector indices and $n_{sv}$ is the number of support vectors~\citep{Huang2006}.
\begin{align}
\label{eqn:bias}
b = \frac{1}{n_{sv}}\sum_{\bm{sv}} Y_{\bm{sv}} - \spa{K}(\bm X_{\bm{sv}},\bm X_{\bm{sv}})*(\bm \alpha_{\bm{sv}}\bm\cdot Y_{\bm{sv}})
\end{align}
\newpage
Algorithm~\ref{alg:mirsvm} and Figure~\ref{fig:mirsvm} show the procedure for training the multi-instance representative SVM classifier, along with obtaining the optimal representatives from each bag. Algorithm~\ref{alg:mirsvmtest} lists the method for testing the model on unseen data. During training, the representatives, $\bm S$, are first initialized by randomly selecting an instance from each bag. A hyper-plane is then obtained using the representative instances, and new optimal representatives are found with respect to the current hyper-plane, by using the rule given in Equation~\eqref{eq:si}. At each step, the previous values in $\bm S$ are stored in $\bm S_{old}$. The training procedure ends when the bag representatives stop changing from one iteration to the next, i.e. when $\bm S = \bm S_{old}$. During the testing procedure, each bag produces an output vector based on the hyper-plane found in the training procedure. The bag label is then assigned by taking the sign of the output vector's maximum value, following the SMI assumption.

\begin{figure}
    \centering
    \label{fig:diff}
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{mirsvm_figure.eps} % first figure itself
    \end{minipage}\hfill
    \begin{minipage}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{misvm_figure.eps} % second figure itself
    \end{minipage}
    \caption{Difference between MIRSVM and MISVM on a random $2$-dimensional toy dataset. The instances of this dataset were drawn from the standard normal distribution, with $6$ bags, $4$ of which are negative (red) and $2$ of which are positive (blue), indicated by the red and blue dotted circles. There are a total of $125$ instances, $65$ belonging to the positive bags and $60$ belonging to the negative bags. The decision boundaries (black lines) are shown for each of the algorithms, along with the SVM margin (red and blue dashed lines) and support vectors (black crosses). In this example, both MIRSVM and MISVM were trained using $C = 1000$ and $\sigma = 1.5$. Note the differing number of support vectors produced by the two methods. MIRSVM has $6$, one for each bag, and MISVM has $29$. Also note the smoother representation of the data distribution given by MIRSVM's decision boundary, unlike MISVM whose decision boundary was greatly affected by the larger number of support vectors belonging to the negative class with respect to the only $2$ positive support vectors. }
\end{figure}
This formulation is designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances. MISVM allows multiple representatives to be chosen from negative bags and limits positive bag-representatives to be one, while MIRSVM allows for balanced bag-representative selection, where each bag is allowed one. MISVM also uses a wrapper technique to initialize the positive bag-representatives by taking the mean vector of the instances within each positive bag. This is an implicit assumption that the instances within the positive bags are all positive, whereas MIRSVM's initialization procedure selects an instance from all bags at random, ensuring no noise is added by any wrapper techniques during initialization and no assumptions are made about the instances. Due to the constraints on the representatives, MIRSVM produces sparser models while MISVM has the freedom to select as many negative support vectors as it needs and restricts the support vectors chosen from positive bags to be one. Figure~\ref{fig:diff} shows the decision boundaries produced by MIRSVM and MISVM to highlight the differences in their solutions. As Figure~\ref{fig:diff} shows, MISVM produces a higher number of support vectors from the negative bags, which greatly influences the final decision boundary in favor of the negative class.

\section{Experiments}\label{sec:experiments}
This section presents the experimental setup and comparison of our contribution, as well as ten other state-of-the-art methods on $15$ different benchmark datasets. First, the experimental setup is described and the state-of-the-art methods are listed. The results for each metric, as well as the statistical analysis, are then presented and analyzed. Finally, the run-time and meta-ranks of each algorithm are shown, and the overall performance of the algorithms across each metric is discussed. The main aim of the experiments is to compare our contribution to other multi-instance support vector machines, state-of-the-art multi-instance learners, and ensemble methods.

\subsection{Experimental Setup}
Table~\ref{tab:Dataset} presents a summary of the $15$ datasets used throughout the experiments, where the number of attributes, bags, and total number of instances are shown. The datasets were obtained from the Weka\footnote{http://www.cs.waikato.ac.nz/ml/weka}~\citep{Hall2009} and KEEL\footnote{http://sci2s.ugr.es/keel/datasets.php}~\citep{Alca2011} dataset repositories.

\begin{table}[t!]
\caption{Datasets used for the experiments in~\ref{subsec:results}}
\small
\label{tab:Dataset}
\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}ccccc}
\hline\noalign{\smallskip}
Dataset & Attributes & Positive Bags & Negative Bags & Total & Instances \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Suramin 			& 20 	& 7 	& 4 	& 11 	& 2378 	\\
EastWest 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
WestEast 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
Musk1 				& 166 	& 47 	& 45 	& 92 	& 476 	\\
Musk2 				& 166 	& 39 	& 63 	& 102 	& 6598 	\\
Webmining			& 5863	& 17	& 58	& 75	& 2212	\\
TRX 				& 8 	& 25 	& 193 	& 168 	& 26611 \\
Mutagenesis-Atoms 	& 10 	& 125 	& 63 	& 188 	& 1618 	\\
Mutagenesis-Bonds 	& 16 	& 125 	& 63 	& 188 	& 3995 	\\
Mutagenesis-Chains 	& 24 	& 125 	& 63 	& 188 	& 5349 	\\
Tiger 				& 230 	& 100 	& 100 	& 200 	& 1391 	\\
Elephant 			& 230 	& 100 	& 100 	& 200 	& 1220 	\\
Fox 				& 230 	& 100 	& 100 	& 200 	& 1320 	\\
Component			& 22	& 423	& 2707	& 3130	& 36894	\\
Function			& 202	& 443	& 4799	& 5242	& 55536	\\
\noalign{\smallskip}\hline
\end{tabularx}
\end{table}

The experimental environment was designed to test the difference in performance of the proposed method against $10$ state-of-the-art algorithms, contrasting instance-level methods and bag-level methods. Instance-level methods include MIOptimalBall, MIBoost, MISVM, MIDD, and MIWrapper. The bag-level methods include MISMO, SimpleMI, and TLC. The ensemble-based bag-space methods, Bagging and Stacking, were also used. The base algorithms selected for the ensembles Bagging and Stacking were TLC, and TLC and SimpleMI, respectively. These algorithms were chosen because they have shown considerable performance in learning multi-instance models, while also having their frameworks readily available for reproducing their results through MILK, the Multi-Instance Learning Kit\footnote{http://www.cs.waikato.ac.nz/ml/milk}~\citep{Xu2003}, used in conjunction with the Weka framework. Experiments were run in an Intel i7-6700k CPU with 32GB RAM. MIRSVM was implemented in MATLAB while the referenced algorithms are available in the Java implementation of Weka.

Experiments were performed using $k$-fold cross validation, with $k = 10$, in order to evaluate the models' performances and tune hyper-parameters. The data is separated fairly into $10$ equally sized sections where, at every iteration of the cross-validation loop, a section is held out as the test set, while the remainder of the data is used for training. This procedure ensures the model is not optimistically biased towards the full dataset. The tuning of the model during cross-validation includes finding the best penalty parameter, $C$, as well as the best shape parameter for the Gaussian radial basis function kernel, $\sigma$. The best hyper-parameters were chosen from the following $6 \times 6$ possible combination runs, shown in Equations~\eqref{eq:paramC} and~\eqref{eq:paramG}, referred to as~\eqref{eq:hyperparam}. 
\begin{subequations}
\label{eq:hyperparam}
\begin{align}
C \in  & \{0.1, 1, 10, 100, 1000, 10000\} \label{eq:paramC}\\
\sigma \in  & \{0.1, 0.5, 1, 2, 5, 10\} \label{eq:paramG}
\end{align}
\end{subequations}

These parameters were also used for the state-of-the-art SVM methods. This was done in order to keep the experimental environment controlled and ensure fair evaluation of the multi-instance SVM algorithms. The parameters for the referenced algorithms used throughout the experiments were those specified by their authors.

\subsection{Results \& Statistical Analysis}\label{subsec:results}
The classification performance was measured using five metrics: Accuracy~\eqref{eq:accuracy}, Precision~\eqref{eq:precision}, Recall~\eqref{eq:recall}, Cohen's kappa rate~\eqref{eq:kappa}, and Area under ROC curve (AUC)~\eqref{eq:auc}. Accuracy can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which have six and ten times as many negative instances than positive, respectively. Cohen's Kappa Rate and the AUC measures are used as complementary measures in order to evaluate the algorithms comprehensively~\citep{Bendavid2008}. Cohen's kappa rate, shown in Equation~\eqref{eq:kappa}, evaluates classifier merit according to the class distribution and ranges between -1 (full disagreement), 0 (random classification), and 1 (full agreement). The AUC metric highlights the trade-off between the true positive rate, or recall, and the false positive rate, as shown in Equation~\eqref{eq:auc}. The values of the true positive (TP), true negative (TN), false positive (FP), and false negative samples (FN) were first collected for each of the classifiers, then the metrics were computed using the equations shown in~\eqref{eq:metrics} on the $n^\prime$ bags of the test data. The run times of each algorithm are also reported to analyze the usability and speed of each of the algorithms across differently sized datasets. The results for these metrics are shown in Tables~\ref{tab:accResults},~\ref{tab:preResults},~\ref{tab:recResults},~\ref{tab:kappaResults},~\ref{tab:aucResults}, and~\ref{tab:time}.
\begin{subequations}
\label{eq:metrics}
\begin{align}
\text{Accuracy} \tab \tab &\dfrac{TP+TN}{n^\prime} \label{eq:accuracy}\\[1.5pt]
\text{Precision} \tab \tab &\dfrac{TP}{TP+FP} \label{eq:precision}\\[1.5pt]
\text{Recall} \tab \tab &\dfrac{TP}{TP+FN} \label{eq:recall}\\[1.5pt]
\text{Cohen's Kappa Rate} \tab \tab &\dfrac{n^\prime - \dfrac{(TP+FN)*(TP+FP)}{n^\prime}}{1 - \dfrac{(TP+FN)*(TP+FP)}{n^\prime}} \label{eq:kappa}\\[1.5pt]
\text{Area Under ROC Curve} \tab \tab &\frac{1 + \dfrac{TP}{TP+FN} - \dfrac{FP}{FP+TN}}{2} \label{eq:auc}
\end{align}
\end{subequations}

In order to analyze the performances of the multiple models, non-parametric statistical tests are used to validate the experimental results obtained~\citep{Derrac2011,Garcia20102044}. The Iman-Davenport non-parametric test is run to investigate whether significant differences exist among the performance of the algorithms~\citep{Garcia2008} by ranking them over the datasets used, using the Friedman test. The algorithm ranks for each metric in Equations~\eqref{eq:metrics} are presented in the last row of the results tables, and the lowest (best) rank value is typeset in bold. Table~\ref{tab:metarank} contains the ranks and meta-rank of all methods, which helps determine and visualize the best performing algorithms across all datasets and metrics.

After the Iman-Davenport test indicates significant differences, the Bonferroni-Dunn post-hoc test~\citep{Dunn1961} is then used to find where they occur between algorithms by assuming the classifiers' performances are different by at least some critical value~\citep{Garcia2009}. Below each result table, a figure highlighting the critical distance (in gray), from the best ranking algorithm to the rest, is shown. The algorithms to the right of the critical distance bar perform statistically significantly worse than the control algorithm, MIRSVM. Figures \ref{fig:BonfDunnacc}, \ref{fig:BonfDunnprec}, \ref{fig:BonfDunnrec}, \ref{fig:BonfDunnkappa}, \ref{fig:BonfDunnauc}, \ref{fig:BonfDunnpmeta} show the results of the Bonferroni-Dunn post-hoc procedure over the metrics in~\eqref{eq:metrics}, as well as the meta-rank results in Table~\ref{tab:metarank}.

The Nemenyi, Holm, and Shaffer post-hoc~\citep{Gibbons2011,Holander1999} tests were then run for each of the metrics to compute multiple pairwise comparisons between the proposed algorithm and the state-of-the-art methods, investigating whether statistical differences exist among pairs of algorithms. Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values for the Nemenyi, Holm, and Shaffer tests for $\alpha = 0.05$.

\subsection{Accuracy}
Table~\ref{tab:accResults} shows the accuracy results of the $11$ algorithms over $15$ multi-instance datasets, along with their average and rank. The results indicate that the bag-based and ensemble learners perform better than the instance-based and wrapper methods. Specifically, MIRSVM achieves the best accuracy over $6$ of the $15$ datasets with a competitive average against the Bagging, Stacking, and TLC algorithms. Note that MIRSVM performs better than MISVM for all datasets, indicating that using representatives from each bag and limiting the number of support-vectors per negative bag improves the classification performance. The instance-level classifiers and wrapper methods, such as MIBoost, MIWrapper, and SimpleMI perform the worst. This behavior emphasizes the importance of not making prior assumptions about the positive bags' distributions.

Figure~\ref{fig:BonfDunnacc} and Table~\ref{tab:statacc} show the results for the statistical analysis on the accuracy results. The algorithms with ranking higher than $5.51$ (MIRSVM rank + Bonferroni-Dunn critical value), to the right of the grey bar in Figure~\ref{fig:BonfDunnacc}, perform statistically worse than MIRSVM. Table~\ref{tab:statacc} shows the $p$-values of the Nemenyi, Holm, and Shaffer tests. The results from these tests are complement each other. Nemenyi's procedure indicates that MIRSVM performs significantly better than all methods (with $p$-values $< 0.01$), except Bagging, Stacking, TLC, and MISMO. The Nemenyi $p$-values for MIBoost, MIWrapper, and SimpleMI are $= 0$, showing that MIRSVM has significantly better accuracy. However, the stricter Holm and Shaffer tests indicate that significant differences exist between MIRSVM and all other classifiers, highlighting MIRSVM's superior classification accuracy.

\begin{table}[th!]
\caption{Accuracy}\label{tab:accResults}
\resizebox{\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &0.6000 &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.2308 &0.6923 &0.6750 &\textbf{0.7564} &  \\
eastWest &\textbf{0.8000} &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.6375 &0.5000 &0.5000 &0.6375 &0.4500 &  \\
westEast &0.6500 &0.5000 &0.3750 &0.4500 &0.5000 &\textbf{0.7375} &0.4625 &0.5000 &0.5000 &0.6875 &0.6375 &  \\
musk1 &\textbf{0.9022} &0.5109 &0.7717 &0.8804 &0.5109 &0.7826 &0.8043 &0.5109 &0.8587 &0.8804 &0.8587 &  \\
musk2 &\textbf{0.8146} &0.6139 &0.7723 &0.7228 &0.6139 &0.7030 &0.7129 &0.6139 &0.6238 &0.7129 &0.6733 &  \\
webmining &\textbf{0.8500} &0.8142 &0.7699 &0.8142 &0.8142 &0.8407 &0.6903 &0.8142 &0.8142 &0.7876 &0.8053 &  \\
trx &0.8825 &0.8705 &\textbf{0.9016} &0.8808 &0.8705 &0.8705 &0.8705 &0.8705 &0.8756 &0.8964 &0.8860 &  \\
mutagenesis-atoms &0.7714 &0.6649 &0.6436 &0.7074 &0.6649 &0.6915 &0.6649 &0.6649 &0.7766 &\textbf{0.8032} &0.7606 &  \\
mutagenesis-bonds &0.8252 &0.6649 &0.6915 &0.7713 &0.6649 &0.7979 &0.6649 &0.6649 &0.8351 &\textbf{0.8830} &0.8564 &  \\
mutagenesis-chains &0.8411 &0.6649 &0.6702 &0.7766 &0.6649 &0.8351 &0.6649 &0.6649 &0.8404 &\textbf{0.8457} &0.8351 &  \\
tiger &\textbf{0.7750} &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &0.7700 &0.7250 &  \\
elephant &0.8300 &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &\textbf{0.8500} &0.8250 &  \\
fox &\textbf{0.6550} &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.5900 &0.5000 &0.6450 &0.6200 &0.6500 &  \\
component &0.9366 &0.8649 &0.8696 &0.8780 &0.8649 &0.8968 &0.8703 &0.8649 &0.9358 &\textbf{0.9371} &0.9355 &  \\
function &0.9523 &0.9155 &0.9138 &0.9193 &0.9155 &0.9376 &0.9195 &0.9155 &0.9649 &\textbf{0.9655} &0.9647 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &\textbf{0.8057} &0.6390 &0.6886 &0.7279 &0.6390 &0.7724 &0.7072 &0.6210 &0.7552 &0.7968 &0.7746 &  \\
Ranks &\textbf{2.4000} &8.8000 &7.2667 &6.0333 &8.8000 &4.8000 &7.0667 &9.0000 &4.7333 &2.7667 &4.3333 &  \\
\noalign{\smallskip}\hline
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (10,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (2.4,0);
\coordinate (c1) at (8.8,0);
\coordinate (c2) at (7.2667,0);
\coordinate (c3) at (6.0333,0);
\coordinate (c4) at (8.8,0);
\coordinate (c5) at (4.8,0);
\coordinate (c6) at (7.0667,0);
\coordinate (c7) at (9,0);
\coordinate (c8) at (4.7333,0);
\coordinate (c9) at (2.7667,0);
\coordinate (c10) at (4.3333,0);

\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l6) at (c6) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l8) at (c8) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l9) at (c9) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l10) at (c10) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (2.4,-0.1) rectangle (5.5196,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}
\captionof{figure}{Bonferroni-Dunn test for Accuracy}\label{fig:BonfDunnacc}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for Accuracy}\label{tab:statacc}
\scriptsize
\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Nemenyi $p$-value & 0.00000 & 0.00006 & 0.00270 & 0.00000 & 0.04751 & 0.00012 & 0.00000 & 0.05402 & 0.76207 & 0.11040\\
Holm $p$-value & 0.00093 & 0.00102 & 0.00139 & 0.00094 & 0.00185 & 0.00104 & 0.00091 & 0.00192 & 0.00833 & 0.00238\\
Shaffer $p$-value & 0.00111 & 0.00111 & 0.00139 & 0.00111 & 0.00185 & 0.00111 & 0.00091 & 0.00192 & 0.00833 & 0.00238\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabularx}
\end{table}
\newpage
\subsection{Precision \& Recall}
Precision and recall are metrics that must be evaluated together in order to observe their behavior simultaneously, since they are both metrics used to measure relevance. Tables~\ref{tab:preResults} and~\ref{tab:recResults} show the precision and recall results obtained by each algorithm. The precision and recall results for MIWrapper and SimpleMI indicate that they are unstable classifiers, exhibiting extreme variance in behavior, making them unsuitable for real-world applications. It is also interesting to analyze the performance on the mutagenesis datasets, where MISVM, MIBoost, MIWrapper, and SimpleMI predict all bags as negative. Additionally, while MISMO obtains unbiased results on these datasets, MIRSVM significantly outperforms it over both precision and recall.

Figure~\ref{fig:BonfDunnprec} shows that there are no statistically significant differences between the precision results obtained by all algorithms, except SimpleMI; and Figure~\ref{fig:BonfDunnrec} shows none over all. It is worth noting that MIRSVM outperforms both ensemble methods according to recall, despite them exhibiting relatively good accuracy and precision. This indicates that they are strongly conservative towards predicting positive bags. The Holm and Shaffer tests indicate that significant differences exist between MIRSVM and the state-of-the-art, with the exception of SimpleMI.

\begin{table}[t!]
\caption{Precision}\label{tab:preResults}
\resizebox{\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &0.6385 &\textbf{1.0000} &\textbf{1.0000} &0.2857 &\textbf{1.0000} &\textbf{1.0000} &0.5000 &0.0000 &0.6667 &0.7333 &0.7116 &  \\
eastWest &0.7143 &0.5000 &\textbf{0.8750} &0.5882 &0.5000 &0.7429 &0.8667 &0.5000 &0.5000 &0.6667 &0.4444 &  \\
westEast &0.6300 &0.5000 &0.2727 &0.4600 &0.5000 &\textbf{0.6939} &0.3846 &0.5000 &0.5000 &0.6364 &0.6038 &  \\
musk1 &0.8519 &\textbf{1.0000} &0.9286 &0.9048 &\textbf{1.0000} &0.8049 &0.8857 &\textbf{1.0000} &0.8478 &0.9250 &0.8478 &  \\
musk2 &0.7167 &0.6139 &\textbf{0.7826} &0.7576 &0.6139 &0.7424 &0.7538 &0.6139 &0.7400 &0.7797 &0.7164 &  \\
webmining &0.7500 &0.8142 &0.8173 &0.8142 &0.8142 &0.8936 &\textbf{1.0000} &0.8142 &0.8817 &0.8469 &0.8500 &  \\
trx &0.6500 &0.8705 &\textbf{0.9306} &0.9191 &0.8705 &0.8705 &0.8705 &0.8705 &0.9138 &0.8936 &0.9011 &  \\
mutagenesis-atoms &0.7872 &\textbf{1.0000} &0.4630 &0.6111 &\textbf{1.0000} &0.5439 &\textbf{1.0000} &\textbf{1.0000} &0.7059 &0.7321 &0.6667 &  \\
mutagenesis-bonds &0.8468 &\textbf{1.0000} &0.5385 &0.7500 &\textbf{1.0000} &0.6812 &\textbf{1.0000} &\textbf{1.0000} &0.7857 &0.8596 &0.8333 &  \\
mutagenesis-chains &0.8571 &\textbf{1.0000} &0.5091 &0.7059 &\textbf{1.0000} &0.7759 &\textbf{1.0000} &\textbf{1.0000} &0.7705 &0.7742 &0.7581 &  \\
tiger &0.7365 &0.5000 &0.5000 &0.6944 &0.5000 &0.7444 &0.7802 &0.5000 &0.6514 &\textbf{0.7935} &0.7320 &  \\
elephant &0.8576 &0.5000 &0.5000 &0.7959 &0.5000 &0.8444 &0.7679 &0.5000 &0.8000 &\textbf{0.8804} &0.8283 &  \\
fox &0.6040 &0.5000 &0.5000 &0.5833 &0.5000 &0.5287 &0.6216 &0.5000 &\textbf{0.6747} &0.6304 &0.6705 &  \\
component &\textbf{0.9866} &0.8649 &0.8778 &0.8902 &0.8649 &0.8958 &0.8696 &0.8649 &0.9462 &0.9431 &0.9449 &  \\
function &0.8459 &0.9155 &0.9202 &0.9317 &0.9155 &0.9376 &0.9197 &0.9155 &\textbf{0.9729} &0.9720 &0.9726 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &0.7649 &0.7719 &0.6944 &0.7128 &0.7719 &0.7800 &\textbf{0.8147} &0.7053 &0.7572 &0.8045 &0.7654 &  \\
Ranks &6.0667 &6.7333 &6.7333 &6.7667 &6.7333 &5.3667 &5.1000 &7.3000 &5.5000 &\textbf{3.9333} &5.7667 &  \\
\noalign{\smallskip}\hline
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (10,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (6.0667,0);
\coordinate (c1) at (6.7333,0);
\coordinate (c2) at (6.7333,0);
\coordinate (c3) at (6.7667,0);
\coordinate (c4) at (6.7333,0);
\coordinate (c5) at (5.3667,0);
\coordinate (c6) at (5.1,0);
\coordinate (c7) at (7.3,0);
\coordinate (c8) at (5.5,0);
\coordinate (c9) at (3.9333,0);
\coordinate (c10) at (5.7667,0);

\node (l0) at (c0) [above left=.3cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [below right=.2cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l2) at (c2) [above right=.45cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l3) at (c3) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l4) at (c4) [above left=.45cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l5) at (c5) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l6) at (c6) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l7) at (c7) [above right=.2cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l8) at (c8) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l9) at (c9) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l10) at (c10) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (3.9333,-0.1) rectangle (7.0529,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}
\captionof{figure}{Bonferroni-Dunn test for Precision}\label{fig:BonfDunnprec}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for Precision}\label{tab:statprec}
\scriptsize
\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Nemenyi $p$-value & 0.58199 & 0.58199 & 0.56326 & 0.58199 & 0.56326 & 0.42475 & 0.30849 & 0.63985 & 0.07815 & 0.80435\\
Holm $p$-value & 0.00263 & 0.00250 & 0.00217 & 0.00278 & 0.00227 & 0.00185 & 0.00156 & 0.00294 & 0.00102 & 0.00500\\
Shaffer $p$-value & 0.00263 & 0.00250 & 0.00217 & 0.00278 & 0.00227 & 0.00185 & 0.00156 & 0.00294 & 0.00102 & 0.00500\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabularx}
\end{table}
\begin{table}[h!]
\caption{Recall}\label{tab:recResults}
\resizebox{\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &\textbf{1.0000} &0.0000 &0.4500 &0.1000 &0.0000 &0.4500 &0.5000 &0.0000 &0.6667 &0.5500 &0.9125 &  \\
eastWest &\textbf{1.0000} &0.7000 &0.5250 &0.7500 &0.7000 &0.6500 &0.3250 &\textbf{1.0000} &0.5000 &0.5500 &0.4000 &  \\
westEast &0.9000 &0.9000 &0.1500 &0.5750 &0.9000 &0.8500 &0.1250 &\textbf{1.0000} &0.5000 &0.8750 &0.8000 &  \\
musk1 &\textbf{0.9787} &0.0000 &0.5778 &0.8444 &0.0000 &0.7333 &0.6889 &0.0000 &0.8667 &0.8222 &0.8667 &  \\
musk2 &0.9250 &\textbf{1.0000} &0.8710 &0.8065 &\textbf{1.0000} &0.7903 &0.7903 &\textbf{1.0000} &0.5968 &0.7419 &0.7742 &  \\
webmining &0.2857 &\textbf{1.0000} &0.9239 &\textbf{1.0000} &\textbf{1.0000} &0.9130 &0.6196 &\textbf{1.0000} &0.8913 &0.9022 &0.9239 &  \\
trx &0.4833 &\textbf{1.0000} &0.9583 &0.9464 &\textbf{1.0000} &\textbf{1.0000} &\textbf{1.0000} &\textbf{1.0000} &0.9464 &\textbf{1.0000} &0.9762 &  \\
mutagenesis-atoms &\textbf{0.8880} &0.0000 &0.3968 &0.3492 &0.0000 &0.4921 &0.0000 &0.0000 &0.5714 &0.6508 &0.5714 &  \\
mutagenesis-bonds &\textbf{0.8960} &0.0000 &0.5556 &0.4762 &0.0000 &0.7460 &0.0000 &0.0000 &0.6984 &0.7778 &0.7143 &  \\
mutagenesis-chains &\textbf{0.9120} &0.0000 &0.4444 &0.5714 &0.0000 &0.7143 &0.0000 &0.0000 &0.7460 &0.7619 &0.7460 &  \\
tiger &0.8700 &0.5000 &\textbf{1.0000} &0.7500 &0.5000 &0.6700 &0.7100 &\textbf{1.0000} &0.7100 &0.7300 &0.7100 &  \\
elephant &0.9100 &0.6000 &\textbf{1.0000} &0.7800 &0.6000 &0.7600 &0.8600 &\textbf{1.0000} &0.8000 &0.8100 &0.8200 &  \\
fox &0.9000 &0.7000 &\textbf{1.0000} &0.5600 &0.7000 &0.4600 &0.4600 &\textbf{1.0000} &0.5600 &0.5800 &0.5900 &  \\
component &0.5839 &\textbf{1.0000} &0.9867 &0.9797 &\textbf{1.0000} &0.9967 &\textbf{1.0000} &\textbf{1.0000} &0.9815 &0.9867 &0.9826 &  \\
function &0.5327 &\textbf{1.0000} &0.9919 &0.9840 &\textbf{1.0000} &0.9983 &0.9994 &\textbf{1.0000} &0.9892 &0.9908 &0.9894 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &\textbf{0.8044} &0.5600 &0.7221 &0.6982 &0.5600 &0.7483 &0.5385 &0.6667 &0.7350 &0.7820 &0.7851 &  \\
Ranks &\textbf{4.4333} &6.2667 &5.8000 &6.7667 &6.2667 &6.2667 &7.4333 &4.5333 &7.0333 &5.3333 &5.8667 &  \\
\noalign{\smallskip}\hline
\end{tabular}}
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (10,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (4.4333,0);
\coordinate (c1) at (6.2667,0);
\coordinate (c2) at (5.8,0);
\coordinate (c3) at (6.7667,0);
\coordinate (c4) at (6.2667,0);
\coordinate (c5) at (6.2667,0);
\coordinate (c6) at (7.4333,0);
\coordinate (c7) at (4.5333,0);
\coordinate (c8) at (7.0333,0);
\coordinate (c9) at (5.3333,0);
\coordinate (c10) at (5.8667,0);

\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l2) at (c2) [below left=.25cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l3) at (c3) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l4) at (c4) [above right=.35cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l5) at (c5) [above left=.35cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l6) at (c6) [below right=.025cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l7) at (c7) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l8) at (c8) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l9) at (c9) [above left=.3cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (4.4333,-0.1) rectangle (7.5529,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}
\captionof{figure}{Bonferroni-Dunn test for Recall}\label{fig:BonfDunnrec}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for Recall}\label{tab:statrec}
\scriptsize
\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Nemenyi $p$-value & 0.13007 & 0.25911 & 0.05402 & 0.13007 & 0.13007 & 0.01324 & 0.93419 & 0.03180 & 0.45739 & 0.23660\\
Holm $p$-value & 0.00104 & 0.00135 & 0.00098 & 0.00106 & 0.00109 & 0.00090 & 0.01000 & 0.00094 & 0.00208 & 0.00132\\
Shaffer $p$-value & 0.00104 & 0.00135 & 0.00098 & 0.00106 & 0.00109 & 0.00090 & 0.01000 & 0.00094 & 0.00208 & 0.00132\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabularx}
\end{table}

\subsection{Cohen's Kappa Rate}
Table~\ref{tab:kappaResults} shows the Cohen's Kappa rate results obtained by the algorithms. These results support the accuracy achieved by the algorithms, in the sense that the instance-based and wrapper methods perform worse than bag-based and ensemble learners. Specifically, MIRSVM achieves the best kappa rate over $7$ of the $15$ datasets with a competitive average against the Bagging, Stacking, SMO, and TLC algorithms. MIRSVM's kappa values all fall within the range ($0.5$-$1$], indicating that its merit as a classifier agrees with the class distribution and is not random. Note that SimpleMI, MIOptimalBall, MIDD, MISVM, and Stacking contain some negative kappa values, indicating performance worse than the default-hypothesis. MIBoost and MIWrapper are shown to randomly classify all $15$ datasets.

Figure~\ref{fig:BonfDunnkappa} and Table~\ref{tab:statkappa} show the results of the statistical analysis on the Cohen's Kappa Rate results. Nemenyi's procedure reflects results similar to the $p$-values obtained from the accuracy results, where MIRSVM performs significantly better than MIOptimalBall, MIDD, MISVM, MIWrapper, MIBoost, and SimpleMI, having $p$-values $< 0.01$. The Holm and Shaffer procedures indicate that significant differences exist among all algorithms results, supporting MIRSVM's performance as a competitive classifier.

\begin{table}[t!]
\caption{Cohen's Kappa Rate}\label{tab:kappaResults}
\resizebox{\textwidth}{!}{\begin{tabular}{lcccccccccccc}
\noalign{\smallskip}\hline\noalign{\smallskip}
Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\noalign{\smallskip}\hline\noalign{\smallskip}
suramin &\textbf{0.6320} &0.0000 &0.4500 &-0.1500 &0.0000 &0.4500 &0.0000 &-0.5854 &0.3810 &0.3500 &0.5121 &  \\
eastWest &\textbf{0.6000} &0.0000 &0.4500 &0.2250 &0.0000 &0.4250 &0.2750 &0.0000 &0.0000 &0.2750 &-0.1000 &  \\
westEast &0.3500 &0.0000 &-0.2500 &-0.1000 &0.0000 &\textbf{0.4750} &-0.0750 &0.0000 &0.0000 &0.3750 &0.2750 &  \\
musk1 &\textbf{0.8036} &0.0000 &0.5396 &0.7604 &0.0000 &0.5642 &0.6067 &0.0000 &0.7174 &0.7602 &0.7174 &  \\
musk2 &\textbf{0.6263} &0.0000 &0.5031 &0.4039 &0.0000 &0.3613 &0.3856 &0.0000 &0.2492 &0.4029 &0.2940 &  \\
webmining &0.3468 &0.0000 &0.0246 &0.0000 &0.0000 &\textbf{0.4535} &0.3771 &0.0000 &0.3744 &0.2112 &0.2458 &  \\
trx &0.4542 &0.0000 &\textbf{0.5228} &0.4224 &0.0000 &0.0000 &0.0000 &0.0000 &0.3858 &0.3032 &0.3364 &  \\
mutagenesis-atoms &0.5395 &0.0000 &0.1709 &0.2654 &0.0000 &0.2909 &0.0000 &0.0000 &0.4738 &\textbf{0.5458} &0.4431 &  \\
mutagenesis-bonds &0.5699 &0.0000 &0.3131 &0.4356 &0.0000 &0.5569 &0.0000 &0.0000 &0.6195 &\textbf{0.7310} &0.6659 &  \\
mutagenesis-chains &0.6303 &0.0000 &0.2359 &0.4738 &0.0000 &0.6225 &0.0000 &0.0000 &0.6391 &\textbf{0.6525} &0.6285 &  \\
tiger &\textbf{0.5500} &0.0000 &0.0000 &0.4200 &0.0000 &0.4400 &0.5100 &0.0000 &0.3300 &0.5400 &0.4500 &  \\
elephant &\textbf{0.7000} &0.0000 &0.0000 &0.5800 &0.0000 &0.6200 &0.6000 &0.0000 &0.6000 &\textbf{0.7000} &0.6500 &  \\
fox &\textbf{0.3100} &0.0000 &0.0000 &0.1600 &0.0000 &0.0500 &0.1800 &0.0000 &0.2900 &0.2400 &0.3000 &  \\
component &0.6644 &0.0000 &0.1613 &0.2836 &0.0000 &0.3656 &0.0675 &0.0000 &\textbf{0.6945} &0.6924 &0.6906 &  \\
function &0.6292 &0.0000 &0.0966 &0.2801 &0.0000 &0.4083 &0.0933 &0.0000 &0.7529 &\textbf{0.7534} &0.7507 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &\textbf{0.5604} &0.0000 &0.2145 &0.2973 &0.0000 &0.4055 &0.2013 &-0.0390 &0.4338 &0.5022 &0.4573 &  \\
Ranks &\textbf{2.2333} &9.2333 &6.5333 &6.1667 &9.2333 &4.7667 &6.7667 &9.4333 &4.4000 &3.0000 &4.2333 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (10,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (2.2333,0);
\coordinate (c1) at (9.2333,0);
\coordinate (c2) at (6.5333,0);
\coordinate (c3) at (6.1667,0);
\coordinate (c4) at (9.2333,0);
\coordinate (c5) at (4.7667,0);
\coordinate (c6) at (6.7667,0);
\coordinate (c7) at (9.4333,0);
\coordinate (c8) at (4.4,0);
\coordinate (c9) at (3,0);
\coordinate (c10) at (4.2333,0);

\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l2) at (c2) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l8) at (c8) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l10) at (c10) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (2.2333,-0.1) rectangle (5.3529,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}
\captionof{figure}{Bonferroni-Dunn test for Cohen's Kappa rate}\label{fig:BonfDunnkappa}
\vspace{0.5cm}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for Cohen's Kappa rate}\label{tab:statkappa}
\scriptsize
\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Nemenyi $p$-value & 0.00000 & 0.00105 & 0.00353 & 0.00000 & 0.03180 & 0.00018 & 0.00000 & 0.03899 & 0.49139 & 0.13720\\
Holm $p$-value & 0.00091 & 0.00128 & 0.00143 & 0.00093 & 0.00200 & 0.00119 & 0.00094 & 0.00208 & 0.00556 & 0.00263\\
Shaffer $p$-value & 0.00091 & 0.00135 & 0.00143 & 0.00111 & 0.00200 & 0.00135 & 0.00111 & 0.00208 & 0.00556 & 0.00263\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabularx}
\end{table}
\bigskip
\begin{table}[H]
\caption{AUC}\label{tab:aucResults}
\resizebox{\textwidth}{!}{\begin{tabular}{lcccccccccccc}
\hline\noalign{\smallskip}
Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\hline\noalign{\smallskip}
suramin &0.5000 &0.5000 &\textbf{0.7250} &0.4250 &0.5000 &\textbf{0.7250} &0.5000 &0.2143 &0.6905 &0.6750 &0.6811 &  \\
eastWest &\textbf{0.8000} &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.6375 &0.5000 &0.5000 &0.6375 &0.4500 &  \\
westEast &0.6500 &0.5000 &0.3750 &0.4500 &0.5000 &\textbf{0.7375} &0.4625 &0.5000 &0.5000 &0.6875 &0.6375 &  \\
musk1 &\textbf{0.9005} &0.5000 &0.7676 &0.8797 &0.5000 &0.7816 &0.8019 &0.5000 &0.8589 &0.8792 &0.8589 &  \\
musk2 &\textbf{0.8351} &0.5000 &0.7432 &0.6981 &0.5000 &0.6772 &0.6900 &0.5000 &0.6317 &0.7043 &0.6435 &  \\
webmining &0.6320 &0.5000 &0.5096 &0.5000 &0.5000 &0.7184 &\textbf{0.8098} &0.5000 &0.6837 &0.5939 &0.6048 &  \\
trx &0.7243 &0.5000 &\textbf{0.7392} &0.6932 &0.5000 &0.5000 &0.5000 &0.5000 &0.6732 &0.6000 &0.6281 &  \\
mutagenesis-atoms &0.7106 &0.5000 &0.5824 &0.6186 &0.5000 &0.6420 &0.5000 &0.5000 &0.7257 &\textbf{0.7654} &0.7137 &  \\
mutagenesis-bonds &0.7856 &0.5000 &0.6578 &0.6981 &0.5000 &0.7850 &0.5000 &0.5000 &0.8012 &\textbf{0.8569} &0.8211 &  \\
mutagenesis-chains &\textbf{0.8252} &0.5000 &0.6142 &0.7257 &0.5000 &0.8051 &0.5000 &0.5000 &0.8170 &0.8250 &0.8130 &  \\
tiger &\textbf{0.7750} &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &0.7700 &0.7250 &  \\
elephant &0.8200 &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &\textbf{0.8500} &0.8250 &  \\
fox &\textbf{0.6550} &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.5900 &0.5000 &0.6450 &0.6200 &0.6500 &  \\
component &0.7855 &0.5000 &0.5536 &0.6033 &0.5000 &0.6272 &0.5201 &0.5000 &\textbf{0.8123} &0.8030 &0.8081 &  \\
function &0.7563 &0.5000 &0.5298 &0.6015 &0.5000 &0.6391 &0.5268 &0.5000 &\textbf{0.8456} &0.8408 &0.8434 &  \\
\hline\noalign{\smallskip}\noalign{\smallskip}
Average &\textbf{0.7437} &0.5000 &0.6015 &0.6390 &0.5000 &0.6937 &0.6062 &0.4810 &0.7100 &0.7406 &0.7135 &  \\
Ranks &\textbf{2.7667} &9.2000 &6.4000 &6.2333 &9.2000 &4.7000 &6.6667 &9.4333 &4.2000 &3.1000 &4.1000 &  \\
\hline\noalign{\smallskip}
\end{tabular}}
\centering
\resizebox{0.9\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (10,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (2.7667,0);
\coordinate (c1) at (9.2,0);
\coordinate (c2) at (6.4,0);
\coordinate (c3) at (6.2333,0);
\coordinate (c4) at (9.2,0);
\coordinate (c5) at (4.7,0);
\coordinate (c6) at (6.6667,0);
\coordinate (c7) at (9.4333,0);
\coordinate (c8) at (4.2,0);
\coordinate (c9) at (3.1,0);
\coordinate (c10) at (4.1,0);

\node (l0) at (c0) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l2) at (c2) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l4) at (c4) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l5) at (c5) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l8) at (c8) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l10) at (c10) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (2.7667,-0.1) rectangle (5.8863,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}
\captionof{figure}{Bonferroni-Dunn test for AUC}\label{fig:BonfDunnauc}
\vspace{0.5cm}
\captionof{table}{Nemenyi, Holm, and Shaffer tests for AUC}\label{tab:statauc}
\scriptsize
\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Nemenyi $p$-value & 0.00000 & 0.00270 & 0.00420 & 0.00000 & 0.11040 & 0.00128 & 0.00000 & 0.23660 & 0.78313 & 0.27091\\
Holm $p$-value & 0.00093 & 0.00128 & 0.00135 & 0.00094 & 0.00278 & 0.00125 & 0.00091 & 0.00357 & 0.00714 & 0.00385\\
Shaffer $p$-value & 0.00111 & 0.00135 & 0.00135 & 0.00111 & 0.00278 & 0.00135 & 0.00091 & 0.00357 & 0.00714 & 0.00385\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabularx}
\end{table}

\newpage
\subsection{AUC}
Table~\ref{tab:aucResults} shows AUC results obtained by the algorithms. These results complement the accuracy and kappa rate, emphasizing the better performance of bag-based methods. MIRSVM achieves the best AUC score on $6$ of the $15$ datasets, while MIBoost, SimpleMI, and MIWrapper obtain the worst results. Their AUC score indicates random predictor behavior, having values $\leq 0.5$. Bag-level methods all obtain scores between $0.7$ and $0.75$ indicating a high true positive rate and a low false positive rate, which is reflected by the precision and recall results.

Figure~\ref{fig:BonfDunnauc} and Table~\ref{tab:statauc} show that MIRSVM performs significantly better than $6$ out of the $10$ competing algorithms. Nemenyi's procedure indicates that significant differences exist between MIRSVM and all algorithms except MISMO, TLC, Bagging, and Stacking. MISVM is ranked $8^{th}$ with respect to the other state-of-the-art methods. MISVM's true positive rate could be affected because of the possible imbalance of support vectors from the positive and negative classes (favoring the negative). Note that the Nemenyi $p$-values for MIWrapper, MIBoost, and SimpleMI are $= 0$. 
\begin{table}[b!]
\centering
\caption{Run Time (seconds)}\label{tab:time}
\resizebox{\textwidth}{!}{\begin{tabular}{lrrrrrrrrrrrr}
\hline\noalign{\smallskip}
Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\hline\noalign{\smallskip}
suramin &\textbf{0.1} &8.8 &30.5 &7922.0 &9.5 &52.3 &333.9 &7.3 &35.5 &80.5 &1085.0 &  \\
eastWest &\textbf{0.1} &5.5 &9.4 &217.1 &6.3 &14.8 &21.4 &5.8 &15.4 &14.2 &15.3 &  \\
westEast &\textbf{0.1} &6.5 &7.8 &79.7 &6.5 &14.7 &99.5 &6.0 &16.6 &11.1 &10.8 &  \\
musk1 &\textbf{0.4} &13.4 &32.1 &3542.6 &20.6 &89.7 &198.4 &11.1 &93.0 &474.3 &759.5 &  \\
musk2 &\textbf{2.3} &97.3 &782.9 &126016.8 &208.3 &1799.4 &26093.5 &16.1 &1772.2 &14817.3 &16759.0 &  \\
webmining &300.6 &45745.4 &60474.8 &47601.4 &68736.7 &51923.6 &105622.3 &2685.9 &86272.6 &667636.3 &\textbf{10.8} &  \\
trx &61.8 &17.6 &682.3 &339110.5 &19.3 &8670.3 &134622.1 &\textbf{7.4} &2229.3 &17887.3 &592948.9 &  \\
mutagenesis-atoms &9.8 &8.8 &99.2 &2623.0 &8.0 &55.0 &53.5 &\textbf{6.4} &44.0 &182.8 &153.9 &  \\
mutagenesis-bonds &\textbf{8.3} &10.2 &310.2 &17538.7 &12.3 &457.4 &2794.8 &8.4 &131.1 &755.5 &853.1 &  \\
mutagenesis-chains &19.3 &12.0 &525.0 &48982.7 &14.9 &2451.9 &6637.4 &\textbf{7.2} &224.4 &1449.6 &1619.0 &  \\
tiger &29.5 &44.5 &157.8 &23220.5 &56.2 &208.0 &608.8 &\textbf{16.3} &183.0 &1276.7 &11927.9 &  \\
elephant &47.7 &45.5 &243.9 &56456.3 &69.7 &232.1 &1114.3 &\textbf{20.8} &212.1 &1030.7 &1462.2 &  \\
fox &81.0 &44.3 &206.1 &27773.8 &66.0 &369.6 &891.5 &\textbf{23.5} &243.3 &1332.5 &1729.1 &  \\
component &231.7 &572.5 &228209.6 &96263.9 &1096.9 &629366.4 &37224.6 &\textbf{144.0} &9861.5 &74860.9 &79149.8 &  \\
function &740.3 &935.5 &768458.0 &350124.7 &1887.5 &1052225.3 &565026.4 &\textbf{232.8} &12128.2 &138742.0 &185918.5 &  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Average &\textbf{102.2} &3171.2 &70682.0 &76498.2 &4814.6 &116528.7 &58756.2 &213.3 &7564.1 &61370.1 &59626.8 &  \\
Rank &2.2 &2.8 &6.3 &10.1 &3.9 &7.5 &8.9 &\textbf{1.6} &6.3 &8.1 &8.4 &  \\
\hline\noalign{\smallskip}
\end{tabular}}
\captionof{table}{Overall ranks comparison}\label{tab:metarank}
\resizebox{\textwidth}{!}{\begin{tabular}{lcccccccccccc}
\hline\noalign{\smallskip}
Ranks &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
\midrule
accuracy &\textbf{2.4000} &8.8000 &7.2667 &6.0333 &8.8000 &4.8000 &7.0667 &9.0000 &4.7333 &2.7667 &4.3333 &  \\
precision &6.0667 &6.7333 &6.7333 &6.7667 &6.7333 &5.3667 &5.1000 &7.3000 &5.5000 &\textbf{3.9333} &5.7667 &  \\
recall &\textbf{4.4333} &6.2667 &5.8000 &6.7667 &6.2667 &6.2667 &7.4333 &4.5333 &7.0333 &5.3333 &5.8667 &  \\
kappa &\textbf{2.2333} &9.2333 &6.5333 &6.1667 &9.2333 &4.7667 &6.7667 &9.4333 &4.4000 &3.0000 &4.2333 &  \\
auc &\textbf{2.7667} &9.2000 &6.4000 &6.2333 &9.2000 &4.7000 &6.6667 &9.4333 &4.2000 &3.1000 &4.1000 &  \\
run-time &2.2000 &2.7667 &6.2667 &10.1333 &3.9000 &7.5333 &8.8667 &\textbf{1.6000} &6.2667 &8.0667 &8.4000 &  \\
\hline\noalign{\smallskip}\noalign{\smallskip}
Average &\textbf{3.3500} &7.1667 &6.5000 &7.0167 &7.3556 &5.5722 &6.9833 &6.8833 &5.3556 &4.3667 &5.4500 &  \\
Rank &\textbf{2.0000} &7.7500 &6.5833 &8.0000 &7.9167 &5.3333 &7.6667 &7.8333 &5.2500 &3.0000 &4.6667 &  \\
\hline\noalign{\smallskip}
\end{tabular}}
\centering
\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
\draw (1,0) -- (10,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (2,0);
\coordinate (c1) at (7.75,0);
\coordinate (c2) at (6.5833,0);
\coordinate (c3) at (8,0);
\coordinate (c4) at (7.9167,0);
\coordinate (c5) at (5.3333,0);
\coordinate (c6) at (7.6667,0);
\coordinate (c7) at (7.8333,0);
\coordinate (c8) at (5.25,0);
\coordinate (c9) at (3,0);
\coordinate (c10) at (4.6667,0);

\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
\node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l3) at (c3) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l4) at (c4) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l5) at (c5) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l6) at (c6) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l7) at (c7) [below right=.27cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l8) at (c8) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (2,-0.1) rectangle (6.26,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}}
\captionof{figure}{Bonferroni-Dunn test for overall ranks comparison}\label{fig:BonfDunnpmeta}
\end{table}

\subsection{Overall Comparison}
Table~\ref{tab:time} shows the run time results, in seconds, for each algorithm. MIRSVM has the fastest run time and is ranked second. MIRSVM shows very good scalability considering the number of features, such as in the webmining dataset which comprises of $5863$ attributes. Additionally, taking into account the number of instances as seen in the two largest datasets, component and function, MIRSVM displays superior scalability. It is important to note that quadratic programming solvers are not the most efficient tools for solving optimization problems in terms of run time, and yet MIRSVM still is shown to perform competitively against the current state-of-the-art algorithms.

SimpleMI achieves the highest rank and competitive run times because, rather than use the instances in each bag to train a model, it takes the mean value of the instances in a bag and uses that for training. Even though SimpleMI has fast run-times, its performance over the previous metrics has been shown to be random and not as efficient as the bag-level methods.

Table~\ref{tab:metarank} shows the ranks achieved by each of the metrics along with the average and meta-ranks. MIRSVM has the best meta-rank (rank of the ranks) and the Bagging ensemble method has the next best. The meta-ranks also highlight the better performance of bag-level methods over instance-level and wrapper methods, emphasizing the importance of training at the bag-level. Not only does MIRSVM use bag-level information during classification, but it also optimizes over the instances within the bag, which helps determine which instances contribute the most information about the bags label. SimpleMI, MIWrapper, MIBoost, MISVM, MIOptimalBall, and MDD have the worst performance compared to MIRSVM and Bagging. Although these algorithms are popular in literature, the experimental study clearly shows that recent bag-level and ensemble methods easily overcome traditional multi-instance learning algorithms.

In summary, MIRSVM offers improvement in terms of both accuracy and run-time when compared to referenced methods, especially those utilizing SVM-based algorithms.

\section{Conclusion}\label{sec:conclusion}
This paper proposed a novel formulation and algorithm for the multiple-instance support vector machine problem, which optimizes bags classification via bag-representative selection. First, the primal formulation was posed and its dual was then derived and computed using a quadratic programming solver. This formulation was designed to utilize bag-level information and find an optimal separating hyperplane between bags, rather than individual instances, using the standard multi-instance assumption. The SMI assumption states that a bag is labeled positive if and only if at least one instance within a bag is positive, and is negative otherwise. The key features of the proposed algorithm MIRSVM are its ability to identify instances within positive and negative bags, i.e. the support vectors or representatives, that highly impact the decision boundaries as well as avoiding uncertainties and issues caused by techniques that flatten, subset, or under-represent positive instances within positively labeled bags. Additionally, it exhibits desirable scalability, making it suitable for large-scale learning tasks.

The experimental study showed the better performance of MIRSVM compared with multi-instance support vector machines, traditional multi-instance learners, as well as with ensemble methods. The results, according to a variety of performance metrics, were compared and further validated using statistical analysis with non-parametric tests which highlight the advantages of using bag-level based and ensemble learners such as Bagging and Stacking, while showing the instance-level based learners performed poorly in comparison or were deemed as strongly biased and unstable classifiers. On the contrary, our proposal MIRSVM performs statistically better, neither compromising accuracy nor run-time while displaying a robust performance across all of the evaluated datasets.

\begin{acknowledgements}
This research was supported by the Spanish Ministry of Economy and Competitiveness, project TIN2014-55252-P, and by FEDER funds.
\end{acknowledgements}

% BibTeX users please use one of
\bibliographystyle{natbib}
\bibliography{references}

\end{document}

### 2017-06-11 Article/question_answers/InformationSheet.tex
Initial commit

\documentclass[a4paper,notitlepage]{article}
\usepackage[colorlinks,linkcolor=blue,citecolor=green,filecolor=magenta,urlcolor=blue]{hyperref}
\usepackage{url}
\setlength{\parskip}{2ex}

\usepackage{geometry}
 \geometry{
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=20mm,
 }

\begin{document}

\noindent \textbf{\small TITLE:} {\small MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives}

\noindent \textbf{\small AUTHORS:} {\small Gabriella Melki, Alberto Cano, and Sebasti\'{a}n~Ventura}

\bigskip

\noindent Machine learning contribution information:

\begin{itemize}
\item \textbf{\textit{What is the main claim of the paper? Why is this an important contribution to the machine learning literature?}}

This paper proposes a novel L$1$ support vector machine (SVM) formulation, with a bag-representative selector, called Multiple-Instance Representative Support Vector Machine (MIRSVM). Our approach was based on how SVMs identify key instances (support vectors) that highly impact classification using bag-level information. Combining SVMs with a bag-representative selector aims to remedy potential bias towards the negative class issues present in many multiple-instance learning approaches. The proposed method makes no assumptions regarding the distribution of the instances within positive bags caused by methods such as wrappers. This ensures all the information contained within each bag is properly utilized during training.

\item \textbf{\textit{What is the evidence you provide to support your claim?}}

MIRSVM's bag-representative selector is designed to optimize over both positive and negative bags, ensuring each class is properly accounted for during learning. The primal L$1$-SVM problem was reformulated to optimize the margin over bag-representatives, using bag-level information. The dual was then derived and solved using a quadratic programming solver, producing a sparse model. MIRSVM's performance was evaluated with the usage of multiple metrics: accuracy, precision, recall, Cohen's Kappa rate, and Area Under Receiver Operating Characteristic curve (AUC) and the results indicate that the representative selection process contributes to the algorithm's better performance against the state-of-the-art algorithms. MIRSVM achieves the best average efficacy over the 15 benchmark datasets used, especially in comparison to current multi-instance SVM methods. MIRSVM outperforms the ensemble methods used in the experiments according to recall, despite them exhibiting relatively good accuracy and precision indicating them being strongly conservative towards predicting positive bags. MIRSVM's kappa values all fall within the range (0.5-1], highlighting its merit as a classifier. This is also supported by the AUC results which shows a high true positive rate, which is reflected by the precision and recall results. Even though MIRSVM uses a quadratic programming solver to compute the dual SVM problem, it still outperforms all the algorithms compared in terms of run-time, especially over datasets with large number of features and instances.

\item \textbf{\textit{What papers by other authors make the most closely related contributions, and how is your paper related to them?}}

The most closely related contributions include:
\begin{itemize}
\item[-] G. Doran and S. Ray. A theoretical and empirical analysis of support vector machine methods for multiple-instance classification. Machine Learning, 97(1-2):79–-102, 2014.
\item[-] S. Andrews, I. Tsochantaridis, and T. Hofmann. Support Vector Machines for Multiple-Instance Learning. 15th International Conference on Neural Information Processing Systems,  577–-584, 2002.
\item[-] A.W.C. Faria, F.G.F. Coelho, A.M. Silva, H.P. Rocha, G.M. Almeida, A.P. Lemos, and A.P. Braga. Milkde: A new approach for multiple instance learning based on positive instance selection and kernel density estimation. Engineering Applications of Artiﬁcial Intelligence, 59:196–-204, 2017.
\end{itemize}

We addressed the issues and shortcomings of existing multi-instance SVM methods. Specifically, we targeted the issues of biased classification caused by the limited available information about instances within positive bags.

\item \textbf{\textit{Have you published parts of your paper before, for instance in a conference? If so, give details of your previous paper(s) and a precise statement detailing how your paper provides a significant contribution beyond the previous paper(s).}}

No, this is a novel contribution that has not been published nor submitted elsewhere in part or it's entirety.
\end{itemize}

\pagenumbering{gobble}

\end{document}

### 2017-06-11 ArticleRevision/article/article.tex
Initial commit

--- 2017-06-11 Article/MIRSVM_corrected.tex
@@
 \begin{abstract}
-\textit{Multiple-instance learning} (MIL) is a generalization of \textit{supervised learning}, where samples are represented by labeled bags, each containing sets of instances.
+\textit{Multiple-instance learning} (MIL) is a variation of \textit{supervised learning}, where samples are represented by labeled bags, each containing sets of instances.
 The individual labels of the samples within a bag are unknown, and labels are assigned based on a multi-instance assumption.
@@
 In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns that exist between training samples and their class label.
-\textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008,Wei2016155}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
+\textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008,Wei2016155}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
 
@@
 
-\iitem Devising a unique bag-representative selector method that makes no presumptions about the underlying distributions of the instances within each bag, while maintaining the default MIL assumption.
+\iitem Devising a unique bag-representative selection method that makes no presumptions about the underlying distributions of the instances within each bag, while maintaining the default MIL assumption.
 This approach eliminates the issue of class imbalance caused by techniques such as flattening or subsetting positive instances from each bag.
@@
 Let $\bm{X} \in \mathcal{D}$ be a matrix consisting of $d$ input variables and $m$ instances, having a domain of $\bm{X} \in \mathbb{R}^{m \times d}$.
-Let $\bm B$ be the set of bags which contain a number of instances, sometimes of different size, and usually non-overlapping, such as $\bm{B}_I = \{\bm x_{1}, \ldots, \bm x_{|\bm B_I|}\}$ for index set $I \subseteq \set{1,\ldots,n}$, where $|\bm B_I|$ is the number of instances in bag $I$.
+Let $\mathcal{B}$ be the set of bags which contain a number of instances, sometimes of different size, and usually non-overlapping, such as $\bm{B}_I = \{\bm x_{1}, \ldots, \bm x_{|\bm B_I|}\}$ for index set $I \subseteq \set{1,\ldots,n}$, where $|\bm B_I|$ is the number of instances in bag $I$.
 Using the training dataset $\mathcal{D} = \{(\bm B_1,Y_1), \ldots, (\bm B_n,Y_n)\}$, the goal is to learn a model $f : \bm{X} \times Y$, that assigns a label, $Y_I \in \set{-1,\,+1}$, for each input bag $\bm{B}_I$.
@@
 Number of Input Attributes & $d$ \\
-Set of Bags & $\bm B = \set{\bm B_1,\, \ldots,\, \bm B_n}$ \\
+Set of Bags & $\mathcal{B} = \set{\bm B_1,\, \ldots,\, \bm B_n}$ \\
 Bag Index Set & $I \in \ints_+^n$ \\
@@
 Bag Labels & $\bm{Y} \in \{-1,\,1\}^n$ \\
-Individual Instance Label $i$ & $y_i \in \set{-1,+1}$ \\
+Unknown Individual Instance Label $i$ & $y_i \in \set{-1,+1}$ \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 Each bag is assigned a label, unlike traditional classification problems, where individual samples are assigned a label.
-Input instances, $\set{\bm x_1,\, \bm x_2,\, \ldots,\, \bm x_m}$, are grouped into bags with unique identifiers, $\bm B = \set{\bm B_1,\, \bm B_2,\, \ldots,\, \bm B_n \st \bm B_I = \set{\bm x_i \st \forall i \in I}}$, $\forall I \in \set{1, \ldots, n}$ and assigned a label, $Y_I$.
+Input instances, $\set{\bm x_1,\, \bm x_2,\, \ldots,\, \bm x_m}$, are grouped into bags with unique identifiers, $\mathcal{B} = \set{\bm B_1,\, \bm B_2,\, \ldots,\, \bm B_n \st \bm B_I = \set{\bm x_i \st \forall i \in I}}$, $\forall I \in \set{1, \ldots, n}$ and assigned a label, $Y_I$.
 An example representation of an MI dataset is shown in Figure~\ref{fig:mirep}.
@@
 \hline
-$\bm B$ & $F_1$ & $F_2$ & $F_3$ & \ldots & $F_d$ & $Y$ \\        
+$\mathcal{B}$ & $F_1$ & $F_2$ & $F_3$ & \ldots & $F_d$ & $\bm Y$ \\        
 \hline
@@
     $B_1$ 	  & 0.2 & 2.0 & 5.5 & \ldots & 3.0 & POS \\
-    	  & 0.1 & ?   & 4.5 & \ldots & 0.1 &    \\
+    	  & 0.1 & 0.1   & 4.5 & \ldots & 0.1 &    \\
 \hline
@@
     $B_2$	  & 2.3 & 0.2 & 4.0 & \ldots & 5.5 & NEG \\
-    	  & 6.7 & 5.0 & ?   & \ldots & 0.5 &    \\
+    	  & 6.7 & 5.0 & 0.1  & \ldots & 0.5 &    \\
     	  & 0.1 & 4.0 & 8.7 & \ldots & 3.3 &    \\
@@
 The figure shows a sample binary MI dataset with $2$ bags, identified as $B_1$ and $B_2$.
-The bags each contain differing number of instances, each with $d$ dimension, and are assigned positive and negative labels indicated by column $Y$.
-Missing instance feature values are denoted by a question mark.}%
+The bags each contain differing number of instances, each with $d$ dimension, and are assigned positive and negative labels indicated by column $\bm Y$.}%
   \label{fig:mirep}%
@@
 Figure~\ref{fig:diff} shows the decision boundaries produced by MIRSVM and MISVM to highlight the differences in their solutions.
-As Figure~\ref{fig:diff} shows, MISVM produces a higher number of support vectors from the negative bags, which greatly influences the final decision boundary in favor of the negative class.
+As Figure~\ref{fig:diff} shows, MISVM produces a larger number of support vectors from the negative bags, which greatly influences the final decision boundary in favor of the negative class.
 

### 2017-06-11 FormatResults.m

@@ -1,0 +1,32 @@
+% Create Excel File
+clear; clc; close all;
+
+% Get algorithm names
+path = 'C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\';
+names = getList(path,'.');
+excelFile = [path 'Results.xlsx'];
+
+%metrics = {'Accuracy','Precision','Recall','Kappa','AUC'};
+metrics = {'Accuracy'};
+algorithms = {'MIRSVM','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking'};
+line1 = {'Dataset','MIRSVM','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking'};
+columns = {'B','C','D','E','F','G','H','I','J','K','L'};
+ImportTime
+data = DataSet(1:15);
+clearvars DataSet;
+
+for m = 1:length(metrics)
+    sheet = metrics{m};
+    xlswrite(excelFile,line1,sheet,'A1');
+    xlswrite(excelFile,data,sheet,'A2:A16');
+    
+    for a=2:length(algorithms)
+        ind = strmatch(algorithms{a},Algorithm);
+        ind2 = strmatch(algorithms{a},algorithms);
+        m_vals = round(Time(ind,m),4);
+        range = strjoin([columns(ind2) '2:' columns(ind2) '16'],'');
+        xlswrite(excelFile,m_vals,sheet,range);
+    end
+end
+
+

### 2017-06-11 ImportTime.m

@@ -1,0 +1,27 @@
+%% Import data from spreadsheet
+% Script for importing data from the following spreadsheet:
+%
+%    Workbook: C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\ResultsTime.xlsx
+%    Worksheet: Sheet1
+%
+% To extend the code for use with different selected data or a different
+% spreadsheet, generate a function instead of a script.
+
+% Auto-generated by MATLAB on 2017/03/23 17:32:12
+
+%% Import the data
+[~, ~, raw] = xlsread('C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\ResultsTime.xlsx','Sheet1','A2:C150');
+raw(cellfun(@(x) ~isempty(x) && isnumeric(x) && isnan(x),raw)) = {''};
+cellVectors = raw(:,[1,2]);
+raw = raw(:,3);
+
+%% Create output variable
+data = reshape([raw{:}],size(raw));
+
+%% Allocate imported array to column variable names
+Algorithm = cellVectors(:,1);
+DataSet = cellVectors(:,2);
+Time = data(:,1);
+
+%% Clear temporary variables
+clearvars data raw cellVectors;

### 2017-06-11 WekaTesting/BaggingTLCTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.BaggingTLCTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/FormatOutputMI.m

@@ -1,0 +1,69 @@
+% Create Excel File
+clear; clc; close all;
+
+% Get algorithm names
+path = 'C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\';
+names = getList(path,'.');
+
+%metrics = {'Total','Accuracy','Precision','Recall','Kappa','AUC'};
+metrics = {'Time'};
+
+% Create Excel File
+fold = 0;
+excelFile = [path 'ResultsTime.xlsx'];
+sheet = 1;
+startRange = 2;
+xlRange = ['B' num2str(startRange)];
+
+%[status,~] = xlswrite(excelFile,{'Algorithm','DataSet','NumData','Accuracy','Precision','Recall','Kappa','AUC'},sheet,'A1');
+[status,~] = xlswrite(excelFile,{'Algorithm','DataSet','Time'},sheet,'A1');
+
+for n = 1:length(names)
+    folder = names{n};
+    files = getList([path folder '\*.txt'],'');
+    disp(['Reading ' folder]);
+    for f = 1:length(files)
+        line{1} = folder;
+        [resFile, ~] = fopen([path folder '\' files{f}],'r');
+        resText = fscanf(resFile,'%s');
+        fclose(resFile);
+        line{2} = files{f};
+        disp(['Reading ' files{f}]);
+        
+        TP = regexp(resText,'TP=(\d+[.\d+]+)','tokens'); TP = str2double(TP{1});
+        FP = regexp(resText,'FP=(\d+[.\d+]+)','tokens'); FP = str2double(FP{1});
+        TN = regexp(resText,'TN=(\d+[.\d+]+)','tokens'); TN = str2double(TN{1});
+        FN = regexp(resText,'FN=(\d+[.\d+]+)','tokens'); FN = str2double(FN{1});
+        traintime = regexp(resText,'TrainTime=(\d+[.\d+]+)','tokens'); traintime = str2double(traintime{1});
+        testtime = regexp(resText,'TestTime=(\d+[.\d+]+)','tokens'); testtime = str2double(testtime{1});
+        time = (traintime + testtime)/2;
+        
+        num = (TP+FP+TN+FN);
+        accuracy = (TP+TN)/num;
+        precision = TP/(TP+FP);
+        recall = TP/(TP+FN);
+        EA = (TP+FN)*(TP+FP) + (FP + TN)*(FN + TN);
[…]

### 2017-06-11 WekaTesting/MIBoostTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.MIBoostTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/MIDDTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.MIDDTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/MINNDTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.MINNDTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/MIOptimalBallTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.MIOptimalBallTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/MISMOTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.MISMOTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/MISVMTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.MISVMTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/MIWrapperTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.MIWrapperTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/SMITest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.SMITest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/StackingTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.StackingTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/TLCTest.sh

@@ -1,0 +1,1 @@
+java -cp MIexperiments.jar mi.experimental.TLCTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast

### 2017-06-11 WekaTesting/createScripts.m

@@ -1,0 +1,44 @@
+cclear;
+option = 1;
+algorithms = dir('C:/Code/EclipseWorkspace/MultiInstanceSVM/src/mi/experimental/*.java');
+datasets = dir('./Research/Cano/MultiInstanceClassification/WekaTesting/data/*.arff');
+
+% creates bash script to run SOA in parallel
+if option == 1
+    try     
+        fid = fopen('./Research/Cano/MultiInstanceClassification/WekaTesting/parallel_script.sh','w+');  % for removing the extension
+        for alg = algorithms'
+            algorithm = alg.name(1:end-5);
+            string_comm = ['java -cp MIexperiments.jar mi.experimental.' algorithm];
+            for data = datasets' % create a command for each dataset
+                data_name = data.name(1:end-5);
+                string_comm = [string_comm ' ' data_name];
+            end
+            string_comm = [string_comm ' &'];
+            %disp(string_comm);
+            fprintf(fid,'%s\n',string_comm);
+        end
+    catch
+        fclose('all');
+        exit;
+    end
+else
+    for alg = algorithms'
+        algorithm = alg.name(1:end-5);
+        try
+            fid = fopen(['./Research/Cano/MultiInstanceClassification/WekaTesting/' algorithm '.sh'],'w+');  % for removing the extension
+            string_comm = ['java -cp MIexperiments.jar mi.experimental.' algorithm];
+            for data = datasets'
+                data_name = data.name(1:end-5);
+                string_comm = [string_comm ' ' data_name];
+            end
+            %disp(string_comm);
+            fprintf(fid,'%s\n',string_comm);
+        catch
+            fclose('all');
+            exit;
+        end
+    end
+
+end
+fclose('all');

### 2017-06-11 WekaTesting/parallel_script.sh

@@ -1,0 +1,12 @@
+#!/bin/sh
+java -cp MIexperiments.jar mi.experimental.BaggingTLCTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.MIBoostTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.MIDDTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.MINNDTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.MIOptimalBallTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.MISMOTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.MISVMTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.MIWrapperTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.SMITest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
+java -cp MIexperiments.jar mi.experimental.StackingTest component eastWest elephant fox function musk1 musk2 mutagenesis-atoms mutagenesis-bonds mutagenesis-chains suramin tiger trx webmining westEast &
[…]

### 2017-06-11 current_code/DualTest.m

@@ -1,0 +1,22 @@
+function [TP,TN,FP,FN] = DualTest(X,XS,Y,B,alphay,bias,param)
+
+[unique_bag_ids,id] = unique(B);
+Yb = Y(id);
+numb_bags = length(unique_bag_ids);
+output = zeros(numb_bags,1);
+
+for I = 1:numb_bags
+    o_temp = GaussianKernel(X(B == unique_bag_ids(I),:),XS,param)*alphay + bias;
+    o_temp(abs(o_temp) <= 1e-7) = NaN;
+    output(I,1) = sign(max(o_temp));
+end
+
+indP = (Yb == 1);
+indN = (Yb == -1);
+
+TP = sum(Yb(indP) == output(indP));
+TN = sum(Yb(indN) == output(indN));
+FP = sum(Yb(indN) ~= output(indN));
+FN = sum(Yb(indP) ~= output(indP));
+
+end

### 2017-06-11 current_code/DualTrain.m

@@ -1,0 +1,53 @@
+function [alphay,bias,S,iter,sums] = DualTrain(X,Y,B,C,param,options,Bsizes)
+
+[unique_bag_ids,~] = unique(B);
+numb_bags = length(unique_bag_ids);
+%%%%%%%% Initialize %%%%%%%%
+S = []; S_old = zeros(numb_bags,1); ytrain = zeros(numb_bags,1);
+
+offset = 0;
+for I = 1:numb_bags
+    temp = X(B == unique_bag_ids(I),:);
+    len = length(temp(:,1));
+    ind = randi(len,1,1);
+    S(I,:) = ind+offset;
+    offset = offset + len;
+end
+
+Xn = X(S,:); Yn = Y(S); Bn = B(S);
+%%%%%%%% Compute QP Solution %%%%%%%%
+iter = 1; scurrent = 1;
+while(scurrent ~= numb_bags && iter < numb_bags)
+    S_old = [S_old S];
+    H = (Yn*Yn').*GaussianKernel(Xn,Xn,param);
+    f = -1*ones(numb_bags,1);
+    Aeq = Yn';
+    beq = 0;
+    LB = zeros(numb_bags,1);
+    UB = ones(numb_bags,1)*C; 
+    
+    alpha = quadprog(H,f,[],[],Aeq,beq,LB,UB,[],options);
+    indSV = find(1e-7 <= abs(alpha) & abs(alpha) <= (C+1e-7));
+    alphay = Yn.*alpha;
+    bias = (1/length(indSV))*sum(Yn(indSV) - grbf_fast(Xn(indSV,:),Xn(indSV,:),param)*alphay(indSV));
+    
+    offset = 0;
+    for I = 1:numb_bags
+        o = GaussianKernel(X(B == Bn(I),:),Xn,param)*alphay + bias;        
+        o(abs(o) <= 1e-5) = NaN;
+        [ytrain(I),ind] = max(o);
+        ytrain(I) = sign(ytrain(I));
+        S(I,1) = ind+offset;
+        offset = offset + Bsizes(S(I,1));
+    end
+    Xn = X(S,:); Yn = Y(S); Bn = B(S);
+    sums(iter) = sum(S_old(:,iter) == S);
+    scurrent = sums(iter);
+    iter = iter + 1;
+end
+%figure, plot(sums); hold on; title('Sums'); grid on;
+%S = S_old(:,ind_max);
+%alphay = alphay(:,ind_max);
+%bias = bias(ind_max);
+
+end

### 2017-06-11 current_code/best_svm_params.m

@@ -1,0 +1,14 @@
+function [max_val,indBestC,indBestSigma] = best_svm_params(A)
+%% Returns best value in A with min C and max sigma
+
+% find best accuracy with respect to columns (sigma)
+[max_vals_sigma, ind_sigma] = max(A);
+
+% find best accuracy
+max_val = max(max_vals_sigma);
+
+% find best accuracy with respect to rows
+max_ind_C = find(max_vals_sigma == max_val);
+indBestSigma = max_ind_C(end);
+indBestC = ind_sigma(indBestSigma);
+

### 2017-06-11 current_code/cv_tests.m

@@ -1,0 +1,45 @@
+function [acc, iter, precision, recall, kappa, AUC] = cv_tests(Xtrain,Ytrain,Btrain,Bsizes,Xtest,Ytest,Btest,C,param,randomnum)
+rng(randomnum);
+options = optimoptions('quadprog','Algorithm','interior-point-convex','Display','off');
+iter = zeros(10,1);
+TP = zeros(10,1);
+TN = zeros(10,1);
+FP = zeros(10,1);
+FN = zeros(10,1);
+
+for i = 0:9
+    index = i + 1;
+    [alphay,bias,S,iter(index)] = DualTrain(Xtrain{index},Ytrain{index},Btrain{index},C,param,options,Bsizes{index});
+
+    XS = Xtrain{index}(S,:);
+    %%%%%%%% MISVM Testing %%%%%%%%
+    [TP(index),TN(index),FP(index),FN(index)] = DualTest(Xtest{index},XS,Ytest{index},Btest{index},alphay,bias,param);
+    disp(['Iteration ' num2str(i) ' complete.']);
+end
+
+TP = sum(TP);
+TN = sum(TN);
+FP = sum(FP);
+FN = sum(FN);
+numb_data = (TP + TN + FP + FN);
+%%%%%%%% Results %%%%%%%%%%%%%%
+acc = (TP+TN)/numb_data;
+precision = TP/(TP+FP);
+recall = TP/(TP+FN);
+EA = (TP+FN)*(TP+FP) + (FP + TN)*(FN + TN);
+kappa = (numb_data*(TP+TN) - EA)/(numb_data^2 - EA);
+AUC = (1 + recall - (FP/(FP+TN)))/2;
+
+precision(isnan(precision)) = 0;
+recall(isnan(recall)) = 0;
+kappa(isnan(kappa)) = 0;
+AUC(isnan(AUC)) = 0;
+
+acc = mean(acc);
+iter = mean(iter);
+precision = mean(precision);
+recall = mean(recall);
+kappa = mean(kappa);
+AUC = mean(AUC);
+
+end

### 2017-06-11 current_code/mirsvm_script.m

@@ -1,0 +1,36 @@
+function [acc,iter,precision,recall,kappa,AUC] = mirsvm_script(path,name,C,param,rnd,p)
+% [acc,iter,precision,recall,kappa,AUC] = mirsvm_script('Google Drive/data/midata/libsvm/','musk1',1000,4.6,1,1)
+
+rng('default'); rng(rnd); 
+options = optimoptions('quadprog','Algorithm','interior-point-convex','Display','off');
+
+[Y,X] = libsvmread([path name]); X = full(X);  Y(Y==2) = -1;
+B = X(:,2); Bsizes = X(:,1); X = X(:,3:end); X = scale(X,2); X(isnan(X)) = 0;
+[unique_bag_ids,~] = unique(B);
+numb_bags = length(unique_bag_ids);
+% train
+[alphay,bias,S,iter,sums] = DualTrain(X,Y,B,C,param,options,Bsizes);
+XS = X(S,:);
+% test
+[TP,TN,FP,FN] = DualTest(X,XS,Y,B,alphay,bias,param);
+num_data = (TP + TN + FP + FN);
+
+acc = (TP+TN)/num_data;
+precision = TP/(TP+FP);
+recall = TP/(TP+FN);
+EA = (TP+FN)*(TP+FP) + (FP + TN)*(FN + TN);
+kappa = (num_data*(TP+TN) - EA)/(num_data^2 - EA);
+AUC = (1 + recall - (FP/(FP+TN)))/2;
+
+if p == 1
+    fig = figure; plot(sums); hold on; title(name,'Interpreter','latex'); 
+    grid minor; xlabel('Iterations','Interpreter','latex'); ylabel('Equal Representatives','Interpreter','latex');
+    plot(numb_bags.*ones(length(sums),1),'r'); axis([1 length(sums) 1 numb_bags+1]);
+    set(gca,'fontsize',11);
+    set(gca,'TickLabelInterpreter', 'latex');
+    print(fig,name,'-dpng');
+end
+
+
+%disp('[acc,iter,precision,recall,kappa,AUC] = mirsvm_script(path,name,C,param,rnd,p)');
+end

### 2017-06-11 current_code/testing.m

@@ -1,0 +1,59 @@
+warning off;
+name = 'musk1/';
+path = './data/midata/CVSets/';
+num = 10; C = 1000; param = 4.5; randomnum = 2;
+
+TP = zeros(num,1); TN = zeros(num,1); FP = zeros(num,1); FN = zeros(num,1);
+Time = zeros(num,1);
+
+options = optimoptions('quadprog','Algorithm','interior-point-convex','Display','off');
+rng(randomnum);
+
+for i = 0:9
+    index = i + 1;
+    [Ytrain, Xtrain] = libsvmread([path name 'train_' num2str(i)]);
+    Xtrain = full(Xtrain);
+    Ytrain(Ytrain==2) = -1;
+    [~, dim] = size(Xtrain);
+    Bsizes = Xtrain(:,1);
+    Btrain = Xtrain(:,2);
+    Xtrain = Xtrain(:,3:dim);
+    Xtrain(isnan(Xtrain)) = 0;
+
+    [Ytest,Xtest] = libsvmread([path name 'test_' num2str(i)]);
+    Xtest = full(Xtest);
+    Ytest(Ytest==2) = -1;
+    [~, dim] = size(Xtest);
+    Btest = Xtest(:,2);
+    Xtest = Xtest(:,3:dim);
+    [~,dim] = size(Xtest); 
+    Xtest(isnan(Xtest)) = 0;
+    disp(['Reading data ' num2str(i) ' has finished..']);
+    
+    % Training
+    t0 = cputime;
+    [alphay,bias,S] = DualTrain(Xtrain,Ytrain,Btrain,C,param,options,Bsizes);
+    t = cputime - t0;
+    XS = Xtrain(S,:);
+    % Testing
+    tt0 = cputime;
+    [TP(index),TN(index),FP(index),FN(index)] = DualTest(Xtest,XS,Ytest,Btest,alphay,bias,param);
+    tt = cputime - tt0;
+    Time(index) = t + tt;
+end
+
+% Results
+
+TP = sum(TP);
+TN = sum(TN);
+FP = sum(FP);
+FN = sum(FN);
+numb_data = (TP + TN + FP + FN);
+
+acc = (TP+TN)/numb_data;
+precision = TP/(TP+FP);
+recall = TP/(TP+FN);
+EA = (TP+FN)*(TP+FP) + (FP + TN)*(FN + TN);
[…]

### 2017-06-11 current_code/testing_convergence.m

@@ -1,0 +1,41 @@
+cclear;
+path = 'C:\Users\melkiga\Google Drive\data\midata\libsvm';
+datasets = dir(path);
+datasets([1:2 3 7 16],:) = [];
+C = [0.1 1 10 100 1000];
+Sigma = [0.05 0.1 0.5 1 2.5 5 7 10 15];
+acc = zeros(length(C),length(Sigma));
+
+fid = fopen('best_vars.txt','w+');
+fprintf(fid,'Dataset, C, Sigma, Iter, Accuracy, Precision, Recall, Kappa, AUC\n');
+j = 1;
+for data = datasets'
+    for c = 1:length(C)
+        for s = 1:length(Sigma)
+            [acc(c,s)] = mirsvm_script([path '\'],data.name,C(c),Sigma(s),1,0);
+        end
+    end
+    [max_val,indBestC,indBestSigma] = best_svm_params(acc);
+    BestC(j) = C(indBestC); BestS(j) = Sigma(indBestSigma);
+    [acc,iter,precision,recall,kappa,AUC] = mirsvm_script([path '\'],data.name,C(indBestC),Sigma(indBestSigma),1,1);
+    fprintf(fid,'%s, %.4f, %.4f, %d, %.4f, %.4f, %.4f, %.4f, %.4f\n'...
+           ,data.name,C(indBestC),Sigma(indBestSigma),iter,acc,precision,recall,kappa,AUC);
+    j = j + 1;
+end
+fclose(fid);
+
+%%
+fid = fopen('best_rand_vars.txt','w+');
+fprintf(fid,'Dataset, C, Sigma, Iter, Accuracy, Precision, Recall, Kappa, AUC, RND\n');
+BestC = [1 0.1 0.1 0.1 1 0.1 1 100 0.1 0.1 1 0.1];
+BestS = [0.5 0.5 0.5 5 1 0.1 0.5 0.05 10 1 0.1 0.1];
+j = 1;
+for data = datasets'
+    for i = 1:10
+        [acc,iter,precision,recall,kappa,AUC] = mirsvm_script([path '\'],data.name,BestC(j),BestS(j),i,0);
+        fprintf(fid,'%s, %.4f, %.4f, %d, %.4f, %.4f, %.4f, %.4f, %.4f, %d\n'...
+           ,data.name,C(indBestC),Sigma(indBestSigma),iter,acc,precision,recall,kappa,AUC);
+    end
+    j = j + 1;
+end
+fclose(fid);

### 2017-06-11 post_hoc_script.m

@@ -1,0 +1,49 @@
+clear; clc; close all;
+
+filename = 'Results.xlsx';
+path_in = 'C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\';
+path_out = 'C:\Users\melkiga\Google Drive\MatlabHelpers\stats_tables\';
+file_path = [path_in filename];
+metrics = {'accuracy','precision','recall','kappa','auc','Time'};
+num_metrics = length(metrics);
+alpha = 0.1;
+
+% Get algorithm and datasets names and lengths
+[~, ~, prints] = xlsread(file_path,2,'A1:L1');
+prints(cellfun(@(x) ~isempty(x) && isnumeric(x) && isnan(x),prints)) = {NaN};
+algorithms = prints(2:end);
+num_algorithms = length(algorithms);
+
+[~, ~, datasets] = xlsread(file_path,2,'A2:A16');
+datasets(cellfun(@(x) ~isempty(x) && isnumeric(x) && isnan(x),datasets)) = {NaN};
+datasets = datasets';
+num_datasets = length(datasets);
+latex_data_rows = datasets; latex_data_rows{end+1} = 'Average'; latex_data_rows{end+1} = 'Rank';
+
+% Allocate memory
+ranks = zeros(num_metrics,num_algorithms);
+
+for m = 1:length(metrics)
+    metric = metrics{m};
+    disp(metric);
+    
+    [~, ~, data] = xlsread(file_path,metric,'B2:L16');
+    data(cellfun(@(x) ~isempty(x) && isnumeric(x) && isnan(x),data)) = {NaN};
+    data = cell2mat(data);
+    
+    [avg_ranks,chi_statistics] = avg_rank(-data);
+    ranks(m,:) = avg_ranks;
+    %max_rank = round(max(avg_ranks))+1;
+    %[stats,headers] = wilcoxon(data,alpha);
+    
+    %data(end+1,:) = mean(data);
+    %data(end+1,:) = avg_ranks;
+    
+    %matrix2latex_metrics(data, [path_out [metric '.tex']], 'rowLabels', latex_data_rows, 'columnLabels', algorithms, 'alignment', 'c', 'format', '%-1.1f', 'rank', 'yes');
+    % create results table latex
[…]

### 2017-06-11 prototype_code/DualCV.m

@@ -1,0 +1,88 @@
+clear; clc; close all;
+
+C = 10;
+param = 0.2;
+seed = 1;
+k = 2;
+rng(seed);
+options = optimoptions('quadprog','Algorithm','interior-point-convex','Display','off');
+%%%%%%%% Load Data %%%%%%%%
+%bag3data; l = 1;
+%loaddataoverlap; l = 1;
+%loadrandommidata; l = 0;
+% data_nonlin; l = 1;
+% [numb_data,dim] = size(X);
+
+[Y,X] = libsvmread('C:\Code\MIRSVM\data\suraminsvm');
+%[Y,X] = libsvmread('C:\Code\MIQP\data\nonlin'); l = 1;
+X = full(X);
+Y(Y==2) = -1;
+[numb_data, dim] = size(X);
+B = X(:,2);
+Bsizes = X(:,1);
+X = X(:,3:dim);
+[~,dim] = size(X);
+
+%%%%%%%% Preprocess %%%%%%%%
+%args = shuffle(numb_data,seed,X,Y,B);
+%X = args{1}; Y = args{2}; B = args{3};
+X = scale(X,0); 
+X(isnan(X)) = 0;
+
+if dim == 2 && l == 0; plot2D(X,Y,1); end
+
+unique_bag_ids = unique(B);
+numb_bags = length(unique_bag_ids);
+
+for bl = 1:numb_bags
+    bagLabels(bl,1) = Y(min(find(B == unique_bag_ids(bl))));
+end
+
+[cv] = crossvalind('Kfold',bagLabels,k);
+
+acc = zeros(k,1);
+accCV = zeros(length(C), length(param));
+
+for c = 1:length(C)
+    c0 = C(c);
+    for p = 1:length(param)
+        p0 = param(p);
+        for i = 1:k
+            if k == 1
+                tr = ismember(B,unique_bag_ids);
+                tst = ismember(B,unique_bag_ids);
+            else
+                teIdx = (cv == i); trIdx = ~teIdx;
+                tr = ismember(B,unique_bag_ids(trIdx));
+                tst = ismember(B,unique_bag_ids(teIdx));
+            end
+
+            Xtr = X(tr,:); Ytr = Y(tr); Btr = B(tr); 
+            Xtst = X(tst,:); Ytst = Y(tst); Btst = B(tst);
+            
+            %%%%%%%% MISVM Training %%%%%%%%
[…]

### 2017-06-11 prototype_code/DualQP.m

@@ -1,0 +1,126 @@
+clear; clc; close all;
+C = 1000;
+param = 2;
+seed = 1;
+rng(seed);
+options = optimoptions('quadprog','Algorithm','interior-point-convex','Display','off');
+%%%%%%%% Load Data %%%%%%%%
+%bag3data; l = 1;
+%loaddataoverlap; l = 1;
+%loadrandommidata; l = 0;
+%data_nonlin; l = 1;
+%[numb_data,dim] = size(X);
+% l = 0;
+% [Y,X] = libsvmread('C:\Code\MIQP\data\nonlin');
+% X = full(X);
+% Y(Y==2) = -1;
+% [numb_data,dim] = size(X);
+% B = X(:,2);
+% Bsizes = X(:,1);
+% X = X(:,3:dim);
+% [~,dim] = size(X);
+
+[Y,X] = libsvmread('./Research/Cano/MultiInstanceClassification/musk1svm');
+X = full(X);
+Y(Y==2) = -1;
+[numb_data,dim] = size(X);
+B = X(:,2);
+Bsizes = X(:,1);
+X = X(:,3:dim);
+[~,dim] = size(X);
+
+%%%%%%%% Preprocess %%%%%%%%
+%args = shuffle(numb_data,seed,X,Y,B);
+%X = args{1}; Y = args{2}; B = args{3};
+%X = scale(X,2); 
+
+if dim == 2 && l == 0; plot2D(X,Y,1); end
+
+unique_bag_ids = unique(B);
+numb_bags = length(unique_bag_ids);
+%%%%%%%% Initialize %%%%%%%%
+S = zeros(numb_bags,1);
+S_old = [];
+Ybt = zeros(numb_bags,1);
+output = zeros(numb_bags,1);
+
+for I = 1:numb_bags
+    temp = X(B == unique_bag_ids(I),:);
+    Ybt(I,1) = max(Y(B == unique_bag_ids(I),1));
+    ind = randi(length(temp(:,1)),1,1);
+    [~,t] = ismember(temp(ind,:),X,'rows');
+    S(I,:) = t;
+end
+
+Xn = X(S,:);
+Yn = Y(S);
+Bn = B(S);
+G = grbf_fast(X,X,param);
+%%%%%%%% Compute QP Solution %%%%%%%%
+iter = 0;
+while(sum(ismember(S_old,S)) ~= numb_bags)
+    iter = iter + 1;
+    S_old = [S_old S];
+    Gn = G(S,S);
+    H = (Yn*Yn').*Gn;
[…]

### 2017-06-11 prototype_code/DualTest.m

@@ -1,0 +1,22 @@
+function [TP,TN,FP,FN] = DualTest(X,XS,Y,B,alphay,bias,param)
+
+[unique_bag_ids,id] = unique(B);
+Yb = Y(id);
+numb_bags = length(unique_bag_ids);
+output = zeros(numb_bags,1);
+
+for I = 1:numb_bags
+    o_temp = grbf_fast(X(B == unique_bag_ids(I),:),XS,param)*alphay + bias;
+    o_temp(abs(o_temp) <= 1e-7) = NaN;
+    output(I,1) = sign(max(o_temp));
+end
+
+indP = (Yb == 1);
+indN = (Yb == -1);
+
+TP = sum(Yb(indP) == output(indP));
+TN = sum(Yb(indN) == output(indN));
+FP = sum(Yb(indN) ~= output(indN));
+FN = sum(Yb(indP) ~= output(indP));
+
+end

### 2017-06-11 prototype_code/DualTrain.m

@@ -1,0 +1,79 @@
+function [alphay,bias,S,iter] = DualTrain(X,Y,B,C,param,options,Bsizes)
+
+[unique_bag_ids,~] = unique(B);
+numb_bags = length(unique_bag_ids);
+%%%%%%%% Initialize %%%%%%%%
+S = zeros(numb_bags,1);
+S_old = ones(numb_bags,1);
+p=0;
+offset = 0;
+for I = 1:numb_bags
+    temp = X(B == unique_bag_ids(I),:);
+    ind = randi(length(temp(:,1)),1,1);
+    S(I,:) = ind+offset;
+    offset = offset + length(temp(:,1));
+end
+
+Xn = X(S,:);
+Yn = Y(S);
+Bn = B(S);
+%%%%%%%% Compute QP Solution %%%%%%%%
+iter = 0;
+while(max(sum(ismember(S_old,S))) ~= numb_bags && iter < 3)
+%while(sum(S == S_old) ~= numb_bags)
+    iter = iter + 1;
+    S_old = [S_old S];
+    %S_old = S;
+    H = (Yn*Yn').*grbf_fast(Xn,Xn,param);
+    f = -1*ones(numb_bags,1);
+    Aeq = Yn';
+    beq = 0;
+    LB = zeros(numb_bags,1);
+    UB = ones(numb_bags,1)*C; 
+    
+    alpha = quadprog(H,f,[],[],Aeq,beq,LB,UB,[],options);
+    indSV = find(1e-7 <= abs(alpha) & abs(alpha) <= (C+1e-7));
+    alphay(:,iter) = Yn.*alpha;
+    bias(iter) = (1/length(indSV))*sum(Yn(indSV) - grbf_fast(Xn(indSV,:),Xn(indSV,:),param)*alphay(indSV,iter));
+    
+    if p==1
+        plot2D(X,Y,iter);
+        hold on;
+        minnum = min(min(X))-1;
+        maxnum = max(max(X))+1;
+        x1 = linspace(minnum,maxnum,99);
+        x2 = linspace(minnum,maxnum,100);
+        X0 = centri(x1,x2);
+        Gp = grbf_fast(X0,X(S,:),param);
+        O = Gp*alphay(:,iter) + bias(iter);
+        O = reshape(O,length(x1),length(x2));
+        contour(x1,x2,(O'),[0 0],'k','ShowText','on');
+        plot(X(S,1),X(S,2),'mx');
[…]

### 2017-06-11 prototype_code/MISVM.m

@@ -1,0 +1,45 @@
+function [alphay,bias,S,indSV] = MISVM(X,Y,B,C,param,options,Bsizes)
+
+[unique_pos_bags,~] = unique(B(Y==1));
+numb_pos_bags = length(unique_pos_bags);
+%%%%%%%% Initialize %%%%%%%%
+S_old = zeros(numb_pos_bags,1);
+S = ones(numb_pos_bags,1);
+
+for I = 1:numb_pos_bags
+    Xp(I,:) = mean(X(B == unique_pos_bags(I),:));
+end
+
+Xn = [Xp; X(Y==-1,:)];
+Yn = [ones(numb_pos_bags,1); Y(Y==-1)];
+len_neg = length(Y(Y==-1));
+nbag = numb_pos_bags + len_neg;
+
+while(sum(S == S_old) ~= numb_pos_bags)
+    S_old = S;
+    H = (Yn*Yn').*grbf_fast(Xn,Xn,param);
+    f = -1*ones(nbag,1);
+    Aeq = Yn';
+    beq = 0;
+    LB = zeros(nbag,1);
+    UB = ones(nbag,1)*C; 
+    
+    alpha = quadprog(H,f,[],[],Aeq,beq,LB,UB,[],options);
+    indSV = find(1e-7 <= abs(alpha) & abs(alpha) <= (C+1e-7));
+    alphay = Yn.*alpha;
+    bias = (1/length(indSV))*sum(Yn(indSV) - grbf_fast(Xn(indSV,:),Xn(indSV,:),param)*alphay(indSV,1));
+    %w = Xn'*alphay;
+    
+    offset = 0;
+    for I = 1:numb_pos_bags
+        o = grbf_fast(X(B == unique_pos_bags(I),:),Xn,param)*alphay + bias;
+        [~,ind] = max(o);
+        S(I,1) = ind+offset;
+        offset = offset + Bsizes(S(I,1));
+    end
+    
+    Xn = [X(S,:); X(Y==-1,:)];
+    Yn = [ones(numb_pos_bags,1); Y(Y==-1)];
+end
+
+end

### 2017-06-11 prototype_code/PrimalQP.m

@@ -1,0 +1,118 @@
+clear; clc; close all;
+
+C = 1000;
+param = 1;
+N = 0.1;
+seed = 1;
+rng(seed);
+%%%%%%%% Load Data %%%%%%%%
+%loaddataoverlap
+%loadrandommidata
+[X,Y,B] = MuskData('musk1');
+[numb_data,dim] = size(X);
+
+%%%%%%%% Preprocess %%%%%%%%
+args = shuffle(numb_data,seed,X,Y,B);
+X = args{1}; Y = args{2}; B = args{3};
+X = scale(X,2); 
+
+if dim == 2
+   plot2D(X,Y,1);
+end
+
+b_ind_p = find(Y == 1);
+b_p_labels = unique(B(b_ind_p));
+numb_p_bags = length(b_p_labels);
+
+b_ind_n = find(Y == -1);
+b_n_labels = unique(B(b_ind_n));
+numb_n_bags = length(b_n_labels);
+
+numb_bags = numb_p_bags + numb_n_bags;
+unique_bag_ids = unique(B);
+
+%%%%%%%% Initialize %%%%%%%%
+% S = zeros(numb_p_bags,1);
+% S_old = zeros(numb_p_bags,1);
+
+% %also try setting N to the number of +ive bags, to make it balanced
+model = svmtrain(Y(b_ind_n),X(b_ind_n,:),['-s 2 -t 1 -g ' num2str(param) ' -n ' num2str(N) ' -q ' num2str(0) ' -v' num2str(1)]);
+[~,t] = ismember(full(model.SVs),X,'rows');
+index_neg = t(:,1);
+
+model2 = svmtrain(Y(b_ind_p),X(b_ind_p,:),['-s 2 -t 1 -g ' num2str(param) ' -n ' num2str(N) ' -q ' num2str(0) ' -v' num2str(1)]);
+[~,t] = ismember(full(model2.SVs),X,'rows');
+S = t(:,1);
+endlength = length(S);
+S_old = zeros(endlength,1);
+
+% for I = 1:numb_p_bags
+%     temp = X(B == b_p_labels(I),:);
+%     ind = randi(length(temp(:,1)),1,1);
+%     [~,t] = ismember(temp(ind,:),X,'rows');
+%     S(I,:) = t;
+% end
+clearvars I t x cur_bag;
+
+%%%%%%%% Compute QP Solution %%%%%%%%
+iter = 1;
+while(sum(S_old == S) ~= endlength)
+    S_old = S;
+    index = [index_neg; S];
[…]

### 2017-06-11 prototype_code/PrimalQPKernelized.m

@@ -1,0 +1,112 @@
+clear; clc; close all;
+
+C = 1000;
+param = 1;
+N = 0.1;
+seed = 1;
+rng(seed);
+%%%%%%%% Load Data %%%%%%%%
+%loaddataoverlap
+%loadrandommidata
+[X,Y,B] = MuskData('musk1');
+[numb_data,dim] = size(X);
+
+%%%%%%%% Preprocess %%%%%%%%
+args = shuffle(numb_data,seed,X,Y,B);
+X = args{1}; Y = args{2}; B = args{3};
+X = scale(X,2); 
+
+if dim == 2
+   plot2D(X,Y,1);
+end
+
+b_ind_p = find(Y == 1);
+b_p_labels = unique(B(b_ind_p));
+numb_p_bags = length(b_p_labels);
+
+b_ind_n = find(Y == -1);
+b_n_labels = unique(B(b_ind_n));
+numb_n_bags = length(b_n_labels);
+
+numb_bags = numb_p_bags + numb_n_bags;
+unique_bag_ids = unique(B);
+
+%%%%%%%% Initialize %%%%%%%%
+% %also try setting N to the number of +ive bags, to make it balanced
+model = svmtrain(Y(b_ind_n),X(b_ind_n,:),['-s 2 -t 1 -g ' num2str(param) ' -n ' num2str(N) ' -q ' num2str(0) ' -v' num2str(1)]);
+[~,t] = ismember(full(model.SVs),X,'rows');
+index_neg = t(:,1);
+
+model2 = svmtrain(Y(b_ind_p),X(b_ind_p,:),['-s 2 -t 1 -g ' num2str(param) ' -n ' num2str(N) ' -q ' num2str(0) ' -v' num2str(1)]);
+[~,t] = ismember(full(model2.SVs),X,'rows');
+S = t(:,1);
+endlength = length(S);
+S_old = zeros(endlength,1);
+
+clearvars I t x cur_bag;
+
+%%%%%%%% Compute QP Solution %%%%%%%%
+iter = 1;
+while(sum(S_old == S) ~= endlength)
+    S_old = S;
+    index = [index_neg; S];
+    nnew = length(index);
+    args = shuffle(nnew,seed,index);
+    index = args{1};
+    Xn = X(index,:);
+    Yn = Y(index);
+    G = grbf_fast(Xn,Xn,param);
+    
+    H = diag([ones(1,nnew), zeros(1, nnew+1)]);
[…]

### 2017-06-11 prototype_code/mirsvm_vs_misvm.m

@@ -1,0 +1,131 @@
+clear; clc; close all;
+
+C = 1000;
+param = 1.5;
+seed = 1;
+dim = 2;
+rng(seed);
+bnump = 2;
+bnumn = 4;
+numb = bnump + bnumn;
+num = [30 35 15 15 15 15]';
+shiftx = [4 6 3 4.7 5.1 7];
+shifty = [4 4 4.5 5 2.5 5];
+vari = [0.4 0.4 0.4 0.3 0.3 0.4];	
+
+%%%%%%%% Load Data %%%%%%%%
+
+X = []; Y = []; B = []; Bsizes = [];
+for x = 1:bnump
+    X = [X; shiftx(x)+randn(num(x),1)*vari(x) shifty(x)+randn(num(x),1)*vari(x)];
+    Y = [Y; ones(num(x),1)];
+    B = [B; x*ones(num(x),1)];
+    Bsizes = [Bsizes; num(x)*ones(num(x),1)];
+end
+for x = 1:bnumn
+    n = bnump+x;
+    X = [X; shiftx(n)+randn(num(n),1)*vari(n) shifty(n)+randn(num(n),1)*vari(n)];
+    Y = [Y; -ones(num(n),1)];
+    B = [B; (n)*ones(num(n),1)];
+    Bsizes = [Bsizes; num(n)*ones(num(n),1)];
+end
+
+%plot2D(X,Y,1);
+
+%% MIRSVM is here
+options = optimoptions('quadprog','Algorithm','interior-point-convex','Display','off');
+
+[alphay,bias,S] = DualTrain(X,Y,B,C,param,options,Bsizes);
+XS = X(S,:);
+[TP,TN,FP,FN] = DualTest(X,XS,Y,B,alphay,bias,param);
+acc = (TP+TN)/numb;
+MIRSVM_acc = acc
+
+plot2D(X,Y,1);
+%hold on;
+minnum = min(min(X))-1;
+maxnum = max(max(X))+1;
+x1 = linspace(minnum,maxnum,99);
+x2 = linspace(minnum,maxnum,100);
+X0 = centri(x1,x2);
+Gp = grbf_fast(X0,X(S,:),param);
+O = Gp*alphay + bias;
+O = reshape(O,length(x1),length(x2));
+[~,h] = contour(x1,x2,(O'),[0 0],'k','DisplayName','decision boundary');
+set(h,'linewidth',1.5);
[…]

### 2017-06-11 prototype_code/tst.m

@@ -1,0 +1,49 @@
+function [acc, iter, precision, recall, kappa, AUC, Time] = tst(Xtrain,Ytrain,Btrain,Bsizes,Xtest,Ytest,Btest,C,param,randomnum)
+%[acc, iter, precision, recall, kappa, AUC] = tst('tiger',1000,3,2)
+rng(randomnum);
+options = optimoptions('quadprog','Algorithm','interior-point-convex','Display','off');
+iter = zeros(10,1);
+TP = zeros(10,1);
+TN = zeros(10,1);
+FP = zeros(10,1);
+FN = zeros(10,1);
+Time = zeros(10,1);
+
+for i = 0:9
+    index = i + 1;
+    t0 = cputime;
+    [alphay,bias,S,iter(index)] = DualTrain(Xtrain{index},Ytrain{index},Btrain{index},C,param,options,Bsizes{index});
+    t = cputime - t0;
+    XS = Xtrain{index}(S,:);
+    %%%%%%%% MISVM Testing %%%%%%%%
+    t1 = cputime;
+    [TP(index),TN(index),FP(index),FN(index)] = DualTest(Xtest{index},XS,Ytest{index},Btest{index},alphay,bias,param);
+    tt = cputime - t1;
+    Time(index) = t + tt;
+    disp(['Iteration ' num2str(i) ' complete.']);
+end
+
+TP = sum(TP);
+TN = sum(TN);
+FP = sum(FP);
+FN = sum(FN);
+numb_data = (TP + TN + FP + FN);
+%%%%%%%% Results %%%%%%%%%%%%%%
+acc = (TP+TN)/numb_data;
+precision = TP/(TP+FP);
+recall = TP/(TP+FN);
+EA = (TP+FN)*(TP+FP) + (FP + TN)*(FN + TN);
+kappa = (numb_data*(TP+TN) - EA)/(numb_data^2 - EA);
+AUC = (1 + recall - (FP/(FP+TN)))/2;
+
+precision(isnan(precision)) = 1;
+recall(isnan(recall)) = 1;
+
+acc = mean(acc);
+iter = mean(iter);
+precision = mean(precision);
+recall = mean(recall);
+kappa = mean(kappa);
+AUC = mean(AUC);
+Time = mean(Time);
+end

### 2017-06-11 prototype_code/tstt.m

@@ -1,0 +1,78 @@
+%clear; clc;
+warning off;
+name = 'function/';
+path = './data/midata/CVSets/';
+n = 1;
+C = 1;
+param = 1;
+rnum = 1;
+%ii = [21:40];
+
+Xtrain = cell(10,1); Xtest = cell(10,1);
+Ytrain = cell(10,1); Ytest = cell(10,1);
+Btrain = cell(10,1); Btest = cell(10,1);
+Bsizes = cell(10,1);
+
+for i = 0:9
+    index = i + 1;
+    [Ytrain{index},Xtrain{index}] = libsvmread([path name 'train_' num2str(i)]);
+    Xtrain{index} = full(Xtrain{index});
+    Ytrain{index}(Ytrain{index}==2) = -1;
+    [~, dim] = size(Xtrain{index});
+    Bsizes{index} = Xtrain{index}(:,1);
+    Btrain{index} = Xtrain{index}(:,2);
+    Xtrain{index} = Xtrain{index}(:,3:dim);
+    Xtrain{index}(isnan(Xtrain{index})) = 0;
+    indred = abs(sum(Xtrain{index})) < 1e-5;
+    Xtrain{index}(:,indred) = [];
+
+    [Ytest{index},Xtest{index}] = libsvmread([path name 'test_' num2str(i)]);
+    Xtest{index} = full(Xtest{index});
+    Ytest{index}(Ytest{index}==2) = -1;
+    [numb_data, dim] = size(Xtest{index});
+    Btest{index} = Xtest{index}(:,2);
+    Xtest{index} = Xtest{index}(:,3:dim);
+    [~,dim] = size(Xtest{index}); 
+    Xtest{index}(isnan(Xtest{index})) = 0;
+    Xtest{index}(:,indred) = [];
+    disp(['Data ' num2str(i) ' has finished..']);
+end
+disp('Finished reading data...');
+
+%% 
+% n = 4;
+% C = 1000;
+% param = 4;
+% rnum = 2;
+% ii = [21:24];
+
+if n == 1
+    t0 = cputime;
+    [acc, iter, precision, recall, kappa, AUC, Time] = tst(Xtrain,Ytrain,Btrain,Bsizes,Xtest,Ytest,Btest,C,param,rnum);
+    t = cputime - t0;
+    disp(['Finished after ' num2str(t) ' seconds.']);
+else
+    acc = zeros(n,1);
+    iter = zeros(n,1);
+    precision = zeros(n,1);
[…]

### 2017-06-12 ArticleRevision/article/article.tex
Removed ML citiations from text

@@
 In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns that exist between training samples and their class label.
-\textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008,Wei2016155}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
+\textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
 
@@
 Another similar method is the Diverse Density (DD)~\citep{Maron1998} framework which is maximized for instances in feature space that are near at least one instance in a positive bag and far from all instances in negative bags.
-In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\cite{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\cite{Auer2004} present a boosting approach~\citep{Schapire19981651} that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall).
+In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\cite{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\cite{Auer2004} present a boosting approach that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall).
 This approach is similar to that of APR and DD, except that~\cite{Auer2004} propose computing optimal balls per positive bags.
@@
 \subsection{Support Vector Machines}\label{subsec:svms}
-Most classical machine learning techniques require knowledge of the data distribution in order to learn accurate models~\citep{Alabdulmohsin2016215,Suzumura20171}.
+Most classical machine learning techniques require knowledge of the data distribution in order to learn accurate models.
 This is a serious restriction because, in most cases, the distribution of the data is unknown.
-Another disadvantage of these methods stems from high dimensional, sparse datasets, which are very common in real-world applications~\citep{durrant2015random}.
+Another disadvantage of these methods stems from high dimensional, sparse datasets, which are very common in real-world applications.
 Small sample size also poses problems of model reliability, especially when coupled with high dimensional feature spaces.
@@
 The first tries to identify instances, either all within a bag or just key instances, that help find the optimal separating hyperplane between positive and negative bags.
-The latter uses kernels defined over whole bags to optimize the margin~\citep{Doran201479}.
+The latter uses kernels defined over whole bags to optimize the margin.
 

### 2017-06-12 count_unique_journals.m
Journal count + references + tasks
Wrote up some matlab code to count the number of unique journals and put in csv.
Wrote up review tasks based on Alberto's meeting.

@@ -1,0 +1,20 @@
+cclear;
+
+fid = fopen('./Research/MultiInstanceLearning/ArticleRevision/article/references.bib','r');
+text = fscanf(fid,'%s');
+fclose(fid);
+text_trim = strtrim(text); % remove white spaces
+text_trim_lower = lower(text_trim); % make all lower case
+pat = 'journal=[{|"](\w)+[}|"]'; 
+journals = regexp(text_trim_lower,pat,'tokens'); % find journal names
+journals = [journals{:}]; % convert to cell array of strings
+
+[unique_names, ~, inds] = unique(journals); 
+counts = histc(inds, 1:numel(unique_names));
+
+unique_journal_counts = table(unique_names',counts);
+unique_journal_counts.Properties.VariableNames = {'JournalName','Count'};
+unique_journal_counts
+writetable(unique_journal_counts,'./Research/MultiInstanceLearning/ArticleRevision/journal_counts.csv');
+
+clearvars fid text_trim text_trim_lower journals counts unique_names inds counts

### 2017-06-12 ArticleRevision/article/article.tex
Updated ReviewerTasks and Notation
> re-ordered the notation
> changed argmax to max
> removed "unknown" individual instance label (for clarity with the single instance dataset)

@@
 Input Space & $\bm{X} \in \mathbb{R}^{m \times d}$ \\
+Bag Labels & $\bm{Y} \in \{-1,\,1\}^n$ \\
+Input Instance $i$ from Bag $I$ & $\bm{x}_i = (x_{1}, \ldots, x_{d}),\, i \in I$ \\
+Individual Instance Label $i$ & $y_i \in \set{-1,+1}$ \\
 Bag $I$ & $\bm B_I = \set{\bm x_i \st \forall i \in I}$ \\
-Input Instance $i$ from Bag $I$ & $\bm{x}_i = (x_{1}, \ldots, x_{d}),\, i \in I$ \\
-Bag Labels & $\bm{Y} \in \{-1,\,1\}^n$ \\
-Unknown Individual Instance Label $i$ & $y_i \in \set{-1,+1}$ \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \centering \label{eqn:stasmax}
-Y_I = \text{argmax}_{\forall i \in I}\,\,\, y_i.
+Y_I = \text{max}_{\forall i \in I}\,\,\, y_i.
 \end{equation}

### 2017-06-12 ArticleRevision/article/article.tex
Added 2 references from PR
> added the pdfs
> added the citations in text

@@
 In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns that exist between training samples and their class label.
-\textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification \citep{Herman2008}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
+\textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification and annotation \citep{Herman2008,qi2007}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
 
@@
 A major challenge affecting these methods is that the distributions of the positive and negative bags affect their performance.
-Methods based on the DD metric~\citep{Chen2004,Chen2006,Carbonneau2016,Zhang2001} assume the positive instances form a cluster, which may not be the case.
-Alternatively~\cite{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
+Methods based on the DD metric~\citep{Chen2004,Chen2006,Carbonneau2016,qi2007} assume the positive instances form a cluster, which may not be the case.
+Alternatively, \cite{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
 \begin{figure*}
@@
 Using bag-representatives from one class and all instances from the other is an example of an approach that combines rules from the SMI assumption and the collective assumption.
-A disadvantage of this approach stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\cite{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which does not discard the negative instances of the positive bags.
+This approach was used in the context of active learning.~\cite{Wang20143106} proposed a multi-criteria decision making system that measures the significance of unlabeled instances and selects the best instance iteratively using MISVM.
+A disadvantage of the approach MISVM takes, stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\cite{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which does not discard the negative instances of the positive bags.
 It rather tries to identify the instances within positive bags that are negative and utilize them in the construction of the negative margin.
@@
 Bag level kernels transform the bags into a single-instance representation which enables standard SVMs to be directly applied to multi-instance data~\citep{Herrera2016}.
-
-%In the following section our contribution, MIRSVM, will be introduced, which modifies the traditional SVM optimization problem to accommodate multi-instance datasets, optimizes over representatives chosen per positive and negative bags, and is solved iteratively using a quadratic programming solver.
 

### 2017-06-12 current_code/plotting_convergence.m
Convergence subplot
Added method for plotting the convergence of MIRSVM.

@@ -1,0 +1,21 @@
+cclear;
+path = '../Google Drive/data/midata/libsvm';
+datasets = dir(path);
+datasets([1:2 3 7 10:12 16],:) = [];
+C = 1; Sigma = 0.1; 
+
+figure;
+j = 1;
+for data = datasets'
+    name = data.name;
+    [~,~,~,~,~,~,sums,numb_bags] = mirsvm_script([path '/'],name,C,Sigma,1,0);
+    
+    fig = subplot(3,3,j); plot(sums,'LineWidth',1.2); hold on; title(name,'Interpreter','latex'); 
+    grid minor; xlabel('Iterations','Interpreter','latex'); ylabel('Equal Representatives','Interpreter','latex');
+    plot(numb_bags.*ones(length(sums),1),'r--','LineWidth',1); axis([1 length(sums) 1 numb_bags+2]);
+    set(gca,'fontsize',11);
+    set(gca,'TickLabelInterpreter', 'latex');
+    j = j + 1;
+end
+
+%print(gcf,'Research/MultiInstanceLearning/convergence/subplot','-dpng');

### 2017-06-12 ArticleRevision/article/article.tex
Updated the article
> changed the unbounded SV to bounded
> added the convergence plot
> removed the testing procedure
> minor edits

@@
 all instances are guaranteed to be negative.
-This is evident during the representative selection process, by taking the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
+This is evident during the representative selection process, by taking the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{max}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
 In other words, the most positive sample is chosen from each positive bag and the least negative sample is chosen from each negative bag (samples with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
@@
 \item[1.] If $\alpha_I = 0$, then $\beta_I = C/n$ and $\xi_I = 0$, implying the instance is correctly classified and outside the margin. 
-\item[2.] If $0 \leq \alpha_I \leq C/n$, then $\beta_I > 0$ and $\xi_I = 0$, indicating that the instance sits on the margin boundary, i.e. is an \textit{unbounded support vector}.
+\item[2.] If $0 < \alpha_I < C/n$, then $\beta_I > 0$ and $\xi_I = 0$, indicating that the instance sits on the margin boundary, i.e. is an \textit{unbounded support vector}.
 \item[3.] If $\alpha_I = C/n$, then $\beta_I = 0$ and there is no restriction for $\xi_I \geq 0$.
-This also indicates that the instance is a support vector that is \textit{unbounded}.
+This also indicates that the instance is a support vector that is \textit{bounded}.
 If $0 \leq \xi_I < 1$, then the instance is correctly classified, and is misclassified otherwise.
@@
 \end{algorithm}
-\begin{algorithm}[H]
-\caption{MIRSVM Prediction}
-\label{alg:mirsvmtest} 
-\begin{algorithmic}[1]
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-\Require Testing dataset $\mathcal{D^\prime}$ with $n^\prime$ bags, Representatives $\bm S$, Classifier $\bm \alpha$ and $b$, SVM Parameter $\sigma$
-\Ensure Classifier output $\bm O$
-\For {$I \in \set{1,\ldots,n^\prime}$}
-\State $\bm G_I \leftarrow (Y_I \times Y_S) \bm \cdot \mathcal{K}\left( \bm B_I,\,\bm X_S,\,\sigma\right)$
-\State $\bm O_I \leftarrow \text{sign}(\text{max}\left(\bm G_I*\bm{\alpha} + b \right))$
-\EndFor 
-\end{algorithmic} 
-\end{algorithm}
 \end{figure}
@@
 \end{align}
-\newpage
-Algorithm~\ref{alg:mirsvm} and Figure~\ref{fig:mirsvm} show the procedure for training the multi-instance representative SVM classifier, along with obtaining the optimal representatives from each bag.
-Algorithm~\ref{alg:mirsvmtest} lists the method for testing the model on unseen data.
+
+Algorithm~\ref{alg:mirsvm} shows the procedures for training the multi-instance representative SVM classifier and obtaining the optimal representatives from each bag.
 During training, the representatives, $\bm S$, are first initialized by randomly selecting an instance from each bag.
@@
 At each step, the previous values in $\bm S$ are stored in $\bm S_{old}$.
-The training procedure ends when the bag representatives stop changing from one iteration to the next, i.e.
-when $\bm S = \bm S_{old}$.
+The training procedure ends when the bag representatives stop changing from one iteration to the next ($\bm S = \bm S_{old}$).
 During the testing procedure, each bag produces an output vector based on the hyper-plane found in the training procedure.
@@
 \end{figure}
+\begin{figure}
+\centering
+\label{fig:convergence}
+\includegraphics[width=0.95\textwidth]{convergence.eps} 
+\caption{Bag representative convergence plots on 9 datasets.
+The blue line shows the number of bag representatives that are equal from one iteration to the next.
+The red dashed line represents the total number of bags.}
+\end{figure}
+
 This formulation is designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances.

### 2017-06-12 ArticleRevision/article/article.tex
Edits
> Re-formatting text. Removed "procedure(s)", and edited the text so the bottom paragraph is on the same page.
> Fixed error with figure labeling
> Next: begin reformatting to els

@@
 
-Algorithm~\ref{alg:mirsvm} shows the procedures for training the multi-instance representative SVM classifier and obtaining the optimal representatives from each bag.
+Algorithm~\ref{alg:mirsvm} shows the procedure for training the multi-instance representative SVM classifier and obtaining the optimal representatives from each bag.
 During training, the representatives, $\bm S$, are first initialized by randomly selecting an instance from each bag.
@@
 The training procedure ends when the bag representatives stop changing from one iteration to the next ($\bm S = \bm S_{old}$).
+Examples of the convergence of bag-representatives are shown in Figure~\ref{fig:convegence}.
 During the testing procedure, each bag produces an output vector based on the hyper-plane found in the training procedure.
@@
 \centering
-    \label{fig:diff}
+\label{fig:convegence}
+\includegraphics[width=0.95\textwidth]{convergence.eps} 
+\caption{Bag representative convergence plots on 9 datasets.
+The blue line shows the number of bag representatives that are equal from one iteration to the next.
+The red dashed line represents the total number of bags.}
+\end{figure}
+
+\begin{figure}
+    \centering
     \begin{minipage}{0.5\textwidth}
@@
 Also note the smoother representation of the data distribution given by MIRSVM's decision boundary, unlike MISVM whose decision boundary was greatly affected by the larger number of support vectors belonging to the negative class with respect to the only $2$ positive support vectors.
-}
-\end{figure}
-\begin{figure}
-\centering
-\label{fig:convergence}
-\includegraphics[width=0.95\textwidth]{convergence.eps} 
-\caption{Bag representative convergence plots on 9 datasets.
-The blue line shows the number of bag representatives that are equal from one iteration to the next.
-The red dashed line represents the total number of bags.}
+}\label{fig:diff}
 \end{figure}
@@
 MISVM allows multiple representatives to be chosen from negative bags and limits positive bag-representatives to be one, while MIRSVM allows for balanced bag-representative selection, where each bag is allowed one.
-MISVM also uses a wrapper technique to initialize the positive bag-representatives by taking the mean vector of the instances within each positive bag.
+MISVM also uses a wrapper method to initialize the positive bag-representatives by taking the mean vector of the instances within each positive bag.
 This is an implicit assumption that the instances within the positive bags are all positive, whereas MIRSVM's initialization procedure selects an instance from all bags at random, ensuring no noise is added by any wrapper techniques during initialization and no assumptions are made about the instances.

### 2017-06-12 ArticleRevision/article/article.tex
Begin port to elsarticle
Reformatting required

@@
-%\begin{filecontents*}{MIRSVM.eps}
-%gsave
-%newpath
-%  20 20 moveto
-%  20 220 lineto
-%  220 220 lineto
-%  220 20 lineto
-%closepath
-%2 setlinewidth
-%gsave
-%  .4 setgray fill
-%grestore
-%stroke
-%grestore
-%\end{filecontents*}
-\RequirePackage{fix-cm}
-\documentclass[smallcondensed]{svjour3}                 
-\smartqed  
+\documentclass[preprint,12pt]{elsarticle}
 \hyphenation{op-tical net-works semi-conduc-tor}
@@
 
-\journalname{Machine Learning}
+\journal{Pattern Recognition}
 
@@
 
+\begin{frontmatter}
+
 \title{MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives}
 
-\author{Gabriella Melki \and
-        Alberto Cano			\and
-        Sebasti\'an Ventura
-}
-
-\institute{Gabriella Melki \at
-			Virginia Commonwealth University, 401 W. Main St. E2264, Richmond, VA 23284\\
-            \email{melkiga@vcu.edu}          
-           \and
-           Alberto Cano \at
-           	Virginia Commonwealth University, 401 W. Main St. E4251, Richmond, VA 23284\\
-            \email{acano@vcu.edu}
-           \and
-           Sebasti\'an Ventura \at
-            University of C\'{o}rdoba, ``Albert Einstein Building'', 3rd floor, 14071 C\'{o}rdoba, Spain\\
-            \email{sventura@uco.es}
-}
+\author[a]{Gabriella Melki}\author[a]{Alberto Cano}\author[b,c]{Sebasti\'an Ventura}
+\address[a]{Department of Computer Science, Virginia Commonwealth University, USA}
+\address[b]{Department of Computer Science and Numerical Analysis, University of Cordoba, Spain}
+\address[c]{Department of Computer Science, King Abdulaziz University, Saudi Arabia Kingdom}
 
@@
 % The correct dates will be entered by the editor
-
-\maketitle
 
@@
 The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as this proposal's overall superior performance against other multi-instance SVM models.
-\keywords{Machine learning \and multiple-instance learning \and support vector machines \and bag-level multi-instance classification \and bag-representative selection}
 \end{abstract}
+
+\begin{keyword}
+Machine learning \sep multiple-instance learning \sep support vector machines \sep bag-level multi-instance classification \sep bag-representative selection
+\end{keyword}
+
+\end{frontmatter}
 
@@
 
-\begin{acknowledgements}
+\section*{Acknowledgment}
 This research was supported by the Spanish Ministry of Economy and Competitiveness, project TIN2014-55252-P, and by FEDER funds.
-\end{acknowledgements}
 
 % BibTeX users please use one of
-\bibliographystyle{natbib}
+\bibliographystyle{model1-num-names}
 \bibliography{references}

### 2017-06-14 ArticleRevision/article/article.tex
Updated references
> added elsarticle-num-names
> formatted the citations (in text) correctly. To get the name, use citet{}
> removed the Machine learning classes
> updated lettering-case for the references
> made sure the in-text numbers are in order

@@
 \section{Introduction}\label{intro}
-In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns that exist between training samples and their class label.
-\textit{Multi-instance} (MI) learning (or \textit{multiple-instance} learning) is a variation of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification and annotation \citep{Herman2008,qi2007}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
+In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns between training samples and their class label.
+\textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification and annotation \citep{Herman2008,qi2007}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
 
@@
 The individual labels of the samples within a bag, referred to as \textit{instances}, are unknown, and labels are assigned based on a multi-instance assumption, or hypothesis.
-Introduced by~\cite{Dietterich1997}, the standard MI assumption states that a bag is labeled as positive if and only if it contains at least one positive instance.
-More recently, other MI hypotheses and frameworks have been proposed by~\cite{Foulds2010} to encompass a wider range of applications with multi-instance data.
+Introduced by~\citet{Dietterich1997}, the standard MI assumption states that a bag is labeled as positive if and only if it contains at least one positive instance.
+Recently, other hypotheses and frameworks have been proposed by~\citet{Foulds2010} to encompass a wider range of applications with MI data.
 
@@
 One approach involves ``flattenning" the MIL datasets, meaning samples contained in positive bags each adopt a positive label, allowing the use of classical supervised learning techniques~\citep{Ray2005}.
-This approach assumes that positive bags contain a significant number of positive samples, which may not be the case, causing the classifier to mislabel negative instances within the bag, decreasing the power of the resulting MIL model.
+This approach assumes that positive bags contain a significant number of positive samples, which may not be the case, causing the classifier to mislabel negative instances within the bag, decreasing the power of the MI model.
 
@@
 In MIL, the goal is to train a classifier that predicts the label of an unseen bag, $f(\bm B_{n+1}) \rightarrow Y_{n+1}$~\citep{Amores2013}.
-In order to build a classifier without any knowledge of the individual training instance labels,~\cite{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the domain of drug-activity prediction, shown in Equation~\ref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
+In order to build a classifier without any knowledge of the individual training instance labels,~\citet{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the domain of drug-activity prediction, shown in Equation~\ref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
 \begin{equation}
@@
 In addition to the SMI assumption, alternative MI assumptions have been proposed to date~\citep{Foulds2010}.
-A recent review describing the taxonomy of multi-instance classification was presented by~\cite{Amores2013}.
+A recent review describing the taxonomy of multi-instance classification was presented by~\citet{Amores2013}.
 The review presents various methods and algorithms used in literature which are categorized based on their approach to handling the MI input space.
@@
 Another similar method is the Diverse Density (DD)~\citep{Maron1998} framework which is maximized for instances in feature space that are near at least one instance in a positive bag and far from all instances in negative bags.
-In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\cite{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\cite{Auer2004} present a boosting approach that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall).
-This approach is similar to that of APR and DD, except that~\cite{Auer2004} propose computing optimal balls per positive bags.
+In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\citet{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\citet{Auer2004} present a boosting approach that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall).
+This approach is similar to that of APR and DD, except that~\citet{Auer2004} propose computing optimal balls per positive bags.
 A major challenge affecting these methods is that the distributions of the positive and negative bags affect their performance.
-Methods based on the DD metric~\citep{Chen2004,Chen2006,Carbonneau2016,qi2007} assume the positive instances form a cluster, which may not be the case.
-Alternatively, \cite{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
+Methods based on the DD metric~\citep{qi2007,Carbonneau2016,Chen2006,Chen2004} assume the positive instances form a cluster, which may not be the case.
+Alternatively, \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
 \begin{figure*}
@@
 Simple-MI represents each bag with the mean vector of the instances within it.
-This approach was evaluated by~\cite{Bunescu2007} and they proposed mapping each bag to a max-min vector, a concatenation of the features with the highest and lowest values.
+This approach was evaluated by~\citet{Bunescu2007} and they proposed mapping each bag to a max-min vector, a concatenation of the features with the highest and lowest values.
 The major disadvantage of these types of approaches is that they assume the distribution the instances in positive bags is positive, when it may not be.
 
-An extension of traditional single-instance $k$-nearest neighbors method (KNN) was proposed by~\cite{Wang2000} to be applied to the bag-level, named CitationKNN.
+An extension of traditional single-instance $k$-nearest neighbors method (KNN) was proposed by~\citet{Wang2000} to be applied to the bag-level, named CitationKNN.
 This method uses a distance function between bags in order to determine bag similarities.
 Not only are the set of closest bags to a single bag  considered, but also how many bags is the single bag closest to.
-A voting scheme is then used to determine the bag class labels.~\cite{Xu2011} proposed a multi-instance Decision-Based Neural Network (MI-DBNN), a probabilistic variant of the traditional DBNN, which is a neural network with a modular structure~\citep{Herrera2016}.
-
-~\cite{Blockeel2005} introduced the Multi-Instance Tree Inducer (MITI), based on the standard MI assumption, which uses decision trees as a heuristic to solve the MI problem.
+A voting scheme is then used to determine the bag class labels.~\citet{Xu2011} proposed a multi-instance Decision-Based Neural Network (MI-DBNN), a probabilistic variant of the traditional DBNN, which is a neural network with a modular structure~\citep{Herrera2016}.
+
+~\citet{Blockeel2005} introduced the Multi-Instance Tree Inducer (MITI), based on the standard MI assumption, which uses decision trees as a heuristic to solve the MI problem.
 This approach aims to identify whether an instance within a bag is truly positive and eliminate false positives within the same bag.
-The disadvantage of this approach stems from removing instances considered as false positives from partially grown trees without updating the existing tree structure.~\cite{Bjerring2011} then enhanced this approach by creating the method Multi-Instance Rule Induction (MIRI).
+The disadvantage of this approach stems from removing instances considered as false positives from partially grown trees without updating the existing tree structure.~\citet{Bjerring2011} then enhanced this approach by creating the method Multi-Instance Rule Induction (MIRI).
 The algorithm aims to eliminate any possibility of a suboptimal split because the tree is discarded and regrown.
-Other popular methods include MIBoost~\citep{Hall2009}, MIWrapper~\citep{Hall2009}, and Two-Level Classifier (TLC)~\citep{Wang2014}.
+Other popular methods include MIBoost~\citep{Hall2009}, MIWrapper~\citep{Frank2003}, and Two-Level Classifier (TLC)~\citep{Wang2014}.
 
@@
 No feasible solution exists for the Hard-Margin SVM problem if the dataset is non-linearly separable, which is the case for most datasets.
-To overcome this,~\cite{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:
+To overcome this,~\citet{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:
 \begin{subequations} 
@@
 
-A traditional and widely used method of solving the L1-SVM problem is the \textit{Sequential Minimal Optimization} (SMO) technique proposed by~\cite{Platt1998}.
+A traditional and widely used method of solving the L1-SVM problem is the \textit{Sequential Minimal Optimization} (SMO) technique proposed by~\citet{Platt1998}.
 It is an iterative procedure that divides the SVM dual problem into a series of sub-problems, which are then solved analytically by finding the optimal $\bm \alpha$ values that satisfy the Karush-Kuhn-Tucker (KKT) conditions~\citep{Boyd2004}.
@@
 
-\cite{Andrews2002} proposed a mixed-integer quadratic program that solves the MI problem at an instance-level, using a support vector machine, named MISVM, that can be solved heuristically.
+\citet{Andrews2002} proposed a mixed-integer quadratic program that solves the MI problem at an instance-level, using a support vector machine, named MISVM, that can be solved heuristically.
 Rather than maximizing the margin of separability between instances of different classes, this instance-based method maximizes the margin between bags.
@@
 Using bag-representatives from one class and all instances from the other is an example of an approach that combines rules from the SMI assumption and the collective assumption.
-This approach was used in the context of active learning.~\cite{Wang20143106} proposed a multi-criteria decision making system that measures the significance of unlabeled instances and selects the best instance iteratively using MISVM.
-A disadvantage of the approach MISVM takes, stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\cite{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which does not discard the negative instances of the positive bags.
+This approach was used in the context of active learning.~\citet{Wang20143106} proposed a multi-criteria decision making system that measures the significance of unlabeled instances and selects the best instance iteratively using MISVM.
+A disadvantage of the approach MISVM takes, stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\citet{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which does not discard the negative instances of the positive bags.
 It rather tries to identify the instances within positive bags that are negative and utilize them in the construction of the negative margin.
@@
 
-\cite{Yang2006} presented an instance-based SVM that uses an asymmetric loss function that follows the SMI assumption.
+\citet{Yang2006} presented an instance-based SVM that uses an asymmetric loss function that follows the SMI assumption.
 The idea behind this loss function is that positive and negative misclassification costs are different.
@@
 
-One of the first bag-level approaches to the multi-instance SVM problem was proposed by~\cite{Smola2002}, who defined a bag-level kernel.
-A bag-level kernel determines the similarity between two bags in a higher dimensional space and using such a kernel with the standard SVM problem, the margin can be optimized over bag classes without any modification to the SVM problem.~\cite{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance, without affecting the angles between vectors in the transformed space.
+One of the first bag-level approaches to the multi-instance SVM problem was proposed by~\citet{Smola2002}, who defined a bag-level kernel.
+A bag-level kernel determines the similarity between two bags in a higher dimensional space and using such a kernel with the standard SVM problem, the margin can be optimized over bag classes without any modification to the SVM problem.~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance, without affecting the angles between vectors in the transformed space.
 Bag level kernels transform the bags into a single-instance representation which enables standard SVMs to be directly applied to multi-instance data~\citep{Herrera2016}.
@@
 % BibTeX users please use one of
-\bibliographystyle{model1-num-names}
+\bibliographystyle{elsarticle-num-names}
 \bibliography{references}

### 2017-06-14 ArticleRevision/article/article.tex
Edited Introduction

@@
 bag-representatives, for both positive and negative bags, while finding the optimal class separation hyperplane.
-Unlike other multi-instance SVM methods, this approach eliminates possible class imbalance issues by allowing both positive and negative bags to have at most one representative, while highlighting the instances that contribute most to the classification model.
+Unlike other multi-instance SVM methods, this approach eliminates possible class imbalance issues by allowing both positive and negative bags to have at most one representative, which constitute as the most contributing instances to the model.
 The experimental study evaluates and compares the performance of this proposal against $10$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis.
@@
 
-The difference between MIL and traditional learning is the nature of the data samples.
-In the traditional setting, each sample is represented by a single feature vector that has its own class label.
-In multi-instance learning, a sample is considered to be a \textit{bag} that contains multiple instances, and is associated with a single label.
-The individual labels of the samples within a bag, referred to as \textit{instances}, are unknown, and labels are assigned based on a multi-instance assumption, or hypothesis.
-Introduced by~\citet{Dietterich1997}, the standard MI assumption states that a bag is labeled as positive if and only if it contains at least one positive instance.
-Recently, other hypotheses and frameworks have been proposed by~\citet{Foulds2010} to encompass a wider range of applications with MI data.
-
-One of the major complexities associated with multi-instance learning is the ambiguity of the relationship between a bag label and instances within the bag~\citep{Alpaydin2015}.
-This stems from the standard MIL assumption, where the underlying distribution among instances within positive bags is unknown.
-All that is known is that at least one instance has a positive label within a positive bag.
-There have been different attempts to overcome this complexity.
-One approach involves ``flattenning" the MIL datasets, meaning samples contained in positive bags each adopt a positive label, allowing the use of classical supervised learning techniques~\citep{Ray2005}.
+The difference between MIL and traditional learning is the nature of the data.
+In the multi-instance setting, a sample is considered a \textit{bag} that contains multiple \textit{instances} and is associated with a single label.
+The individual instance labels within a bag are unknown and bag labels are assigned based on a multi-instance assumption, or hypothesis.
+Introduced by~\citet{Dietterich1997}, the standard MI assumption states that a bag is labeled positive if and only if it contains at least one positive instance.
+More recently, other hypotheses and frameworks have been proposed by~\citet{Foulds2010} to encompass a wider range of applications with MI data.
+
+One of the major complexities associated with MIL is the ambiguity of the relationship between a bag label and the instances within the bag~\citep{Alpaydin2015}.
+This stems from the standard MI assumption, where the underlying distribution among instances within positive bags is unknown.
+There have been different attempts to overcome this complexity, such as ``flattenning" the MIL datasets, meaning instances contained in positive bags each adopt a positive label, allowing the use of classical supervised learning techniques~\citep{Ray2005}.
 This approach assumes that positive bags contain a significant number of positive samples, which may not be the case, causing the classifier to mislabel negative instances within the bag, decreasing the power of the MI model.
@@
 To overcome this, a different MIL approach was proposed, where subsets of instances are selected from positive bags for classifier training~\citep{Maron1998,Zhang2001}.
-One drawback of this type of method is that the resulting training datasets become imbalanced towards positive instances by significantly decreasing the number of negative instances.
-The performance of these methods deteriorates when more instances are selected as subsets than needed~\citep{Carbonneau2016,Faria2017196,Vanwinckelen2016}.
+One drawback of this type of method is that the resulting training datasets become imbalanced towards positive instances.
+Model performance further deteriorates when more instances are selected as subsets than needed~\citep{Carbonneau2016,Faria2017196,Vanwinckelen2016}.
 Our proposal aims to deal with this drawback by minimizing class imbalance.
-This is achieved by optimally selecting bag-representatives from both classes using Support Vector Machines.
-
-Support Vector Machines (SVMs) represent a set of supervised, linear and nonlinear, classification and regression methods that have theoretical foundations on Vapnik-Chervonenkis (VC) theory~\citep{Huang2006,Schoelkopf2002}.
+This is achieved by optimally selecting bag-representatives from both classes using support vector machines.
+
+Support vector machines represent a set of supervised, linear and nonlinear, classification and regression methods that have theoretical foundations on Vapnik-Chervonenkis (VC) theory~\citep{Huang2006,Schoelkopf2002}.
 SVM models are similar to other machine learning algorithms and techniques, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, which makes them a useful data mining tool for various real-world applications.
@@
 To address the limitations presented by MIL algorithms, this paper proposes a novel support vector machine formulation with a bag-representative selector, called Multiple-Instance Representative Support Vector Machine (MIRSVM).
-SVMs are known to perform well when data is limited, therefore combining them with a bag-representative selector aims to remedy class imbalance caused by limited positive bags, without assuming their internal distributions.
+SVMs are known to perform well when data is limited, therefore combining them with a bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without assuming the bags' internal distributions.
 The algorithm selects bag-representatives iteratively according to the standard MI assumption, ensuring known information, such as the negative bag labels, are fully utilized during the training process.
 The optimal separating hyperplane between bags is then found with respect to the bag-representatives using a Gaussian kernel and a quadratic programming solver.
-The optimal set of representatives is found when they have stopped changing from one iteration to the next.
+The optimal set of representatives is found when they have converged, or stopped changing from one iteration to the next.
 The algorithm does not assume any distribution of the instances and is not affected by the number of samples within a bag, making it applicable to a variety of contexts.
@@
 
-\iitem Devising a unique bag-representative selection method that makes no presumptions about the underlying distributions of the instances within each bag, while maintaining the default MIL assumption.
+\iitem Devising a unique bag-representative selection method that makes no presumptions about the underlying distributions of the instances within each bag, while maintaining the default MI assumption.
 This approach eliminates the issue of class imbalance caused by techniques such as flattening or subsetting positive instances from each bag.
@@
 This work is organized as follows.
-First, the notation used throughout the paper is provided, the MIL problem is formalized, and recent multiple-instance learning methods, traditional support vector machines, and state-of-the-art multi-instance SVM methods are reviewed in Section~\ref{sec:background}.
-The primal L$1$-SVM is formulated with respect to optimizing over bags, the dual formulation is then derived, along with the conditions for optimality, and the proposed algorithm, MIRSVM, is listed and described in Section~\ref{sec:contribution}.
+First, the notation used throughout the paper is provided, the MIL problem is formalized, and recent MIL methods, traditional support vector machines, and state-of-the-art multi-instance SVM methods are reviewed in Section~\ref{sec:background}.
+The primal L$1$-SVM is formulated with respect to optimizing over bags, the dual formulation is then derived along with conditions for optimality, and the proposed algorithm, MIRSVM, is listed and described in Section~\ref{sec:contribution}.
 Section~\ref{sec:experiments} presents the experimental environment, including results from various metrics, run-time, and non-parametric statistical analysis over $15$ benchmark MI datasets compared with $10$ state-of-the-art algorithms.
@@
 \section{Background}\label{sec:background}
-This section defines the notation that will be used throughout the paper, and reviews related works on multi-instance learning, traditional support vector machines, and multi-instance support vector machines.
+This section defines the notation that will be used throughout the paper, and reviews related works on multi-instance learning, traditional SVMs, and multi-instance support vector machines.
 
@@
 Let $\mathcal{D}$ be a training dataset of $n$ bags.
-Let $\bm{Y} \in \mathcal{D}$ be a vector of $n$ labels corresponding to each bag, having a domain of $\bm{Y} \in \set{-1,\,+1}^n$.
+Let $\bm{Y} \in \mathcal{D}$ be a vector of $n$ labels corresponding to each bag, having a domain of $\bm{Y} \in \set{-1,1}^n$.
 Let $\bm{X} \in \mathcal{D}$ be a matrix consisting of $d$ input variables and $m$ instances, having a domain of $\bm{X} \in \mathbb{R}^{m \times d}$.
-Let $\mathcal{B}$ be the set of bags which contain a number of instances, sometimes of different size, and usually non-overlapping, such as $\bm{B}_I = \{\bm x_{1}, \ldots, \bm x_{|\bm B_I|}\}$ for index set $I \subseteq \set{1,\ldots,n}$, where $|\bm B_I|$ is the number of instances in bag $I$.
-Using the training dataset $\mathcal{D} = \{(\bm B_1,Y_1), \ldots, (\bm B_n,Y_n)\}$, the goal is to learn a model $f : \bm{X} \times Y$, that assigns a label, $Y_I \in \set{-1,\,+1}$, for each input bag $\bm{B}_I$.
-The model will then be used to predict the labels of new, unlabeled, and unseen input bags.
+Let $\mathcal{B}$ be the set of bags which contain a number of instances, sometimes of different size and usually non-overlapping, such as $\bm{B}_I = \{\bm x_{1}, \ldots, \bm x_{|\bm B_I|}\}$ for index set $I \subseteq \set{1,\ldots,n}$, where $|\bm B_I|$ is the number of instances in bag $I$.
+Using the training dataset $\mathcal{D} = \{(\bm B_1,Y_1), \ldots, (\bm B_n,Y_n)\}$, the goal is to learn a model $f : \bm{B} \rightarrow Y$, that assigns a label for each input bag.
+The model will then be used to predict the labels of new and unseen input bags.
 Table~\ref{tab:Notation} provides a summary of the notation used in this paper.
@@
 Input Space & $\bm{X} \in \mathbb{R}^{m \times d}$ \\
-Bag Labels & $\bm{Y} \in \{-1,\,1\}^n$ \\
+Bag Labels & $\bm{Y} \in \{-1,1\}^n$ \\
 Input Instance $i$ from Bag $I$ & $\bm{x}_i = (x_{1}, \ldots, x_{d}),\, i \in I$ \\
-Individual Instance Label $i$ & $y_i \in \set{-1,+1}$ \\
+Individual Instance Label $i$ & $y_i \in \set{-1,1}$ \\
 Bag $I$ & $\bm B_I = \set{\bm x_i \st \forall i \in I}$ \\

### 2017-06-14 ArticleRevision/article/article.tex
Notation & Background
> changed notation of bags to be mathcal to represent sets
> condensed the background and MI sections in section 2 (redundant)
> removed F in the figures (features), not in notation, replaced with lower-case x
> shortened the SVM background (no need for that much)

@@
 \usepackage[hidelinks]{hyperref}
-\usepackage{amsmath,amssymb,mathtools,float,times,bm,tikz,proof,tabularx,capt-of,natbib}
+\usepackage{amsmath,amssymb,mathtools,float,times,bm,tikz,proof,tabularx,capt-of,natbib,siunitx}
 \usepackage{graphicx,amsfonts,array,url,algorithm,algorithmicx,algpseudocode,booktabs}
@@
 Let $\bm{X} \in \mathcal{D}$ be a matrix consisting of $d$ input variables and $m$ instances, having a domain of $\bm{X} \in \mathbb{R}^{m \times d}$.
-Let $\mathcal{B}$ be the set of bags which contain a number of instances, sometimes of different size and usually non-overlapping, such as $\bm{B}_I = \{\bm x_{1}, \ldots, \bm x_{|\bm B_I|}\}$ for index set $I \subseteq \set{1,\ldots,n}$, where $|\bm B_I|$ is the number of instances in bag $I$.
-Using the training dataset $\mathcal{D} = \{(\bm B_1,Y_1), \ldots, (\bm B_n,Y_n)\}$, the goal is to learn a model $f : \bm{B} \rightarrow Y$, that assigns a label for each input bag.
-The model will then be used to predict the labels of new and unseen input bags.
+Let $\mathcal{B}$ be the set of bags which contain a number of instances, sometimes of different size and usually non-overlapping, such as $\mathcal{B}_I = \{\bm x_{1}, \ldots, \bm x_{|\mathcal{B}_I|}\}$ for index set $I \subseteq \set{1,\ldots,n}$, where $|\mathcal{B}_I|$ is the number of instances in bag $I$.
 Table~\ref{tab:Notation} provides a summary of the notation used in this paper.
+
 \begin{table}
@@
 Number of Input Attributes & $d$ \\
-Set of Bags & $\mathcal{B} = \set{\bm B_1,\, \ldots,\, \bm B_n}$ \\
+Set of Bags & $\mathcal{B} = \set{\mathcal{B}_1,\, \ldots,\, \mathcal{B}_n}$ \\
 Bag Index Set & $I \in \ints_+^n$ \\
@@
 Input Instance $i$ from Bag $I$ & $\bm{x}_i = (x_{1}, \ldots, x_{d}),\, i \in I$ \\
-Individual Instance Label $i$ & $y_i \in \set{-1,1}$ \\
-Bag $I$ & $\bm B_I = \set{\bm x_i \st \forall i \in I}$ \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Full Multi-Instance Training Dataset & $\mathcal{D} = \{(\bm B_1,Y_1), \ldots, (\bm B_n,Y_n)\}$ \\
-Full Single-Instance Training Dataset & $\mathcal{S} = \{(\bm x_1,y_1), \ldots, (\bm x_m,y_m)\} $\\
+Unknown Individual Instance Label $i$ & $y_i \in \set{-1,1}$ \\
+Bag $I$ & $\mathcal{B}_I = \set{\bm x_i \st \forall i \in I}$ \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Full Multi-Instance Training Dataset & $\mathcal{D} = \{(\mathcal{B}_1,Y_1), \ldots, (\mathcal{B}_n,Y_n)\}$ \\
 \noalign{\smallskip}\hline
@@
 \subsection{Multiple-Instance Learning}\label{subsec:mil}
+\begin{sloppypar}
 In traditional binary classification problems, the goal is to learn a model that maps input samples to labels, $f: \reals^{m \times d} \rightarrow Y^m \in \set{-1,\,+1}$.
-Multiple instance learning generalizes this framework and makes weaker assumptions about sample labeling.
-In the MIL case, samples are called \textit{bags} and each bag contains one or more input instances.
-Each bag is assigned a label, unlike traditional classification problems, where individual samples are assigned a label.
-Input instances, $\set{\bm x_1,\, \bm x_2,\, \ldots,\, \bm x_m}$, are grouped into bags with unique identifiers, $\mathcal{B} = \set{\bm B_1,\, \bm B_2,\, \ldots,\, \bm B_n \st \bm B_I = \set{\bm x_i \st \forall i \in I}}$, $\forall I \in \set{1, \ldots, n}$ and assigned a label, $Y_I$.
-An example representation of an MI dataset is shown in Figure~\ref{fig:mirep}.
-
-In MIL, the goal is to train a classifier that predicts the label of an unseen bag, $f(\bm B_{n+1}) \rightarrow Y_{n+1}$~\citep{Amores2013}.
-In order to build a classifier without any knowledge of the individual training instance labels,~\citet{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the domain of drug-activity prediction, shown in Equation~\ref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
+In the MIL case, samples are called \textit{bags} and each bag contains one or more input instances and is assigned a single bag-level label.
+Input instances, $\set{\bm x_1,\, \bm x_2,\, \ldots,\, \bm x_m}$, are grouped into bags with unique identifiers, $\mathcal{B} = \set{\mathcal{B}_1,\, \mathcal{B}_2,\, \ldots,\, \mathcal{B}_n \st \mathcal{B}_I = \set{\bm x_i \st \forall i \in I},\, \forall I \in \set{1, \ldots, n}}$ and assigned a label, $Y_I$.
+An example MI dataset representation is shown in Figure~\ref{fig:mirep}.
+Using the training dataset $\mathcal{D} = \{(\mathcal{B}_1,Y_1), \ldots, (\mathcal{B}_n,Y_n)\}$, the goal is to train a classifier that predicts the label of an unseen bag, $f(\mathcal{B}_{n+1}) \rightarrow Y_{n+1}$~\citep{Amores2013}.
+In order to build a classifier without any knowledge of the individual training instance labels,~\citet{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the drug-activity prediction domain, shown in Equation~\ref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
+\end{sloppypar}
 \begin{equation}
@@
 
-This implies that individual instance labels $y_i$ exist, but are not known during training. Equation~\ref{eqn:stas} can also be rewritten as Equation~\ref{eqn:stasmax} for simplicity:
+This implies that individual instance labels $y_i$ exist, but are not known (for positive bags) during training.
+Equation~\ref{eqn:stas} can also be rewritten as Equation~\ref{eqn:stasmax} for simplicity:
 \begin{equation}
@@
 \hline
-$\mathcal{B}$ & $F_1$ & $F_2$ & $F_3$ & \ldots & $F_d$ & $\bm Y$ \\        
+$\mathcal{B}$ & $x_1$ & $x_2$ & $x_3$ & \ldots & $x_d$ & $\bm Y$ \\        
 \hline
     	  & 0.1 & 0.8 & 2.5 & \ldots & 0.8 &    \\        
-    $B_1$ 	  & 0.2 & 2.0 & 5.5 & \ldots & 3.0 & POS \\
+    $\mathcal{B}_1$ 	  & 0.2 & 2.0 & 5.5 & \ldots & 3.0 & POS \\
     	  & 0.1 & 0.1   & 4.5 & \ldots & 0.1 &    \\
@@
     	  & 0.8 & 0.4 & 2.9 & \ldots & 1.1 &    \\
-    $B_2$	  & 2.3 & 0.2 & 4.0 & \ldots & 5.5 & NEG \\
+    $\mathcal{B}_2$	  & 2.3 & 0.2 & 4.0 & \ldots & 5.5 & NEG \\
     	  & 6.7 & 5.0 & 0.1  & \ldots & 0.5 &    \\
@@
   \end{tabular}
-  \caption{Example of multi-instance data representation.
-The figure shows a sample binary MI dataset with $2$ bags, identified as $B_1$ and $B_2$.
-The bags each contain differing number of instances, each with $d$ dimension, and are assigned positive and negative labels indicated by column $\bm Y$.}%
+  \caption{Example multi-instance data representation.
+The figure shows a sample binary MI dataset with $2$ bags of different sizes and labels, $\mathcal{B}_1$ and $\mathcal{B}_2$.
+The instances are $d$-dimensional.}%
   \label{fig:mirep}%
@@
 \subsection{Support Vector Machines}\label{subsec:svms}
-Most classical machine learning techniques require knowledge of the data distribution in order to learn accurate models.
-This is a serious restriction because, in most cases, the distribution of the data is unknown.
-Another disadvantage of these methods stems from high dimensional, sparse datasets, which are very common in real-world applications.
-Small sample size also poses problems of model reliability, especially when coupled with high dimensional feature spaces.
-SVMs represent learning techniques that have been introduced under the \textit{structural risk minimization} (SRM) framework and VC theory~\citep{Kecman2001}.
+Most classical learning techniques require knowledge of the data distribution to build accurate models.
+This is a serious restriction because, in most cases, the data distribution is unknown~\citep{Kecman2001}.
+SVMs represent learning techniques that have been introduced under the \textit{structural risk minimization} (SRM) framework and VC theory.
 Rather than optimizing over L1 or L2 norms and classification error, SVMs perform SRM~\citep{Shalev2014}, minimizing the expected probability of classification error, resulting in a generalized model without making assumptions about the data distribution~\citep{Cortes1995}.
 
-SVMs are a particularly useful for learning linear predictors in high dimensional feature spaces, which is a computationally complex learning problem.
+SVMs are a particularly useful for learning linear predictors in high dimensional feature spaces, which is a computationally complex problem.
 In the context of classification, this problem is approached by searching for the optimal \textit{maximal margin} of separability between classes.
-A training set $\mathcal{D}$ is \textit{linearly separable} if a halfspace exists, $(\bm{w},b)$, such that $y_i = \text{sign }(\langle \bm{w},\bm{x}_i\rangle+b), \forall i \in \{1,\ldots,m\}$, where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, and $b \in \reals$ is a bias term.
-All halfspaces, defined as $d(\bm{x}_i) = \langle \bm{w},\bm{x}_i\rangle + b$, satisfying $y_i \left(\langle \bm{w},\bm{x}_i\rangle + b\right) > 0,\,\, \forall i \in \{1,\ldots,m\}$, have no error.
-This hard constraint is associated with the \textit{Hard-Margin SVM}.
-No feasible solution exists for the Hard-Margin SVM problem if the dataset is non-linearly separable, which is the case for most datasets.
-To overcome this,~\citet{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:
+Since most real-world datasets are non-linearly separable, ~\citet{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:
 \begin{subequations} 
@@
 \end{subequations} 
-where $C \in \reals$ is the penalty parameter that controls the trade-off between margin maximization and classification error minimization, penalizing large norms and errors.
+where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term, and $C \in \reals$ is the penalty parameter that controls the trade-off between margin maximization and classification error minimization.
 The slack variable $\bm \xi \in \reals^m$ allows for optimizing over sample errors.
-The resulting hyperplane is called \textit{soft-margin hyperplane}.
-Although the Soft-SVM learns an optimal hyperplane, if the training data set is not linearly separable, the classifier learned may not have a good generalization capability~\citep{Nocedal2006}.
+However, if the training dataset is not linearly separable, the classifier may not have a good generalization capability~\citep{Nocedal2006}.
 Generalization and linear separability can be enhanced by mapping the original input space to a higher dimensional dot-product space by using a kernel function shown in Equation~\ref{eqn:kerneltrick}:
@@
 where $\phi\left(\cdot\right)$ represents a function mapping from the original feature space to a higher dimensional space.
-This kernel mapping is particularly helpful when solving the dual SVM optimization problem shown in Equation~\eqref{eq:dualsvm}.
-Rather than calculating the inner product of two mapped vectors, their corresponding \textit{scalar} kernel value can be used.
+This kernel mapping is helpful when solving the dual SVM optimization problem shown in Equation~\eqref{eq:dualsvm}.
 \begin{subequations}
@@
 It iteratively updates the objective function by working on one data point at a time, using coordinate descent to find the optimal objective function value.
-Other methods for solving the SVM problem include \textit{Quadratic Programming} solvers, such as the interior point method.
+Other methods for solving the SVM problem include \textit{Quadratic Programming} solvers.
 These types of algorithms find the true optimal objective function value at the trade-off of having a relatively slower run-time.

### 2017-06-14 ArticleRevision/article/article.tex
Updated the contribution section

@@
 Using the training dataset $\mathcal{D} = \{(\mathcal{B}_1,Y_1), \ldots, (\mathcal{B}_n,Y_n)\}$, the goal is to train a classifier that predicts the label of an unseen bag, $f(\mathcal{B}_{n+1}) \rightarrow Y_{n+1}$~\citep{Amores2013}.
-In order to build a classifier without any knowledge of the individual training instance labels,~\citet{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the drug-activity prediction domain, shown in Equation~\ref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
+In order to build a classifier without any knowledge of the individual training instance labels,~\citet{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the drug-activity prediction domain, shown in Equation~\eqref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
 \end{sloppypar}
@@
 This implies that individual instance labels $y_i$ exist, but are not known (for positive bags) during training.
-Equation~\ref{eqn:stas} can also be rewritten as Equation~\ref{eqn:stasmax} for simplicity:
+Equation~\eqref{eqn:stas} can also be rewritten as Equation~\eqref{eqn:stasmax} for simplicity:
 \begin{equation}
@@
 However, if the training dataset is not linearly separable, the classifier may not have a good generalization capability~\citep{Nocedal2006}.
-Generalization and linear separability can be enhanced by mapping the original input space to a higher dimensional dot-product space by using a kernel function shown in Equation~\ref{eqn:kerneltrick}:
+Generalization and linear separability can be enhanced by mapping the original input space to a higher dimensional dot-product space by using a kernel function shown in Equation~\eqref{eqn:kerneltrick}:
 \begin{equation}
@@
 
-One of the first bag-level approaches to the multi-instance SVM problem was proposed by~\citet{Smola2002}, who defined a bag-level kernel.
+One of the first bag-level approaches to the multi-instance SVM problem was proposed by \citet{Smola2002}, who defined a bag-level kernel.
 A bag-level kernel determines the similarity between two bags in a higher dimensional space and using such a kernel with the standard SVM problem, the margin can be optimized over bag classes without any modification to the SVM problem.~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance, without affecting the angles between vectors in the transformed space.
@@
 all instances are guaranteed to be negative.
-This is evident during the representative selection process, by taking the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{max}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
+This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{max}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
 In other words, the most positive sample is chosen from each positive bag and the least negative sample is chosen from each negative bag (samples with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
@@
 \min\limits_{\bm w, b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{n}\sum_I \xi_I, \tag{\ref{eq:primalmirsvm}}\\ 
-\text{s.t.}& {\,\,} y_I(\langle\bm{w},\bm{x}_{s_I}\rangle + b) \geq 1 - \xi_I,\, \forall I \in \set{1,\ldots,n}  \label{eq:primalmirsvm1}\\
+\text{s.t.}& {\,\,} y_I(\langle\bm{w},x_{s_I}\rangle + b) \geq 1 - \xi_I,\, \forall I \in \set{1,\ldots,n}  \label{eq:primalmirsvm1}\\
 {} & {\,\,} \xi_I \geq 0,\, \forall I \in \set{1,\ldots,n}, 
@@
 \end{subequations} 
-where $\bm S_I$ is a set of the bag representatives' indices and $\bm x_{s_I}$ is the sample representative of bag $\bm B_I$.
+where $\bm S_I$ is a set of the bag representatives' indices and $\bm x_{s_I}$ is the sample representative of bag $\mathcal{B}_I$.
 Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.
@@
 
-The dual can be found by first forming the primal Lagrangian given by Equation~\ref{eqn:svmlagrangian}, where $\bm{\alpha}$ and $\bm{\beta}$ are the non-negative Lagrange multipliers.
+The dual can be formed by taking the Lagrangian of~\eqref{eq:primalmirsvm}, given by Equation~\eqref{eqn:svmlagrangian}, where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers.
 \begin{equation}
-\centering
+\centering \label{eqn:svmlagrangian}
 \resizebox{.9\textwidth}{!}{$
 \begin{aligned}
-\label{eqn:svmlagrangian}
 \mathcal{L}\left(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}\right) = \frac{1}{2}\sum_{j=1}^d w_j^2  + \frac{C}{n}\sum_I \xi_I - \sum_I{\beta_I \xi_I} - \sum_I{\alpha_I\left(y_I\left(\sum_{j=1}^d w_j \bm x_{s_Ij} + b\right) -1 + \xi_I\right)}
@@
 \end{equation}
-The following Karush-Kuhn-Tucker (KKT)~\citep{Boyd2004} conditions must be satisfied:
-\begin{align*}
-&\frac{\partial\mathcal{L}}{\partial w_j} = 0, \,\forall j \in \{1,\ldots,d\} \\
-&\frac{\partial\mathcal{L}}{\partial b} = 0     \\
-&\frac{\partial\mathcal{L}}{\partial\xi_I} = 0,\,\forall I \in \set{1,\ldots,n}\\
-&\alpha_I\left(y_I(\langle\bm{w},\bm{x}_{s_I}\rangle + b)-1+\xi_{I}\right) = 0,\, \forall I \in \set{1,\ldots,n}\\
-&\beta_I\xi_I = 0, \forall I \in \set{1,\ldots,n} \\
-&\alpha_I \geq 0,\, \beta_I \geq 0,\, \xi_I \geq 0,\, \forall I \in \set{1,\ldots,n}
-\end{align*}
-At optimality, $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$ and the following conditions are met:
+
+At optimality~\citep{Boyd2004}, $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$ and the following conditions are met:
 \begin{align}
-&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,y_I\,\bm x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
+&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,y_I\, x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
 &\frac{\partial\mathcal{L}}{\partial b}: \sum_I{\alpha_Iy_I} = 0,\label{eqn:optcond2}\\
@@
 \end{align}
-By substituting Equations~\ref{eqn:optcond1},~\ref{eqn:optcond2}, and~\ref{eqn:optcond3} into the Lagrangian in~\ref{eqn:svmlagrangian}, the following dual problem, $q(\bm \alpha, \bm \beta)$, is obtained:
-\begin{align*}
-q(\bm \alpha, \bm \beta) &= \underset{\bm w, b, \bm \xi}{\text{ inf }} \frac{1}{2} \sum_I \sum_{K \in I} \sum_{j=1}^d \alpha_I \alpha_K y_I y_K  x_{s_I j} x_{s_K j} + \sum_I \xi_I \left( \alpha_I + \beta_I \right) - \sum_I \xi_I \left( \alpha_I + \beta_I \right) \\
-{} & - \sum_I \sum_{K\in I} \sum_{j=1}^d \alpha_I \alpha_K y_I y_K  x_{s_I j} x_{s_K j} - \sum_I \alpha_I y_I b  + \sum_I \alpha_I.
-\end{align*}
-
-At optimality, $\sum_I{\alpha_Iy_I} = 0$, so the term with $b$ can be removed.
-The terms with $\bm \xi$ can also be removed because they negate each other.
-The resulting function is now with respect to the dual variables, so the infimum can be dropped.
-The dual MIRSVM formulation then becomes:
+\newpage
+By substituting Equations~\eqref{eqn:optcond1},~\eqref{eqn:optcond2}, and~\eqref{eqn:optcond3} into the Lagrangian in~\eqref{eqn:svmlagrangian}, the dual MIRSVM formulation becomes the following:
 \begin{subequations} 
@@
 {} & \alpha_I \geq 0,\, \forall I \in \set{1,\ldots,n}  \label{eq:implicit2} \\
-{} & \beta_I \geq 0,\, \forall I \in \set{1,\ldots,n}  \label{eq:implicit3}
+{} & \beta_I \geq 0,\, \forall I \in \set{1,\ldots,n},  \label{eq:implicit3}
 \end{alignat}
@@
 \centering
-s_I = \underset{i \in I}{\text{argmax}}(\sum_{K\in I} \sum_{j=1}^d \alpha_K y_K x_{s_K j} x_{ij} + b),\, \forall I \in \set{1,\ldots,n}.
+s_I = \underset{i \in I}{\text{max}}(\sum_{K\in I} \sum_{j=1}^d \alpha_K y_K x_{s_K j} x_{ij} + b),\, \forall I \in \set{1,\ldots,n}.
 \end{equation}
@@
 \item[3.] If $\alpha_I = C/n$, then $\beta_I = 0$ and there is no restriction for $\xi_I \geq 0$.
-This also indicates that the instance is a support vector that is \textit{bounded}.
+This also indicates that the instance is a support vector, but one that is \textit{bounded}.
 If $0 \leq \xi_I < 1$, then the instance is correctly classified, and is misclassified otherwise.
@@
 \end{equation}
-\begin{figure}[tpb]
+\begin{figure}[tpb!]
 \centering
@@
 \end{tikzpicture}}
-\caption{MIRSVM Flow Diagram.
+\caption{MIRSVM flow diagram.
 This figure represents a summary of the steps performed by the MIRSVM algorithm.
@@
 \end{minipage}
+
 \begin{algorithm}[H]
@@
 
-To evaluate the output vector, $\bm o_I$, of bag $I$ using the kernel, the following equation is used~\citep{Huang2006},
+\newpage
+\begin{figure}
+\centering
+\label{fig:convegence}
+\includegraphics[width=0.95\textwidth]{convergence.eps} 
+\caption{Bag representative convergence plots on 9 datasets.
+The blue line shows the number of bag representatives that are equal from one iteration to the next.
+The red dashed line represents the total number of bags.}
+\end{figure}
+To evaluate the output vector, $\bm o_I$, of bag $I$ using the kernel, the following equation is used~\citep{Huang2006}, where $\bm B_I$ are the instances of bag $I$, $\bm X_S$ are the optimal bag representatives, and $Y_S$ are the representative bag labels.
 \begin{align}
-\bm o = \spa{K}(\bm B_I,\bm X_S)*(\bm\alpha \cdot Y_S) + b
+\bm o_I = \spa{K}(\bm B_I,\bm X_S)*(\bm\alpha \cdot Y_S) + b
 \end{align}
-where $\bm B_I$ are the instances of bag $I$, $\bm X_S$ are the optimal bag representatives, and $Y_S$ are the representative bag labels.
-The bias term $b$ is calculated as shown in Equation~\ref{eqn:bias}, where $\bm{sv}$ is the vector of support vector indices and $n_{sv}$ is the number of support vectors~\citep{Huang2006}.
+
+The bias term $b$ is calculated as shown in Equation~\eqref{eqn:bias}, where $\bm{sv}$ is the vector of support vector indices and $n_{sv}$ is the number of support vectors~\citep{Huang2006}.
 \begin{align}
@@
 The bag label is then assigned by taking the sign of the output vector's maximum value, following the SMI assumption.
-
-\begin{figure}
-\centering
-\label{fig:convegence}
-\includegraphics[width=0.95\textwidth]{convergence.eps} 
-\caption{Bag representative convergence plots on 9 datasets.
-The blue line shows the number of bag representatives that are equal from one iteration to the next.
-The red dashed line represents the total number of bags.}
-\end{figure}
 
@@
 \end{figure}
-
 This formulation is designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances.
@@
 As Figure~\ref{fig:diff} shows, MISVM produces a larger number of support vectors from the negative bags, which greatly influences the final decision boundary in favor of the negative class.
-
+\newpage
 \section{Experiments}\label{sec:experiments}

### 2017-06-14 ArticleRevision/article/article.tex
Formatted results
TODO: extend overall comparison

@@
 \label{fig:convegence}
-\includegraphics[width=0.95\textwidth]{convergence.eps} 
+\includegraphics[width=0.99\textwidth]{convergence.eps} 
 \caption{Bag representative convergence plots on 9 datasets.
@@
 \subsection{Results \& Statistical Analysis}\label{subsec:results}
-The classification performance was measured using five metrics: Accuracy~\eqref{eq:accuracy}, Precision~\eqref{eq:precision}, Recall~\eqref{eq:recall}, Cohen's kappa rate~\eqref{eq:kappa}, and Area under ROC curve (AUC)~\eqref{eq:auc}.
+The classification performance was measured using five metrics: Accuracy~\eqref{eq:accuracy}, Precision \eqref{eq:precision}, Recall~\eqref{eq:recall}, Cohen's kappa rate~\eqref{eq:kappa}, and Area under ROC curve (AUC)~\eqref{eq:auc}.
 Accuracy can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which have six and ten times as many negative instances than positive, respectively.
@@
 The run times of each algorithm are also reported to analyze the usability and speed of each of the algorithms across differently sized datasets.
+
 The results for these metrics are shown in Tables~\ref{tab:accResults},~\ref{tab:preResults},~\ref{tab:recResults},~\ref{tab:kappaResults},~\ref{tab:aucResults}, and~\ref{tab:time}.
@@
 Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values for the Nemenyi, Holm, and Shaffer tests for $\alpha = 0.05$.
-
+\newpage
 \subsection{Accuracy}
-Table~\ref{tab:accResults} shows the accuracy results of the $11$ algorithms over $15$ multi-instance datasets, along with their average and rank.
-The results indicate that the bag-based and ensemble learners perform better than the instance-based and wrapper methods.
-Specifically, MIRSVM achieves the best accuracy over $6$ of the $15$ datasets with a competitive average against the Bagging, Stacking, and TLC algorithms.
-Note that MIRSVM performs better than MISVM for all datasets, indicating that using representatives from each bag and limiting the number of support-vectors per negative bag improves the classification performance.
-The instance-level classifiers and wrapper methods, such as MIBoost, MIWrapper, and SimpleMI perform the worst.
-This behavior emphasizes the importance of not making prior assumptions about the positive bags' distributions.
-
-Figure~\ref{fig:BonfDunnacc} and Table~\ref{tab:statacc} show the results for the statistical analysis on the accuracy results.
-The algorithms with ranking higher than $5.51$ (MIRSVM rank + Bonferroni-Dunn critical value), to the right of the grey bar in Figure~\ref{fig:BonfDunnacc}, perform statistically worse than MIRSVM.
-Table~\ref{tab:statacc} shows the $p$-values of the Nemenyi, Holm, and Shaffer tests.
-The results from these tests are complement each other.
-Nemenyi's procedure indicates that MIRSVM performs significantly better than all methods (with $p$-values $< 0.01$), except Bagging, Stacking, TLC, and MISMO.
-The Nemenyi $p$-values for MIBoost, MIWrapper, and SimpleMI are $= 0$, showing that MIRSVM has significantly better accuracy.
-However, the stricter Holm and Shaffer tests indicate that significant differences exist between MIRSVM and all other classifiers, highlighting MIRSVM's superior classification accuracy.
-
-\begin{table}[th!]
+\begin{table}[t!]
 \caption{Accuracy}\label{tab:accResults}
-\resizebox{\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 };
-\end{tikzpicture}}
-\captionof{figure}{Bonferroni-Dunn test for Accuracy}\label{fig:BonfDunnacc}
+\end{tikzpicture}}\vspace{-0.6em}
+\captionof{figure}{Bonferroni-Dunn test for Accuracy}\label{fig:BonfDunnacc}\vspace{-0.5em}
 \captionof{table}{Nemenyi, Holm, and Shaffer tests for Accuracy}\label{tab:statacc}
 \scriptsize
-\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
 MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabularx}
+\end{tabular}}
 \end{table}
-\newpage
-\subsection{Precision \& Recall}
-Precision and recall are metrics that must be evaluated together in order to observe their behavior simultaneously, since they are both metrics used to measure relevance.
-Tables~\ref{tab:preResults} and~\ref{tab:recResults} show the precision and recall results obtained by each algorithm.
-The precision and recall results for MIWrapper and SimpleMI indicate that they are unstable classifiers, exhibiting extreme variance in behavior, making them unsuitable for real-world applications.
-It is also interesting to analyze the performance on the mutagenesis datasets, where MISVM, MIBoost, MIWrapper, and SimpleMI predict all bags as negative.
-Additionally, while MISMO obtains unbiased results on these datasets, MIRSVM significantly outperforms it over both precision and recall.
-
-Figure~\ref{fig:BonfDunnprec} shows that there are no statistically significant differences between the precision results obtained by all algorithms, except SimpleMI; and Figure~\ref{fig:BonfDunnrec} shows none over all.
-It is worth noting that MIRSVM outperforms both ensemble methods according to recall, despite them exhibiting relatively good accuracy and precision.
-This indicates that they are strongly conservative towards predicting positive bags.
-The Holm and Shaffer tests indicate that significant differences exist between MIRSVM and the state-of-the-art, with the exception of SimpleMI.
-
-\begin{table}[t!]
+Table~\ref{tab:accResults} shows the accuracy results of the $11$ algorithms over $15$ multi-instance datasets, along with their average and rank.
+The results indicate that the bag-based and ensemble learners perform better than the instance-based and wrapper methods.
+Specifically, MIRSVM achieves the best accuracy over $6$ of the $15$ datasets with a competitive average against the Bagging, Stacking, and TLC algorithms.
+Note that MIRSVM performs better than MISVM for all datasets, indicating that using representatives from each bag and limiting the number of support-vectors per negative bag improves the classification performance.
+The instance-level classifiers and wrapper methods, such as MIBoost, MIWrapper, and SimpleMI perform the worst.
+This behavior emphasizes the importance of not making prior assumptions about the positive bags' distributions.
+
+Figure~\ref{fig:BonfDunnacc} and Table~\ref{tab:statacc} show the results for the statistical analysis on the accuracy results.
+The algorithms with ranking higher than $5.51$ (MIRSVM rank + Bonferroni-Dunn critical value), to the right of the grey bar in Figure~\ref{fig:BonfDunnacc}, perform statistically worse than MIRSVM.
+Table~\ref{tab:statacc} shows the $p$-values of the Nemenyi, Holm, and Shaffer tests and their results complement one another.
+Nemenyi's procedure indicates that MIRSVM performs significantly better than all methods (with $p$-values $< 0.01$), except Bagging, Stacking, TLC, and MISMO.
+The Nemenyi $p$-values for MIBoost, MIWrapper, and SimpleMI are $0$, showing that MIRSVM has significantly better accuracy.
+However, the stricter Holm and Shaffer tests indicate that significant differences exist between MIRSVM and all other classifiers, highlighting MIRSVM's superior classification accuracy.
+
+\begin{table}[H]
 \caption{Precision}\label{tab:preResults}
-\resizebox{\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
-\draw (l\x) -| (c\x);
-};
-\end{tikzpicture}}
-\captionof{figure}{Bonferroni-Dunn test for Precision}\label{fig:BonfDunnprec}
+\draw (l\x) -| (c\x);};
+\end{tikzpicture}}\vspace{-1.1em}
+\captionof{figure}{Bonferroni-Dunn test for Precision}\label{fig:BonfDunnprec}\vspace{-0.5em}
 \captionof{table}{Nemenyi, Holm, and Shaffer tests for Precision}\label{tab:statprec}
 \scriptsize
-\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
 MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabularx}
-\end{table}
-\begin{table}[h!]
-\caption{Recall}\label{tab:recResults}
-\resizebox{\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
+\end{tabular}}
+\captionof{table}{Recall}\label{tab:recResults}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
-\draw (l\x) -| (c\x);
-};
-\end{tikzpicture}}
-\captionof{figure}{Bonferroni-Dunn test for Recall}\label{fig:BonfDunnrec}
+\draw (l\x) -| (c\x);};
+\end{tikzpicture}}\vspace{-1.1em}
+\captionof{figure}{Bonferroni-Dunn test for Recall}\label{fig:BonfDunnrec}\vspace{-0.5em}
 \captionof{table}{Nemenyi, Holm, and Shaffer tests for Recall}\label{tab:statrec}
 \scriptsize
-\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
 MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabularx}
+\end{tabular}}
 \end{table}
 
+\subsection{Precision \& Recall}
+Precision and recall are metrics that must be evaluated together in order to observe their behavior simultaneously, since they are both metrics used to measure relevance.
+Tables~\ref{tab:preResults} and~\ref{tab:recResults} show the precision and recall results obtained by each algorithm.
+The precision and recall results for MIWrapper and SimpleMI indicate that they are unstable classifiers, exhibiting extreme variance in behavior, making them unsuitable for real-world applications.
+It is also interesting to analyze the performance on the mutagenesis datasets, where MISVM, MIBoost, MIWrapper, and SimpleMI predict all bags as negative.
+Additionally, while MISMO obtains unbiased results on these datasets, MIRSVM significantly outperforms it over both precision and recall.
+
+Figure~\ref{fig:BonfDunnprec} shows that there are no statistically significant differences between the precision results obtained by all algorithms, except SimpleMI; and Figure~\ref{fig:BonfDunnrec} shows none over all.
+It is worth noting that MIRSVM outperforms both ensemble methods according to recall, despite them exhibiting relatively good accuracy and precision.
+This indicates that they are strongly conservative towards predicting positive bags.
+The Holm and Shaffer tests indicate that significant differences exist between MIRSVM and the state-of-the-art, with the exception of SimpleMI.
+
 \subsection{Cohen's Kappa Rate}
-Table~\ref{tab:kappaResults} shows the Cohen's Kappa rate results obtained by the algorithms.
-These results support the accuracy achieved by the algorithms, in the sense that the instance-based and wrapper methods perform worse than bag-based and ensemble learners.
-Specifically, MIRSVM achieves the best kappa rate over $7$ of the $15$ datasets with a competitive average against the Bagging, Stacking, SMO, and TLC algorithms.
-MIRSVM's kappa values all fall within the range ($0.5$-$1$], indicating that its merit as a classifier agrees with the class distribution and is not random.
-Note that SimpleMI, MIOptimalBall, MIDD, MISVM, and Stacking contain some negative kappa values, indicating performance worse than the default-hypothesis.
-MIBoost and MIWrapper are shown to randomly classify all $15$ datasets.
-
-Figure~\ref{fig:BonfDunnkappa} and Table~\ref{tab:statkappa} show the results of the statistical analysis on the Cohen's Kappa Rate results.
-Nemenyi's procedure reflects results similar to the $p$-values obtained from the accuracy results, where MIRSVM performs significantly better than MIOptimalBall, MIDD, MISVM, MIWrapper, MIBoost, and SimpleMI, having $p$-values $< 0.01$.
-The Holm and Shaffer procedures indicate that significant differences exist among all algorithms results, supporting MIRSVM's performance as a competitive classifier.
-
-\begin{table}[t!]
+\begin{table}[b!]
 \caption{Cohen's Kappa Rate}\label{tab:kappaResults}
-\resizebox{\textwidth}{!}{\begin{tabular}{lcccccccccccc}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 };
-\end{tikzpicture}}
+\end{tikzpicture}}\vspace{-0.6em}
 \captionof{figure}{Bonferroni-Dunn test for Cohen's Kappa rate}\label{fig:BonfDunnkappa}
-\vspace{0.5cm}
+\vspace{-0.5em}
 \captionof{table}{Nemenyi, Holm, and Shaffer tests for Cohen's Kappa rate}\label{tab:statkappa}
 \scriptsize
-\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
 MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabularx}
+\end{tabular}}
 \end{table}
-\bigskip
-\begin{table}[H]
+Table~\ref{tab:kappaResults} shows the Cohen's Kappa rate results obtained by the algorithms.
+These results support the accuracy achieved by the algorithms, in the sense that the instance-based and wrapper methods perform worse than bag-based and ensemble learners.
+MIRSVM's kappa values all fall within the range ($0.5$-$1$], indicating that its merit as a classifier agrees with the class distribution and is not random.
+Note that SimpleMI, MIOptimalBall, MIDD, MISVM, and Stacking contain some negative kappa values, indicating performance worse than the default-hypothesis.
+MIBoost and MIWrapper are shown to randomly classify all $15$ datasets.
+Figure~\ref{fig:BonfDunnkappa} and Table~\ref{tab:statkappa} show the results of the statistical analysis on the Cohen's Kappa Rate results.
+Nemenyi's procedure reflects results similar to the $p$-values obtained from the accuracy results, where MIRSVM performs significantly better than MIOptimalBall, MIDD, MISVM, MIWrapper, MIBoost, and SimpleMI, having $p$-values $< 0.01$.
+The Holm and Shaffer procedures indicate that significant differences exist among all algorithms results, supporting MIRSVM's performance as a competitive classifier.
+
+\subsection{AUC}
+\begin{table}[b!]
 \caption{AUC}\label{tab:aucResults}
-\resizebox{\textwidth}{!}{\begin{tabular}{lcccccccccccc}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}
 \hline\noalign{\smallskip}
@@
 \centering
-\resizebox{0.9\textwidth}{!}{\begin{tikzpicture}
+\resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
 \draw (1,0) -- (10,0);
@@
 };
-\end{tikzpicture}}
+\end{tikzpicture}}\vspace{-0.6em}
 \captionof{figure}{Bonferroni-Dunn test for AUC}\label{fig:BonfDunnauc}
-\vspace{0.5cm}
+\vspace{-0.5em}
 \captionof{table}{Nemenyi, Holm, and Shaffer tests for AUC}\label{tab:statauc}
 \scriptsize
-\begin{tabularx}{\textwidth}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
 MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabularx}
+\end{tabular}}
 \end{table}
-
-\newpage
-\subsection{AUC}
-Table~\ref{tab:aucResults} shows AUC results obtained by the algorithms.
-These results complement the accuracy and kappa rate, emphasizing the better performance of bag-based methods.
+Table~\ref{tab:aucResults} shows AUC results obtained by the algorithms, which complement the accuracy and kappa rate, emphasizing the better performance of bag-based methods.
 MIRSVM achieves the best AUC score on $6$ of the $15$ datasets, while MIBoost, SimpleMI, and MIWrapper obtain the worst results.
@@
 Bag-level methods all obtain scores between $0.7$ and $0.75$ indicating a high true positive rate and a low false positive rate, which is reflected by the precision and recall results.
-
 Figure~\ref{fig:BonfDunnauc} and Table~\ref{tab:statauc} show that MIRSVM performs significantly better than $6$ out of the $10$ competing algorithms.
 Nemenyi's procedure indicates that significant differences exist between MIRSVM and all algorithms except MISMO, TLC, Bagging, and Stacking.
-MISVM is ranked $8^{th}$ with respect to the other state-of-the-art methods.
 MISVM's true positive rate could be affected because of the possible imbalance of support vectors from the positive and negative classes (favoring the negative).
-Note that the Nemenyi $p$-values for MIWrapper, MIBoost, and SimpleMI are $= 0$.
-\begin{table}[b!]
+Note that the Nemenyi $p$-values for MIWrapper, MIBoost, and SimpleMI are $0$.
+
+\subsection{Overall Comparison}
+\begin{table}[t!]
 \centering
 \caption{Run Time (seconds)}\label{tab:time}
-\resizebox{\textwidth}{!}{\begin{tabular}{lrrrrrrrrrrrr}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lrrrrrrrrrrrr}
 \hline\noalign{\smallskip}
@@
 \captionof{table}{Overall ranks comparison}\label{tab:metarank}
-\resizebox{\textwidth}{!}{\begin{tabular}{lcccccccccccc}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}
 \hline\noalign{\smallskip}
@@
 };
-\end{tikzpicture}}
+\end{tikzpicture}}\vspace{-1.2em}
 \captionof{figure}{Bonferroni-Dunn test for overall ranks comparison}\label{fig:BonfDunnpmeta}
 \end{table}
-
-\subsection{Overall Comparison}
 Table~\ref{tab:time} shows the run time results, in seconds, for each algorithm.

### 2017-06-15 ArticleRevision/article/article.tex
Updated convergence figure
The figure wasnt clear in the pdf, so I reran it and saved it as a png after editing it in the preview app (cutting it into a new figure). Deleted the eps files since they dont belong.

@@
 \label{fig:convegence}
-\includegraphics[width=0.99\textwidth]{convergence.eps} 
+\includegraphics[width=0.94\textwidth]{convergence.png} 
 \caption{Bag representative convergence plots on 9 datasets.
@@
 \end{figure}
+\newpage
 This formulation is designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances.

### 2017-06-15 current_code/DualTrain.m

@@ -16,8 +16,8 @@ end
 
 Xn = X(S,:); Yn = Y(S); Bn = B(S);
 %%%%%%%% Compute QP Solution %%%%%%%%
-iter = 1; scurrent = 1;
-while(scurrent ~= numb_bags && iter < numb_bags)
+iter = 1; scurrent = 1; max_iter = 10;
+while(iter <= max_iter)%(scurrent ~= numb_bags && iter < numb_bags)
     S_old = [S_old S];
     H = (Yn*Yn').*GaussianKernel(Xn,Xn,param);
     f = -1*ones(numb_bags,1);

### 2017-06-15 current_code/mirsvm_script.m

@@ -1,4 +1,4 @@
-function [acc,iter,precision,recall,kappa,AUC] = mirsvm_script(path,name,C,param,rnd,p)
+function [acc,iter,precision,recall,kappa,AUC,sums,numb_bags] = mirsvm_script(path,name,C,param,rnd,p)
 % [acc,iter,precision,recall,kappa,AUC] = mirsvm_script('Google Drive/data/midata/libsvm/','musk1',1000,4.6,1,1)
 
 rng('default'); rng(rnd); 

### 2017-06-15 current_code/plotting_convergence.m

@@ -4,18 +4,21 @@ datasets = dir(path);
 datasets([1:2 3 7 10:12 16],:) = [];
 C = 1; Sigma = 0.1; 
 
-figure;
+figure('Position',[1 1 1100 500]); 
 j = 1;
 for data = datasets'
     name = data.name;
     [~,~,~,~,~,~,sums,numb_bags] = mirsvm_script([path '/'],name,C,Sigma,1,0);
     
-    fig = subplot(3,3,j); plot(sums,'LineWidth',1.2); hold on; title(name,'Interpreter','latex'); 
-    grid minor; xlabel('Iterations','Interpreter','latex'); ylabel('Equal Representatives','Interpreter','latex');
-    plot(numb_bags.*ones(length(sums),1),'r--','LineWidth',1); axis([1 length(sums) 1 numb_bags+2]);
-    set(gca,'fontsize',11);
+    subplot(3,3,j); hold on; grid minor;
+    plot(sums,'LineWidth',2.2); plot(numb_bags.*ones(length(sums),1),'r--','LineWidth',1.8);
+    xlabel('Iterations','Interpreter','latex','fontsize',13); 
+    ylabel('Equal Representatives','Interpreter','latex','fontsize',13);
+    title(name,'Interpreter','latex','fontsize',16); axis([1 length(sums) 1 numb_bags+2]);
     set(gca,'TickLabelInterpreter', 'latex');
     j = j + 1;
 end
+
+%matlabfrag('Research/MultiInstanceLearning/convergence/convergence');
 
 %print(gcf,'Research/MultiInstanceLearning/convergence/subplot','-dpng');

### 2017-06-16 ArticleRevision/article/article.tex
Added space between equation metrics

@@
 \begin{align}
-\text{Accuracy} \tab \tab &\dfrac{TP+TN}{n^\prime} \label{eq:accuracy}\\[1.5pt]
-\text{Precision} \tab \tab &\dfrac{TP}{TP+FP} \label{eq:precision}\\[1.5pt]
-\text{Recall} \tab \tab &\dfrac{TP}{TP+FN} \label{eq:recall}\\[1.5pt]
-\text{Cohen's Kappa Rate} \tab \tab &\dfrac{n^\prime - \dfrac{(TP+FN)*(TP+FP)}{n^\prime}}{1 - \dfrac{(TP+FN)*(TP+FP)}{n^\prime}} \label{eq:kappa}\\[1.5pt]
+\text{Accuracy} \tab \tab &\dfrac{TP+TN}{n^\prime} \label{eq:accuracy}\\[10pt]
+\text{Precision} \tab \tab &\dfrac{TP}{TP+FP} \label{eq:precision}\\[10pt]
+\text{Recall} \tab \tab &\dfrac{TP}{TP+FN} \label{eq:recall}\\[10pt]
+\text{Cohen's Kappa Rate} \tab \tab &\dfrac{n^\prime - \dfrac{(TP+FN)*(TP+FP)}{n^\prime}}{1 - \dfrac{(TP+FN)*(TP+FP)}{n^\prime}} \label{eq:kappa}\\[10pt]
 \text{Area Under ROC Curve} \tab \tab &\frac{1 + \dfrac{TP}{TP+FN} - \dfrac{FP}{FP+TN}}{2} \label{eq:auc}

### 2017-06-16 ArticleRevision/article/article.tex
Added small elaboration on convergence in overall comparison
Edits to Formulae
> reverted back to argmax because it is corrent
> there were still some old notation B bags in the contribution section
> there were errors with the y_I, it should be Y_I
> fixed the algorithm as well (there were still B, and bold faces where incorrect)

@@
 \centering \label{eqn:stasmax}
-Y_I = \text{max}_{\forall i \in I}\,\,\, y_i.
+Y_I = \text{argmax}_{\forall i \in I}\,\,\, y_i.
 \end{equation}
@@
 all instances are guaranteed to be negative.
-This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{max}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
+This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
 In other words, the most positive sample is chosen from each positive bag and the least negative sample is chosen from each negative bag (samples with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
@@
 \min\limits_{\bm w, b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{n}\sum_I \xi_I, \tag{\ref{eq:primalmirsvm}}\\ 
-\text{s.t.}& {\,\,} y_I(\langle\bm{w},x_{s_I}\rangle + b) \geq 1 - \xi_I,\, \forall I \in \set{1,\ldots,n}  \label{eq:primalmirsvm1}\\
+\text{s.t.}& {\,\,} Y_I(\langle\bm{w},\bm x_{s_I}\rangle + b) \geq 1 - \xi_I,\, \forall I \in \set{1,\ldots,n}  \label{eq:primalmirsvm1}\\
 {} & {\,\,} \xi_I \geq 0,\, \forall I \in \set{1,\ldots,n}, 
@@
 \begin{aligned}
-\mathcal{L}\left(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}\right) = \frac{1}{2}\sum_{j=1}^d w_j^2  + \frac{C}{n}\sum_I \xi_I - \sum_I{\beta_I \xi_I} - \sum_I{\alpha_I\left(y_I\left(\sum_{j=1}^d w_j \bm x_{s_Ij} + b\right) -1 + \xi_I\right)}
+\mathcal{L}\left(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}\right) = \frac{1}{2}\sum_{j=1}^d w_j^2  + \frac{C}{n}\sum_I \xi_I - \sum_I{\beta_I \xi_I} - \sum_I{\alpha_I\left(Y_I\left(\sum_{j=1}^d w_j x_{s_Ij} + b\right) -1 + \xi_I\right)}
 \end{aligned}$} 
@@
 \begin{align}
-&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,y_I\, x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
-&\frac{\partial\mathcal{L}}{\partial b}: \sum_I{\alpha_Iy_I} = 0,\label{eqn:optcond2}\\
+&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,Y_I\, x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
+&\frac{\partial\mathcal{L}}{\partial b}: \sum_I{\alpha_IY_I} = 0,\label{eqn:optcond2}\\
 &\frac{\partial\mathcal{L}}{\partial\xi_I}: \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}\label{eqn:optcond3} 
@@
 \begin{alignat}{2}
-\max\limits_{\bm \alpha,\bm \beta}& \sum_I \alpha_I -\frac{1}{2}\sum_I \sum_{K\in I} \sum_{j=1}^d \alpha_I \alpha_K y_I y_K  x_{s_I j} x_{s_K j} \tag{\ref{eq:dualmirsvm1}}\\
-\text{s.t.}&  \sum_I{\alpha_Iy_I} = 0\, \\
+\max\limits_{\bm \alpha,\bm \beta}& \sum_I \alpha_I -\frac{1}{2}\sum_I \sum_{K\in I} \sum_{j=1}^d \alpha_I \alpha_K Y_I Y_K  x_{s_I j} x_{s_K j} \tag{\ref{eq:dualmirsvm1}}\\
+\text{s.t.}&  \sum_I{\alpha_IY_I} = 0\, \\
 {} & \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}   \label{eq:implicit1}\\
@@
 \centering
-s_I = \underset{i \in I}{\text{max}}(\sum_{K\in I} \sum_{j=1}^d \alpha_K y_K x_{s_K j} x_{ij} + b),\, \forall I \in \set{1,\ldots,n}.
+s_I = \underset{i \in I}{\text{argmax}}(\sum_{K\in I} \sum_{j=1}^d \alpha_K Y_K x_{s_K j} x_{ij} + b),\, \forall I \in \set{1,\ldots,n}.
 \end{equation}
@@
 \begin{alignat}{2}
-\max\limits_{\bm \alpha}& \sum_I \alpha_I - \frac{1}{2}\sum_I \sum_{K\in I} \alpha_I \alpha_K y_I y_K  \spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right) \tag{\ref{eq:dualmirsvm}}\\
-\text{s.t.}&  \sum_I{\alpha_Iy_I} = 0\,  \\
+\max\limits_{\bm \alpha}& \sum_I \alpha_I - \frac{1}{2}\sum_I \sum_{K\in I} \alpha_I \alpha_K Y_I Y_K  \spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right) \tag{\ref{eq:dualmirsvm}}\\
+\text{s.t.}&  \sum_I{\alpha_IY_I} = 0\,  \\
 {} & 0 \leq \alpha_I \leq \frac{C}{n},\, \forall I \in \set{1,\ldots,n}.
@@
 \For {$I \in \set{1,\ldots,n}$}
-\State $S_I \leftarrow \text{ rand}\left(|\bm B_I|,1,1\right)$ \Comment{Assign each bag a random instance}
+\State $\bm S_I \leftarrow \text{ rand}\left(|\mathcal{B}_I|,1,1\right)$ \Comment{Assign each bag a random instance}
 \EndFor
-\State $\bm X_S \leftarrow \bm X(\bm S),\,Y_S \leftarrow Y(\bm S)$ \Comment{Initialize the representative dataset}
+\State $\bm X_S \leftarrow \bm X(\bm S),\,\bm Y_S \leftarrow \bm Y(\bm S)$ \Comment{Initialize the representative dataset}
 \While {$\bm S \neq \bm S_{old}$}
 \State $\bm S_{old} \leftarrow \bm S$
-\State $\bm G \leftarrow (Y_S \times Y_S) \bm \cdot \mathcal{K}\left( \bm X_S,\,\bm X_S,\,\sigma\right)$ \Comment{Build Graham matrix}
-\State $\bm \alpha \leftarrow \text{ quadprog}\left(\bm G, \bm{-1}^n, Y_S, \bm 0^n, \bm 0^n, \bm C^n\right)$ \Comment{Solve QP Problem}
+\State $\bm G \leftarrow (\bm Y_S \times \bm Y_S) \bm \cdot \mathcal{K}\left( \bm X_S,\,\bm X_S,\,\sigma\right)$ \Comment{Build Graham matrix}
+\State $\bm \alpha \leftarrow \text{ quadprog}\left(\bm G, \bm{-1}^n, \bm Y_S, \bm 0^n, \bm 0^n, \bm C^n\right)$ \Comment{Solve QP Problem}
 \State $\bm{sv} \leftarrow \text{find}\left(0 < \bm \alpha \leq C \right)$ \Comment{Get the support vector indices}
-\State $n_{sv} \leftarrow \text{count}\left(0 < \bm \alpha \leq C \right)$ \Comment{Get the number of support vectors}
-\State $b \leftarrow \frac{1}{n_{sv}}\sum_{i=1}^{n_{sv}} \left(Y_{\bm sv} - \bm G_{\bm sv}*\left(\bm{\alpha_{\bm sv}} \cdot Y_{\bm sv}\right)\right)$ \Comment{Calculate the bias term}
+\State $n_{\bm{sv}} \leftarrow \text{count}\left(0 < \bm \alpha \leq C \right)$ \Comment{Get the number of support vectors}
+\State $b \leftarrow \frac{1}{n_{\bm{sv}}}\sum_{i=1}^{n_{\bm{sv}}} \left(\bm Y_{\bm{sv}} - \bm G_{\bm{sv}}*\left(\bm{\alpha_{\bm{sv}}} \cdot \bm Y_{\bm{sv}}\right)\right)$ \Comment{Calculate the bias term}
 \For {$I \in \set{1,\ldots,n}$} 
-\State $\bm G_I \leftarrow (Y_I \times Y_S) \bm \cdot \mathcal{K}\left( \bm B_I,\,\bm X_S,\,\sigma\right)$
-\State $\bm S_I \leftarrow \text{argmax}_{i \in I}\left(\bm G_I*\bm{\alpha} + b \right)$ \tab\tab[0.62cm]\Comment{Select optimal bag-representatives using SMI assumption}
+\State $\bm G_I \leftarrow (Y_I \times \bm Y_S) \bm \cdot \mathcal{K}\left( \mathcal{B}_I,\,\bm X_S,\,\sigma\right)$
+\State $\bm S_I \leftarrow \text{argmax}_{i \in I}\left(\bm G_I*\bm{\alpha} + b \right)$ \tab\tab[0.62cm]\Comment{Select optimal bag-representatives}
 \EndFor
-\State $\bm X_S \leftarrow \bm X(\bm S),\,Y_S \leftarrow Y(\bm S)$ \Comment{Re-set the representative dataset}
+\State $\bm X_S \leftarrow \bm X(\bm S),\,\bm Y_S \leftarrow \bm Y(\bm S)$ \Comment{Re-set the representative dataset}
 \EndWhile 
@@
 \end{figure}
-To evaluate the output vector, $\bm o_I$, of bag $I$ using the kernel, the following equation is used~\citep{Huang2006}, where $\bm B_I$ are the instances of bag $I$, $\bm X_S$ are the optimal bag representatives, and $Y_S$ are the representative bag labels.
+To evaluate the output vector, $\bm o_I$, of bag $I$ using the kernel, the following equation is used~\citep{Huang2006}, where $\mathcal{B}_I$ are the instances of bag $I$, $\bm X_S$ are the optimal bag representatives, and $\bm Y_S$ are the representative bag labels.
 \begin{align}
-\bm o_I = \spa{K}(\bm B_I,\bm X_S)*(\bm\alpha \cdot Y_S) + b
+\bm o_I = \spa{K}(\mathcal{B}_I,\bm X_S)*(\bm\alpha \cdot \bm Y_S) + b
 \end{align}
@@
 \label{eqn:bias}
-b = \frac{1}{n_{sv}}\sum_{\bm{sv}} Y_{\bm{sv}} - \spa{K}(\bm X_{\bm{sv}},\bm X_{\bm{sv}})*(\bm \alpha_{\bm{sv}}\bm\cdot Y_{\bm{sv}})
+b = \frac{1}{n_{\bm{sv}}}\sum_{\bm{sv}} Y_{\bm{sv}} - \spa{K}(\bm X_{\bm{sv}},\bm X_{\bm{sv}})*(\bm \alpha_{\bm{sv}}\bm\cdot Y_{\bm{sv}})
 \end{align}
@@
 It is important to note that quadratic programming solvers are not the most efficient tools for solving optimization problems in terms of run time, and yet MIRSVM still is shown to perform competitively against the current state-of-the-art algorithms.
+The scalability of MIRSVM is founded on the speedy rate of bag-represenative convergence, as shown in Figure~\ref{fig:convegence}.
 

### 2017-06-16 ArticleRevision/article/article.tex
Updated Gaussian formula + conclusion

@@
 \centering
-\mathcal{K}(\bm x_i, \bm x_j) = e^{-\frac{\norm{x_i - x_j}^2}{2\sigma^2}}
+\mathcal{K}(\bm x_i, \bm x_j) = e^{-\frac{\norm{\bm x_i - \bm x_j}^2}{2\sigma^2}}
 \end{equation}
@@
 \section{Conclusion}\label{sec:conclusion}
-This paper proposed a novel formulation and algorithm for the multiple-instance support vector machine problem, which optimizes bags classification via bag-representative selection.
-First, the primal formulation was posed and its dual was then derived and computed using a quadratic programming solver.
+This paper proposed a novel formulation and algorithm for the multiple-instance support vector machine problem, which optimizes bag classification via bag-representative selection.
+First, the primal formulation was posed and its dual was then derived and solution computed using a quadratic programming solver.
 This formulation was designed to utilize bag-level information and find an optimal separating hyperplane between bags, rather than individual instances, using the standard multi-instance assumption.
@@
 The key features of the proposed algorithm MIRSVM are its ability to identify instances within positive and negative bags, i.e.
-the support vectors or representatives, that highly impact the decision boundaries as well as avoiding uncertainties and issues caused by techniques that flatten, subset, or under-represent positive instances within positively labeled bags.
-Additionally, it exhibits desirable scalability, making it suitable for large-scale learning tasks.
-
-The experimental study showed the better performance of MIRSVM compared with multi-instance support vector machines, traditional multi-instance learners, as well as with ensemble methods.
-The results, according to a variety of performance metrics, were compared and further validated using statistical analysis with non-parametric tests which highlight the advantages of using bag-level based and ensemble learners such as Bagging and Stacking, while showing the instance-level based learners performed poorly in comparison or were deemed as strongly biased and unstable classifiers.
+the support vectors or representatives, that highly impact the decision boundary and margin, as well as avoiding uncertainties and issues caused by techniques that flatten, subset, or under-represent positive instances within positively labeled bags.
+Additionally, it exhibits desirable convergence and scalability, making it suitable for large-scale learning tasks.
+
+The experimental study showed the better performance of MIRSVM compared with state-of-the-art multi-instance support vector machines, traditional multi-instance learners, as well as ensemble methods.
+The results, according to a variety of performance metrics, were compared and further validated using statistical analysis with non-parametric tests which highlight the advantages of using bag-level based and ensemble learners, such as Bagging and Stacking, while showing the instance-level based learners performed poorly in comparison or were deemed as strongly biased and unstable classifiers.
 On the contrary, our proposal MIRSVM performs statistically better, neither compromising accuracy nor run-time while displaying a robust performance across all of the evaluated datasets.

### 2017-06-16 ArticleRevision/article/article.tex
Dataset table, run-time, ignore *.m~
> added explanation of run-time (train+test)
> ignore m~ files
> re-ordered dataset table to be in order of increasing bag size

@@
 WestEast 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
+Webmining			& 5863	& 17	& 58	& 75	& 2212	\\
 Musk1 				& 166 	& 47 	& 45 	& 92 	& 476 	\\
 Musk2 				& 166 	& 39 	& 63 	& 102 	& 6598 	\\
-Webmining			& 5863	& 17	& 58	& 75	& 2212	\\
 TRX 				& 8 	& 25 	& 193 	& 168 	& 26611 \\
@@
 The values of the true positive (TP), true negative (TN), false positive (FP), and false negative samples (FN) were first collected for each of the classifiers, then the metrics were computed using the equations shown in~\eqref{eq:metrics} on the $n^\prime$ bags of the test data.
-The run times of each algorithm are also reported to analyze the usability and speed of each of the algorithms across differently sized datasets.
+The run times (training and testing times) of each algorithm are also reported to analyze the usability and speed of each of the algorithms across differently sized datasets.
 

### 2017-06-16 ArticleRevision/article/article.tex
Average Bag Size
> edited dataset table in paper to have average bag size
> wrote script to calculate dataset statistics and output them to a tex file

@@
 \label{tab:Dataset}
-\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}ccccc}
+\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}cccccc}
 \hline\noalign{\smallskip}
-Dataset & Attributes & Positive Bags & Negative Bags & Total & Instances \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Suramin 			& 20 	& 7 	& 4 	& 11 	& 2378 	\\
-EastWest 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
-WestEast 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
-Webmining			& 5863	& 17	& 58	& 75	& 2212	\\
-Musk1 				& 166 	& 47 	& 45 	& 92 	& 476 	\\
-Musk2 				& 166 	& 39 	& 63 	& 102 	& 6598 	\\
-TRX 				& 8 	& 25 	& 193 	& 168 	& 26611 \\
-Mutagenesis-Atoms 	& 10 	& 125 	& 63 	& 188 	& 1618 	\\
-Mutagenesis-Bonds 	& 16 	& 125 	& 63 	& 188 	& 3995 	\\
-Mutagenesis-Chains 	& 24 	& 125 	& 63 	& 188 	& 5349 	\\
-Tiger 				& 230 	& 100 	& 100 	& 200 	& 1391 	\\
-Elephant 			& 230 	& 100 	& 100 	& 200 	& 1220 	\\
-Fox 				& 230 	& 100 	& 100 	& 200 	& 1320 	\\
-Component			& 22	& 423	& 2707	& 3130	& 36894	\\
-Function			& 202	& 443	& 4799	& 5242	& 55536	\\
+Dataset & Attributes & Positive Bags & Negative Bags & Total & Instances & Average Bag Size\\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Suramin & 20 & 7 & 6 & 13 & 2898 &  222.92 \\ 
+EastWest & 24 & 10 & 10 & 20 & 213 &  10.65  \\ 
+WestEast & 24 & 10 & 10 & 20 & 213 &  10.65  \\ 
+Musk1 & 166 & 47 & 45 & 92 & 476 &  5.17  \\ 
+Musk2 & 166 & 39 & 62 & 101 & 6728 &  66.61  \\ 
+Webmining & 5863 & 21 & 92 & 113 & 3423 &  30.29  \\ 
+Mutagenesis-atoms & 10 & 125 & 63 & 188 & 1618 &  8.61  \\ 
+Mutagenesis-bonds & 16 & 125 & 63 & 188 & 4081 &  21.71  \\ 
+Mutagenesis-chains & 24 & 125 & 63 & 188 & 5424 &  28.85  \\ 
+TRX & 8 & 25 & 168 & 193 & 26611 &  137.88 \\ 
+Elephant & 230 & 100 & 100 & 200 & 1391 &  6.96 \\ 
+Fox & 230 & 100 & 100 & 200 & 1320 &  6.60 \\ 
+Tiger & 230 & 100 & 100 & 200 & 1188 &  5.94  \\ 
+Component & 200 & 423 & 2707 & 3130 & 36894 &  11.79  \\ 
+Function & 200 & 443 & 4799 & 5242 & 55536 &  10.59  \\ 
 \noalign{\smallskip}\hline

### 2017-06-16 MIDatasetStatsToTable.m

@@ -1,0 +1,42 @@
+cclear;
+path = '../../../Google Drive/data/midata/libsvm/';
+cols = {'Dimensionality','Positive Bags','Negative Bags' ...
+    ,'Total Bags','Instances','Average Bag Size'};
+datasets = dir([path '*']);
+datasets(1:2,:) = [];
+
+i = 1;
+for data = datasets'
+    name = data.name;
+    % get data
+    [Y,X] = libsvmread([path name]); 
+    X = full(X); Y(Y==2) = -1; B = X(:,2); 
+    Bsizes = X(:,1); X = X(:,3:end);
+    [num_data, dim] = size(X);
+    [uniqueBid,indU] = unique(B); 
+    num_bags = length(uniqueBid);
+    % get unique labels and sizes
+    YuB = Y(indU); numPos = sum(YuB == 1); numNeg = sum(YuB == -1);
+    BsizeU = Bsizes(indU); % get unique bag sizes
+    
+    % save info
+    attributes(i) = dim;
+    pos_bags(i) = numPos; neg_bags(i) = numNeg;
+    bags(i) = num_bags; instances(i) = num_data;
+    avgBagSize(i) = sum(BsizeU)/num_bags;
+    name(1) = upper(name(1));
+    rows{i} = name;
+    i = i + 1;
+end
+clearvars X Y B Bsizes num_data dim indU uniqueBid num_bags YuB numPos numNeg BsizeU i name;
+% sort based on bag size
+[bags,indSort] = sort(bags,'ascend');
+attributes = attributes(indSort); pos_bags = pos_bags(indSort);
+neg_bags = neg_bags(indSort); instances = instances(indSort);
+avgBagSize = avgBagSize(indSort);
+rows = rows(indSort);
+data = [attributes' pos_bags' neg_bags' bags' instances' avgBagSize'];
+
+matrix2latex(data, 'datasets.tex', ...
+    'rowLabels', rows, 'columnLabels', cols, 'alignment', 'c', ...
+    'format', '%-4.2f', 'size', 'small');

### 2017-06-16 WekaTesting/FormatOutputMI.m
Moved shell files, editing results
> brought back old results because i think the precision and recall are wrong
> editing the format results to read them into excel in proper format

@@ -2,15 +2,15 @@
 clear; clc; close all;
 
 % Get algorithm names
-path = 'C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\';
+path = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/output/';
+alg_names = dir(path); alg_names([1:4 6 13:14]) = [];
 names = getList(path,'.');
 
-%metrics = {'Total','Accuracy','Precision','Recall','Kappa','AUC'};
-metrics = {'Time'};
+metrics = {'Precision','Recall'};
 
 % Create Excel File
 fold = 0;
-excelFile = [path 'ResultsTime.xlsx'];
+excelFile = [path 'ResultsPR.xlsx'];
 sheet = 1;
 startRange = 2;
 xlRange = ['B' num2str(startRange)];

### 2017-06-16 ArticleRevision/article/article.tex
Added why we have precision and recall

@@
 The classification performance was measured using five metrics: Accuracy~\eqref{eq:accuracy}, Precision \eqref{eq:precision}, Recall~\eqref{eq:recall}, Cohen's kappa rate~\eqref{eq:kappa}, and Area under ROC curve (AUC)~\eqref{eq:auc}.
-Accuracy can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which have six and ten times as many negative instances than positive, respectively.
+The Precision and Recall measures were reported because Accuracy alone can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which respectively have six and ten times as many negative instances than positive.
 Cohen's Kappa Rate and the AUC measures are used as complementary measures in order to evaluate the algorithms comprehensively~\citep{Bendavid2008}.

### 2017-06-16 WekaTesting/FormatOutputMI.m
Script for writing output to csvs

@@ -1,69 +1,70 @@
 % Create Excel File
-clear; clc; close all;
-
-% Get algorithm names
+cclear;
+% get dataset names
+path_data = '../../../Google Drive/data/midata/libsvm/';
+Datasets = dir([path_data '*']);
+Datasets(1:2,:) = []; Datasets = {Datasets.name}';
 path = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/output/';
-alg_names = dir(path); alg_names([1:4 6 13:14]) = [];
-names = getList(path,'.');
-
-metrics = {'Precision','Recall'};
-
-% Create Excel File
-fold = 0;
-excelFile = [path 'ResultsPR.xlsx'];
-sheet = 1;
-startRange = 2;
-xlRange = ['B' num2str(startRange)];
-
-%[status,~] = xlswrite(excelFile,{'Algorithm','DataSet','NumData','Accuracy','Precision','Recall','Kappa','AUC'},sheet,'A1');
-[status,~] = xlswrite(excelFile,{'Algorithm','DataSet','Time'},sheet,'A1');
-
-for n = 1:length(names)
-    folder = names{n};
-    files = getList([path folder '\*.txt'],'');
-    disp(['Reading ' folder]);
-    for f = 1:length(files)
-        line{1} = folder;
-        [resFile, ~] = fopen([path folder '\' files{f}],'r');
-        resText = fscanf(resFile,'%s');
-        fclose(resFile);
-        line{2} = files{f};
-        disp(['Reading ' files{f}]);
-        
-        TP = regexp(resText,'TP=(\d+[.\d+]+)','tokens'); TP = str2double(TP{1});
-        FP = regexp(resText,'FP=(\d+[.\d+]+)','tokens'); FP = str2double(FP{1});
-        TN = regexp(resText,'TN=(\d+[.\d+]+)','tokens'); TN = str2double(TN{1});
-        FN = regexp(resText,'FN=(\d+[.\d+]+)','tokens'); FN = str2double(FN{1});
-        traintime = regexp(resText,'TrainTime=(\d+[.\d+]+)','tokens'); traintime = str2double(traintime{1});
-        testtime = regexp(resText,'TestTime=(\d+[.\d+]+)','tokens'); testtime = str2double(testtime{1});
-        time = (traintime + testtime)/2;
-        
-        num = (TP+FP+TN+FN);
[…]

### 2017-06-16 ArticleRevision/article/article.tex
Updated the overall comparison
Emphasized that wrapper methods classify everything as negative

@@
 SimpleMI, MIWrapper, MIBoost, MISVM, MIOptimalBall, and MDD have the worst performance compared to MIRSVM and Bagging.
+Specifically, it is evident from the precision and recall results that MIBoost, MIWrapper, and SimpleMI, for example, classify all bags as negative for datasets that have imbalanced class distributions which favor the negative class.
+This emphasizes the disadvantage of using wrapper methods and assuming the data distribution of the samples within positive bags.
 Although these algorithms are popular in literature, the experimental study clearly shows that recent bag-level and ensemble methods easily overcome traditional multi-instance learning algorithms.

### 2017-06-19 current_code/DualTrain.m
Plotting accuracy vs. sums
Changed code a little to be able to plot, side-by-side, the accuracy per iteration of MIRSVM vs. the sums variable. (Not complete)

@@ -1,4 +1,4 @@
-function [alphay,bias,S,iter,sums] = DualTrain(X,Y,B,C,param,options,Bsizes)
+function [alphay,bias,S,iter,sums,tracc] = DualTrain(X,Y,B,C,param,options,Bsizes)
 
 [unique_bag_ids,~] = unique(B);
 numb_bags = length(unique_bag_ids);
@@ -16,7 +16,7 @@ end
 
 Xn = X(S,:); Yn = Y(S); Bn = B(S);
 %%%%%%%% Compute QP Solution %%%%%%%%
-iter = 1; scurrent = 1; max_iter = 10;
+iter = 1; scurrent = 1; max_iter = numb_bags;
 while(iter <= max_iter)%(scurrent ~= numb_bags && iter < numb_bags)
     S_old = [S_old S];
     H = (Yn*Yn').*GaussianKernel(Xn,Xn,param);
@@ -42,6 +42,7 @@ while(iter <= max_iter)%(scurrent ~= numb_bags && iter < numb_bags)
     end
     Xn = X(S,:); Yn = Y(S); Bn = B(S);
     sums(iter) = sum(S_old(:,iter) == S);
+    tracc(iter) = 100*(sum(ytrain == Yn))/numb_bags;
     scurrent = sums(iter);
     iter = iter + 1;
 end

### 2017-06-19 current_code/mirsvm_script.m

@@ -1,4 +1,4 @@
-function [acc,iter,precision,recall,kappa,AUC,sums,numb_bags] = mirsvm_script(path,name,C,param,rnd,p)
+function [acc,iter,precision,recall,kappa,AUC,sums,numb_bags,tracc] = mirsvm_script(path,name,C,param,rnd,p)
 % [acc,iter,precision,recall,kappa,AUC] = mirsvm_script('Google Drive/data/midata/libsvm/','musk1',1000,4.6,1,1)
 
 rng('default'); rng(rnd); 
@@ -9,7 +9,7 @@ B = X(:,2); Bsizes = X(:,1); X = X(:,3:end); X = scale(X,2); X(isnan(X)) = 0;
 [unique_bag_ids,~] = unique(B);
 numb_bags = length(unique_bag_ids);
 % train
-[alphay,bias,S,iter,sums] = DualTrain(X,Y,B,C,param,options,Bsizes);
+[alphay,bias,S,iter,sums,tracc] = DualTrain(X,Y,B,C,param,options,Bsizes);
 XS = X(S,:);
 % test
 [TP,TN,FP,FN] = DualTest(X,XS,Y,B,alphay,bias,param);

### 2017-06-19 current_code/plotting_convergence_acc.m

@@ -1,0 +1,28 @@
+cclear;
+path = '../../../../Google Drive/data/midata/libsvm';
+datasets = dir(path);
+datasets([1:2 3 7 10:12 16],:) = [];
+C = 1;
+Sigma = 0.1;
+
+figure(1); figure(2);
+j = 1;
+for data = datasets'
+    name = data.name;
+    [~,~,~,~,~,~,sums,numb_bags,tracc] = mirsvm_script([path '/'],data.name,C,Sigma,1,0);
+    % sums
+    figure(1); subplot(3,3,j); hold on; grid minor;
+    plot(sums,'LineWidth',2.2); plot(numb_bags.*ones(length(sums),1),'r--','LineWidth',1.8);
+    xlabel('Iterations','Interpreter','latex','fontsize',13); 
+    ylabel('Equal Representatives','Interpreter','latex','fontsize',13);
+    title(name,'Interpreter','latex','fontsize',16); axis([1 length(sums) 1 numb_bags+2]);
+    set(gca,'TickLabelInterpreter', 'latex');
+    % accs
+    figure(2); subplot(3,3,j); hold on; grid minor;
+    plot(tracc,'LineWidth',2.2);
+    xlabel('Iterations','Interpreter','latex','fontsize',13); 
+    ylabel('Training Accuracy','Interpreter','latex','fontsize',13);
+    title(name,'Interpreter','latex','fontsize',16); axis([1 length(name) 1 100]);
+    set(gca,'TickLabelInterpreter', 'latex');
+    j = j + 1;
+end

### 2017-06-19 current_code/cv_tests.m
New tasks for testing SOA

@@ -35,11 +35,11 @@ recall(isnan(recall)) = 0;
 kappa(isnan(kappa)) = 0;
 AUC(isnan(AUC)) = 0;
 
-acc = mean(acc);
-iter = mean(iter);
-precision = mean(precision);
-recall = mean(recall);
-kappa = mean(kappa);
-AUC = mean(AUC);
+if TP + FP == 0
+    precision = 1;
+end
+if TP + FN == 0
+    recall = 1;
+end
 
 end

### 2017-06-24 WekaTesting/FormatOutputMI.m
changed formatting results script to include time and MIRSVM (which is read from the Results.xlsx file)

@@ -5,10 +5,10 @@ path_data = '/Users/gabriellamelki/Google Drive/data/midata/libsvm/';
 Datasets = dir([path_data '*']);
 Datasets(1:2,:) = []; Datasets = {Datasets.name}';
 path = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/output/';
-names = {'miGraph'};
-%names = {'MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking'};
+%names = {'miGraph'};
+names = {'MIRSVM','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking','miGraph'};
 % metrics
-metrics = {'Accuracy','Precision','Recall','Kappa','AUC'};
+metrics = {'Accuracy','Precision','Recall','Kappa','AUC','Time'};
 ind = [11,2,15,6,7,14,13,9,10,8,12,3,4,1,5];
 % initialize table
 T = table;
@@ -17,52 +17,59 @@ for m = 1:length(metrics)   % for each metric, build a table
     sheet = m;
     for n = 1:length(names) % for each algorithm
         folder = names{n};
-        files = dir([path folder '/*.txt']); files = {files.name}';
-        disp(['Reading ' folder]);
-        for f = 1:length(files) % for each dataset result
-            [resFile, ~] = fopen([path folder '/' files{f}],'r');
-            resText = fscanf(resFile,'%s');
-            fclose(resFile);
-            
-            TP = regexp(resText,'TP=(\d+[.\d+]+)','tokens'); TP = str2double(TP{1});
-            FP = regexp(resText,'FP=(\d+[.\d+]+)','tokens'); FP = str2double(FP{1});
-            TN = regexp(resText,'TN=(\d+[.\d+]+)','tokens'); TN = str2double(TN{1});
-            FN = regexp(resText,'FN=(\d+[.\d+]+)','tokens'); FN = str2double(FN{1});
-            traintime = regexp(resText,'TrainTime=(\d+[.\d+]+)','tokens'); traintime = str2double(traintime{1});
-            testtime = regexp(resText,'TestTime=(\d+[.\d+]+)','tokens'); testtime = str2double(testtime{1});
-            time = (traintime + testtime)/2;
-            
-            num = (TP+FP+TN+FN);
-            switch metrics{m}
-                case 'Accuracy'
[…]

### 2017-06-26 WekaTesting/FormatOutputMI.m
Re-ordered the datasets + algorithms

@@ -6,10 +6,10 @@ Datasets = dir([path_data '*']);
 Datasets(1:2,:) = []; Datasets = {Datasets.name}';
 path = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/output/';
 %names = {'miGraph'};
-names = {'MIRSVM','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking','miGraph'};
+names = {'MIRSVM','miGraph','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking'};
 % metrics
 metrics = {'Accuracy','Precision','Recall','Kappa','AUC','Time'};
-ind = [11,2,15,6,7,14,13,9,10,8,12,3,4,1,5];
+ind = [11,2,15,6,7,14,13,8,9,10,12,3,4,1,5];
 % initialize table
 T = table;
 T.Datasets = Datasets(ind);

### 2017-06-26 FormatResults.m
Removed unused result formatting script

@@ -1,32 +1,0 @@
-% Create Excel File
-clear; clc; close all;
-
-% Get algorithm names
-path = 'C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\';
-names = getList(path,'.');
-excelFile = [path 'Results.xlsx'];
-
-%metrics = {'Accuracy','Precision','Recall','Kappa','AUC'};
-metrics = {'Accuracy'};
-algorithms = {'MIRSVM','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking'};
-line1 = {'Dataset','MIRSVM','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking'};
-columns = {'B','C','D','E','F','G','H','I','J','K','L'};
-ImportTime
-data = DataSet(1:15);
-clearvars DataSet;
-
-for m = 1:length(metrics)
-    sheet = metrics{m};
-    xlswrite(excelFile,line1,sheet,'A1');
-    xlswrite(excelFile,data,sheet,'A2:A16');
-    
-    for a=2:length(algorithms)
-        ind = strmatch(algorithms{a},Algorithm);
-        ind2 = strmatch(algorithms{a},algorithms);
-        m_vals = round(Time(ind,m),4);
-        range = strjoin([columns(ind2) '2:' columns(ind2) '16'],'');
-        xlswrite(excelFile,m_vals,sheet,range);
-    end
-end
-
-

### 2017-06-26 ImportTime.m

@@ -1,27 +1,0 @@
-%% Import data from spreadsheet
-% Script for importing data from the following spreadsheet:
-%
-%    Workbook: C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\ResultsTime.xlsx
-%    Worksheet: Sheet1
-%
-% To extend the code for use with different selected data or a different
-% spreadsheet, generate a function instead of a script.
-
-% Auto-generated by MATLAB on 2017/03/23 17:32:12
-
-%% Import the data
-[~, ~, raw] = xlsread('C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\ResultsTime.xlsx','Sheet1','A2:C150');
-raw(cellfun(@(x) ~isempty(x) && isnumeric(x) && isnan(x),raw)) = {''};
-cellVectors = raw(:,[1,2]);
-raw = raw(:,3);
-
-%% Create output variable
-data = reshape([raw{:}],size(raw));
-
-%% Allocate imported array to column variable names
-Algorithm = cellVectors(:,1);
-DataSet = cellVectors(:,2);
-Time = data(:,1);
-
-%% Clear temporary variables
-clearvars data raw cellVectors;

### 2017-06-26 post_hoc_script.m
Modified the post-hoc script
1. account for OS + paths
2. use tables instead of reading from xlsx

@@ -1,49 +1,45 @@
 clear; clc; close all;
 
-filename = 'Results.xlsx';
-path_in = 'C:\Users\melkiga\Google Drive\Research\Cano\MultiInstanceClassification\WekaTesting\output\';
-path_out = 'C:\Users\melkiga\Google Drive\MatlabHelpers\stats_tables\';
-file_path = [path_in filename];
-metrics = {'accuracy','precision','recall','kappa','auc','Time'};
+if ispc
+    disp('TODO: add paths for windows machine.');
+    disp('Terminating script.'); return;
+else
+    path_in = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/output/';
+    path_out = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/stats/';
+end
+
+metrics = {'Accuracy','Precision','Recall','Kappa','AUC','Time'};
 num_metrics = length(metrics);
 alpha = 0.1;
-
-% Get algorithm and datasets names and lengths
-[~, ~, prints] = xlsread(file_path,2,'A1:L1');
-prints(cellfun(@(x) ~isempty(x) && isnumeric(x) && isnan(x),prints)) = {NaN};
-algorithms = prints(2:end);
+% initialize using Accuracy.csv
+T = readtable([path_in metrics{1} '.csv']);
+% get algorithm names
+algorithms = T.Properties.VariableNames(2:end);
 num_algorithms = length(algorithms);
-
-[~, ~, datasets] = xlsread(file_path,2,'A2:A16');
-datasets(cellfun(@(x) ~isempty(x) && isnumeric(x) && isnan(x),datasets)) = {NaN};
-datasets = datasets';
+% get dataset names + latex table row names
+datasets = table2cell(T(:,1));
 num_datasets = length(datasets);
-latex_data_rows = datasets; latex_data_rows{end+1} = 'Average'; latex_data_rows{end+1} = 'Rank';
-
-% Allocate memory
+latex_data_rows = datasets; latex_data_rows{end+1} = 'Average'; latex_data_rows{end+1} = 'Rank'; 
 ranks = zeros(num_metrics,num_algorithms);
 
-for m = 1:length(metrics)
-    metric = metrics{m};
-    disp(metric);
-    
-    [~, ~, data] = xlsread(file_path,metric,'B2:L16');
[…]

### 2017-06-26 WekaTesting/stats/AUC_Fig.tex
Updated the post-hoc script to remove wilcoxon since it isnt in the paper. Ran it and got results in csv format.

\begin{tikzpicture}
\draw (1,0) -- (11,0);
\foreach \x in {1,2,3,4,5,6,7,8,9,10,11} {
\draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
\ifthenelse{\x < 11}{\draw (\x+.5, 0) -- ++(0,.03);}{}
}

\coordinate (c0) at (2.8667,0);
\coordinate (c1) at (4.2333,0);
\coordinate (c2) at (10.1667,0);
\coordinate (c3) at (6.9333,0);
\coordinate (c4) at (6.6,0);
\coordinate (c5) at (10.1667,0);
\coordinate (c6) at (5.1,0);
\coordinate (c7) at (8.2333,0);
\coordinate (c8) at (10.1667,0);
\coordinate (c9) at (4.3333,0);
\coordinate (c10) at (4.2667,0);
\coordinate (c11) at (4.9333,0);

\node (l0) at (c0) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIRSVM};
\node (l1) at (c1) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
\node (l2) at (c2) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
\node (l3) at (c3) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
\node (l4) at (c4) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
\node (l5) at (c5) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
\node (l6) at (c6) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
\node (l7) at (c7) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
\node (l8) at (c8) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
\node (l9) at (c9) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
\node (l10) at (c10) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
\node (l11) at (c11) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny Stacking};

\fill[fill=gray,fill opacity=0.5] (2.8667,-0.1) rectangle (3.8667,0.1);

\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11,12} {
\draw (l\x) -| (c\x);
};
\end{tikzpicture}

### 2017-06-26 post_hoc_script.m

@@ -30,16 +30,14 @@ for m = 1:num_metrics
     [avg_ranks,chi_statistics] = avg_rank(-data);
     ranks(m,:) = avg_ranks;
     max_rank = round(max(avg_ranks))+1;
-    [stats,headers] = wilcoxon(data,alpha);
+    %[stats,headers] = wilcoxon(data,alpha);
     
     % add average + ranks to data
     data(end+1,:) = mean(data);
     data(end+1,:) = avg_ranks;
     
     % create latex table
-    matrix2latex_metrics(data, [path_out [metric '.tex']], 'rowLabels', latex_data_rows, 'columnLabels', algorithms, 'alignment', 'c', 'format', '%-1.1f', 'rank', 'yes');
-    % create results table
-    matrix2latex(stats, [path_out [metric '_wx.tex']], 'rowLabels', algorithms, 'columnLabels', headers, 'alignment', 'c', 'format', '%-1.4f');
+    matrix2latex_metrics(data, [path_out [metrics{m} '.tex']], 'rowLabels', latex_data_rows, 'columnLabels', algorithms, 'alignment', 'c', 'format', '%-1.4f', 'rank', 'yes');
     % create bonferroni-dunn figure
-    bonferroni_dunn_tikz([path_out [metric '_Fig.tex']],avg_ranks,1,num_algorithms,algorithms,max_rank);
+    bonferroni_dunn_tikz([path_out [metrics{m} '_Fig.tex']],avg_ranks,1,num_algorithms,algorithms,max_rank);
 end

### 2017-06-27 ArticleRevision/article/article.tex
Changed $10$ to $11$ to add miGraph in the count

@@
 Unlike other multi-instance SVM methods, this approach eliminates possible class imbalance issues by allowing both positive and negative bags to have at most one representative, which constitute as the most contributing instances to the model.
-The experimental study evaluates and compares the performance of this proposal against $10$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis.
+The experimental study evaluates and compares the performance of this proposal against $11$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis.
 The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as this proposal's overall superior performance against other multi-instance SVM models.
@@
 The primal L$1$-SVM is formulated with respect to optimizing over bags, the dual formulation is then derived along with conditions for optimality, and the proposed algorithm, MIRSVM, is listed and described in Section~\ref{sec:contribution}.
-Section~\ref{sec:experiments} presents the experimental environment, including results from various metrics, run-time, and non-parametric statistical analysis over $15$ benchmark MI datasets compared with $10$ state-of-the-art algorithms.
+Section~\ref{sec:experiments} presents the experimental environment, including results from various metrics, run-time, and non-parametric statistical analysis over $15$ benchmark MI datasets compared with $11$ state-of-the-art algorithms.
 Finally, Section~\ref{sec:conclusion} presents the conclusions of this contribution.
@@
 
-The experimental environment was designed to test the difference in performance of the proposed method against $10$ state-of-the-art algorithms, contrasting instance-level methods and bag-level methods.
+The experimental environment was designed to test the difference in performance of the proposed method against $11$ state-of-the-art algorithms, contrasting instance-level methods and bag-level methods.
 Instance-level methods include MIOptimalBall, MIBoost, MISVM, MIDD, and MIWrapper.
@@
 Bag-level methods all obtain scores between $0.7$ and $0.75$ indicating a high true positive rate and a low false positive rate, which is reflected by the precision and recall results.
-Figure~\ref{fig:BonfDunnauc} and Table~\ref{tab:statauc} show that MIRSVM performs significantly better than $6$ out of the $10$ competing algorithms.
+Figure~\ref{fig:BonfDunnauc} and Table~\ref{tab:statauc} show that MIRSVM performs significantly better than $6$ out of the $11$ competing algorithms.
 Nemenyi's procedure indicates that significant differences exist between MIRSVM and all algorithms except MISMO, TLC, Bagging, and Stacking.

### 2017-06-27 current_code/testing.m

@@ -1,7 +1,7 @@
 warning off;
-name = 'musk1/';
-path = './data/midata/CVSets/';
-num = 10; C = 1000; param = 4.5; randomnum = 2;
+name = 'elephant/';
+path = '/Users/gabriellamelki/Google Drive/data/midata/CVSets/';
+num = 10; C = 1000; param = 4.5; randomnum = 6;
 
 TP = zeros(num,1); TN = zeros(num,1); FP = zeros(num,1); FN = zeros(num,1);
 Time = zeros(num,1);
@@ -50,7 +50,7 @@ FP = sum(FP);
 FN = sum(FN);
 numb_data = (TP + TN + FP + FN);
 
-acc = (TP+TN)/numb_data;
+acc = (TP+TN)/numb_data
 precision = TP/(TP+FP);
 recall = TP/(TP+FN);
 EA = (TP+FN)*(TP+FP) + (FP + TN)*(FN + TN);

### 2017-07-03 ArticleRevision/article/article.tex
Modified SVM-MI background to include miGraph + other
> added miGraph to experimental environment
> added small description of miGraph in background (SVM background)

@@
 where $\phi\left(\cdot\right)$ represents a function mapping from the original feature space to a higher dimensional space.
-This kernel mapping is helpful when solving the dual SVM optimization problem shown in Equation~\eqref{eq:dualsvm}.
+This kernel mapping is helpful when solving the dual SVM problem shown in Equation~\eqref{eq:dualsvm}.
 \begin{subequations}
@@
 
-\citet{Yang2006} presented an instance-based SVM that uses an asymmetric loss function that follows the SMI assumption.
-The idea behind this loss function is that positive and negative misclassification costs are different.
+\citet{Yang2006} presented an instance-based SVM that uses an asymmetric loss function in which positive and negative misclassification costs are different, ensuring all negative instances are correctly classified while minimizing false positives.
 A false negative instance in a positive bag might not cause an error on the bag label, but a false positive instance within a negative bag would lead to a misclassification error.
-The algorithm ensures all negative instances are correctly classified while minimizing false positives.
-
-One of the first bag-level approaches to the multi-instance SVM problem was proposed by \citet{Smola2002}, who defined a bag-level kernel.
-A bag-level kernel determines the similarity between two bags in a higher dimensional space and using such a kernel with the standard SVM problem, the margin can be optimized over bag classes without any modification to the SVM problem.~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance, without affecting the angles between vectors in the transformed space.
-Bag level kernels transform the bags into a single-instance representation which enables standard SVMs to be directly applied to multi-instance data~\citep{Herrera2016}.
+
+One of the first bag-level approaches to the multi-instance SVM problem was proposed by \citet{Smola2002}, who defined a bag-level kernel, which determines the similarity between two bags in a higher dimensional space.
+Using such a kernel, the margin can be optimized over bags without any modification to the SVM problem~\citep{Herrera2016}.~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance.
+
+\citet{Zhou2009} proposed miGraph, which implicitely constructs a graph by deriving affinity matrices while using a graph kernel.
+It assumes the instances are not independently and identically distributed because of the nature of MI data.
+Bags imply relationships among the instances within it, and miGraph was designed to exploit them.
 
@@
 Instance-level methods include MIOptimalBall, MIBoost, MISVM, MIDD, and MIWrapper.
-The bag-level methods include MISMO, SimpleMI, and TLC.
+Bag-level methods include MISMO, SimpleMI, miGraph, and TLC.
 The ensemble-based bag-space methods, Bagging and Stacking, were also used.
@@
 Experiments were run in an Intel i7-6700k CPU with 32GB RAM.
-MIRSVM was implemented in MATLAB while the referenced algorithms are available in the Java implementation of Weka.
+MIRSVM was implemented in MATLAB while the referenced algorithms are available in the Java implementation of Weka with the exception of miGraph which was made available \textbf{add website and footnote here} and tested in MATLAB.
 

### 2017-07-03 ArticleRevision/article/article.tex
Added website for miGraph in experimental environment

@@
 Experiments were run in an Intel i7-6700k CPU with 32GB RAM.
-MIRSVM was implemented in MATLAB while the referenced algorithms are available in the Java implementation of Weka with the exception of miGraph which was made available \textbf{add website and footnote here} and tested in MATLAB.
+MIRSVM was implemented in MATLAB while the referenced algorithms are available in the Java implementation of Weka with the exception of miGraph which was made available by Zhou et al.\footnote{http://lamda.nju.edu.cn/code\_miGraph.ashx} and tested in MATLAB.
 

### 2017-07-03 WekaTesting/FormatOutputMI.m
Added write csv for keep software

@@ -5,6 +5,7 @@ path_data = '/Users/gabriellamelki/Google Drive/data/midata/libsvm/';
 Datasets = dir([path_data '*']);
 Datasets(1:2,:) = []; Datasets = {Datasets.name}';
 path = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/output/';
+keel_path = '/Users/gabriellamelki/Documents/EclipseWorkspace/evaluation/data/';
 %names = {'miGraph'};
 names = {'MIRSVM','miGraph','MIBoost','MIOptimalBall','MIDD','MIWrapper','MISMO','MISVM','SimpleMI','TLC','Bagging','Stacking'};
 % metrics
@@ -69,6 +70,7 @@ for m = 1:length(metrics)   % for each metric, build a table
         eval(sprintf('T.%s=results;',folder));
     end
     writetable(T,[path metrics{m} '.csv']);
+    writetable(T(:,2:end),[keel_path metrics{m} '.csv'],'WriteVariableNames',false);
     %excel = table2array(T(1:end,2:end));
     %xlswrite([path 'Results_new.xlsx'],metrics{m},'B2:L16');
     clearvars T; T = table; T.Datasets = Datasets(ind);

### 2017-07-03 post_hoc_script.m
Updated post hoc script
> added option for setting time as min for best value
> ran and updated tex files

@@ -9,6 +9,7 @@ else
 end
 
 metrics = {'Accuracy','Precision','Recall','Kappa','AUC','Time'};
+%metrics = {'Time'};
 num_metrics = length(metrics);
 alpha = 0.1;
 % initialize using Accuracy.csv
@@ -27,7 +28,17 @@ for m = 1:num_metrics
     T = readtable([path_in metrics{m} '.csv']);
     data = T{:,2:end};
     disp(['Analyzing ' metrics{m}]);
-    [avg_ranks,chi_statistics] = avg_rank(-data);
+    
+    if strmatch('Time',metrics{m})
+        rank_val = 'time';
+        format = '%-1.1f';
+    else
+        data = -data;
+        rank_val = 'yes';
+        format = '%-1.4f';
+    end
+    
+    [avg_ranks,chi_statistics] = avg_rank(data);
     ranks(m,:) = avg_ranks;
     max_rank = round(max(avg_ranks))+1;
     %[stats,headers] = wilcoxon(data,alpha);
@@ -37,7 +48,20 @@ for m = 1:num_metrics
     data(end+1,:) = avg_ranks;
     
     % create latex table
-    matrix2latex_metrics(data, [path_out [metrics{m} '.tex']], 'rowLabels', latex_data_rows, 'columnLabels', algorithms, 'alignment', 'c', 'format', '%-1.4f', 'rank', 'yes');
+    matrix2latex_metrics(data, [path_out [metrics{m} '.tex']], 'rowLabels', latex_data_rows, 'columnLabels', algorithms, 'alignment', 'c', 'format', format, 'rank', rank_val);
     % create bonferroni-dunn figure
     bonferroni_dunn_tikz([path_out [metrics{m} '_Fig.tex']],avg_ranks,1,num_algorithms,algorithms,max_rank);
 end
+
+% create latex table
+disp('Analyzing Meta-Ranks');
+[avg_ranks,~] = avg_rank(ranks);
+ranks(end+1,:) = mean(ranks);
+ranks(end+1,:) = avg_ranks;
+max_rank = round(max(avg_ranks))+1;
+rank_val = 'time';
+format = '%-1.4f';
+metrics{end+1} = 'Average'; metrics{end+1} = 'Rank'; 
+
[…]

### 2017-07-03 ArticleRevision/article/article.tex
Added results to article
TODO: still need to do the statistical analysis in Keel

@@
 \caption{Accuracy}\label{tab:accResults}
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-suramin &0.6000 &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.2308 &0.6923 &0.6750 &\textbf{0.7564} &  \\
-eastWest &\textbf{0.8000} &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.6375 &0.5000 &0.5000 &0.6375 &0.4500 &  \\
-westEast &0.6500 &0.5000 &0.3750 &0.4500 &0.5000 &\textbf{0.7375} &0.4625 &0.5000 &0.5000 &0.6875 &0.6375 &  \\
-musk1 &\textbf{0.9022} &0.5109 &0.7717 &0.8804 &0.5109 &0.7826 &0.8043 &0.5109 &0.8587 &0.8804 &0.8587 &  \\
-musk2 &\textbf{0.8146} &0.6139 &0.7723 &0.7228 &0.6139 &0.7030 &0.7129 &0.6139 &0.6238 &0.7129 &0.6733 &  \\
-webmining &\textbf{0.8500} &0.8142 &0.7699 &0.8142 &0.8142 &0.8407 &0.6903 &0.8142 &0.8142 &0.7876 &0.8053 &  \\
-trx &0.8825 &0.8705 &\textbf{0.9016} &0.8808 &0.8705 &0.8705 &0.8705 &0.8705 &0.8756 &0.8964 &0.8860 &  \\
-mutagenesis-atoms &0.7714 &0.6649 &0.6436 &0.7074 &0.6649 &0.6915 &0.6649 &0.6649 &0.7766 &\textbf{0.8032} &0.7606 &  \\
-mutagenesis-bonds &0.8252 &0.6649 &0.6915 &0.7713 &0.6649 &0.7979 &0.6649 &0.6649 &0.8351 &\textbf{0.8830} &0.8564 &  \\
-mutagenesis-chains &0.8411 &0.6649 &0.6702 &0.7766 &0.6649 &0.8351 &0.6649 &0.6649 &0.8404 &\textbf{0.8457} &0.8351 &  \\
-tiger &\textbf{0.7750} &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &0.7700 &0.7250 &  \\
-elephant &0.8300 &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &\textbf{0.8500} &0.8250 &  \\
-fox &\textbf{0.6550} &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.5900 &0.5000 &0.6450 &0.6200 &0.6500 &  \\
-component &0.9366 &0.8649 &0.8696 &0.8780 &0.8649 &0.8968 &0.8703 &0.8649 &0.9358 &\textbf{0.9371} &0.9355 &  \\
-function &0.9523 &0.9155 &0.9138 &0.9193 &0.9155 &0.9376 &0.9195 &0.9155 &0.9649 &\textbf{0.9655} &0.9647 &  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Average &\textbf{0.8057} &0.6390 &0.6886 &0.7279 &0.6390 &0.7724 &0.7072 &0.6210 &0.7552 &0.7968 &0.7746 &  \\
-Ranks &\textbf{2.4000} &8.8000 &7.2667 &6.0333 &8.8000 &4.8000 &7.0667 &9.0000 &4.7333 &2.7667 &4.3333 &  \\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+suramin &0.7000 &\textbf{0.8462} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4615 &  \\
+eastWest &\textbf{0.8000} &0.7000 &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.5625 &0.5000 &0.6000 &0.6000 &0.4500 &  \\
+westEast &0.7000 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.9649} &0.6375 &  \\
+musk1 &\textbf{0.9022} &0.8152 &0.5109 &0.7717 &0.8804 &0.5109 &0.7826 &0.7609 &0.5109 &0.8587 &0.8142 &0.8587 &  \\
+musk2 &0.8218 &0.7426 &0.6139 &0.7723 &0.7228 &0.6139 &0.7030 &0.7129 &0.6139 &0.6238 &\textbf{0.8756} &0.6733 &  \\
+webmining &0.8500 &0.8142 &0.8142 &0.7699 &0.8142 &0.8142 &0.8407 &0.6903 &0.8142 &0.8142 &\textbf{0.9358} &0.8053 &  \\
+trx &0.8825 &0.8964 &0.8705 &\textbf{0.9016} &0.8808 &0.8705 &0.8705 &0.8705 &0.8705 &0.8756 &0.6450 &0.8860 &  \\
+mutagenesis-atoms &0.7714 &0.7606 &0.6649 &0.6436 &0.7074 &0.6649 &0.6915 &0.6649 &0.6649 &\textbf{0.7766} &\textbf{0.7766} &0.7606 &  \\
+mutagenesis-bonds &0.8252 &0.7872 &0.6649 &0.6915 &0.7713 &0.6649 &0.7979 &0.6649 &0.6649 &0.8351 &0.8351 &\textbf{0.8564} &  \\
+mutagenesis-chains &\textbf{0.8411} &0.7926 &0.6649 &0.6702 &0.7766 &0.6649 &0.8351 &0.6649 &0.6649 &0.8404 &0.8404 &0.8351 &  \\
+tiger &0.7750 &0.7950 &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &\textbf{0.8000} &0.7250 &  \\
+elephant &\textbf{0.8300} &\textbf{0.8300} &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &0.5625 &0.8250 &  \\
+fox &0.6550 &0.6300 &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.4750 &0.5000 &0.6450 &\textbf{0.8587} &0.6500 &  \\
+component &\textbf{0.9366} &0.9153 &0.8649 &0.8696 &0.8780 &0.8649 &0.8968 &0.8703 &0.8649 &0.9358 &0.6000 &0.9355 &  \\
+function &0.9523 &0.9405 &0.9155 &0.9138 &0.9193 &0.9155 &0.9376 &0.9195 &0.9155 &\textbf{0.9649} &0.6238 &0.9647 &  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Average &\textbf{0.8162} &0.8010 &0.6390 &0.6886 &0.7279 &0.6390 &0.7724 &0.6883 &0.6390 &0.7598 &0.7598 &0.7550 &  \\
+Rank &\textbf{2.4333} &3.8333 &9.6000 &7.8000 &6.5667 &9.6000 &5.2000 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
 \noalign{\smallskip}\hline
@@
 \resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
-\draw (1,0) -- (10,0);
-\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
+\draw (1,0) -- (11,0);
+\foreach \x in {1,2,3,4,5,6,7,8,9,10,11} {
 \draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
-\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
+\ifthenelse{\x < 11}{\draw (\x+.5, 0) -- ++(0,.03);}{}
 }
-
-\coordinate (c0) at (2.4,0);
-\coordinate (c1) at (8.8,0);
-\coordinate (c2) at (7.2667,0);
-\coordinate (c3) at (6.0333,0);
-\coordinate (c4) at (8.8,0);
-\coordinate (c5) at (4.8,0);
-\coordinate (c6) at (7.0667,0);
-\coordinate (c7) at (9,0);
-\coordinate (c8) at (4.7333,0);
-\coordinate (c9) at (2.7667,0);
-\coordinate (c10) at (4.3333,0);
+\coordinate (c0) at (2.4333,0);
+\coordinate (c1) at (3.8333,0);
+\coordinate (c2) at (9.6,0);
+\coordinate (c3) at (7.8,0);
+\coordinate (c4) at (6.5667,0);
+\coordinate (c5) at (9.6,0);
+\coordinate (c6) at (5.2,0);
+\coordinate (c7) at (8.5667,0);
+\coordinate (c8) at (9.6,0);
+\coordinate (c9) at (4.7,0);
+\coordinate (c10) at (4.8667,0);
+\coordinate (c11) at (5.2333,0);
 
 \node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l6) at (c6) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l8) at (c8) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l9) at (c9) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l10) at (c10) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (2.4,-0.1) rectangle (5.5196,0.1);
-
-\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
+\node (l1) at (c1) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [above left=.22cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [above left=.22cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (2.4333,-0.1) rectangle (5.8733,0.1);
+
+\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
 \draw (l\x) -| (c\x);
@@
 \caption{Precision}\label{tab:preResults}
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-suramin &0.6385 &\textbf{1.0000} &\textbf{1.0000} &0.2857 &\textbf{1.0000} &\textbf{1.0000} &0.5000 &0.0000 &0.6667 &0.7333 &0.7116 &  \\
-eastWest &0.7143 &0.5000 &\textbf{0.8750} &0.5882 &0.5000 &0.7429 &0.8667 &0.5000 &0.5000 &0.6667 &0.4444 &  \\
-westEast &0.6300 &0.5000 &0.2727 &0.4600 &0.5000 &\textbf{0.6939} &0.3846 &0.5000 &0.5000 &0.6364 &0.6038 &  \\
-musk1 &0.8519 &\textbf{1.0000} &0.9286 &0.9048 &\textbf{1.0000} &0.8049 &0.8857 &\textbf{1.0000} &0.8478 &0.9250 &0.8478 &  \\
-musk2 &0.7167 &0.6139 &\textbf{0.7826} &0.7576 &0.6139 &0.7424 &0.7538 &0.6139 &0.7400 &0.7797 &0.7164 &  \\
-webmining &0.7500 &0.8142 &0.8173 &0.8142 &0.8142 &0.8936 &\textbf{1.0000} &0.8142 &0.8817 &0.8469 &0.8500 &  \\
-trx &0.6500 &0.8705 &\textbf{0.9306} &0.9191 &0.8705 &0.8705 &0.8705 &0.8705 &0.9138 &0.8936 &0.9011 &  \\
-mutagenesis-atoms &0.7872 &\textbf{1.0000} &0.4630 &0.6111 &\textbf{1.0000} &0.5439 &\textbf{1.0000} &\textbf{1.0000} &0.7059 &0.7321 &0.6667 &  \\
-mutagenesis-bonds &0.8468 &\textbf{1.0000} &0.5385 &0.7500 &\textbf{1.0000} &0.6812 &\textbf{1.0000} &\textbf{1.0000} &0.7857 &0.8596 &0.8333 &  \\
-mutagenesis-chains &0.8571 &\textbf{1.0000} &0.5091 &0.7059 &\textbf{1.0000} &0.7759 &\textbf{1.0000} &\textbf{1.0000} &0.7705 &0.7742 &0.7581 &  \\
-tiger &0.7365 &0.5000 &0.5000 &0.6944 &0.5000 &0.7444 &0.7802 &0.5000 &0.6514 &\textbf{0.7935} &0.7320 &  \\
-elephant &0.8576 &0.5000 &0.5000 &0.7959 &0.5000 &0.8444 &0.7679 &0.5000 &0.8000 &\textbf{0.8804} &0.8283 &  \\
-fox &0.6040 &0.5000 &0.5000 &0.5833 &0.5000 &0.5287 &0.6216 &0.5000 &\textbf{0.6747} &0.6304 &0.6705 &  \\
-component &\textbf{0.9866} &0.8649 &0.8778 &0.8902 &0.8649 &0.8958 &0.8696 &0.8649 &0.9462 &0.9431 &0.9449 &  \\
-function &0.8459 &0.9155 &0.9202 &0.9317 &0.9155 &0.9376 &0.9197 &0.9155 &\textbf{0.9729} &0.9720 &0.9726 &  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Average &0.7649 &0.7719 &0.6944 &0.7128 &0.7719 &0.7800 &\textbf{0.8147} &0.7053 &0.7572 &0.8045 &0.7654 &  \\
-Ranks &6.0667 &6.7333 &6.7333 &6.7667 &6.7333 &5.3667 &5.1000 &7.3000 &5.5000 &\textbf{3.9333} &5.7667 &  \\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+suramin &0.6383 &0.7778 &\textbf{1.0000} &\textbf{1.0000} &0.2857 &\textbf{1.0000} &\textbf{1.0000} &0.5000 &\textbf{1.0000} &0.6429 &0.6514 &0.4000 &  \\
+eastWest &0.7143 &0.7000 &0.5000 &0.8750 &0.5882 &0.5000 &0.7429 &\textbf{1.0000} &0.5000 &0.6053 &0.6053 &0.4444 &  \\
+westEast &0.6700 &0.7273 &0.5000 &0.2727 &0.4600 &0.5000 &0.6939 &0.3600 &0.5000 &0.5581 &\textbf{0.9729} &0.6038 &  \\
+musk1 &0.8519 &0.7778 &\textbf{1.0000} &0.9286 &0.9048 &\textbf{1.0000} &0.8049 &0.8108 &\textbf{1.0000} &0.8478 &0.8817 &0.8478 &  \\
+musk2 &0.7059 &0.7826 &0.6139 &0.7826 &0.7576 &0.6139 &0.7424 &0.7538 &0.6139 &0.7400 &\textbf{0.9138} &0.7164 &  \\
+webmining &0.7500 &\textbf{1.0000} &0.8142 &0.8173 &0.8142 &0.8142 &0.8936 &\textbf{1.0000} &0.8142 &0.8817 &0.9462 &0.8500 &  \\
+trx &0.6500 &0.8571 &0.8705 &\textbf{0.9306} &0.9191 &0.8705 &0.8705 &0.8705 &0.8705 &0.9138 &0.6747 &0.9011 &  \\
+mutagenesis-atoms &0.7872 &0.7985 &\textbf{1.0000} &0.4630 &0.6111 &\textbf{1.0000} &0.5439 &\textbf{1.0000} &\textbf{1.0000} &0.7059 &0.7059 &0.6667 &  \\
+mutagenesis-bonds &0.8468 &0.8195 &\textbf{1.0000} &0.5385 &0.7500 &\textbf{1.0000} &0.6812 &\textbf{1.0000} &\textbf{1.0000} &0.7857 &0.7857 &0.8333 &  \\
+mutagenesis-chains &0.8571 &0.8116 &\textbf{1.0000} &0.5091 &0.7059 &\textbf{1.0000} &0.7759 &\textbf{1.0000} &\textbf{1.0000} &0.7705 &0.7705 &0.7581 &  \\
+tiger &0.7365 &0.7323 &0.5000 &0.5000 &0.6944 &0.5000 &0.7444 &0.7802 &0.5000 &0.6514 &\textbf{0.8000} &0.7320 &  \\
+elephant &0.8576 &\textbf{0.8750} &0.5000 &0.5000 &0.7959 &0.5000 &0.8444 &0.7679 &0.5000 &0.8000 &0.5581 &0.8283 &  \\
+fox &0.6040 &0.6275 &0.5000 &0.5000 &0.5833 &0.5000 &0.5287 &0.4854 &0.5000 &0.6747 &\textbf{0.8478} &0.6705 &  \\
+component &\textbf{0.9866} &0.7782 &0.8649 &0.8778 &0.8902 &0.8649 &0.8958 &0.8696 &0.8649 &0.9462 &0.6429 &0.9449 &  \\
+function &0.8459 &0.6775 &0.9155 &0.9202 &0.9317 &0.9155 &0.9376 &0.9197 &0.9155 &\textbf{0.9729} &0.7400 &0.9726 &  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Average &0.7668 &0.7828 &0.7719 &0.6944 &0.7128 &0.7719 &0.7800 &\textbf{0.8079} &0.7719 &0.7665 &0.7665 &0.7447 &  \\
+Rank &6.3333 &6.0000 &7.0333 &7.2667 &7.3000 &7.0333 &\textbf{5.7333} &5.8000 &7.0333 &5.7667 &6.2000 &6.5000 &  \\
 \noalign{\smallskip}\hline
@@
 \resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
-\draw (1,0) -- (10,0);
-\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
+\draw (3,0) -- (12,0);
+\foreach \x in {3,4,5,6,7,8,9,10,11,12} {
 \draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
-\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
+\ifthenelse{\x < 12}{\draw (\x+.5, 0) -- ++(0,.03);}{}
 }
 
-\coordinate (c0) at (6.0667,0);
-\coordinate (c1) at (6.7333,0);
-\coordinate (c2) at (6.7333,0);
-\coordinate (c3) at (6.7667,0);
-\coordinate (c4) at (6.7333,0);
-\coordinate (c5) at (5.3667,0);
-\coordinate (c6) at (5.1,0);
-\coordinate (c7) at (7.3,0);
-\coordinate (c8) at (5.5,0);
-\coordinate (c9) at (3.9333,0);
-\coordinate (c10) at (5.7667,0);
-
-\node (l0) at (c0) [above left=.3cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [below right=.2cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l2) at (c2) [above right=.45cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l3) at (c3) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l4) at (c4) [above left=.45cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l5) at (c5) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l6) at (c6) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l7) at (c7) [above right=.2cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l8) at (c8) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l9) at (c9) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l10) at (c10) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (3.9333,-0.1) rectangle (7.0529,0.1);
-
-\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
+\coordinate (c0) at (6.3333,0);
+\coordinate (c1) at (6,0);
+\coordinate (c2) at (7.0333,0);
+\coordinate (c3) at (7.2667,0);
+\coordinate (c4) at (7.3,0);
+\coordinate (c5) at (7.0333,0);
+\coordinate (c6) at (5.7333,0);
+\coordinate (c7) at (5.8,0);
+\coordinate (c8) at (7.0333,0);
+\coordinate (c9) at (5.7667,0);
+\coordinate (c10) at (6.2,0);
+\coordinate (c11) at (6.5,0);
+
+\node (l0) at (c0) [above left=.38cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
+\node (l1) at (c1) [below left=.2cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [below right=.17cm and 0cm, align=left,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above right=.35cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [above left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [above right=.5cm and 0cm, align=left,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below right=.25cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (5.7333,-0.1) rectangle (9.17,0.1);
+
+\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
 \draw (l\x) -| (c\x);};
@@
 \captionof{table}{Recall}\label{tab:recResults}
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}cccccccccccc}
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-suramin &\textbf{1.0000} &0.0000 &0.4500 &0.1000 &0.0000 &0.4500 &0.5000 &0.0000 &0.6667 &0.5500 &0.9125 &  \\
-eastWest &\textbf{1.0000} &0.7000 &0.5250 &0.7500 &0.7000 &0.6500 &0.3250 &\textbf{1.0000} &0.5000 &0.5500 &0.4000 &  \\
-westEast &0.9000 &0.9000 &0.1500 &0.5750 &0.9000 &0.8500 &0.1250 &\textbf{1.0000} &0.5000 &0.8750 &0.8000 &  \\
-musk1 &\textbf{0.9787} &0.0000 &0.5778 &0.8444 &0.0000 &0.7333 &0.6889 &0.0000 &0.8667 &0.8222 &0.8667 &  \\
-musk2 &0.9250 &\textbf{1.0000} &0.8710 &0.8065 &\textbf{1.0000} &0.7903 &0.7903 &\textbf{1.0000} &0.5968 &0.7419 &0.7742 &  \\
-webmining &0.2857 &\textbf{1.0000} &0.9239 &\textbf{1.0000} &\textbf{1.0000} &0.9130 &0.6196 &\textbf{1.0000} &0.8913 &0.9022 &0.9239 &  \\
-trx &0.4833 &\textbf{1.0000} &0.9583 &0.9464 &\textbf{1.0000} &\textbf{1.0000} &\textbf{1.0000} &\textbf{1.0000} &0.9464 &\textbf{1.0000} &0.9762 &  \\
-mutagenesis-atoms &\textbf{0.8880} &0.0000 &0.3968 &0.3492 &0.0000 &0.4921 &0.0000 &0.0000 &0.5714 &0.6508 &0.5714 &  \\
-mutagenesis-bonds &\textbf{0.8960} &0.0000 &0.5556 &0.4762 &0.0000 &0.7460 &0.0000 &0.0000 &0.6984 &0.7778 &0.7143 &  \\
-mutagenesis-chains &\textbf{0.9120} &0.0000 &0.4444 &0.5714 &0.0000 &0.7143 &0.0000 &0.0000 &0.7460 &0.7619 &0.7460 &  \\
-tiger &0.8700 &0.5000 &\textbf{1.0000} &0.7500 &0.5000 &0.6700 &0.7100 &\textbf{1.0000} &0.7100 &0.7300 &0.7100 &  \\
-elephant &0.9100 &0.6000 &\textbf{1.0000} &0.7800 &0.6000 &0.7600 &0.8600 &\textbf{1.0000} &0.8000 &0.8100 &0.8200 &  \\
-fox &0.9000 &0.7000 &\textbf{1.0000} &0.5600 &0.7000 &0.4600 &0.4600 &\textbf{1.0000} &0.5600 &0.5800 &0.5900 &  \\
-component &0.5839 &\textbf{1.0000} &0.9867 &0.9797 &\textbf{1.0000} &0.9967 &\textbf{1.0000} &\textbf{1.0000} &0.9815 &0.9867 &0.9826 &  \\
-function &0.5327 &\textbf{1.0000} &0.9919 &0.9840 &\textbf{1.0000} &0.9983 &0.9994 &\textbf{1.0000} &0.9892 &0.9908 &0.9894 &  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Average &\textbf{0.8044} &0.5600 &0.7221 &0.6982 &0.5600 &0.7483 &0.5385 &0.6667 &0.7350 &0.7820 &0.7851 &  \\
-Ranks &\textbf{4.4333} &6.2667 &5.8000 &6.7667 &6.2667 &6.2667 &7.4333 &4.5333 &7.0333 &5.3333 &5.8667 &  \\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{l@{\extracolsep{\fill}}ccccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+suramin &\textbf{1.0000} &\textbf{1.0000} &0.0000 &0.4500 &0.1000 &0.0000 &0.4500 &0.5000 &0.0000 &0.4500 &0.7100 &0.3333 &  \\
+eastWest &\textbf{1.0000} &0.7000 &0.7000 &0.5250 &0.7500 &0.7000 &0.6500 &0.1250 &\textbf{1.0000} &0.5750 &0.5750 &0.4000 &  \\
+westEast &0.8000 &0.8000 &0.9000 &0.1500 &0.5750 &0.9000 &0.8500 &0.2250 &\textbf{1.0000} &0.6000 &0.9892 &0.8000 &  \\
+musk1 &\textbf{0.9787} &0.8936 &0.0000 &0.5778 &0.8444 &0.0000 &0.7333 &0.6667 &0.0000 &0.8667 &0.8913 &0.8667 &  \\
+musk2 &0.9231 &0.4615 &\textbf{1.0000} &0.8710 &0.8065 &\textbf{1.0000} &0.7903 &0.7903 &\textbf{1.0000} &0.5968 &0.9464 &0.7742 &  \\
+webmining &0.2857 &0.0000 &\textbf{1.0000} &0.9239 &\textbf{1.0000} &\textbf{1.0000} &0.9130 &0.6196 &\textbf{1.0000} &0.8913 &0.9815 &0.9239 &  \\
+trx &0.4833 &0.2400 &\textbf{1.0000} &0.9583 &0.9464 &\textbf{1.0000} &\textbf{1.0000} &\textbf{1.0000} &\textbf{1.0000} &0.9464 &0.5600 &0.9762 &  \\
+mutagenesis-atoms &\textbf{0.8880} &0.8560 &0.0000 &0.3968 &0.3492 &0.0000 &0.4921 &0.0000 &0.0000 &0.5714 &0.5714 &0.5714 &  \\
+mutagenesis-bonds &\textbf{0.8960} &0.8720 &0.0000 &0.5556 &0.4762 &0.0000 &0.7460 &0.0000 &0.0000 &0.6984 &0.6984 &0.7143 &  \\
+mutagenesis-chains &\textbf{0.9120} &0.8960 &0.0000 &0.4444 &0.5714 &0.0000 &0.7143 &0.0000 &0.0000 &0.7460 &0.7460 &0.7460 &  \\
+tiger &0.8700 &0.9300 &0.5000 &\textbf{1.0000} &0.7500 &0.5000 &0.6700 &0.7100 &\textbf{1.0000} &0.7100 &0.8000 &0.7100 &  \\
+elephant &0.9100 &0.7700 &0.6000 &\textbf{1.0000} &0.7800 &0.6000 &0.7600 &0.8600 &\textbf{1.0000} &0.8000 &0.6000 &0.8200 &  \\
+fox &0.9000 &0.6400 &0.7000 &\textbf{1.0000} &0.5600 &0.7000 &0.4600 &0.8300 &\textbf{1.0000} &0.5600 &0.8667 &0.5900 &  \\
+component &0.5839 &0.5225 &\textbf{1.0000} &0.9867 &0.9797 &\textbf{1.0000} &0.9967 &\textbf{1.0000} &\textbf{1.0000} &0.9815 &0.4500 &0.9826 &  \\
+function &0.5327 &0.5643 &\textbf{1.0000} &0.9919 &0.9840 &\textbf{1.0000} &0.9983 &0.9994 &\textbf{1.0000} &0.9892 &0.5968 &0.9894 &  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Average &\textbf{0.7976} &0.6764 &0.5600 &0.7221 &0.6982 &0.5600 &0.7483 &0.5551 &0.6667 &0.7322 &0.7322 &0.7465 &  \\
+Rank &4.8667 &6.5667 &6.8667 &6.3333 &7.3667 &6.8667 &6.7000 &7.4333 &\textbf{4.8333} &7.3667 &6.0667 &6.7333 &  \\
 \noalign{\smallskip}\hline
@@
 \resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
-\draw (1,0) -- (10,0);
-\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
+\draw (2,0) -- (11,0);
+\foreach \x in {2,3,4,5,6,7,8,9,10,11,11} {
 \draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
-\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
+\ifthenelse{\x < 11}{\draw (\x+.5, 0) -- ++(0,.03);}{}
 }
 
-\coordinate (c0) at (4.4333,0);
-\coordinate (c1) at (6.2667,0);
-\coordinate (c2) at (5.8,0);
-\coordinate (c3) at (6.7667,0);
-\coordinate (c4) at (6.2667,0);
-\coordinate (c5) at (6.2667,0);
-\coordinate (c6) at (7.4333,0);
-\coordinate (c7) at (4.5333,0);
-\coordinate (c8) at (7.0333,0);
-\coordinate (c9) at (5.3333,0);
-\coordinate (c10) at (5.8667,0);
+\coordinate (c0) at (4.8667,0);
+\coordinate (c1) at (6.5667,0);
+\coordinate (c2) at (6.8667,0);
+\coordinate (c3) at (6.3333,0);
+\coordinate (c4) at (7.3667,0);
+\coordinate (c5) at (6.8667,0);
+\coordinate (c6) at (6.7,0);
+\coordinate (c7) at (7.4333,0);
+\coordinate (c8) at (4.8333,0);
+\coordinate (c9) at (7.3667,0);
+\coordinate (c10) at (6.0667,0);
+\coordinate (c11) at (6.7333,0);
 
 \node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l2) at (c2) [below left=.25cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l3) at (c3) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l4) at (c4) [above right=.35cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l5) at (c5) [above left=.35cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l6) at (c6) [below right=.025cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l7) at (c7) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l8) at (c8) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l9) at (c9) [above left=.3cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (4.4333,-0.1) rectangle (7.5529,0.1);
-
-\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
+\node (l1) at (c1) [below left=.2cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [above right=.25cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below right=.2cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above right=.35cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [above left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [below right=.025cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (4.8333,-0.1) rectangle (8.2733,0.1);
+
+\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
 \draw (l\x) -| (c\x);};
@@
 \caption{Cohen's Kappa Rate}\label{tab:kappaResults}
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-suramin &\textbf{0.6320} &0.0000 &0.4500 &-0.1500 &0.0000 &0.4500 &0.0000 &-0.5854 &0.3810 &0.3500 &0.5121 &  \\
-eastWest &\textbf{0.6000} &0.0000 &0.4500 &0.2250 &0.0000 &0.4250 &0.2750 &0.0000 &0.0000 &0.2750 &-0.1000 &  \\
-westEast &0.3500 &0.0000 &-0.2500 &-0.1000 &0.0000 &\textbf{0.4750} &-0.0750 &0.0000 &0.0000 &0.3750 &0.2750 &  \\
-musk1 &\textbf{0.8036} &0.0000 &0.5396 &0.7604 &0.0000 &0.5642 &0.6067 &0.0000 &0.7174 &0.7602 &0.7174 &  \\
-musk2 &\textbf{0.6263} &0.0000 &0.5031 &0.4039 &0.0000 &0.3613 &0.3856 &0.0000 &0.2492 &0.4029 &0.2940 &  \\
-webmining &0.3468 &0.0000 &0.0246 &0.0000 &0.0000 &\textbf{0.4535} &0.3771 &0.0000 &0.3744 &0.2112 &0.2458 &  \\
-trx &0.4542 &0.0000 &\textbf{0.5228} &0.4224 &0.0000 &0.0000 &0.0000 &0.0000 &0.3858 &0.3032 &0.3364 &  \\
-mutagenesis-atoms &0.5395 &0.0000 &0.1709 &0.2654 &0.0000 &0.2909 &0.0000 &0.0000 &0.4738 &\textbf{0.5458} &0.4431 &  \\
-mutagenesis-bonds &0.5699 &0.0000 &0.3131 &0.4356 &0.0000 &0.5569 &0.0000 &0.0000 &0.6195 &\textbf{0.7310} &0.6659 &  \\
-mutagenesis-chains &0.6303 &0.0000 &0.2359 &0.4738 &0.0000 &0.6225 &0.0000 &0.0000 &0.6391 &\textbf{0.6525} &0.6285 &  \\
-tiger &\textbf{0.5500} &0.0000 &0.0000 &0.4200 &0.0000 &0.4400 &0.5100 &0.0000 &0.3300 &0.5400 &0.4500 &  \\
-elephant &\textbf{0.7000} &0.0000 &0.0000 &0.5800 &0.0000 &0.6200 &0.6000 &0.0000 &0.6000 &\textbf{0.7000} &0.6500 &  \\
-fox &\textbf{0.3100} &0.0000 &0.0000 &0.1600 &0.0000 &0.0500 &0.1800 &0.0000 &0.2900 &0.2400 &0.3000 &  \\
-component &0.6644 &0.0000 &0.1613 &0.2836 &0.0000 &0.3656 &0.0675 &0.0000 &\textbf{0.6945} &0.6924 &0.6906 &  \\
-function &0.6292 &0.0000 &0.0966 &0.2801 &0.0000 &0.4083 &0.0933 &0.0000 &0.7529 &\textbf{0.7534} &0.7507 &  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Average &\textbf{0.5604} &0.0000 &0.2145 &0.2973 &0.0000 &0.4055 &0.2013 &-0.0390 &0.4338 &0.5022 &0.4573 &  \\
-Ranks &\textbf{2.2333} &9.2333 &6.5333 &6.1667 &9.2333 &4.7667 &6.7667 &9.4333 &4.4000 &3.0000 &4.2333 &  \\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+suramin &0.6320 &\textbf{0.6829} &0.0000 &0.4500 &-0.1500 &0.0000 &0.4500 &0.0000 &0.0000 &0.2000 &0.3300 &-0.0964 &  \\
+eastWest &\textbf{0.6000} &0.4000 &0.0000 &0.4500 &0.2250 &0.0000 &0.4250 &0.1250 &0.0000 &0.2000 &0.2000 &-0.1000 &  \\
+westEast &0.4000 &0.5000 &0.0000 &-0.2500 &-0.1000 &0.0000 &0.4750 &-0.1750 &0.0000 &0.1250 &\textbf{0.7529} &0.2750 &  \\
+musk1 &\textbf{0.8036} &0.6290 &0.0000 &0.5396 &0.7604 &0.0000 &0.5642 &0.5197 &0.0000 &0.7174 &0.3744 &0.7174 &  \\
+musk2 &\textbf{0.6540} &0.4123 &0.0000 &0.5031 &0.4039 &0.0000 &0.3613 &0.3856 &0.0000 &0.2492 &0.3858 &0.2940 &  \\
+webmining &0.3468 &0.0000 &0.0000 &0.0246 &0.0000 &0.0000 &0.4535 &0.3771 &0.0000 &0.3744 &\textbf{0.6945} &0.2458 &  \\
+trx &0.4542 &0.3375 &0.0000 &\textbf{0.5228} &0.4224 &0.0000 &0.0000 &0.0000 &0.0000 &0.3858 &0.2900 &0.3364 &  \\
+mutagenesis-atoms &\textbf{0.5395} &0.4431 &0.0000 &0.1709 &0.2654 &0.0000 &0.2909 &0.0000 &0.0000 &0.4738 &0.4738 &0.4431 &  \\
+mutagenesis-bonds &0.5699 &0.5070 &0.0000 &0.3131 &0.4356 &0.0000 &0.5569 &0.0000 &0.0000 &0.6195 &0.6195 &\textbf{0.6659} &  \\
+mutagenesis-chains &0.6303 &0.5094 &0.0000 &0.2359 &0.4738 &0.0000 &0.6225 &0.0000 &0.0000 &\textbf{0.6391} &\textbf{0.6391} &0.6285 &  \\
+tiger &0.5500 &0.5900 &0.0000 &0.0000 &0.4200 &0.0000 &0.4400 &0.5100 &0.0000 &0.3300 &\textbf{0.6000} &0.4500 &  \\
+elephant &\textbf{0.7000} &0.6600 &0.0000 &0.0000 &0.5800 &0.0000 &0.6200 &0.6000 &0.0000 &0.6000 &0.1250 &0.6500 &  \\
+fox &0.3100 &0.2600 &0.0000 &0.0000 &0.1600 &0.0000 &0.0500 &-0.0500 &0.0000 &0.2900 &\textbf{0.7174} &0.3000 &  \\
+component &0.6644 &0.5795 &0.0000 &0.1613 &0.2836 &0.0000 &0.3656 &0.0675 &0.0000 &\textbf{0.6945} &0.2000 &0.6906 &  \\
+function &0.6292 &0.5838 &0.0000 &0.0966 &0.2801 &0.0000 &0.4083 &0.0933 &0.0000 &\textbf{0.7529} &0.2492 &0.7507 &  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Average &\textbf{0.5656} &0.4730 &0.0000 &0.2145 &0.2973 &0.0000 &0.4056 &0.1635 &0.0000 &0.4434 &0.4434 &0.4167 &  \\
+Rank &\textbf{2.4000} &4.2333 &10.1667 &7.0000 &6.6000 &10.1667 &5.1667 &8.3667 &10.1667 &4.3333 &4.3333 &5.0667 &  \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
-\draw (1,0) -- (10,0);
-\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
+\draw (1,0) -- (11,0);
+\foreach \x in {1,2,3,4,5,6,7,8,9,10,11} {
 \draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
-\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
+\ifthenelse{\x < 11}{\draw (\x+.5, 0) -- ++(0,.03);}{}
 }
 
-\coordinate (c0) at (2.2333,0);
-\coordinate (c1) at (9.2333,0);
-\coordinate (c2) at (6.5333,0);
-\coordinate (c3) at (6.1667,0);
-\coordinate (c4) at (9.2333,0);
-\coordinate (c5) at (4.7667,0);
-\coordinate (c6) at (6.7667,0);
-\coordinate (c7) at (9.4333,0);
-\coordinate (c8) at (4.4,0);
-\coordinate (c9) at (3,0);
-\coordinate (c10) at (4.2333,0);
+\coordinate (c0) at (2.4,0);
+\coordinate (c1) at (4.2333,0);
+\coordinate (c2) at (10.1667,0);
+\coordinate (c3) at (7,0);
+\coordinate (c4) at (6.6,0);
+\coordinate (c5) at (10.1667,0);
+\coordinate (c6) at (5.1667,0);
+\coordinate (c7) at (8.3667,0);
+\coordinate (c8) at (10.1667,0);
+\coordinate (c9) at (4.3333,0);
+\coordinate (c10) at (4.3333,0);
+\coordinate (c11) at (5.0667,0);
 
 \node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l2) at (c2) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l8) at (c8) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l10) at (c10) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (2.2333,-0.1) rectangle (5.3529,0.1);
-
-\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
+\node (l1) at (c1) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (2.4,-0.1) rectangle (5.84,0.1);
+
+\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
 \draw (l\x) -| (c\x);
@@
 \caption{AUC}\label{tab:aucResults}
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccccc}
 \hline\noalign{\smallskip}
-Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
 \hline\noalign{\smallskip}
-suramin &0.5000 &0.5000 &\textbf{0.7250} &0.4250 &0.5000 &\textbf{0.7250} &0.5000 &0.2143 &0.6905 &0.6750 &0.6811 &  \\
-eastWest &\textbf{0.8000} &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.6375 &0.5000 &0.5000 &0.6375 &0.4500 &  \\
-westEast &0.6500 &0.5000 &0.3750 &0.4500 &0.5000 &\textbf{0.7375} &0.4625 &0.5000 &0.5000 &0.6875 &0.6375 &  \\
-musk1 &\textbf{0.9005} &0.5000 &0.7676 &0.8797 &0.5000 &0.7816 &0.8019 &0.5000 &0.8589 &0.8792 &0.8589 &  \\
-musk2 &\textbf{0.8351} &0.5000 &0.7432 &0.6981 &0.5000 &0.6772 &0.6900 &0.5000 &0.6317 &0.7043 &0.6435 &  \\
-webmining &0.6320 &0.5000 &0.5096 &0.5000 &0.5000 &0.7184 &\textbf{0.8098} &0.5000 &0.6837 &0.5939 &0.6048 &  \\
-trx &0.7243 &0.5000 &\textbf{0.7392} &0.6932 &0.5000 &0.5000 &0.5000 &0.5000 &0.6732 &0.6000 &0.6281 &  \\
-mutagenesis-atoms &0.7106 &0.5000 &0.5824 &0.6186 &0.5000 &0.6420 &0.5000 &0.5000 &0.7257 &\textbf{0.7654} &0.7137 &  \\
-mutagenesis-bonds &0.7856 &0.5000 &0.6578 &0.6981 &0.5000 &0.7850 &0.5000 &0.5000 &0.8012 &\textbf{0.8569} &0.8211 &  \\
-mutagenesis-chains &\textbf{0.8252} &0.5000 &0.6142 &0.7257 &0.5000 &0.8051 &0.5000 &0.5000 &0.8170 &0.8250 &0.8130 &  \\
-tiger &\textbf{0.7750} &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &0.7700 &0.7250 &  \\
-elephant &0.8200 &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &\textbf{0.8500} &0.8250 &  \\
-fox &\textbf{0.6550} &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.5900 &0.5000 &0.6450 &0.6200 &0.6500 &  \\
-component &0.7855 &0.5000 &0.5536 &0.6033 &0.5000 &0.6272 &0.5201 &0.5000 &\textbf{0.8123} &0.8030 &0.8081 &  \\
-function &0.7563 &0.5000 &0.5298 &0.6015 &0.5000 &0.6391 &0.5268 &0.5000 &\textbf{0.8456} &0.8408 &0.8434 &  \\
+suramin &0.6700 &\textbf{0.8333} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4524 &  \\
+eastWest &\textbf{0.8000} &0.7000 &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.5625 &0.5000 &0.6000 &0.6000 &0.4500 &  \\
+westEast &0.7000 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.8456} &0.6375 &  \\
+musk1 &\textbf{0.9005} &0.8135 &0.5000 &0.7676 &0.8797 &0.5000 &0.7816 &0.7589 &0.5000 &0.8589 &0.6837 &0.8589 &  \\
+musk2 &\textbf{0.8406} &0.6904 &0.5000 &0.7432 &0.6981 &0.5000 &0.6772 &0.6900 &0.5000 &0.6317 &0.6732 &0.6435 &  \\
+webmining &0.6320 &0.5000 &0.5000 &0.5096 &0.5000 &0.5000 &0.7184 &0.8098 &0.5000 &0.6837 &\textbf{0.8123} &0.6048 &  \\
+trx &0.7243 &0.6170 &0.5000 &\textbf{0.7392} &0.6932 &0.5000 &0.5000 &0.5000 &0.5000 &0.6732 &0.6450 &0.6281 &  \\
+mutagenesis-atoms &0.7106 &0.7137 &0.5000 &0.5824 &0.6186 &0.5000 &0.6420 &0.5000 &0.5000 &\textbf{0.7257} &\textbf{0.7257} &0.7137 &  \\
+mutagenesis-bonds &0.7856 &0.7455 &0.5000 &0.6578 &0.6981 &0.5000 &0.7850 &0.5000 &0.5000 &0.8012 &0.8012 &\textbf{0.8211} &  \\
+mutagenesis-chains &\textbf{0.8252} &0.7417 &0.5000 &0.6142 &0.7257 &0.5000 &0.8051 &0.5000 &0.5000 &0.8170 &0.8170 &0.8130 &  \\
+tiger &0.7750 &0.7950 &0.5000 &0.5000 &0.7100 &0.5000 &0.7200 &0.7550 &0.5000 &0.6650 &\textbf{0.8000} &0.7250 &  \\
+elephant &0.8200 &\textbf{0.8300} &0.5000 &0.5000 &0.7900 &0.5000 &0.8100 &0.8000 &0.5000 &0.8000 &0.5625 &0.8250 &  \\
+fox &0.6550 &0.6300 &0.5000 &0.5000 &0.5800 &0.5000 &0.5250 &0.4750 &0.5000 &0.6450 &\textbf{0.8589} &0.6500 &  \\
+component &0.7855 &0.7496 &0.5000 &0.5536 &0.6033 &0.5000 &0.6272 &0.5201 &0.5000 &\textbf{0.8123} &0.6000 &0.8081 &  \\
+function &0.7563 &0.7698 &0.5000 &0.5298 &0.6015 &0.5000 &0.6391 &0.5268 &0.5000 &\textbf{0.8456} &0.6317 &0.8434 &  \\
 \hline\noalign{\smallskip}\noalign{\smallskip}
-Average &\textbf{0.7437} &0.5000 &0.6015 &0.6390 &0.5000 &0.6937 &0.6062 &0.4810 &0.7100 &0.7406 &0.7135 &  \\
-Ranks &\textbf{2.7667} &9.2000 &6.4000 &6.2333 &9.2000 &4.7000 &6.6667 &9.4333 &4.2000 &3.1000 &4.1000 &  \\
+Average &\textbf{0.7587} &0.7253 &0.5000 &0.6015 &0.6390 &0.5000 &0.6937 &0.5874 &0.5000 &0.7148 &0.7148 &0.6983 &  \\
+Rank &\textbf{2.8667} &4.2333 &10.1667 &6.9333 &6.6000 &10.1667 &5.1000 &8.2333 &10.1667 &4.3333 &4.2667 &4.9333 &  \\
 \hline\noalign{\smallskip}
@@
 \resizebox{0.95\textwidth}{!}{\begin{tikzpicture}
-\draw (1,0) -- (10,0);
-\foreach \x in {1,2,3,4,5,6,7,8,9,10} {
+\draw (1,0) -- (11,0);
+\foreach \x in {1,2,3,4,5,6,7,8,9,10,11} {
 \draw (\x, 0) -- ++(0,.1) node [above,scale=0.7] {\tiny \x};
-\ifthenelse{\x < 10}{\draw (\x+.5, 0) -- ++(0,.03);}{}
+\ifthenelse{\x < 11}{\draw (\x+.5, 0) -- ++(0,.03);}{}
 }
 
-\coordinate (c0) at (2.7667,0);
-\coordinate (c1) at (9.2,0);
-\coordinate (c2) at (6.4,0);
-\coordinate (c3) at (6.2333,0);
-\coordinate (c4) at (9.2,0);
-\coordinate (c5) at (4.7,0);
-\coordinate (c6) at (6.6667,0);
-\coordinate (c7) at (9.4333,0);
-\coordinate (c8) at (4.2,0);
-\coordinate (c9) at (3.1,0);
-\coordinate (c10) at (4.1,0);
+\coordinate (c0) at (2.8667,0);
+\coordinate (c1) at (4.2333,0);
+\coordinate (c2) at (10.1667,0);
+\coordinate (c3) at (6.9333,0);
+\coordinate (c4) at (6.6,0);
+\coordinate (c5) at (10.1667,0);
+\coordinate (c6) at (5.1,0);
+\coordinate (c7) at (8.2333,0);
+\coordinate (c8) at (10.1667,0);
+\coordinate (c9) at (4.3333,0);
+\coordinate (c10) at (4.2667,0);
+\coordinate (c11) at (4.9333,0);
 
 \node (l0) at (c0) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l2) at (c2) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l4) at (c4) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l5) at (c5) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l8) at (c8) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l10) at (c10) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+\node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [above right=.05cm and 0cm, align=left,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below right=.05cm and 0cm, align=left,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
 
@@
 
-\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
+\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
 \draw (l\x) -| (c\x);
@@
 \caption{Run Time (seconds)}\label{tab:time}
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lrrrrrrrrrrrr}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lrrrrrrrrrrrrr}
 \hline\noalign{\smallskip}
-Datasets &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+Datasets &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
 \hline\noalign{\smallskip}
-suramin &\textbf{0.1} &8.8 &30.5 &7922.0 &9.5 &52.3 &333.9 &7.3 &35.5 &80.5 &1085.0 &  \\
-eastWest &\textbf{0.1} &5.5 &9.4 &217.1 &6.3 &14.8 &21.4 &5.8 &15.4 &14.2 &15.3 &  \\
-westEast &\textbf{0.1} &6.5 &7.8 &79.7 &6.5 &14.7 &99.5 &6.0 &16.6 &11.1 &10.8 &  \\
-musk1 &\textbf{0.4} &13.4 &32.1 &3542.6 &20.6 &89.7 &198.4 &11.1 &93.0 &474.3 &759.5 &  \\
-musk2 &\textbf{2.3} &97.3 &782.9 &126016.8 &208.3 &1799.4 &26093.5 &16.1 &1772.2 &14817.3 &16759.0 &  \\
-webmining &300.6 &45745.4 &60474.8 &47601.4 &68736.7 &51923.6 &105622.3 &2685.9 &86272.6 &667636.3 &\textbf{10.8} &  \\
-trx &61.8 &17.6 &682.3 &339110.5 &19.3 &8670.3 &134622.1 &\textbf{7.4} &2229.3 &17887.3 &592948.9 &  \\
-mutagenesis-atoms &9.8 &8.8 &99.2 &2623.0 &8.0 &55.0 &53.5 &\textbf{6.4} &44.0 &182.8 &153.9 &  \\
-mutagenesis-bonds &\textbf{8.3} &10.2 &310.2 &17538.7 &12.3 &457.4 &2794.8 &8.4 &131.1 &755.5 &853.1 &  \\
-mutagenesis-chains &19.3 &12.0 &525.0 &48982.7 &14.9 &2451.9 &6637.4 &\textbf{7.2} &224.4 &1449.6 &1619.0 &  \\
-tiger &29.5 &44.5 &157.8 &23220.5 &56.2 &208.0 &608.8 &\textbf{16.3} &183.0 &1276.7 &11927.9 &  \\
-elephant &47.7 &45.5 &243.9 &56456.3 &69.7 &232.1 &1114.3 &\textbf{20.8} &212.1 &1030.7 &1462.2 &  \\
-fox &81.0 &44.3 &206.1 &27773.8 &66.0 &369.6 &891.5 &\textbf{23.5} &243.3 &1332.5 &1729.1 &  \\
-component &231.7 &572.5 &228209.6 &96263.9 &1096.9 &629366.4 &37224.6 &\textbf{144.0} &9861.5 &74860.9 &79149.8 &  \\
-function &740.3 &935.5 &768458.0 &350124.7 &1887.5 &1052225.3 &565026.4 &\textbf{232.8} &12128.2 &138742.0 &185918.5 &  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Average &\textbf{102.2} &3171.2 &70682.0 &76498.2 &4814.6 &116528.7 &58756.2 &213.3 &7564.1 &61370.1 &59626.8 &  \\
-Rank &2.2 &2.8 &6.3 &10.1 &3.9 &7.5 &8.9 &\textbf{1.6} &6.3 &8.1 &8.4 &  \\
+suramin &\textbf{0.1} &19.7 &8.8 &30.5 &7922.0 &9.5 &52.3 &333.9 &7.2 &35.5 &183.0 &90.6 &  \\
+eastWest &\textbf{0.1} &3.0 &5.5 &9.4 &217.1 &6.3 &14.8 &21.4 &5.8 &15.4 &15.4 &15.2 &  \\
+westEast &\textbf{0.1} &2.8 &6.5 &7.8 &79.7 &6.5 &14.7 &99.5 &6.0 &16.6 &12128.1 &10.8 &  \\
+musk1 &\textbf{0.4} &56.8 &13.4 &32.1 &3542.6 &20.6 &89.7 &198.4 &11.1 &93.0 &86272.6 &759.5 &  \\
+musk2 &\textbf{2.3} &452.3 &97.3 &782.9 &126016.8 &208.3 &1799.4 &26093.5 &16.1 &1772.2 &2229.3 &16759.0 &  \\
+webmining &\textbf{300.6} &302.5 &45745.4 &60474.8 &47601.4 &68736.7 &51923.6 &105622.3 &2685.9 &86272.6 &9861.5 &592948.9 &  \\
+trx &61.8 &2206.4 &17.6 &682.3 &339110.5 &19.3 &8670.3 &134622.1 &\textbf{7.4} &2229.3 &243.3 &11927.9 &  \\
+mutagenesis-atoms &9.8 &193.1 &8.8 &99.2 &2623.0 &8.0 &55.0 &53.5 &\textbf{6.4} &44.0 &44.0 &153.9 &  \\
+mutagenesis-bonds &\textbf{8.3} &410.3 &10.2 &310.2 &17538.7 &12.3 &457.4 &2794.8 &8.4 &131.1 &131.1 &853.1 &  \\
+mutagenesis-chains &19.3 &513.4 &12.0 &525.0 &48982.7 &14.8 &2451.9 &6637.4 &\textbf{7.2} &224.4 &224.4 &1619.0 &  \\
+tiger &29.5 &302.8 &44.5 &157.8 &23220.5 &56.2 &208.0 &608.8 &\textbf{16.2} &183.0 &212.1 &1085.0 &  \\
+elephant &47.7 &306.7 &45.5 &243.9 &56456.2 &69.7 &232.1 &1114.3 &20.8 &212.1 &\textbf{16.6} &1462.2 &  \\
+fox &81.0 &303.1 &44.2 &206.1 &27773.8 &66.0 &369.6 &891.5 &\textbf{23.5} &243.3 &93.0 &1729.1 &  \\
+component &231.7 &3091.0 &572.5 &228209.6 &96263.9 &1096.9 &629366.4 &37224.6 &144.0 &9861.5 &\textbf{35.5} &79149.8 &  \\
+function &740.3 &8162.7 &935.5 &768458.0 &350124.7 &1887.5 &1052225.3 &565026.4 &\textbf{232.8} &12128.1 &1772.2 &185918.5 &  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Average &\textbf{102.2} &1088.4 &3171.2 &70682.0 &76498.2 &4814.6 &116528.7 &58756.2 &213.3 &7564.1 &7564.1 &59632.2 &  \\
+Rank &2.3 &6.2 &3.1 &7.2 &11.1 &4.3 &8.5 &10.1 &\textbf{1.9} &7.2 &6.5 &9.7 &  \\
 \hline\noalign{\smallskip}
@@
 \captionof{table}{Overall ranks comparison}\label{tab:metarank}
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccccc}
 \hline\noalign{\smallskip}
-Ranks &MIRSVM &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+Ranks &MIRSVM & miGraph & MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
 \midrule
-accuracy &\textbf{2.4000} &8.8000 &7.2667 &6.0333 &8.8000 &4.8000 &7.0667 &9.0000 &4.7333 &2.7667 &4.3333 &  \\
-precision &6.0667 &6.7333 &6.7333 &6.7667 &6.7333 &5.3667 &5.1000 &7.3000 &5.5000 &\textbf{3.9333} &5.7667 &  \\
-recall &\textbf{4.4333} &6.2667 &5.8000 &6.7667 &6.2667 &6.2667 &7.4333 &4.5333 &7.0333 &5.3333 &5.8667 &  \\
-kappa &\textbf{2.2333} &9.2333 &6.5333 &6.1667 &9.2333 &4.7667 &6.7667 &9.4333 &4.4000 &3.0000 &4.2333 &  \\
-auc &\textbf{2.7667} &9.2000 &6.4000 &6.2333 &9.2000 &4.7000 &6.6667 &9.4333 &4.2000 &3.1000 &4.1000 &  \\
-run-time &2.2000 &2.7667 &6.2667 &10.1333 &3.9000 &7.5333 &8.8667 &\textbf{1.6000} &6.2667 &8.0667 &8.4000 &  \\
+Accuracy &\textbf{2.4333} &3.8333 &9.6000 &7.8000 &6.5667 &9.6000 &5.2000 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
+Precision &6.3333 &6.0000 &7.0333 &7.2667 &7.3000 &7.0333 &\textbf{5.7333} &5.8000 &7.0333 &5.7667 &6.2000 &6.5000 &  \\
+Recall &4.8667 &6.5667 &6.8667 &6.3333 &7.3667 &6.8667 &6.7000 &7.4333 &\textbf{4.8333} &7.3667 &6.0667 &6.7333 &  \\
+Kappa &\textbf{2.4000} &4.2333 &10.1667 &7.0000 &6.6000 &10.1667 &5.1667 &8.3667 &10.1667 &4.3333 &4.3333 &5.0667 &  \\
+AUC &\textbf{2.8667} &4.2333 &10.1667 &6.9333 &6.6000 &10.1667 &5.1000 &8.2333 &10.1667 &4.3333 &4.2667 &4.9333 &  \\
+Run-Time &2.2667 &6.2000 &3.1000 &7.2000 &11.0667 &4.3000 &8.5333 &10.1333 &\textbf{1.8667} &7.2000 &6.4667 &9.6667 &  \\
 \hline\noalign{\smallskip}\noalign{\smallskip}
-Average &\textbf{3.3500} &7.1667 &6.5000 &7.0167 &7.3556 &5.5722 &6.9833 &6.8833 &5.3556 &4.3667 &5.4500 &  \\
-Rank &\textbf{2.0000} &7.7500 &6.5833 &8.0000 &7.9167 &5.3333 &7.6667 &7.8333 &5.2500 &3.0000 &4.6667 &  \\
+Average &\textbf{3.5278} &5.1778 &7.8222 &7.0889 &7.5833 &8.0222 &6.0722 &8.0889 &7.2778 &5.6167 &5.3667 &6.3556 &  \\
+Rank &\textbf{2.1667} &3.3333 &8.9167 &7.7500 &9.2500 &9.0833 &5.5000 &8.8333 &7.3333 &5.0833 &4.0833 &6.6667 &  \\
 \hline\noalign{\smallskip}
@@
 
-\coordinate (c0) at (2,0);
-\coordinate (c1) at (7.75,0);
-\coordinate (c2) at (6.5833,0);
-\coordinate (c3) at (8,0);
-\coordinate (c4) at (7.9167,0);
-\coordinate (c5) at (5.3333,0);
-\coordinate (c6) at (7.6667,0);
-\coordinate (c7) at (7.8333,0);
-\coordinate (c8) at (5.25,0);
-\coordinate (c9) at (3,0);
-\coordinate (c10) at (4.6667,0);
+\coordinate (c0) at (2.1667,0);
+\coordinate (c1) at (3.3333,0);
+\coordinate (c2) at (8.9167,0);
+\coordinate (c3) at (7.75,0);
+\coordinate (c4) at (9.25,0);
+\coordinate (c5) at (9.0833,0);
+\coordinate (c6) at (5.5,0);
+\coordinate (c7) at (8.8333,0);
+\coordinate (c8) at (7.3333,0);
+\coordinate (c9) at (5.0833,0);
+\coordinate (c10) at (4.0833,0);
+\coordinate (c11) at (6.6667,0);
 
 \node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l3) at (c3) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l4) at (c4) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l5) at (c5) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l6) at (c6) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l7) at (c7) [below right=.27cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l8) at (c8) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (2,-0.1) rectangle (6.26,0.1);
-
-\foreach \x in {0,1,2,3,4,5,6,7,8,9,10} {
+\node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (2.166,-0.1) rectangle (5.59,0.1);
+
+\foreach \x in {0,1,2,3,4,5,6,7,8,9,10,11} {
 \draw (l\x) -| (c\x);

### 2017-07-04 ArticleRevision/article/article.tex
Mult-compare for accuracy in R and new reference for pattern recognition stats software
> added table for accuracy for p-values

@@
 First, the experimental setup is described and the state-of-the-art methods are listed.
-The results for each metric, as well as the statistical analysis, are then presented and analyzed.
+The results for each metric, as well as the statistical analysis~\citep{ulas2012M2Test}, are then presented and analyzed.
 Finally, the run-time and meta-ranks of each algorithm are shown, and the overall performance of the algorithms across each metric is discussed.
@@
 \scriptsize
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
-MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Nemenyi $p$-value & 0.00000 & 0.00006 & 0.00270 & 0.00000 & 0.04751 & 0.00012 & 0.00000 & 0.05402 & 0.76207 & 0.11040\\
-Holm $p$-value & 0.00093 & 0.00102 & 0.00139 & 0.00094 & 0.00185 & 0.00104 & 0.00091 & 0.00192 & 0.00833 & 0.00238\\
-Shaffer $p$-value & 0.00111 & 0.00111 & 0.00139 & 0.00111 & 0.00185 & 0.00111 & 0.00091 & 0.00192 & 0.00833 & 0.00238\\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
+MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging& Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Nemenyi $p$-value &0.9961 &0.0000 &0.0027 &0.0734 &0.0000 &0.6218 &0.0002 &0.0000 &0.8586 &0.7910 &0.6034 &  \\
+Holm $p$-value &1.0000 &0.0000 &0.0188 &0.4405 &0.0000 &1.0000 &0.0016 &0.0000 &1.0000 &1.0000 &1.0000 &  \\
+Shaffer $p$-value &0.9961 &0.0002 &0.1207 &1.0000 &0.0002 &1.0000 &0.0090 &0.0002 &1.0000 &1.0000 &1.0000 &  \\
 \noalign{\smallskip}\hline\noalign{\smallskip}

### 2017-07-04 WekaTesting/output/multiple_comparison.R
Added multiple comparison reading from R to MATLAB, and tex and csv files generated by R

@@ -1,0 +1,32 @@
+rm(list = ls())
+library(PMCMR)
+library(scmamp)
+setwd("/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/output")
+
+metrics = c("accuracy","precision","recall","kappa","auc","time");
+
+for (metric in metrics){
+  print(paste("Analyzing: ", metric))
+  
+  # get data & form into matrix
+  data <- read.csv(file = paste(metric,".csv", sep = ""), head = TRUE, sep = ",")
+  numAlgs <- length(data)
+  data <- data[2:numAlgs]
+  data <- data.matrix(data)
+  
+  # run friedman & get p-values for Nemenyi, Holm, and Shaffer
+  friedman.test(data)
+  stats <- posthoc.friedman.nemenyi.test(data)
+  matrix_stats <- stats[3]
+  mat_st <- do.call(rbind, matrix_stats)
+  mat_st[upper.tri(mat_st)] <- t(mat_st)[upper.tri(mat_st)]
+  shaffer_mat <- adjustShaffer(mat_st)
+  full <- matrix(unlist(stats[3]))
+  nemenyi <- full[1:11]
+  holm <- p.adjust(nemenyi, method = 'holm', n = length(nemenyi))
+  shaf <- shaffer_mat[,1]
+  pvals <- data.frame(nemenyi,holm,shaf)
+  
+  # write file
+  write.csv(pvals, file = paste("/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/stats/",metric,"_pVal.csv", sep = ""))
+}

### 2017-07-04 multiple_comparisons.m

@@ -1,0 +1,31 @@
+clear; clc; close all;
+
+if ispc
+    disp('TODO: add paths for windows machine.');
+    disp('Terminating script.'); return;
+else
+    path_in = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/stats/';
+    path_out = '/Users/gabriellamelki/Documents/Research/MultiInstanceLearning/WekaTesting/stats/';
+end
+
+metrics = {'Accuracy','Precision','Recall','Kappa','AUC','Time'};
+%metrics = {'accuracy'};
+num_metrics = length(metrics);
+alpha = 0.1;
+% initialize using Accuracy.csv
+T = readtable([path_in metrics{1} '_pVal.csv']);
+% get algorithm names
+algorithms = {'MIRSVM vs.'};
+algorithms(2:size(T(:,1),1)+1) = table2cell(T(:,1));
+num_algorithms = length(algorithms);
+% get dataset names + latex table row names
+methods = {'Nemenyi $p$-value', 'Holm $p$-value', 'Shaffer $p$-value'};
+
+for m = 1:num_metrics
+    % get data
+    T = readtable([path_in metrics{m} '_pVal.csv']);
+    data = T{:,2:end}'; 
+    disp(['Analyzing ' metrics{m}]);
+    % create latex table
+    matrix2latex_metrics(data, [path_out [metrics{m} '_pV.tex']], 'rowLabels', methods, 'columnLabels', algorithms, 'alignment', 'c', 'format', '%1.4f', 'rank', 'no');
+end

### 2017-07-13 current_code/best_svm_params.m
Removed best_svm_params

@@ -1,14 +1,0 @@
-function [max_val,indBestC,indBestSigma] = best_svm_params(A)
-%% Returns best value in A with min C and max sigma
-
-% find best accuracy with respect to columns (sigma)
-[max_vals_sigma, ind_sigma] = max(A);
-
-% find best accuracy
-max_val = max(max_vals_sigma);
-
-% find best accuracy with respect to rows
-max_ind_C = find(max_vals_sigma == max_val);
-indBestSigma = max_ind_C(end);
-indBestC = ind_sigma(indBestSigma);
-

### 2017-07-13 post_hoc_script.m
updated post hoc script to accept Dataset as a header (since changed matrix2latex_metrics)
> also added data2 since was printing -data in the latex table

@@ -15,8 +15,8 @@ alpha = 0.1;
 % initialize using Accuracy.csv
 T = readtable([path_in metrics{1} '.csv']);
 % get algorithm names
-algorithms = T.Properties.VariableNames(2:end);
-num_algorithms = length(algorithms);
+algorithms = T.Properties.VariableNames;
+num_algorithms = length(algorithms)-1;
 % get dataset names + latex table row names
 datasets = table2cell(T(:,1));
 num_datasets = length(datasets);
@@ -30,15 +30,16 @@ for m = 1:num_metrics
     disp(['Analyzing ' metrics{m}]);
     
     if strmatch('Time',metrics{m})
+        data2 = data;
         rank_val = 'time';
         format = '%-1.1f';
     else
-        data = -data;
+        data2 = -data;
         rank_val = 'yes';
         format = '%-1.4f';
     end
     
-    [avg_ranks,chi_statistics] = avg_rank(data);
+    [avg_ranks,chi_statistics] = avg_rank(data2);
     ranks(m,:) = avg_ranks;
     max_rank = round(max(avg_ranks))+1;
     %[stats,headers] = wilcoxon(data,alpha);

### 2017-07-13 post_hoc_script.m
Updated post hoc script to have CD value for MIRSVM and use 'Datasets' as a row header

@@ -51,7 +51,7 @@ for m = 1:num_metrics
     % create latex table
     matrix2latex_metrics(data, [path_out [metrics{m} '.tex']], 'rowLabels', latex_data_rows, 'columnLabels', algorithms, 'alignment', 'c', 'format', format, 'rank', rank_val);
     % create bonferroni-dunn figure
-    bonferroni_dunn_tikz([path_out [metrics{m} '_Fig.tex']],avg_ranks,1,num_algorithms,algorithms,max_rank);
+    bonferroni_dunn_tikz([path_out [metrics{m} '_Fig.tex']],avg_ranks,3.435,num_algorithms,algorithms(2:end),max_rank);
 end
 
 % create latex table
@@ -65,4 +65,4 @@ format = '%-1.4f';
 metrics{end+1} = 'Average'; metrics{end+1} = 'Rank'; 
 
 matrix2latex_metrics(ranks, [path_out 'metaranks.tex'], 'rowLabels', metrics, 'columnLabels', algorithms, 'alignment', 'c', 'format', format, 'rank', rank_val);
-bonferroni_dunn_tikz([path_out 'metaranks_Fig.tex'],avg_ranks,1,num_algorithms,algorithms,max_rank);
+bonferroni_dunn_tikz([path_out 'metaranks_Fig.tex'],avg_ranks,3.435,num_algorithms,algorithms(2:end),max_rank);

### 2017-07-13 ArticleRevision/article/article.tex
Integrated new stats into article

@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-suramin &0.7000 &\textbf{0.8462} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4615 &  \\
+suramin &0.8000 &\textbf{0.8462} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4615 &  \\
 eastWest &\textbf{0.8000} &0.7000 &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.5625 &0.5000 &0.6000 &0.6000 &0.4500 &  \\
-westEast &0.7000 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.9649} &0.6375 &  \\
+westEast &0.7500 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.9649} &0.6375 &  \\
 musk1 &\textbf{0.9022} &0.8152 &0.5109 &0.7717 &0.8804 &0.5109 &0.7826 &0.7609 &0.5109 &0.8587 &0.8142 &0.8587 &  \\
@@
 webmining &0.8500 &0.8142 &0.8142 &0.7699 &0.8142 &0.8142 &0.8407 &0.6903 &0.8142 &0.8142 &\textbf{0.9358} &0.8053 &  \\
-trx &0.8825 &0.8964 &0.8705 &\textbf{0.9016} &0.8808 &0.8705 &0.8705 &0.8705 &0.8705 &0.8756 &0.6450 &0.8860 &  \\
+trx &0.8860 &0.8964 &0.8705 &\textbf{0.9016} &0.8808 &0.8705 &0.8705 &0.8705 &0.8705 &0.8756 &0.6450 &0.8860 &  \\
 mutagenesis-atoms &0.7714 &0.7606 &0.6649 &0.6436 &0.7074 &0.6649 &0.6915 &0.6649 &0.6649 &\textbf{0.7766} &\textbf{0.7766} &0.7606 &  \\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-Average &\textbf{0.8162} &0.8010 &0.6390 &0.6886 &0.7279 &0.6390 &0.7724 &0.6883 &0.6390 &0.7598 &0.7598 &0.7550 &  \\
-Rank &\textbf{2.4333} &3.8333 &9.6000 &7.8000 &6.5667 &9.6000 &5.2000 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
+Average &\textbf{0.8264} &0.8010 &0.6390 &0.6886 &0.7279 &0.6390 &0.7724 &0.6883 &0.6390 &0.7598 &0.7598 &0.7550 &  \\
+Rank &\textbf{2.2000} &3.8667 &9.6000 &7.8667 &6.5667 &9.6000 &5.3333 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
 \noalign{\smallskip}\hline
@@
 }
-\coordinate (c0) at (2.4333,0);
-\coordinate (c1) at (3.8333,0);
+
+\coordinate (c0) at (2.2,0);
+\coordinate (c1) at (3.8667,0);
 \coordinate (c2) at (9.6,0);
-\coordinate (c3) at (7.8,0);
+\coordinate (c3) at (7.8667,0);
 \coordinate (c4) at (6.5667,0);
 \coordinate (c5) at (9.6,0);
-\coordinate (c6) at (5.2,0);
+\coordinate (c6) at (5.3333,0);
 \coordinate (c7) at (8.5667,0);
@@
 
-\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
+\node (l0) at (c0) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
 \node (l1) at (c1) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
-\node (l2) at (c2) [above left=.22cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l7) at (c7) [above left=.22cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l2) at (c2) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below left=.16cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
 \node (l9) at (c9) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l11) at (c11) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (2.4333,-0.1) rectangle (5.8733,0.1);
+\node (l10) at (c10) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [below right=.01cm and 0cm, align=left,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (2.2,-0.1) rectangle (5.635,0.1);
 
@@
 \scriptsize
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
-MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging& Stacking \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Nemenyi $p$-value &0.9961 &0.0000 &0.0027 &0.0734 &0.0000 &0.6218 &0.0002 &0.0000 &0.8586 &0.7910 &0.6034 &  \\
-Holm $p$-value &1.0000 &0.0000 &0.0188 &0.4405 &0.0000 &1.0000 &0.0016 &0.0000 &1.0000 &1.0000 &1.0000 &  \\
-Shaffer $p$-value &0.9961 &0.0002 &0.1207 &1.0000 &0.0002 &1.0000 &0.0090 &0.0002 &1.0000 &1.0000 &1.0000 &  \\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Holm $p$-value &0.0500 &0.0045 &0.0071 &0.0083 &0.0050 &0.0100 &0.0063 &0.0056 &0.0250 &0.0167 &0.0125 \\\noalign{\smallskip}\hline\noalign{\smallskip}
+Wilcoxon $p$-value &0.0279 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0067 & $\geq$ 0.2 &0.0103 \\
+Wilcoxon R$^+$ &98.500 &120.00 &119.00 &120.00 &120.00 &120.00 &120.00 &120.00 &106.00 &79.000 &104.00 \\
+Wilcoxon R$^-$ &21.500 & 0.0000 &1.0000 & 0.0000 &0.0000 &0.0000 &0.0000 &0.0000 &14.000 &41.000 &16.000 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-suramin &0.6383 &0.7778 &\textbf{1.0000} &\textbf{1.0000} &0.2857 &\textbf{1.0000} &\textbf{1.0000} &0.5000 &\textbf{1.0000} &0.6429 &0.6514 &0.4000 &  \\
+suramin &0.7778 &0.7778 &\textbf{1.0000} &\textbf{1.0000} &0.2857 &\textbf{1.0000} &\textbf{1.0000} &0.5000 &\textbf{1.0000} &0.6429 &0.6514 &0.4000 &  \\
 eastWest &0.7143 &0.7000 &0.5000 &0.8750 &0.5882 &0.5000 &0.7429 &\textbf{1.0000} &0.5000 &0.6053 &0.6053 &0.4444 &  \\
-westEast &0.6700 &0.7273 &0.5000 &0.2727 &0.4600 &0.5000 &0.6939 &0.3600 &0.5000 &0.5581 &\textbf{0.9729} &0.6038 &  \\
+westEast &0.7272 &0.7273 &0.5000 &0.2727 &0.4600 &0.5000 &0.6939 &0.3600 &0.5000 &0.5581 &\textbf{0.9729} &0.6038 &  \\
 musk1 &0.8519 &0.7778 &\textbf{1.0000} &0.9286 &0.9048 &\textbf{1.0000} &0.8049 &0.8108 &\textbf{1.0000} &0.8478 &0.8817 &0.8478 &  \\
@@
 webmining &0.7500 &\textbf{1.0000} &0.8142 &0.8173 &0.8142 &0.8142 &0.8936 &\textbf{1.0000} &0.8142 &0.8817 &0.9462 &0.8500 &  \\
-trx &0.6500 &0.8571 &0.8705 &\textbf{0.9306} &0.9191 &0.8705 &0.8705 &0.8705 &0.8705 &0.9138 &0.6747 &0.9011 &  \\
+trx &\textbf{1.0000} &0.8571 &0.8705 &0.9306 &0.9191 &0.8705 &0.8705 &0.8705 &0.8705 &0.9138 &0.6747 &0.9011 &  \\
 mutagenesis-atoms &0.7872 &0.7985 &\textbf{1.0000} &0.4630 &0.6111 &\textbf{1.0000} &0.5439 &\textbf{1.0000} &\textbf{1.0000} &0.7059 &0.7059 &0.6667 &  \\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-Average &0.7668 &0.7828 &0.7719 &0.6944 &0.7128 &0.7719 &0.7800 &\textbf{0.8079} &0.7719 &0.7665 &0.7665 &0.7447 &  \\
-Rank &6.3333 &6.0000 &7.0333 &7.2667 &7.3000 &7.0333 &\textbf{5.7333} &5.8000 &7.0333 &5.7667 &6.2000 &6.5000 &  \\
+Average &0.8033 &0.7828 &0.7719 &0.6944 &0.7128 &0.7719 &0.7800 &\textbf{0.8079} &0.7719 &0.7665 &0.7665 &0.7447 &  \\
+Rank &\textbf{5.3333} &6.1333 &7.1000 &7.3333 &7.3667 &7.1000 &5.8667 &5.8667 &7.1000 &5.9000 &6.3333 &6.5667 &  \\
 \noalign{\smallskip}\hline
@@
 
-\coordinate (c0) at (6.3333,0);
-\coordinate (c1) at (6,0);
-\coordinate (c2) at (7.0333,0);
-\coordinate (c3) at (7.2667,0);
-\coordinate (c4) at (7.3,0);
-\coordinate (c5) at (7.0333,0);
-\coordinate (c6) at (5.7333,0);
-\coordinate (c7) at (5.8,0);
-\coordinate (c8) at (7.0333,0);
-\coordinate (c9) at (5.7667,0);
-\coordinate (c10) at (6.2,0);
-\coordinate (c11) at (6.5,0);
-
-\node (l0) at (c0) [above left=.38cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [below left=.2cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
-\node (l2) at (c2) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\coordinate (c0) at (5.3333,0);
+\coordinate (c1) at (6.1333,0);
+\coordinate (c2) at (7.1,0);
+\coordinate (c3) at (7.3333,0);
+\coordinate (c4) at (7.3667,0);
+\coordinate (c5) at (7.1,0);
+\coordinate (c6) at (5.8667,0);
+\coordinate (c7) at (5.8667,0);
+\coordinate (c8) at (7.1,0);
+\coordinate (c9) at (5.9,0);
+\coordinate (c10) at (6.3333,0);
+\coordinate (c11) at (6.5667,0);
+
+\node (l0) at (c0) [below left=.01cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
+\node (l1) at (c1) [below right=.16cm and 0cm, align=left,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [above right=.05cm and 0cm, align=left,scale=0.7] {\tiny MIBoost};
 \node (l3) at (c3) [below right=.17cm and 0cm, align=left,scale=0.7] {\tiny MIOptimalBall};
-\node (l4) at (c4) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l5) at (c5) [above right=.35cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
-\node (l6) at (c6) [above left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l7) at (c7) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l8) at (c8) [above right=.5cm and 0cm, align=left,scale=0.7] {\tiny SimpleMI};
-\node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l10) at (c10) [below right=.25cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l11) at (c11) [below right=.1cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (5.7333,-0.1) rectangle (9.17,0.1);
+\node (l4) at (c4) [below right=.01cm and 0cm, align=left,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above right=.15cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [above right=.3cm and 0cm, align=left,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [above left=.24cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below right=.01cm and 0cm, align=left,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.24cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (5.3333,-0.1) rectangle (8.7683,0.1);
 
@@
 \scriptsize
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
-MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Nemenyi $p$-value & 0.58199 & 0.58199 & 0.56326 & 0.58199 & 0.56326 & 0.42475 & 0.30849 & 0.63985 & 0.07815 & 0.80435\\
-Holm $p$-value & 0.00263 & 0.00250 & 0.00217 & 0.00278 & 0.00227 & 0.00185 & 0.00156 & 0.00294 & 0.00102 & 0.00500\\
-Shaffer $p$-value & 0.00263 & 0.00250 & 0.00217 & 0.00278 & 0.00227 & 0.00185 & 0.00156 & 0.00294 & 0.00102 & 0.00500\\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Holm $p$-value &0.0125 &0.0056 &0.0050 &0.0045 &0.0063 &0.0250 &0.0500 &0.0071 &0.0167 &0.0100 &0.0083 \\\noalign{\smallskip}\hline\noalign{\smallskip}
+Wilcoxon $p$-value & $\geq$ 0.2 & $\geq$ 0.2 &0.0946 &0.0256 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 &0.1354 & $\geq$ 0.2 &0.1354 \\
+Wilcoxon R$^+$ &75.000 &71.000 &90.000 &99.000 &71.000 &75.000 &55.000 &71.000 &87.000 &74.000 &87.000 \\
+Wilcoxon R$^-$ &45.000 &49.000 &30.000 &21.000 &49.000 &45.000 &65.000 &49.000 &33.000 &46.000 &33.000 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 
-\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
+\node (l0) at (c0) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
 \node (l1) at (c1) [below left=.2cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
-\node (l2) at (c2) [above right=.25cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l3) at (c3) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l4) at (c4) [below right=.2cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l5) at (c5) [above right=.35cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l6) at (c6) [above left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l7) at (c7) [below right=.025cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l8) at (c8) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l9) at (c9) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l10) at (c10) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l11) at (c11) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (4.8333,-0.1) rectangle (8.2733,0.1);
+\node (l2) at (c2) [above right=.3cm and 0cm, align=left,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [above left=.2cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below right=.2cm and 0cm, align=left,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above right=.43cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [below right=.1cm and 0cm, align=left,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [above right=.23cm and 0cm, align=left,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [below right=.05cm and 0cm, align=left,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.37cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (4.8333,-0.1) rectangle (8.2683,0.1);
 
@@
 \scriptsize
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
-MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Nemenyi $p$-value & 0.13007 & 0.25911 & 0.05402 & 0.13007 & 0.13007 & 0.01324 & 0.93419 & 0.03180 & 0.45739 & 0.23660\\
-Holm $p$-value & 0.00104 & 0.00135 & 0.00098 & 0.00106 & 0.00109 & 0.00090 & 0.01000 & 0.00094 & 0.00208 & 0.00132\\
-Shaffer $p$-value & 0.00104 & 0.00135 & 0.00098 & 0.00106 & 0.00109 & 0.00090 & 0.01000 & 0.00094 & 0.00208 & 0.00132\\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Holm $p$-value &0.0125 &0.0063 &0.0167 &0.0050 &0.0071 &0.0100 &0.0045 &0.0500 &0.0056 &0.0250 &0.0083 \\\noalign{\smallskip}\hline\noalign{\smallskip}
+Wilcoxon $p$-value &0.0060 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 &0.1070 & $\geq$ 0.2 & $\geq$ 0.2 &0.1354 & $\geq$ 0.2 \\
+Wilcoxon R$^+$ &106.50 &83.000 &71.000 &74.000 &83.000 &69.000 &89.000 &60.000 &70.000 &87.000 &62.000 \\
+Wilcoxon R$^-$ &13.500 &37.000 &49.000 &46.000 &37.000 &51.000 &31.000 &45.000 &50.000 &33.000 &43.000 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-suramin &0.6320 &\textbf{0.6829} &0.0000 &0.4500 &-0.1500 &0.0000 &0.4500 &0.0000 &0.0000 &0.2000 &0.3300 &-0.0964 &  \\
+suramin &\textbf{0.6829} &\textbf{0.6829} &0.0000 &0.4500 &-0.1500 &0.0000 &0.4500 &0.0000 &0.0000 &0.2000 &0.3300 &-0.0964 &  \\
 eastWest &\textbf{0.6000} &0.4000 &0.0000 &0.4500 &0.2250 &0.0000 &0.4250 &0.1250 &0.0000 &0.2000 &0.2000 &-0.1000 &  \\
-westEast &0.4000 &0.5000 &0.0000 &-0.2500 &-0.1000 &0.0000 &0.4750 &-0.1750 &0.0000 &0.1250 &\textbf{0.7529} &0.2750 &  \\
+westEast &0.5000 &0.5000 &0.0000 &-0.2500 &-0.1000 &0.0000 &0.4750 &-0.1750 &0.0000 &0.1250 &\textbf{0.7529} &0.2750 &  \\
 musk1 &\textbf{0.8036} &0.6290 &0.0000 &0.5396 &0.7604 &0.0000 &0.5642 &0.5197 &0.0000 &0.7174 &0.3744 &0.7174 &  \\
@@
 webmining &0.3468 &0.0000 &0.0000 &0.0246 &0.0000 &0.0000 &0.4535 &0.3771 &0.0000 &0.3744 &\textbf{0.6945} &0.2458 &  \\
-trx &0.4542 &0.3375 &0.0000 &\textbf{0.5228} &0.4224 &0.0000 &0.0000 &0.0000 &0.0000 &0.3858 &0.2900 &0.3364 &  \\
+trx &0.2100 &0.3375 &0.0000 &\textbf{0.5228} &0.4224 &0.0000 &0.0000 &0.0000 &0.0000 &0.3858 &0.2900 &0.3364 &  \\
 mutagenesis-atoms &\textbf{0.5395} &0.4431 &0.0000 &0.1709 &0.2654 &0.0000 &0.2909 &0.0000 &0.0000 &0.4738 &0.4738 &0.4431 &  \\
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-Average &\textbf{0.5656} &0.4730 &0.0000 &0.2145 &0.2973 &0.0000 &0.4056 &0.1635 &0.0000 &0.4434 &0.4434 &0.4167 &  \\
-Rank &\textbf{2.4000} &4.2333 &10.1667 &7.0000 &6.6000 &10.1667 &5.1667 &8.3667 &10.1667 &4.3333 &4.3333 &5.0667 &  \\
+Average &\textbf{0.5594} &0.4730 &0.0000 &0.2145 &0.2973 &0.0000 &0.4056 &0.1635 &0.0000 &0.4434 &0.4434 &0.4167 &  \\
+Rank &\textbf{2.6333} &4.2000 &10.1667 &7.0000 &6.5333 &10.1667 &5.2333 &8.3667 &10.1667 &4.2667 &4.2667 &5.0000 &  \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 
-\coordinate (c0) at (2.4,0);
-\coordinate (c1) at (4.2333,0);
+\coordinate (c0) at (2.6333,0);
+\coordinate (c1) at (4.2,0);
 \coordinate (c2) at (10.1667,0);
 \coordinate (c3) at (7,0);
-\coordinate (c4) at (6.6,0);
+\coordinate (c4) at (6.5333,0);
 \coordinate (c5) at (10.1667,0);
-\coordinate (c6) at (5.1667,0);
+\coordinate (c6) at (5.2333,0);
 \coordinate (c7) at (8.3667,0);
 \coordinate (c8) at (10.1667,0);
-\coordinate (c9) at (4.3333,0);
-\coordinate (c10) at (4.3333,0);
-\coordinate (c11) at (5.0667,0);
-
-\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
-\node (l2) at (c2) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l3) at (c3) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\coordinate (c9) at (4.2667,0);
+\coordinate (c10) at (4.2667,0);
+\coordinate (c11) at (5,0);
+
+\node (l0) at (c0) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
+\node (l1) at (c1) [above right=.1cm and 0cm, align=left,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [above right=.27cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [below right=.05cm and 0cm, align=left,scale=0.7] {\tiny MIOptimalBall};
 \node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l5) at (c5) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l6) at (c6) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l9) at (c9) [above right=.1cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l11) at (c11) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (2.4,-0.1) rectangle (5.84,0.1);
+\node (l5) at (c5) [below right=.05cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [above right=.1cm and 0cm, align=left,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [below right=.05cm and 0cm, align=left,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [above right=.1cm and 0cm, align=left,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [below left=.2cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below left=.02cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (2.6333,-0.1) rectangle (6.0683,0.1);
 
@@
 \scriptsize
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
-MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Nemenyi $p$-value & 0.00000 & 0.00105 & 0.00353 & 0.00000 & 0.03180 & 0.00018 & 0.00000 & 0.03899 & 0.49139 & 0.13720\\
-Holm $p$-value & 0.00091 & 0.00128 & 0.00143 & 0.00093 & 0.00200 & 0.00119 & 0.00094 & 0.00208 & 0.00556 & 0.00263\\
-Shaffer $p$-value & 0.00091 & 0.00135 & 0.00143 & 0.00111 & 0.00200 & 0.00135 & 0.00111 & 0.00208 & 0.00556 & 0.00263\\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Holm $p$-value &0.0500 &0.0045 &0.0071 &0.0083 &0.0050 &0.0100 &0.0063 &0.0056 &0.0167 &0.0250 &0.0125 \\\noalign{\smallskip}\hline\noalign{\smallskip}
+Wilcoxon $p$-value &0.0121 &0.0001 &0.0012 &0.0012 &0.0001 &0.0006 &0.0001 &0.0001 &0.1205 & $\geq$ 0.2 &0.0946 \\
+Wilcoxon R$^+$ &91.500 &120.00 &113.00 &113.00 &120.00 &115.00 &119.00 &120.00 &88.000 &83.000 &90.000 \\
+Wilcoxon R$^-$ &13.500 &0.0000 &7.0000 &7.0000 &0.0000 &5.0000 &1.0000 &0.0000 &32.000 &37.000 &30.000 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \hline\noalign{\smallskip}
-suramin &0.6700 &\textbf{0.8333} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4524 &  \\
+suramin &\textbf{0.8333} &\textbf{0.8333} &0.5000 &0.7250 &0.4250 &0.5000 &0.7250 &0.5000 &0.5000 &0.6000 &0.6650 &0.4524 &  \\
 eastWest &\textbf{0.8000} &0.7000 &0.5000 &0.7250 &0.6125 &0.5000 &0.7125 &0.5625 &0.5000 &0.6000 &0.6000 &0.4500 &  \\
-westEast &0.7000 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.8456} &0.6375 &  \\
+westEast &0.7500 &0.7500 &0.5000 &0.3750 &0.4500 &0.5000 &0.7375 &0.4125 &0.5000 &0.5625 &\textbf{0.8456} &0.6375 &  \\
 musk1 &\textbf{0.9005} &0.8135 &0.5000 &0.7676 &0.8797 &0.5000 &0.7816 &0.7589 &0.5000 &0.8589 &0.6837 &0.8589 &  \\
@@
 webmining &0.6320 &0.5000 &0.5000 &0.5096 &0.5000 &0.5000 &0.7184 &0.8098 &0.5000 &0.6837 &\textbf{0.8123} &0.6048 &  \\
-trx &0.7243 &0.6170 &0.5000 &\textbf{0.7392} &0.6932 &0.5000 &0.5000 &0.5000 &0.5000 &0.6732 &0.6450 &0.6281 &  \\
+trx &0.6500 &0.6170 &0.5000 &\textbf{0.7392} &0.6932 &0.5000 &0.5000 &0.5000 &0.5000 &0.6732 &0.6450 &0.6281 &  \\
 mutagenesis-atoms &0.7106 &0.7137 &0.5000 &0.5824 &0.6186 &0.5000 &0.6420 &0.5000 &0.5000 &\textbf{0.7257} &\textbf{0.7257} &0.7137 &  \\
@@
 function &0.7563 &0.7698 &0.5000 &0.5298 &0.6015 &0.5000 &0.6391 &0.5268 &0.5000 &\textbf{0.8456} &0.6317 &0.8434 &  \\
-\hline\noalign{\smallskip}\noalign{\smallskip}
-Average &\textbf{0.7587} &0.7253 &0.5000 &0.6015 &0.6390 &0.5000 &0.6937 &0.5874 &0.5000 &0.7148 &0.7148 &0.6983 &  \\
-Rank &\textbf{2.8667} &4.2333 &10.1667 &6.9333 &6.6000 &10.1667 &5.1000 &8.2333 &10.1667 &4.3333 &4.2667 &4.9333 &  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Average &\textbf{0.7680} &0.7253 &0.5000 &0.6015 &0.6390 &0.5000 &0.6937 &0.5874 &0.5000 &0.7148 &0.7148 &0.6983 &  \\
+Rank &\textbf{2.7667} &4.2667 &10.1667 &7.0000 &6.5333 &10.1667 &5.2333 &8.2333 &10.1667 &4.2667 &4.2667 &4.9333 &  \\
 \hline\noalign{\smallskip}
@@
 
-\coordinate (c0) at (2.8667,0);
-\coordinate (c1) at (4.2333,0);
+\coordinate (c0) at (2.7667,0);
+\coordinate (c1) at (4.2667,0);
 \coordinate (c2) at (10.1667,0);
-\coordinate (c3) at (6.9333,0);
-\coordinate (c4) at (6.6,0);
+\coordinate (c3) at (7,0);
+\coordinate (c4) at (6.5333,0);
 \coordinate (c5) at (10.1667,0);
-\coordinate (c6) at (5.1,0);
+\coordinate (c6) at (5.2333,0);
 \coordinate (c7) at (8.2333,0);
 \coordinate (c8) at (10.1667,0);
-\coordinate (c9) at (4.3333,0);
+\coordinate (c9) at (4.2667,0);
 \coordinate (c10) at (4.2667,0);
@@
 \node (l0) at (c0) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
-\node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
-\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l3) at (c3) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l4) at (c4) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l5) at (c5) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l6) at (c6) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l7) at (c7) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
-\node (l9) at (c9) [above right=.05cm and 0cm, align=left,scale=0.7] {\tiny TLC};
-\node (l10) at (c10) [below right=.05cm and 0cm, align=left,scale=0.7] {\tiny Bagging};
-\node (l11) at (c11) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (2.7667,-0.1) rectangle (5.8863,0.1);
+\node (l1) at (c1) [below left=.02cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
+\node (l2) at (c2) [above right=.1cm and 0cm, align=left,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [below right=.1cm and 0cm, align=left,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [below left=.02cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [below right=.01cm and 0cm, align=left,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [below left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [above right=.1cm and 0cm, align=left,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below right=.16cm and 0cm, align=left,scale=0.7] {\tiny SimpleMI};
+\node (l9) at (c9) [below left=.34cm and 0cm, align=right,scale=0.7] {\tiny TLC};
+\node (l10) at (c10) [below left=.16cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (2.7667,-0.1) rectangle (6.2017,0.1);
 
@@
 \scriptsize
-\resizebox{0.95\textwidth}{!}{\begin{tabular}{lcccccccccc}\noalign{\smallskip}\hline\noalign{\smallskip}
-MIRSVM vs. & MIBoost & MIOptimalBall & MIDD & MIWrapper & MISMO & MISVM & SimpleMI & TLC & Bagging & Stacking\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-Nemenyi $p$-value & 0.00000 & 0.00270 & 0.00420 & 0.00000 & 0.11040 & 0.00128 & 0.00000 & 0.23660 & 0.78313 & 0.27091\\
-Holm $p$-value & 0.00093 & 0.00128 & 0.00135 & 0.00094 & 0.00278 & 0.00125 & 0.00091 & 0.00357 & 0.00714 & 0.00385\\
-Shaffer $p$-value & 0.00111 & 0.00135 & 0.00135 & 0.00111 & 0.00278 & 0.00135 & 0.00091 & 0.00357 & 0.00714 & 0.00385\\
+\resizebox{0.95\textwidth}{!}{\begin{tabular}{lccccccccccc}
+\noalign{\smallskip}\hline\noalign{\smallskip}
+MIRSVM vs. &miGraph &MIBoost &MIOptimalBall &MIDD &MIWrapper &MISMO &MISVM &SimpleMI &TLC &Bagging &Stacking \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Holm $p$-value &0.0167 &0.0045 &0.0071 &0.0083 &0.0050 &0.0100 &0.0063 &0.0056 &0.0250 &0.0500 &0.0125 \\\noalign{\smallskip}\hline\noalign{\smallskip}
+Wilcoxon $p$-value &0.0166 &0.0001 &0.0002 &0.0003 &0.0001 &0.0012 &0.0009 &0.0001 & $\geq$ 0.2 & $\geq$ 0.2 &0.0781 \\
+Wilcoxon R$^+$ &90.000 &120.00 &118.00 &117.00 &120.00 &113.00 &114.00 &120.00 &81.000 &79.000 &91.500 \\
+Wilcoxon R$^-$ &15.000 &0.0000 &2.0000 &3.0000 &0.0000 &7.0000 &6.0000 &0.0000 &39.000 &41.000 &28.500 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 \midrule
-Accuracy &\textbf{2.4333} &3.8333 &9.6000 &7.8000 &6.5667 &9.6000 &5.2000 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
-Precision &6.3333 &6.0000 &7.0333 &7.2667 &7.3000 &7.0333 &\textbf{5.7333} &5.8000 &7.0333 &5.7667 &6.2000 &6.5000 &  \\
+Accuracy &\textbf{2.2000} &3.8667 &9.6000 &7.8667 &6.5667 &9.6000 &5.3333 &8.5667 &9.6000 &4.7000 &4.8667 &5.2333 &  \\
+Precision &\textbf{5.3333} &6.1333 &7.1000 &7.3333 &7.3667 &7.1000 &5.8667 &5.8667 &7.1000 &5.9000 &6.3333 &6.5667 &  \\
 Recall &4.8667 &6.5667 &6.8667 &6.3333 &7.3667 &6.8667 &6.7000 &7.4333 &\textbf{4.8333} &7.3667 &6.0667 &6.7333 &  \\
-Kappa &\textbf{2.4000} &4.2333 &10.1667 &7.0000 &6.6000 &10.1667 &5.1667 &8.3667 &10.1667 &4.3333 &4.3333 &5.0667 &  \\
-AUC &\textbf{2.8667} &4.2333 &10.1667 &6.9333 &6.6000 &10.1667 &5.1000 &8.2333 &10.1667 &4.3333 &4.2667 &4.9333 &  \\
-Run-Time &2.2667 &6.2000 &3.1000 &7.2000 &11.0667 &4.3000 &8.5333 &10.1333 &\textbf{1.8667} &7.2000 &6.4667 &9.6667 &  \\
-\hline\noalign{\smallskip}\noalign{\smallskip}
-Average &\textbf{3.5278} &5.1778 &7.8222 &7.0889 &7.5833 &8.0222 &6.0722 &8.0889 &7.2778 &5.6167 &5.3667 &6.3556 &  \\
-Rank &\textbf{2.1667} &3.3333 &8.9167 &7.7500 &9.2500 &9.0833 &5.5000 &8.8333 &7.3333 &5.0833 &4.0833 &6.6667 &  \\
+Kappa &\textbf{2.6333} &4.2000 &10.1667 &7.0000 &6.5333 &10.1667 &5.2333 &8.3667 &10.1667 &4.2667 &4.2667 &5.0000 &  \\
+AUC &\textbf{2.7667} &4.2667 &10.1667 &7.0000 &6.5333 &10.1667 &5.2333 &8.2333 &10.1667 &4.2667 &4.2667 &4.9333 &  \\
+Time &2.2667 &6.2000 &3.1000 &7.2000 &11.0667 &4.3000 &8.5333 &10.1333 &\textbf{1.8667} &7.2000 &6.4667 &9.6667 &  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+Average &\textbf{3.3444} &5.2056 &7.8333 &7.1222 &7.5722 &8.0333 &6.1500 &8.1000 &7.2889 &5.6167 &5.3778 &6.3556 &  \\
+Rank &\textbf{1.3333} &3.6667 &8.9167 &7.7500 &9.2500 &9.0833 &5.9167 &8.7500 &7.3333 &5.2500 &4.2500 &6.5000 &  \\
 \hline\noalign{\smallskip}
@@
 
-\coordinate (c0) at (2.1667,0);
-\coordinate (c1) at (3.3333,0);
+\coordinate (c0) at (1.3333,0);
+\coordinate (c1) at (3.6667,0);
 \coordinate (c2) at (8.9167,0);
@@
 \coordinate (c5) at (9.0833,0);
-\coordinate (c6) at (5.5,0);
-\coordinate (c7) at (8.8333,0);
+\coordinate (c6) at (5.9167,0);
+\coordinate (c7) at (8.75,0);
 \coordinate (c8) at (7.3333,0);
-\coordinate (c9) at (5.0833,0);
-\coordinate (c10) at (4.0833,0);
-\coordinate (c11) at (6.6667,0);
-
-\node (l0) at (c0) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
+\coordinate (c9) at (5.25,0);
+\coordinate (c10) at (4.25,0);
+\coordinate (c11) at (6.5,0);
+
+\node (l0) at (c0) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny \textbf{MIRSVM}};
 \node (l1) at (c1) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny miGraph};
-\node (l2) at (c2) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MIBoost};
-\node (l3) at (c3) [above left=.25cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
-\node (l4) at (c4) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny MIDD};
-\node (l5) at (c5) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
-\node (l6) at (c6) [above right=.23cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
-\node (l7) at (c7) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
-\node (l8) at (c8) [below right=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
+\node (l2) at (c2) [below right=.05cm and 0cm, align=left,scale=0.7] {\tiny MIBoost};
+\node (l3) at (c3) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIOptimalBall};
+\node (l4) at (c4) [above right=.05cmand 0cm, align=left,scale=0.7] {\tiny MIDD};
+\node (l5) at (c5) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny MIWrapper};
+\node (l6) at (c6) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny MISMO};
+\node (l7) at (c7) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny MISVM};
+\node (l8) at (c8) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny SimpleMI};
 \node (l9) at (c9) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny TLC};
-\node (l10) at (c10) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
-\node (l11) at (c11) [below left=.05cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
-
-\fill[fill=gray,fill opacity=0.5] (2.166,-0.1) rectangle (5.59,0.1);
+\node (l10) at (c10) [above left=.1cm and 0cm, align=right,scale=0.7] {\tiny Bagging};
+\node (l11) at (c11) [above left=.23cm and 0cm, align=right,scale=0.7] {\tiny Stacking};
+
+\fill[fill=gray,fill opacity=0.5] (1.3333,-0.1) rectangle (4.7683,0.1);
 
@@
 };
-\end{tikzpicture}}\vspace{-1.2em}
+\end{tikzpicture}}\vspace{-0.6em}
 \captionof{figure}{Bonferroni-Dunn test for overall ranks comparison}\label{fig:BonfDunnpmeta}

### 2017-07-20 ArticleRevision/article/article.tex
Added analysis with new results
Added analysis + wilcoxon real pvalues for those with >= 0.2

Still need to give it another once over to make sure it's good.

@@
 \section{Experiments}\label{sec:experiments}
-This section presents the experimental setup and comparison of our contribution, as well as ten other state-of-the-art methods on $15$ different benchmark datasets.
+This section presents the experimental setup and comparison of our contribution, as well as eleven other state-of-the-art methods on $15$ different benchmark datasets.
 First, the experimental setup is described and the state-of-the-art methods are listed.
@@
 
-The experimental environment was designed to test the difference in performance of the proposed method against $11$ state-of-the-art algorithms, contrasting instance-level methods and bag-level methods.
+The experimental environment was designed to test the difference in performance of the proposed method against $11$ state-of-the-art algorithms, contrasting instance-level, bag-level, and ensemble methods.
 Instance-level methods include MIOptimalBall, MIBoost, MISVM, MIDD, and MIWrapper.
@@
 These algorithms were chosen because they have shown considerable performance in learning multi-instance models, while also having their frameworks readily available for reproducing their results through MILK, the Multi-Instance Learning Kit\footnote{http://www.cs.waikato.ac.nz/ml/milk}~\citep{Xu2003}, used in conjunction with the Weka framework.
-Experiments were run in an Intel i7-6700k CPU with 32GB RAM.
+Experiments were run on an Intel i7-6700k CPU with 32GB RAM.
 MIRSVM was implemented in MATLAB while the referenced algorithms are available in the Java implementation of Weka with the exception of miGraph which was made available by Zhou et al.\footnote{http://lamda.nju.edu.cn/code\_miGraph.ashx} and tested in MATLAB.
 
-Experiments were performed using $k$-fold cross validation, with $k = 10$, in order to evaluate the models' performances and tune hyper-parameters.
+Experiments were performed using $k$-fold cross validation, with $k = 10$, in order to objectively evaluate the models' performances and tune hyper-parameters.
 The data is separated fairly into $10$ equally sized sections where, at every iteration of the cross-validation loop, a section is held out as the test set, while the remainder of the data is used for training.
-This procedure ensures the model is not optimistically biased towards the full dataset.
+These sets are stored and used by each algorithm, ensuring the cross-validation folds are controlled for each algorithm.
+This procedure ensures the model is not optimistically biased towards the full dataset and the algorithms are evaluated fairly over the same data in each fold.
 The tuning of the model during cross-validation includes finding the best penalty parameter, $C$, as well as the best shape parameter for the Gaussian radial basis function kernel, $\sigma$.
@@
 
-The results for these metrics are shown in Tables~\ref{tab:accResults},~\ref{tab:preResults},~\ref{tab:recResults},~\ref{tab:kappaResults},~\ref{tab:aucResults}, and~\ref{tab:time}.
+The results for the following are shown in Tables~\ref{tab:accResults},~\ref{tab:preResults},~\ref{tab:recResults},~\ref{tab:kappaResults},~\ref{tab:aucResults}, and~\ref{tab:time}.
 \begin{subequations}
@@
 
-The Nemenyi, Holm, and Shaffer post-hoc~\citep{Gibbons2011,Holander1999} tests were then run for each of the metrics to compute multiple pairwise comparisons between the proposed algorithm and the state-of-the-art methods, investigating whether statistical differences exist among pairs of algorithms.
-Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values for the Nemenyi, Holm, and Shaffer tests for $\alpha = 0.05$.
+The Holm and pairwise Wilcoxon rank-sum post-hoc~\citep{Gibbons2011,Holander1999} tests were then run for each of the metrics to compute multiple pairwise comparisons between the proposed algorithm and the state-of-the-art methods, investigating whether statistical differences exist among pairs of algorithms.
+Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values and Wilcoxon rank-sums for the Holm and Wilcoxon tests for $\alpha = 0.01$.
 \newpage
@@
 Holm $p$-value &0.0500 &0.0045 &0.0071 &0.0083 &0.0050 &0.0100 &0.0063 &0.0056 &0.0250 &0.0167 &0.0125 \\\noalign{\smallskip}\hline\noalign{\smallskip}
-Wilcoxon $p$-value &0.0279 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0067 & $\geq$ 0.2 &0.0103 \\
+Wilcoxon $p$-value &0.0279 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0001 &0.0067 & 0.3028 &0.0103 \\
 Wilcoxon R$^+$ &98.500 &120.00 &119.00 &120.00 &120.00 &120.00 &120.00 &120.00 &106.00 &79.000 &104.00 \\
@@
 The results indicate that the bag-based and ensemble learners perform better than the instance-based and wrapper methods.
-Specifically, MIRSVM achieves the best accuracy over $6$ of the $15$ datasets with a competitive average against the Bagging, Stacking, and TLC algorithms.
+Specifically, MIRSVM achieves the best accuracy over $5$ of the $15$ datasets with a competitive average against the miGraph, Bagging, Stacking, and TLC algorithms.
 Note that MIRSVM performs better than MISVM for all datasets, indicating that using representatives from each bag and limiting the number of support-vectors per negative bag improves the classification performance.
@@
 Figure~\ref{fig:BonfDunnacc} and Table~\ref{tab:statacc} show the results for the statistical analysis on the accuracy results.
-The algorithms with ranking higher than $5.51$ (MIRSVM rank + Bonferroni-Dunn critical value), to the right of the grey bar in Figure~\ref{fig:BonfDunnacc}, perform statistically worse than MIRSVM.
-Table~\ref{tab:statacc} shows the $p$-values of the Nemenyi, Holm, and Shaffer tests and their results complement one another.
-Nemenyi's procedure indicates that MIRSVM performs significantly better than all methods (with $p$-values $< 0.01$), except Bagging, Stacking, TLC, and MISMO.
-The Nemenyi $p$-values for MIBoost, MIWrapper, and SimpleMI are $0$, showing that MIRSVM has significantly better accuracy.
-However, the stricter Holm and Shaffer tests indicate that significant differences exist between MIRSVM and all other classifiers, highlighting MIRSVM's superior classification accuracy.
+The algorithms with ranking higher than $5.63$ (MIRSVM rank + Bonferroni-Dunn critical value), to the right of the grey bar in Figure~\ref{fig:BonfDunnacc}, perform statistically worse than MIRSVM.
+Table~\ref{tab:statacc} shows the $p$-values of the Holm and Wilcoxon tests and their results complement one another.
+Holms's procedure indicates that MIRSVM performs significantly better than all methods (with $p$-values $< 0.01$), except miGraph, Bagging, Stacking, TLC, and MISMO.
+The Wilcoxon $p$-values show significant differences exist among all algorithms except miGraph, Bagging, and Stacking.
+They also show that MIRSVM has significantly better accuracy than MIBoost, MIOptimalBall, MIDD, MIWrapper, MISMO, MISVM, and SimpleMI, with $p$-values of $0.0001$, highlighting MIRSVM's superior classification accuracy.
 
@@
 Holm $p$-value &0.0125 &0.0056 &0.0050 &0.0045 &0.0063 &0.0250 &0.0500 &0.0071 &0.0167 &0.0100 &0.0083 \\\noalign{\smallskip}\hline\noalign{\smallskip}
-Wilcoxon $p$-value & $\geq$ 0.2 & $\geq$ 0.2 &0.0946 &0.0256 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 &0.1354 & $\geq$ 0.2 &0.1354 \\
+Wilcoxon $p$-value & 0.4212 & 0.5614 &0.0946 &0.0256 & 0.5614 & 0.4212 & 0.8039 & 0.5614 &0.1354 & 0.4543 &0.1354 \\
 Wilcoxon R$^+$ &75.000 &71.000 &90.000 &99.000 &71.000 &75.000 &55.000 &71.000 &87.000 &74.000 &87.000 \\
@@
 Holm $p$-value &0.0125 &0.0063 &0.0167 &0.0050 &0.0071 &0.0100 &0.0045 &0.0500 &0.0056 &0.0250 &0.0083 \\\noalign{\smallskip}\hline\noalign{\smallskip}
-Wilcoxon $p$-value &0.0060 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 & $\geq$ 0.2 &0.1070 & $\geq$ 0.2 & $\geq$ 0.2 &0.1354 & $\geq$ 0.2 \\
+Wilcoxon $p$-value &0.0060 & 0.2077 & 0.5614 & 0.4543 & 0.2077 & 0.6387 &0.1070 & 0.6603 & 0.5995 &0.1354 & 0.5721 \\
 Wilcoxon R$^+$ &106.50 &83.000 &71.000 &74.000 &83.000 &69.000 &89.000 &60.000 &70.000 &87.000 &62.000 \\
@@
 The precision and recall results for MIWrapper and SimpleMI indicate that they are unstable classifiers, exhibiting extreme variance in behavior, making them unsuitable for real-world applications.
-It is also interesting to analyze the performance on the mutagenesis datasets, where MISVM, MIBoost, MIWrapper, and SimpleMI predict all bags as negative.
+It is also interesting to analyze the performance on the mutagenesis datasets which have a larger number of positive bags than negative, where MISVM, MIBoost, MIWrapper, and SimpleMI predict all bags as negative.
 Additionally, while MISMO obtains unbiased results on these datasets, MIRSVM significantly outperforms it over both precision and recall.
 
-Figure~\ref{fig:BonfDunnprec} shows that there are no statistically significant differences between the precision results obtained by all algorithms, except SimpleMI; and Figure~\ref{fig:BonfDunnrec} shows none over all.
+Figure~\ref{fig:BonfDunnprec} and Figure~\ref{fig:BonfDunnrec} show that there are no statistically significant differences between the precision and recall results obtained by all algorithms.
 It is worth noting that MIRSVM outperforms both ensemble methods according to recall, despite them exhibiting relatively good accuracy and precision.
 This indicates that they are strongly conservative towards predicting positive bags.
-The Holm and Shaffer tests indicate that significant differences exist between MIRSVM and the state-of-the-art, with the exception of SimpleMI.
+The Holm test indicates significant differences exist between MIRSVM and MIBoost, MIOptimalBall, MIDD, MIWrapper, SimpleMI, and Stacking for precision and all the above, except MIOptimalBall for recall.
+The Wilcoxon $p$-values reflect the results shown in Figure~\ref{fig:BonfDunnprec} and Figure~\ref{fig:BonfDunnrec}.
 
@@
 Holm $p$-value &0.0500 &0.0045 &0.0071 &0.0083 &0.0050 &0.0100 &0.0063 &0.0056 &0.0167 &0.0250 &0.0125 \\\noalign{\smallskip}\hline\noalign{\smallskip}
-Wilcoxon $p$-value &0.0121 &0.0001 &0.0012 &0.0012 &0.0001 &0.0006 &0.0001 &0.0001 &0.1205 & $\geq$ 0.2 &0.0946 \\
+Wilcoxon $p$-value &0.0121 &0.0001 &0.0012 &0.0012 &0.0001 &0.0006 &0.0001 &0.0001 &0.1205 & 0.2077 &0.0946 \\
 Wilcoxon R$^+$ &91.500 &120.00 &113.00 &113.00 &120.00 &115.00 &119.00 &120.00 &88.000 &83.000 &90.000 \\
@@
 MIRSVM's kappa values all fall within the range ($0.5$-$1$], indicating that its merit as a classifier agrees with the class distribution and is not random.
-Note that SimpleMI, MIOptimalBall, MIDD, MISVM, and Stacking contain some negative kappa values, indicating performance worse than the default-hypothesis.
-MIBoost and MIWrapper are shown to randomly classify all $15$ datasets.
+Note that MIOptimalBall, MIDD, MISVM, and Stacking contain some negative kappa values, indicating performance worse than the default-hypothesis.
+MIBoost, SimpleMI, and MIWrapper are shown to randomly classify all $15$ datasets.
 Figure~\ref{fig:BonfDunnkappa} and Table~\ref{tab:statkappa} show the results of the statistical analysis on the Cohen's Kappa Rate results.
-Nemenyi's procedure reflects results similar to the $p$-values obtained from the accuracy results, where MIRSVM performs significantly better than MIOptimalBall, MIDD, MISVM, MIWrapper, MIBoost, and SimpleMI, having $p$-values $< 0.01$.
-The Holm and Shaffer procedures indicate that significant differences exist among all algorithms results, supporting MIRSVM's performance as a competitive classifier.
+The Holm and Wilcoxon procedures reflect results similar to the Bonferroni-Dunn test, where MIRSVM performs significantly better than MIOptimalBall, MIDD, MISVM, MIWrapper, MIBoost, and SimpleMI (with the stricter Holm's procedure including differences against MISMO), having $p$-values $< 0.01$.
+This supports MIRSVM's performance as a competitive classifier.
 
@@
 Holm $p$-value &0.0167 &0.0045 &0.0071 &0.0083 &0.0050 &0.0100 &0.0063 &0.0056 &0.0250 &0.0500 &0.0125 \\\noalign{\smallskip}\hline\noalign{\smallskip}
-Wilcoxon $p$-value &0.0166 &0.0001 &0.0002 &0.0003 &0.0001 &0.0012 &0.0009 &0.0001 & $\geq$ 0.2 & $\geq$ 0.2 &0.0781 \\
+Wilcoxon $p$-value &0.0166 &0.0001 &0.0002 &0.0003 &0.0001 &0.0012 &0.0009 &0.0001 & 0.2523 & 0.3028 &0.0781 \\
 Wilcoxon R$^+$ &90.000 &120.00 &118.00 &117.00 &120.00 &113.00 &114.00 &120.00 &81.000 &79.000 &91.500 \\
@@
 Table~\ref{tab:aucResults} shows AUC results obtained by the algorithms, which complement the accuracy and kappa rate, emphasizing the better performance of bag-based methods.
-MIRSVM achieves the best AUC score on $6$ of the $15$ datasets, while MIBoost, SimpleMI, and MIWrapper obtain the worst results.
-Their AUC score indicates random predictor behavior, having values $\leq 0.5$.
-Bag-level methods all obtain scores between $0.7$ and $0.75$ indicating a high true positive rate and a low false positive rate, which is reflected by the precision and recall results.
+MIRSVM achieves the best AUC score on $5$ of the $15$ datasets, while MIBoost, SimpleMI, and MIWrapper obtain the worst results.
+Their AUC score indicates random predictor behavior, having values $= 0.5$.
+Bag-level methods all obtain scores between $0.7$ and $0.77$ indicating a high true positive rate and a low false positive rate, which is reflected by the precision and recall results.
 Figure~\ref{fig:BonfDunnauc} and Table~\ref{tab:statauc} show that MIRSVM performs significantly better than $6$ out of the $11$ competing algorithms.
-Nemenyi's procedure indicates that significant differences exist between MIRSVM and all algorithms except MISMO, TLC, Bagging, and Stacking.
+Holm's procedure indicates that significant differences exist between MIRSVM and all algorithms except miGraph, MISMO, TLC, Bagging, and Stacking.
 MISVM's true positive rate could be affected because of the possible imbalance of support vectors from the positive and negative classes (favoring the negative).
-Note that the Nemenyi $p$-values for MIWrapper, MIBoost, and SimpleMI are $0$.
+Note that the Wilcoxon $p$-values for MIWrapper, MIBoost, and SimpleMI are $0.0001$.
 
@@
 Table~\ref{tab:metarank} shows the ranks achieved by each of the metrics along with the average and meta-ranks.
-MIRSVM has the best meta-rank (rank of the ranks) and the Bagging ensemble method has the next best.
+MIRSVM has the best meta-rank (rank of the ranks) and the miGraph method has the next best.
 The meta-ranks also highlight the better performance of bag-level methods over instance-level and wrapper methods, emphasizing the importance of training at the bag-level.
 Not only does MIRSVM use bag-level information during classification, but it also optimizes over the instances within the bag, which helps determine which instances contribute the most information about the bags label.
-SimpleMI, MIWrapper, MIBoost, MISVM, MIOptimalBall, and MDD have the worst performance compared to MIRSVM and Bagging.
+SimpleMI, MIWrapper, MIBoost, MISVM, and MDD have the worst performance compared to MIRSVM and miGraph.
 Specifically, it is evident from the precision and recall results that MIBoost, MIWrapper, and SimpleMI, for example, classify all bags as negative for datasets that have imbalanced class distributions which favor the negative class.
@@
 The experimental study showed the better performance of MIRSVM compared with state-of-the-art multi-instance support vector machines, traditional multi-instance learners, as well as ensemble methods.
-The results, according to a variety of performance metrics, were compared and further validated using statistical analysis with non-parametric tests which highlight the advantages of using bag-level based and ensemble learners, such as Bagging and Stacking, while showing the instance-level based learners performed poorly in comparison or were deemed as strongly biased and unstable classifiers.
-On the contrary, our proposal MIRSVM performs statistically better, neither compromising accuracy nor run-time while displaying a robust performance across all of the evaluated datasets.
+The results, according to a variety of performance metrics, were compared and further validated using statistical analysis with non-parametric tests which highlight the advantages of using bag-level based and ensemble learners, such as miGraph, Bagging, and Stacking, while showing the instance-level based learners performed poorly in comparison or were deemed as strongly biased and unstable classifiers.
+Our proposal, MIRSVM, performs statistically better, neither compromising accuracy nor run-time while displaying a robust performance across all of the evaluated datasets.
 

### 2017-07-22 ArticleRevision/article/article.tex
Updated Article based on Alberto's notes, still need confirmation about questions I asked him in the email.
> Page 1: complete
> Page 2: complete (minus VC dimension, but emailed Alberto for confirmation)
> Page 3: complete
> Page 8: complete
> Page 14: complete (minus the crossed out "imbalanced" word, emailed Alberto for confirmation)
> Page 15: complete
> Page 16: complete (with question about Wx p-value cut-off)
> Page 17: complete
> Page 18: complete (with edits to the text for formatting purposes)
> Page 19: complete
> Page 20: complete
> Page 21: complete

@@
 \textit{Multiple-instance learning} (MIL) is a variation of \textit{supervised learning}, where samples are represented by labeled bags, each containing sets of instances.
-The individual labels of the samples within a bag are unknown, and labels are assigned based on a multi-instance assumption.
+The individual labels of the instances within a bag are unknown, and labels are assigned based on a multi-instance assumption.
 One of the major complexities associated with this type of learning is the ambiguous relationship between a bag's label and the instances it contains.
@@
 This stems from the standard MI assumption, where the underlying distribution among instances within positive bags is unknown.
-There have been different attempts to overcome this complexity, such as ``flattenning" the MIL datasets, meaning instances contained in positive bags each adopt a positive label, allowing the use of classical supervised learning techniques~\citep{Ray2005}.
-This approach assumes that positive bags contain a significant number of positive samples, which may not be the case, causing the classifier to mislabel negative instances within the bag, decreasing the power of the MI model.
-
-To overcome this, a different MIL approach was proposed, where subsets of instances are selected from positive bags for classifier training~\citep{Maron1998,Zhang2001}.
+There have been different attempts to overcome this complexity, such as ``flattening" the MIL datasets, meaning instances contained in positive bags each adopt a positive label, allowing the use of classical supervised learning techniques~\citep{Ray2005}.
+This approach assumes that positive bags contain a significant number of positive instances, which may not be the case, causing the classifier to mislabel negative instances within the bag, decreasing the power of the MI model.
+
+To overcome this issue, a different MIL approach was proposed, where subsets of instances are selected from positive bags for classifier training~\citep{Maron1998,Zhang2001}.
 One drawback of this type of method is that the resulting training datasets become imbalanced towards positive instances.
@@
 The optimal set of representatives is found when they have converged, or stopped changing from one iteration to the next.
-The algorithm does not assume any distribution of the instances and is not affected by the number of samples within a bag, making it applicable to a variety of contexts.
+The algorithm does not assume any distribution of the instances and is not affected by the number of instances within a bag, making it applicable to a variety of contexts.
 The key contributions of this work include,
@@
 This work is organized as follows.
-First, the notation used throughout the paper is provided, the MIL problem is formalized, and recent MIL methods, traditional support vector machines, and state-of-the-art multi-instance SVM methods are reviewed in Section~\ref{sec:background}.
-The primal L$1$-SVM is formulated with respect to optimizing over bags, the dual formulation is then derived along with conditions for optimality, and the proposed algorithm, MIRSVM, is listed and described in Section~\ref{sec:contribution}.
+Section~\ref{sec:background} presents the notation used throughout the paper, formalizes the MIL problem, and reviews recent MIL methods, traditional support vector machines, and state-of-the-art multi-instance SVM methods.
+Section~\ref{sec:contribution} presents the contribution: the primal L$1$-SVM formulation with respect to optimizing over bags, its derived dual formulation along with conditions for optimality, and the proposed algorithm, MIRSVM.
 Section~\ref{sec:experiments} presents the experimental environment, including results from various metrics, run-time, and non-parametric statistical analysis over $15$ benchmark MI datasets compared with $11$ state-of-the-art algorithms.
@@
 
-\begin{table}
+\begin{table}[htbp]
 \caption{Summary of notation used throughout the paper}\label{tab:Notation}
@@
 
-\citet{Zhou2009} proposed miGraph, which implicitely constructs a graph by deriving affinity matrices while using a graph kernel.
+\citet{Zhou2009} proposed miGraph, which implicitly constructs a graph by deriving affinity matrices while using a graph kernel.
 It assumes the instances are not independently and identically distributed because of the nature of MI data.
@@
 This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
-In other words, the most positive sample is chosen from each positive bag and the least negative sample is chosen from each negative bag (samples with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
+In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
 Equation~\eqref{eq:primalmirsvm} presents the primal MIRSVM optimization problem:
@@
 \end{subequations} 
-where $\bm S_I$ is a set of the bag representatives' indices and $\bm x_{s_I}$ is the sample representative of bag $\mathcal{B}_I$.
+where $\bm S_I$ is a set of the bag representatives' indices and $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$.
 Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.
@@
 
-Experiments were performed using $k$-fold cross validation, with $k = 10$, in order to objectively evaluate the models' performances and tune hyper-parameters.
+Experiments were performed using $10$-fold cross validation in order to objectively evaluate the models' performances and tune hyper-parameters.
 The data is separated fairly into $10$ equally sized sections where, at every iteration of the cross-validation loop, a section is held out as the test set, while the remainder of the data is used for training.
@@
 The classification performance was measured using five metrics: Accuracy~\eqref{eq:accuracy}, Precision \eqref{eq:precision}, Recall~\eqref{eq:recall}, Cohen's kappa rate~\eqref{eq:kappa}, and Area under ROC curve (AUC)~\eqref{eq:auc}.
-The Precision and Recall measures were reported because Accuracy alone can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which respectively have six and ten times as many negative instances than positive.
+The Precision and Recall measures were reported because Accuracy alone can be misleading when classes are imbalanced, as is the case with the \textit{component} and \textit{function} datasets, which respectively have six and ten times as many negative bags than positive.
 Cohen's Kappa Rate and the AUC measures are used as complementary measures in order to evaluate the algorithms comprehensively~\citep{Bendavid2008}.
@@
 The AUC metric highlights the trade-off between the true positive rate, or recall, and the false positive rate, as shown in Equation~\eqref{eq:auc}.
-The values of the true positive (TP), true negative (TN), false positive (FP), and false negative samples (FN) were first collected for each of the classifiers, then the metrics were computed using the equations shown in~\eqref{eq:metrics} on the $n^\prime$ bags of the test data.
-The run times (training and testing times) of each algorithm are also reported to analyze the usability and speed of each of the algorithms across differently sized datasets.
+The values of the true positive (TP), true negative (TN), false positive (FP), and false negative samples (FN) were first collected for each of the classifiers, then the metrics were computed using the equations shown in~\eqref{eq:metrics} on the $n^\prime$ bags of the test data, where $n^\prime = TP + FP + TN + FN$.
+The run times (training and testing times) of each algorithm are also reported to analyze the scalability and speed of each of the algorithms across differently sized datasets.
 
@@
 
-The Holm and pairwise Wilcoxon rank-sum post-hoc~\citep{Gibbons2011,Holander1999} tests were then run for each of the metrics to compute multiple pairwise comparisons between the proposed algorithm and the state-of-the-art methods, investigating whether statistical differences exist among pairs of algorithms.
-Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values and Wilcoxon rank-sums for the Holm and Wilcoxon tests for $\alpha = 0.01$.
+The Holm (multiple) and Wilcoxon (pairwise) rank-sum post-hoc tests~\citep{Gibbons2011,Holander1999} were then run for each of the metrics to compute multiple and pairwise comparisons between the proposed algorithm and the state-of-the-art methods, investigating whether statistical differences exist among the algorithms' results.
+Tables~\ref{tab:statacc},~\ref{tab:statprec},~\ref{tab:statrec},~\ref{tab:statkappa}, and~\ref{tab:statauc} show the $p$-values for the Holm test for $\alpha = 0.05$, and the rank-sums and adjusted $p$-values for the Wilcoxon test.
 \newpage
@@
 \captionof{figure}{Bonferroni-Dunn test for Accuracy}\label{fig:BonfDunnacc}\vspace{-0.5em}
-\captionof{table}{Nemenyi, Holm, and Shaffer tests for Accuracy}\label{tab:statacc}
+\captionof{table}{Holm and Wilcoxon tests for Accuracy}\label{tab:statacc}
 \scriptsize
@@
 Table~\ref{tab:statacc} shows the $p$-values of the Holm and Wilcoxon tests and their results complement one another.
-Holms's procedure indicates that MIRSVM performs significantly better than all methods (with $p$-values $< 0.01$), except miGraph, Bagging, Stacking, TLC, and MISMO.
+Holm's procedure rejects those hypotheses having a $p$-value $\leq 0.01$, thus indicating that MIRSVM performs significantly better than all methods except miGraph, Bagging, Stacking, and TLC.
 The Wilcoxon $p$-values show significant differences exist among all algorithms except miGraph, Bagging, and Stacking.
-They also show that MIRSVM has significantly better accuracy than MIBoost, MIOptimalBall, MIDD, MIWrapper, MISMO, MISVM, and SimpleMI, with $p$-values of $0.0001$, highlighting MIRSVM's superior classification accuracy.
+They also show that MIRSVM has significantly better accuracy than MIBoost, MIOptimalBall, MIDD, MIWrapper, MISMO, MISVM, and SimpleMI, each having respectively small $p$-values, highlighting MIRSVM's superior classification accuracy.
 
@@
 \captionof{figure}{Bonferroni-Dunn test for Precision}\label{fig:BonfDunnprec}\vspace{-0.5em}
-\captionof{table}{Nemenyi, Holm, and Shaffer tests for Precision}\label{tab:statprec}
+\captionof{table}{Holm and Wilcoxon tests for Precision}\label{tab:statprec}
 \scriptsize
@@
 \captionof{figure}{Bonferroni-Dunn test for Recall}\label{fig:BonfDunnrec}\vspace{-0.5em}
-\captionof{table}{Nemenyi, Holm, and Shaffer tests for Recall}\label{tab:statrec}
+\captionof{table}{Holm and Wilcoxon tests for Recall}\label{tab:statrec}
 \scriptsize
@@
 \subsection{Precision \& Recall}
-Precision and recall are metrics that must be evaluated together in order to observe their behavior simultaneously, since they are both metrics used to measure relevance.
+Precision and recall are conflicting metrics that must be evaluated together in order to observe their behavior simultaneously, since they are both used to measure relevance.
 Tables~\ref{tab:preResults} and~\ref{tab:recResults} show the precision and recall results obtained by each algorithm.
@@
 It is also interesting to analyze the performance on the mutagenesis datasets which have a larger number of positive bags than negative, where MISVM, MIBoost, MIWrapper, and SimpleMI predict all bags as negative.
-Additionally, while MISMO obtains unbiased results on these datasets, MIRSVM significantly outperforms it over both precision and recall.
-
-Figure~\ref{fig:BonfDunnprec} and Figure~\ref{fig:BonfDunnrec} show that there are no statistically significant differences between the precision and recall results obtained by all algorithms.
+Additionally, while MISMO obtains unbiased results on these datasets, MIRSVM significantly outperforms it over both precision and recall, achieving a better trade-off.
+
+Figure~\ref{fig:BonfDunnprec} and~\ref{fig:BonfDunnrec} show that there are no statistically significant differences between the precision and recall results obtained by all algorithms.
 It is worth noting that MIRSVM outperforms both ensemble methods according to recall, despite them exhibiting relatively good accuracy and precision.
 This indicates that they are strongly conservative towards predicting positive bags.
-The Holm test indicates significant differences exist between MIRSVM and MIBoost, MIOptimalBall, MIDD, MIWrapper, SimpleMI, and Stacking for precision and all the above, except MIOptimalBall for recall.
-The Wilcoxon $p$-values reflect the results shown in Figure~\ref{fig:BonfDunnprec} and Figure~\ref{fig:BonfDunnrec}.
+The Holm test indicates significant differences exist between MIRSVM and all algorithms except miGraph, MISMO, MISVM, and TLC for precision, and all the above along with SimpleMI, MIOptimalBall, and Bagging for recall.
+The Wilcoxon $p$-values do not reflect significant differences for precision, but they do for recall.
+The tests' results are severely biased due to the extreme unbalanced behavior of the classifiers, whereas MIRSVM demonstrates proper balance of the precision-recall trade-off.
 
@@
 \vspace{-0.5em}
-\captionof{table}{Nemenyi, Holm, and Shaffer tests for Cohen's Kappa rate}\label{tab:statkappa}
+\captionof{table}{Holm and Wilcoxon tests for Cohen's Kappa rate}\label{tab:statkappa}
 \scriptsize
@@
 MIRSVM's kappa values all fall within the range ($0.5$-$1$], indicating that its merit as a classifier agrees with the class distribution and is not random.
-Note that MIOptimalBall, MIDD, MISVM, and Stacking contain some negative kappa values, indicating performance worse than the default-hypothesis.
+Note that MIOptimalBall, MIDD, MISVM, MISMO, and Stacking contain some negative kappa values, indicating performance worse than the default-hypothesis.
 MIBoost, SimpleMI, and MIWrapper are shown to randomly classify all $15$ datasets.
 Figure~\ref{fig:BonfDunnkappa} and Table~\ref{tab:statkappa} show the results of the statistical analysis on the Cohen's Kappa Rate results.
-The Holm and Wilcoxon procedures reflect results similar to the Bonferroni-Dunn test, where MIRSVM performs significantly better than MIOptimalBall, MIDD, MISVM, MIWrapper, MIBoost, and SimpleMI (with the stricter Holm's procedure including differences against MISMO), having $p$-values $< 0.01$.
+The Holm and Wilcoxon procedures reflect results similar to the Bonferroni-Dunn test, where MIRSVM performs significantly better than MIOptimalBall, MIDD, MISVM, MIWrapper, MIBoost, and SimpleMI, having $p$-values $< 0.01$.
 This supports MIRSVM's performance as a competitive classifier.
@@
 \vspace{-0.5em}
-\captionof{table}{Nemenyi, Holm, and Shaffer tests for AUC}\label{tab:statauc}
+\captionof{table}{Holm and Wilcoxon tests for AUC}\label{tab:statauc}
 \scriptsize
@@
 Figure~\ref{fig:BonfDunnauc} and Table~\ref{tab:statauc} show that MIRSVM performs significantly better than $6$ out of the $11$ competing algorithms.
-Holm's procedure indicates that significant differences exist between MIRSVM and all algorithms except miGraph, MISMO, TLC, Bagging, and Stacking.
+Holm's procedure indicates that significant differences exist between MIRSVM and all algorithms except miGraph, TLC, Bagging, and Stacking.
 MISVM's true positive rate could be affected because of the possible imbalance of support vectors from the positive and negative classes (favoring the negative).
@@
 \end{table}
-Table~\ref{tab:time} shows the run time results, in seconds, for each algorithm.
+Table~\ref{tab:time} shows the run times, in seconds, for each algorithm.
 MIRSVM has the fastest run time and is ranked second.
@@
 It is important to note that quadratic programming solvers are not the most efficient tools for solving optimization problems in terms of run time, and yet MIRSVM still is shown to perform competitively against the current state-of-the-art algorithms.
-The scalability of MIRSVM is founded on the speedy rate of bag-represenative convergence, as shown in Figure~\ref{fig:convegence}.
+The scalability of MIRSVM is founded on the speedy rate of bag-representative convergence, as shown previously in Figure~\ref{fig:convegence}.
 
 SimpleMI achieves the highest rank and competitive run times because, rather than use the instances in each bag to train a model, it takes the mean value of the instances in a bag and uses that for training.
-Even though SimpleMI has fast run-times, its performance over the previous metrics has been shown to be random and not as efficient as the bag-level methods.
-
-Table~\ref{tab:metarank} shows the ranks achieved by each of the metrics along with the average and meta-ranks.
-MIRSVM has the best meta-rank (rank of the ranks) and the miGraph method has the next best.
+Even though SimpleMI has fast run-times, its performance over the previous metrics has been shown to be random and not as effective as the bag-level methods.
+
+Table~\ref{tab:metarank} shows the ranks achieved by each of the metrics along with the average and meta-ranks, to illustrate the overall performance across all metrics.
+MIRSVM has the best meta-rank (rank of the ranks) and the miGraph method has the second best.
 The meta-ranks also highlight the better performance of bag-level methods over instance-level and wrapper methods, emphasizing the importance of training at the bag-level.
@@
 Specifically, it is evident from the precision and recall results that MIBoost, MIWrapper, and SimpleMI, for example, classify all bags as negative for datasets that have imbalanced class distributions which favor the negative class.
-This emphasizes the disadvantage of using wrapper methods and assuming the data distribution of the samples within positive bags.
+This emphasizes the disadvantage of using wrapper methods and assuming the data distribution of the instances within positive bags.
 Although these algorithms are popular in literature, the experimental study clearly shows that recent bag-level and ensemble methods easily overcome traditional multi-instance learning algorithms.

### 2017-07-22 ArticleRevision/article/article.tex
Added references that Alberto had in this email and integrated them into the text.

@@
 One of the major complexities associated with MIL is the ambiguity of the relationship between a bag label and the instances within the bag~\citep{Alpaydin2015}.
-This stems from the standard MI assumption, where the underlying distribution among instances within positive bags is unknown.
+This stems from the standard MI assumption, where the underlying distribution among instances within positive bags is unknown~\citep{li2013multiple}.
 There have been different attempts to overcome this complexity, such as ``flattening" the MIL datasets, meaning instances contained in positive bags each adopt a positive label, allowing the use of classical supervised learning techniques~\citep{Ray2005}.
@@
 Support vector machines represent a set of supervised, linear and nonlinear, classification and regression methods that have theoretical foundations on Vapnik-Chervonenkis (VC) theory~\citep{Huang2006,Schoelkopf2002}.
-SVM models are similar to other machine learning algorithms and techniques, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, which makes them a useful data mining tool for various real-world applications.
+SVM models are similar to other machine learning algorithms and techniques, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, which makes them a useful data mining tool for various real-world applications~\citep{chen2016structural}.
 
@@
 Instance-based classifiers that fall under the \textit{instance-space paradigm}, aim to separate instances in positive bags from those in negative ones.
-Bag-level classifiers (\textit{bag-space paradigm}) treat each bag as a whole entity, implicitly extracting information from each bag in order to accurately predict their labels.
+Bag-level classifiers (\textit{bag-space paradigm}) treat each bag as a whole entity, implicitly extracting information from each bag in order to accurately predict their labels~\citep{qiao2017diversified}.
 Methods that fall under the \textit{embedded-space paradigm} map the input bags to a single feature vector that explicitly encapsulates all the relevant information contained within each bag.
@@
 
-SVMs are a particularly useful for learning linear predictors in high dimensional feature spaces, which is a computationally complex problem.
-In the context of classification, this problem is approached by searching for the optimal \textit{maximal margin} of separability between classes.
+SVMs are a particularly useful for learning linear predictors in high dimensional feature spaces, which is a computationally complex problem~\citep{wang2016hierarchical}.
+In the context of classification, this problem is approached by searching for the optimal \textit{maximal margin} of separability between classes~\citep{carrasco2015multi,fan2017mreklm}.
 Since most real-world datasets are non-linearly separable, ~\citet{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:

### 2017-09-14 ArticleRevision/article_with_markings/atricle_with_markings.tex
Answered questions 3 and 4, partially 2 but not in the paper.

--- 2017-07-22 ArticleRevision/article/article.tex
@@
 \usepackage{graphicx,amsfonts,array,url,algorithm,algorithmicx,algpseudocode,booktabs}
+\usepackage{xcolor,soulutf8}
 \usepackage[flushleft]{threeparttable}
@@
 \newcommand{\norm}[1]{{||#1||}} 
-\newcommand{\st}{{\,|\,}} 
+\renewcommand{\st}{{\,|\,}} 
 \newcommand{\reals}{{\mathbb R}}
@@
 \newcommand\tab[1][1cm]{\hspace*{#1}}
+
+\definecolor{lightyellow}{cmyk}{0,0,0.5,0}
+\sethlcolor{lightyellow}
+
+\newcommand{\highlight}[1]{%
+  \colorbox{yellow!50}{$\displaystyle#1$}}
 
@@
 \State $\bm S_{old} \leftarrow \bm S$
-\State $\bm G \leftarrow (\bm Y_S \times \bm Y_S) \bm \cdot \mathcal{K}\left( \bm X_S,\,\bm X_S,\,\sigma\right)$ \Comment{Build Graham matrix}
+\State $\bm G \leftarrow (\bm Y_S \times \bm Y_S) \bm \cdot \mathcal{K}\left( \bm X_S,\,\bm X_S,\,\sigma\right)$ \Comment{Build \hl{Gram} matrix}
 \State $\bm \alpha \leftarrow \text{ quadprog}\left(\bm G, \bm{-1}^n, \bm Y_S, \bm 0^n, \bm 0^n, \bm C^n\right)$ \Comment{Solve QP Problem}
@@
 \newpage
-This formulation is designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances.
-MISVM allows multiple representatives to be chosen from negative bags and limits positive bag-representatives to be one, while MIRSVM allows for balanced bag-representative selection, where each bag is allowed one.
+\hl{The MIRSVM formulation and representative selector are} designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances.
+MISVM allows multiple representatives to be chosen from negative bags and limits \hl{the number of positive bag-representatives to be one}, while MIRSVM allows for balanced bag-representative selection, where \hl{bags of each class are allowed a representative}.
 MISVM also uses a wrapper method to initialize the positive bag-representatives by taking the mean vector of the instances within each positive bag.

### 2017-09-15 ArticleRevision/article_with_markings/letter/letter.tex
Added reivewers comments to the text and started some answers.

\documentclass[a4paper,notitlepage]{article}
\usepackage[colorlinks,linkcolor=blue,citecolor=green,filecolor=magenta,urlcolor=blue]{hyperref}
\usepackage{url}
\setlength{\parskip}{2ex}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=20mm,
 }

\begin{document}

\noindent \textbf{\small MANUSCRIPT NUMBER:} PR-D-17-01043

\noindent \textbf{\small TITLE:} {\small MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives}

\noindent \textbf{\small AUTHORS:} {\small Gabriella Melki, Alberto Cano, and Sebasti\'{a}n~Ventura}

\bigskip

\noindent Dear Editor and Reviewers,

\noindent According to your suggestions, we have prepared a new version of our paper, introducing the changes required to incorporate all the reviewers' comments.
The following is our explanation of the changes made, as well as how they address the comments raised by the reviewers. Text in bold corresponds to the original comments. We hope to satisfy the reviewers' expectations. Finally, we are really grateful to the reviewers for their insightful and constructive comments and suggestions in their revisions, which have helped us to improve the quality of the article.

\noindent We hope that the reviewers find the proposed thorough revision of our manuscript satisfactory. We look forward to hearing from you soon.

\section{Reviewer \#1}

\noindent \textbf{\textit{The authors propose MIRSVM, a support vector machine (SVM) based approach for classification which uses the bag-level information for training. The proposed algorithm is able to identify the bag representatives which are the instances that impact the classification the most. One of the strengths of their method is that it deals with the potential class imbalance by incorporating both positive and negative bags and limiting them to have maximum 1 representative. Unlike other methods the MIRSVM doesn't have any assumption about the data distribution. 
I support publication of this paper in this journal because: }}

\noindent \textbf{\textit{The topic is very well-suited to the interests of this Journal.}}
\noindent \textbf{\textit{The paper is very organized and written smoothly.}}
\noindent \textbf{\textit{Enough background information is given about SVM, multi-instance learning and bag level classification.}}
\noindent \textbf{\textit{A comprehensive literature review is provided. Each method is shortly described and the pitfalls are discussed which takes the reader to the idea of why an approach like MIRSVM is needed.}}

\medskip

\noindent Answer...

\noindent \textbf{\textit{The algorithm is clearly described through flowcharts, pseudocodes and examples.}}
\noindent \textbf{\textit{All notations are given at the beginning of the paper which helps the reader to follow the equations easier.}}

\medskip

\noindent Answer...

\noindent \textbf{\textit{This method is very well evaluated by comparison of the results vs. 11 competing techniques on 15  datasets which provides enough data to the solidity of the evaluations.}}
\noindent \textbf{\textit{The authors also have visual comparisons. For example they compare MIRSVM vs MISVM one of the competing techniques which are trained using the same parameters (Fig. 4). The plots clearly indicate the optimal number of support vectors as well as smoother data representation when using MIRSVM.}}
\noindent \textbf{\textit{The authors also showed that their method runs faster than all 11 approaches.}}
\noindent \textbf{\textit{The statistical analysis and tests are described in detail. By using both precision and recall rates they demonstrate that unlike other methods, MIRSVM doesn't have bias toward positive or negative bags and has balance of precision-recall trade-off. They also perform a statistical analysis using Cohen's Kappa Rate which again proves that MIRSMV outperforms the other methods.}}

\smallskip

\noindent  \textbf{\textit{I would strongly recommend this paper to be published in Elsevier, Pattern Recognition Journal.}}

\medskip

\noindent The answer...

\section{Reviewer \#2}

\noindent \textbf{\textit{The paper presents a new approach for solving multiple-instance classification 
problem from bag-level perspective. The authors formulated an SVM classifier such that it finds optimal decision hyperplane that separates positive bags from the negative ones. The key idea is to train the SVM using representative instances from each of the bags. The representative instances are those having the largest magnitude of the dot product with the weight vector. In other words, the most positive instances are chosen from positive bags while the least negative instances are chosen from the 
negative bags. The authors claimed that the approach helps alleviate the data imbalance problem often encountered in multiple-instance learning. The experimental results demonstrated that the proposed method is superior to existing algorithms designed for multiple-instance learning. The proposed method is also faster than many of the existing approaches. }}

\medskip

\noindent Answer...

\noindent \textbf{\textit{Comment 1: First of all, what I like most about the paper is the way the comparisons are conducted. Not many of the papers that I read/reviewed provided such detailed statistics. Please keep up the good practice. }}

\medskip

\noindent Answer...

\noindent \textbf{\textit{Comment 2: However, according to me, I think the technical novelty is somewhat marginal. 
The formulations in section 3 are all standard SVM, except that it now operates at the bag-level. The only (technical) contribution I see is the new measure used to select bag representatives. And this contribution should be highlighted. }}

\medskip

\noindent Answer...

\noindent \textbf{\textit{Comment 3: I also feel that Section 1 and 2 are too lengthy. It feels like reading a 
book chapter on multiple-instance learning. These two parts combined are almost half of the manuscript. Also many of the details in Section 3 could be left out as they are not much different from the standard SVM. That is to say, I would like the authors to consider making those parts more concise. }}

\medskip

\noindent Answer...

\noindent \textbf{\textit{Comment 4: Lastly, I think the standard MI assumption only makes sense in some problem domains. (Dietterich's drug-activity prediction seems to be the case). So, I believe it would make the paper stronger if the authors also present some interesting real-world usage of the proposed algorithm. }}

\medskip

\noindent Answer...

\noindent \textbf{\textit{Speicific Comments:}}
\begin{enumerate}
\item \textbf{\textit{I think your ranges for C parameter and kernel width are too narrow, especially on the lower end. Is there any specific reason for the choice apart from to speed up the cross validation process? Besides, I usually see people using the range $2^i$ where $i = -10:10$. So, how about considering some smaller values as well, say $0.00001$ and/or $0.001$?}}

\medskip

\noindent Answer...

\item \textbf{\textit{Page 5, Line 8: ``they assume the distribution the instances in positive bags is positive", I don't understand this sentence, please clarify. What does 'distribution is positive' mean in this context?}}

\medskip

\noindent Thank you for pointing out that statement. What we meant was that they assume that all the instances within positive bags are assumed to be positive, or to follow the distribution of positively labelled data.

\item \textbf{\textit{Page 12, first sentence: ``This formulation...", what formulation? I suppose some equations are missing?}}

\medskip

\noindent We apologize for the ambiguity. What we were specifying was the MIRSVM bag-representative selector and formutlation. We've made the appropriate change in text.

\item \textbf{\textit{Page 12, Line 5: ``... where each bag is allowed one." $\rightarrow$ I don't think this is grammatical.}}

\medskip

\noindent Answer...

\item \textbf{\textit{Algorithm 1 Line 8: Graham matrix $\rightarrow$ Gram matrix?}}

\medskip

\noindent Answer...

\end{enumerate}

\medskip

\noindent Answer...

\end{document}

### 2017-09-19 ArticleRevision/article_with_markings/atricle_with_markings.tex
Finished shortening sections 1, 2, & 3. Still need to emphasize the bag-representative selector for reviewer 2

@@
 
+\usepackage[most]{tcolorbox}
+\newtcolorbox{highlighted}{colback=lightyellow,coltext=black,breakable,boxrule=0pt,frame hidden}
+
 \definecolor{lightyellow}{cmyk}{0,0,0.5,0}
 \sethlcolor{lightyellow}
-
-\newcommand{\highlight}[1]{%
-  \colorbox{yellow!50}{$\displaystyle#1$}}
 
@@
 In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns between training samples and their class label.
-\textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification and annotation \citep{Herman2008,qi2007}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
+\textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because \hl{of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival} {\citep{Herman2008,qi2007}}, \hl{human action recognition {\citep{Yi2016}}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).}
 
@@
 Support vector machines represent a set of supervised, linear and nonlinear, classification and regression methods that have theoretical foundations on Vapnik-Chervonenkis (VC) theory~\citep{Huang2006,Schoelkopf2002}.
-SVM models are similar to other machine learning algorithms and techniques, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, which makes them a useful data mining tool for various real-world applications~\citep{chen2016structural}.
+\hl{SVM models are similar to other machine learning techniques}, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, \hl{making them a useful tool for various real-world applications}~\citep{chen2016structural}.
 
 To address the limitations presented by MIL algorithms, this paper proposes a novel support vector machine formulation with a bag-representative selector, called Multiple-Instance Representative Support Vector Machine (MIRSVM).
-SVMs are known to perform well when data is limited, therefore combining them with a bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without assuming the bags' internal distributions.
+SVMs are known to perform well when data is limited, \hl{therefore combining them with a novel bag-representative selector aims to remedy class imbalance caused by limited positive bag instances}, without assuming the bags' internal distributions.
 The algorithm selects bag-representatives iteratively according to the standard MI assumption, ensuring known information, such as the negative bag labels, are fully utilized during the training process.
@@
 The dual formulation is kernelized with a Gaussian radial basis function, which calculates the distances between bag representatives.
-
+\newpage
 \iitem Devising a unique bag-representative selection method that makes no presumptions about the underlying distributions of the instances within each bag, while maintaining the default MI assumption.
@@
 An example MI dataset representation is shown in Figure~\ref{fig:mirep}.
-Using the training dataset $\mathcal{D} = \{(\mathcal{B}_1,Y_1), \ldots, (\mathcal{B}_n,Y_n)\}$, the goal is to train a classifier that predicts the label of an unseen bag, $f(\mathcal{B}_{n+1}) \rightarrow Y_{n+1}$~\citep{Amores2013}.
+Using the training dataset $\mathcal{D} = \{(\mathcal{B}_1,Y_1), \ldots, (\mathcal{B}_n,Y_n)\}$, the goal is to train a classifier that predicts the label of an unseen bag, $f(\mathcal{B}_{n+1}) \rightarrow Y_{n+1}$.
 In order to build a classifier without any knowledge of the individual training instance labels,~\citet{Dietterich1997} proposed the \textit{standard MI} (SMI) hypothesis based on the drug-activity prediction domain, shown in Equation~\eqref{eqn:stas}, which states that a bag is labeled positive if and only if at least one of the instances in the bag is positive, and is labeled negative otherwise.
@@
 This implies that individual instance labels $y_i$ exist, but are not known (for positive bags) during training.
-Equation~\eqref{eqn:stas} can also be rewritten as Equation~\eqref{eqn:stasmax} for simplicity:
-\begin{equation}
-\centering \label{eqn:stasmax}
-Y_I = \text{argmax}_{\forall i \in I}\,\,\, y_i.
-\end{equation}
+Equation~\eqref{eqn:stas} \hl{can also be rewritten as $Y_I = \text{argmax}_{\forall i \in I}\,\,\, y_i$, for simplicity.}
 
 In addition to the SMI assumption, alternative MI assumptions have been proposed to date~\citep{Foulds2010}.
-A recent review describing the taxonomy of multi-instance classification was presented by~\citet{Amores2013}.
-The review presents various methods and algorithms used in literature which are categorized based on their approach to handling the MI input space.
-Instance-based classifiers that fall under the \textit{instance-space paradigm}, aim to separate instances in positive bags from those in negative ones.
-Bag-level classifiers (\textit{bag-space paradigm}) treat each bag as a whole entity, implicitly extracting information from each bag in order to accurately predict their labels~\citep{qiao2017diversified}.
+\hl{A recent review describing the taxonomy of multi-instance classification was presented by }\citet{Amores2013}.
+\hl{Classifiers that fall under the \textit{instance-space paradigm} aim to separate instances in positive bags from those in negative ones.} Bag-level classifiers (\textit{bag-space paradigm}) treat each bag as a whole entity, implicitly extracting information from each bag in order to accurately predict their labels~\citep{qiao2017diversified}.
 Methods that fall under the \textit{embedded-space paradigm} map the input bags to a single feature vector that explicitly encapsulates all the relevant information contained within each bag.
 
-Instance-based methods that follow the SMI assumption attempt to identify desirable instance properties that make a bag positive.
-One traditional method in this category is the Axis-Parallel Rectangle (APR)~\citep{Dietterich1997}, which trains a model that assigns a positive label to an instance if it belongs to an axis-parallel rectangle in feature space, and assigns a negative label otherwise.
-The APR is optimized by maximizing the number of positive bags in the training set containing at least one instance in the APR, while concurrently maximizing the number of negative bags that do not contain any instance in the APR.
-Another similar method is the Diverse Density (DD)~\citep{Maron1998} framework which is maximized for instances in feature space that are near at least one instance in a positive bag and far from all instances in negative bags.
-In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\citet{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\citet{Auer2004} present a boosting approach that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall).
-This approach is similar to that of APR and DD, except that~\citet{Auer2004} propose computing optimal balls per positive bags.
-A major challenge affecting these methods is that the distributions of the positive and negative bags affect their performance.
-Methods based on the DD metric~\citep{qi2007,Carbonneau2016,Chen2006,Chen2004} assume the positive instances form a cluster, which may not be the case.
-Alternatively, \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
+\hl{Instance-based methods under the SMI assumption attempt to identify desirable instance properties that make a bag positive.
+One traditional method is the Axis-Parallel Rectangle (APR) {\citep{Dietterich1997}}, which assigns a positive label to an instance if it belongs to an APR.
+The Diverse Density (DD){~\citep{Maron1998}} measure is maximized for instances that are near at least one instance in a positive bag and far from all instances in negative bags.}~\citet{Auer2004} \hl{present a boosting approach that uses balls centered around positive bags, called Multi-Instance Optimal Ball (MIOptimalBall).
+A major challenge of these methods is that the distributions of positive and negative bags affect their performance}~\citep{Chen2006,Chen2004}.
+\hl{Alternatively, }\citet{Fu2011} \hl{models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.}
+
+Some methods in literature~\citep{Ray2005,Viola2005}, such as Simple-MI~\citep{Dong2006}, \hl{transform the MI dataset to a traditional instance-level dataset.
+This approach was evaluated by}~\citet{Bunescu2007} \hl{and they proposed mapping each bag to a max-min vector.
+The disadvantage of these approaches is that they assume the labels of all instances within positive bags are positive, when this may not be the case.}
 \begin{figure*}
 \centering
+\small
 \begin{tabular}{|c|ccccc|c|}
@@
 
-Some methods in literature~\citep{Ray2005,Viola2005}, such as Simple-MI~\citep{Dong2006}, transform the MI dataset to a traditional instance-level dataset.
-Simple-MI represents each bag with the mean vector of the instances within it.
-This approach was evaluated by~\citet{Bunescu2007} and they proposed mapping each bag to a max-min vector, a concatenation of the features with the highest and lowest values.
-The major disadvantage of these types of approaches is that they assume the distribution the instances in positive bags is positive, when it may not be.
-
 An extension of traditional single-instance $k$-nearest neighbors method (KNN) was proposed by~\citet{Wang2000} to be applied to the bag-level, named CitationKNN.
-This method uses a distance function between bags in order to determine bag similarities.
-Not only are the set of closest bags to a single bag  considered, but also how many bags is the single bag closest to.
-A voting scheme is then used to determine the bag class labels.~\citet{Xu2011} proposed a multi-instance Decision-Based Neural Network (MI-DBNN), a probabilistic variant of the traditional DBNN, which is a neural network with a modular structure~\citep{Herrera2016}.
-
-~\citet{Blockeel2005} introduced the Multi-Instance Tree Inducer (MITI), based on the standard MI assumption, which uses decision trees as a heuristic to solve the MI problem.
-This approach aims to identify whether an instance within a bag is truly positive and eliminate false positives within the same bag.
-The disadvantage of this approach stems from removing instances considered as false positives from partially grown trees without updating the existing tree structure.~\citet{Bjerring2011} then enhanced this approach by creating the method Multi-Instance Rule Induction (MIRI).
-The algorithm aims to eliminate any possibility of a suboptimal split because the tree is discarded and regrown.
-Other popular methods include MIBoost~\citep{Hall2009}, MIWrapper~\citep{Frank2003}, and Two-Level Classifier (TLC)~\citep{Wang2014}.
+\hl{This method uses a distance function between bags in order to determine bag similarities and a voting scheme to determine the bag class labels.}~\citet{Xu2011} \hl{proposed a multi-instance Decision-Based Neural Network (MI-DBNN), which is a neural network with a modular structure{~\citep{Herrera2016}}}.
+
+~\citet{Blockeel2005} introduced the \hl{Multi-Instance Tree Inducer (MITI), which uses decision trees as a heuristic to solve the MI problem.
+MITI aims} to identify whether an instance within a bag is truly positive and eliminate false positives within the same bag.
+The disadvantage of this approach stems from removing instances considered as false positives from partially grown trees without updating the existing tree structure.~\citet{Bjerring2011} then enhanced this approach by creating the \hl{method Multi-Instance Rule Induction (MIRI), which eliminates any possibility of a suboptimal split because the tree is discarded and regrown.} Other popular methods include MIBoost~\citep{Hall2009}, MIWrapper~\citep{Frank2003}, and Two-Level Classifier (TLC)~\citep{Wang2014}.
 
@@
 Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}.
-The proposed method, MIRSVM, is a general method that uses support vector machines to design a MIL model without making prior assumptions about the data.
-Classifiers of this type are known to provide better generalization capabilities and performance, as well as sparser models.
+\hl{MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data.
+Classifiers of this type are known to provide better generalization capabilities, performance, and sparser models.}
 
 \subsection{Support Vector Machines}\label{subsec:svms}
-Most classical learning techniques require knowledge of the data distribution to build accurate models.
-This is a serious restriction because, in most cases, the data distribution is unknown~\citep{Kecman2001}.
+Most classical learning techniques require knowledge of the data \hl{distribution to build accurate models, which is a serious restriction because}, in most cases, the distribution is unknown~\citep{Kecman2001}.
 SVMs represent learning techniques that have been introduced under the \textit{structural risk minimization} (SRM) framework and VC theory.
@@
 In the context of classification, this problem is approached by searching for the optimal \textit{maximal margin} of separability between classes~\citep{carrasco2015multi,fan2017mreklm}.
-Since most real-world datasets are non-linearly separable, ~\citet{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:
-\begin{subequations} 
-\label{eq:primalsvm}
-\begin{alignat}{2}
-\min\limits_{\bm w,b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{m}\sum_{i=1}^m \xi_i \tag{\ref{eq:primalsvm}} \\ 
-\text{s.t.}& {\,\,} y_i(\langle\bm{w},\bm{x}_i\rangle + b) \geq 1 - \xi_i,\,\, \forall i \in \{1,\ldots,m\}  \\
-{} & {\,\,} \xi_i \geq 0,\,\, \forall i \in \{1,\ldots,m\},
-\end{alignat}
-\end{subequations} 
-where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term, and $C \in \reals$ is the penalty parameter that controls the trade-off between margin maximization and classification error minimization.
-The slack variable $\bm \xi \in \reals^m$ allows for optimizing over sample errors.
-However, if the training dataset is not linearly separable, the classifier may not have a good generalization capability~\citep{Nocedal2006}.
+Since most real-world datasets are non-linearly separable, ~\citet{Cortes1995} \hl{introduced the \textit{Soft-Margin L$1$-SVM}.
+However, if the training dataset is not linearly separable,} the classifier may not have a good generalization capability~\citep{Nocedal2006}.
 Generalization and linear separability can be enhanced by mapping the original input space to a higher dimensional dot-product space by using a kernel function shown in Equation~\eqref{eqn:kerneltrick}:
@@
 \text{s.t.} &\,\,\,\, \sum_{i=1}^m \alpha_iy_i = 0,  \\
-&\,\,\,\, 0 \leq \alpha_i \leq \frac{C}{m},\,\, \forall i \in \{1,\ldots,m\}. 
+&\,\,\,\, 0 \leq \alpha_i \leq \frac{C}{m},\,\, \forall i \in \{1,\ldots,m\}, 
 \end{alignat}
 \end{subequations}
+
+\hl{where $C \in \reals$ is the penalty parameter that controls the trade-off between margin maximization and classification error minimization.}
 
@@
 It tries to identify the key instance from each positive bag that makes the bag positive by assuming it has the highest margin value~\citep{Herrera2016}.
-Instances from positive bags are selected as bag-representatives, and the algorithm iteratively creates a classifier that separates those representatives from all instances from the negative bags.
-Using bag-representatives from one class and all instances from the other is an example of an approach that combines rules from the SMI assumption and the collective assumption.
-This approach was used in the context of active learning.~\citet{Wang20143106} proposed a multi-criteria decision making system that measures the significance of unlabeled instances and selects the best instance iteratively using MISVM.
-A disadvantage of the approach MISVM takes, stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\citet{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which does not discard the negative instances of the positive bags.
-It rather tries to identify the instances within positive bags that are negative and utilize them in the construction of the negative margin.
-The main disadvantage of these approaches is that they create an imbalanced class problem that favors the negative class, resulting in a biased classifier.
+\hl{Using bag-representatives from the positive class class and all instances from the other is an example of an approach that combines rules from the SMI assumption and the collective assumption.}~\citet{Wang20143106} proposed a multi-criteria decision making system that measures the significance of unlabeled instances and selects the best instance iteratively using MISVM.
+\hl{A disadvantage of this approach stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.}~\citet{Andrews2002} also proposed \hl{a second mixed-integer instance-level approach, named mi-SVM, which tries to identify the instances within positive bags that are negative and utilize them in the construction of the negative margin.} The main disadvantage of these approaches is that they create an imbalanced class problem that favors the negative class, resulting in a biased classifier.
 
@@
 
-One of the first bag-level approaches to the multi-instance SVM problem was proposed by \citet{Smola2002}, who defined a bag-level kernel, which determines the similarity between two bags in a higher dimensional space.
-Using such a kernel, the margin can be optimized over bags without any modification to the SVM problem~\citep{Herrera2016}.~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance.
+One of the first bag-level approaches to the multi-instance SVM problem was proposed by \citet{Smola2002}, \hl{who defined a bag-level kernel, which determines the similarity between two bags in a higher dimensional space.}~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance.
 
@@
 all instances are guaranteed to be negative.
-This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
-In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
+This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$, \hl{where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term.} In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
 Equation~\eqref{eq:primalmirsvm} presents the primal MIRSVM optimization problem:
@@
 \end{subequations} 
-where $\bm S_I$ is a set of the bag representatives' indices and $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$.
-Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.
+\hl{where $\bm S_I$ is a set of the bag representatives' indices, $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$, and the slack variable $\bm \xi \in \reals^m$ allows for optimizing over bag errors.
+Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.}
+
 Solving the optimization problem given in Equation~\eqref{eq:primalmirsvm} using a quadratic programming solver is a computationally expensive task due to the number of constraints, which scales by the number of bags $n$, as well as the calculation of the inner product between two $d$-dimensional vectors in constraint~\eqref{eq:primalmirsvm1}.
 The proposed solution for these problems was deriving and solving the dual of the optimization problem given by Equation~\eqref{eq:primalmirsvm}.
-
 The dual can be formed by taking the Lagrangian of~\eqref{eq:primalmirsvm}, given by Equation~\eqref{eqn:svmlagrangian}, where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers.
@@
 \end{align}
-\newpage
+
 By substituting Equations~\eqref{eqn:optcond1},~\eqref{eqn:optcond2}, and~\eqref{eqn:optcond3} into the Lagrangian in~\eqref{eqn:svmlagrangian}, the dual MIRSVM formulation becomes the following:
@@
 
-We then kernelize the dual function by replacing the inner product of the samples in feature space with their corresponding kernel values, $\spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right)$.
-The dual function is now written as:
-\begin{subequations} 
-\label{eq:dualmirsvm}
-\begin{alignat}{2}
-\max\limits_{\bm \alpha}& \sum_I \alpha_I - \frac{1}{2}\sum_I \sum_{K\in I} \alpha_I \alpha_K Y_I Y_K  \spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right) \tag{\ref{eq:dualmirsvm}}\\
-\text{s.t.}&  \sum_I{\alpha_IY_I} = 0\,  \\
-{} & 0 \leq \alpha_I \leq \frac{C}{n},\, \forall I \in \set{1,\ldots,n}.
-\end{alignat}
-\end{subequations}
-
-One of the biggest advantages of the dual SVM formulation is the sparseness of the resulting model.
-This is because support vectors, instances that have their corresponding $\alpha_I \neq 0$, are only considered when forming the decision boundary.
-MIRSVM uses a Gaussian RBF kernel, given by Equation~\eqref{eq:gaussiankernel}, where $\sigma$ is the Gaussian shape parameter.
+\hl{We then kernelize the dual by replacing the inner product of the samples in feature space with their corresponding kernel values, $\spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right)$.
+One of the biggest advantages of the dual SVM formulation is the sparseness of the resulting model, because support vectors, instances that have their corresponding $\alpha_I \neq 0$, are only considered when forming the decision boundary.} MIRSVM uses a Gaussian RBF kernel, given by Equation~\eqref{eq:gaussiankernel}, where $\sigma$ is the Gaussian shape parameter.
 \begin{equation}
@@
 \begin{minipage}{\textwidth}
-\adjustbox{scale=0.901}{
+\adjustbox{scale=0.9}{
 \begin{tikzpicture}[%
@@
 \end{tikzpicture}}
-\caption{MIRSVM flow diagram.
-This figure represents a summary of the steps performed by the MIRSVM algorithm.
-The representatives are first randomly initialized and continuously updated according to the current hyper-plane, which is found using a quadratic programming (QP) solver.
-Upon completion, the model is returned along with the optimal bag-representatives.}
+\caption{\hl{This figure represents a summary of the steps performed by MIRSVM.
+The representatives are first randomly initialized, then continuously updated according to the current hyper-plane, which is found using a quadratic programming (QP) solver.} Upon completion, the model is returned along with the optimal bag-representatives.}
 \end{minipage}

### 2017-09-19 ArticleRevision/article_with_markings/letter/letter.tex
Finished shortening sections 1, 2, & 3. Still need to emphasize the bag-representative selector for reviewer 2

@@
 
-\medskip
-
-\noindent Answer...
-
 \noindent \textbf{\textit{Comment 1: First of all, what I like most about the paper is the way the comparisons are conducted.
@@
 
-\noindent Answer...
+\noindent We tried to be as thorough as possible during our experimental study and we intend on continuing with this method of experimentation. We really appreciate your comment on this.
 
@@
 
-\noindent \textbf{\textit{Comment 3: I also feel that Section 1 and 2 are too lengthy. It feels like reading a 
-book chapter on multiple-instance learning.
+\noindent \textbf{\textit{Comment 3: I also feel that Section 1 and 2 are too lengthy.
+It feels like reading a book chapter on multiple-instance learning.
 These two parts combined are almost half of the manuscript.
@@
 
-\noindent Answer...
+\noindent We made some changes to sections 1, 2, and 3 to try and condense the information given.
+We shortened and rewrote some of the descriptions on the background of multiple-instance learning, as well as removed some of the basic SVM formulations from the SVM background to avoid repetition in Section 3.
+Your comment on the length of those sections makes sense and we hope to made the information more concise.
 
@@
 
-\noindent Answer...
+\noindent Thank you for noting this.
+As you've suggested, we added a couple of additional applications of the standard MI assumption to the paper.
+We hope that the following real-world scenarios provide a more global picture as to why MI algorithms are useful.
+\begin{enumerate}
+\item Bioinformatics: Protein Identification
+\item Image classification \& retrieval
+\item Web mining \& text classification
+\item Medical diagnosis \& imaging
+\end{enumerate}
 
@@
 
-\noindent Answer...
+\noindent According to your suggestion, we tested the performance of our method using a wider range of parameters (especially with lower C values).
+Results were exactly the same as originally reported, since the best parameters were still selected in the domain we originally defined.
+The only difference of evaluating a larger number of parameters would be a longer runtime, but we observed no performance different in the results for any of the datasets evaluated.
+Thank you.
 
@@
 What we meant was that they assume that all the instances within positive bags are assumed to be positive, or to follow the distribution of positively labelled data.
+This statement was clarified in the text.
+Please let us know if it needs any further explanation.
 
@@
 
-\noindent We apologize for the ambiguity. What we were specifying was the MIRSVM bag-representative selector and formutlation. We've made the appropriate change in text.
+\noindent We apologize for the ambiguity.
+What we were specifying was the MIRSVM bag-representative selector and formutlation, referenced by Equations 12 and 13.
+We've made the appropriate change in text to clarify the thought.
 
@@
 
-\noindent Answer...
+\noindent We've updated the text to the correct grammar. Thanks for pointing that out.
 
@@
 
-\noindent Answer...
+\noindent Yep that's correct, thanks for catching that! We've updated the text to be ``Gram matrix".
 

### 2017-09-19 ArticleRevision/article_with_markings/atricle_with_markings.tex
Made changes according to Alberto + ran spell checker. Going to copy these to dropbox so he can submit it later.

@@
 In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns between training samples and their class label.
-\textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because \hl{of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival} {\citep{Herman2008,qi2007}}, \hl{human action recognition {\citep{Yi2016}}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).}
+\textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because \hl{of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival} {\citep{qi2007,cao2017weakly}}, \hl{human action recognition {\citep{Yi2016}}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).}
 
@@
 
-For most of the methods described above, implicit or explicit assumptions have been made about the distribution of the data.
+For most of the methods described above, implicit or explicit assumptions have been made about the distribution of the data~\citep{2017-KNOSYS-MIMV}.
 Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}.
@@
 Based on the SMI hypothesis, only one instance in a bag is required to be positive for the bag to adopt a positive label.
-Due to the unknown distribution of instances within positive bags, MIRSVM is designed to give preference to negative bags during training, because their distribution is known, i.e.
+\hl{Due to the unknown distribution of instances within positive bags, MIRSVM is designed to give preference to negative bags during training, because their distribution is known, i.e.
 all instances are guaranteed to be negative.
-This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$, \hl{where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term.} In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
+This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule:}
+\begin{equation}
+\label{eq:SIPrimal}
+\centering
+s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n},
+\end{equation}
+\hl{where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term.} In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
 Equation~\eqref{eq:primalmirsvm} presents the primal MIRSVM optimization problem:
@@
 \hl{where $\bm S_I$ is a set of the bag representatives' indices, $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$, and the slack variable $\bm \xi \in \reals^m$ allows for optimizing over bag errors.
-Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.}
+Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.
+This is one of the benefits of the MIRSVM formulation, whereby using a bag-representative selector, traditional SVM solvers can be used for new data representations such the multi-instance data.}
 
@@
 The proposed solution for these problems was deriving and solving the dual of the optimization problem given by Equation~\eqref{eq:primalmirsvm}.
-The dual can be formed by taking the Lagrangian of~\eqref{eq:primalmirsvm}, given by Equation~\eqref{eqn:svmlagrangian}, where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers.
-\begin{equation}
-\centering \label{eqn:svmlagrangian}
-\resizebox{.9\textwidth}{!}{$
-\begin{aligned}
-\mathcal{L}\left(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}\right) = \frac{1}{2}\sum_{j=1}^d w_j^2  + \frac{C}{n}\sum_I \xi_I - \sum_I{\beta_I \xi_I} - \sum_I{\alpha_I\left(Y_I\left(\sum_{j=1}^d w_j x_{s_Ij} + b\right) -1 + \xi_I\right)}
-\end{aligned}$} 
-\end{equation}
-
-At optimality~\citep{Boyd2004}, $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$ and the following conditions are met:
-\begin{align}
-&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,Y_I\, x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
-&\frac{\partial\mathcal{L}}{\partial b}: \sum_I{\alpha_IY_I} = 0,\label{eqn:optcond2}\\
-&\frac{\partial\mathcal{L}}{\partial\xi_I}: \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}\label{eqn:optcond3} 
-\end{align}
-
-By substituting Equations~\eqref{eqn:optcond1},~\eqref{eqn:optcond2}, and~\eqref{eqn:optcond3} into the Lagrangian in~\eqref{eqn:svmlagrangian}, the dual MIRSVM formulation becomes the following:
+
+\hl{The dual can be formed by taking the Lagrangian of~{\eqref{eq:primalmirsvm}}, $\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta})$, and substituting the optimality conditions (from $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$), where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers.
+The dual MIRSVM formulation becomes the following:}
 \begin{subequations} 

### 2017-09-19 ArticleRevision/article_with_markings/letter/letter.tex
Made changes according to Alberto + ran spell checker. Going to copy these to dropbox so he can submit it later.

--- 2017-09-15 ArticleRevision/article_with_markings/letter/letter.tex
@@
 
-\noindent Answer...
+\noindent We appreciate the reivewer's comments on the background we have given to present our contribution.
 
@@
 
-\noindent Answer...
+\noindent We tried our best to provide a comprehensive and detailed explanation of our contribution, and we thank the reviewers for their positive comments on this.
 
@@
 
-\noindent The answer...
+\noindent Again, we would like to express our gratitude on the reviewer's positive comments about our contribution and experimental study.
+We wanted to be as clear as possible when highlighting the differences between our method and the state-of-the-art methods, and Figure 4 was one of the ways to show how selecting representatives from one class and not the other can prove to be biased.
+So, we thank the reviewer on aknowledging this.
 
@@
 
-\noindent Answer...
+\noindent We thank and appreciate the reviewer for the positive and constructive comments given towards improving this paper.
 
@@
 
-\noindent Answer...
+\noindent We tried to be as thorough as possible during our experimental study and we intend on continuing with this method of experimentation. We really appreciate your comment on this.
 
 \noindent \textbf{\textit{Comment 2: However, according to me, I think the technical novelty is somewhat marginal.
-The formulations in section 3 are all standard SVM, except that it now operates at the bag-level.
+The formulations in Section 3 are all standard SVM, except that it now operates at the bag-level.
 The only (technical) contribution I see is the new measure used to select bag representatives.
@@
 
-\noindent Answer...
+\noindent We took your advice on this and removed some of the standard SVM formulations in Section 3 (specifically the Langrangian and derivation of the dual), highlighted the bag-representative selector, as well as emphasized the major benefits using it in conjunction with the bag level formulation of the SVM.
+Therefore, this way we enhance and clarify the benefits of the contribution, without having redundant information within the section.
 
-\noindent \textbf{\textit{Comment 3: I also feel that Section 1 and 2 are too lengthy. It feels like reading a 
-book chapter on multiple-instance learning.
+\noindent \textbf{\textit{Comment 3: I also feel that Section 1 and 2 are too lengthy.
+It feels like reading a book chapter on multiple-instance learning.
 These two parts combined are almost half of the manuscript.
@@
 
-\noindent Answer...
+\noindent We rewrote and reorganized Sections 1, 2, and 3 to condense the information given.
+We shortened and rewrote some of the descriptions on the background of multiple-instance learning, as well as removed some of the basic SVM formulations from the background to avoid repetition in Section 3.
+Your comment on the length of those sections makes sense, thank you.
 
@@
 
-\noindent Answer...
+\noindent Thank you for noting this.
+As you have suggested, we added a couple of additional applications of the standard MI assumption to the paper.
+Specifically, the following real-world scenarios provide a more global picture as to why MI algorithms are useful: bioinformatics (protein identification), image classification \& retrieval, web mining \& text classification, and medical diagnosis \& imaging.
 
@@
 
-\noindent Answer...
+\noindent According to your suggestion, we tested the performance of our method using a wider range of parameters (especially with lower C values).
+Results were exactly the same as originally reported, since the best parameters were still selected in the domain we originally defined.
+The only difference of evaluating a larger number of parameters would be a longer runtime, but we observed no performance difference in the results for any of the datasets evaluated.
+Thank you.
 
@@
 What we meant was that they assume that all the instances within positive bags are assumed to be positive, or to follow the distribution of positively labelled data.
+This statement was clarified in the text.
 
@@
 
-\noindent We apologize for the ambiguity. What we were specifying was the MIRSVM bag-representative selector and formutlation. We've made the appropriate change in text.
+\noindent We apologize for the ambiguity.
+What we were specifying was the MIRSVM bag-representative selector and formulation, referenced by Equations 12 and 13.
+We have made the appropriate change in text to clarify the meaning.
 
@@
 
-\noindent Answer...
+\noindent We've updated the text to the correct grammar. Thank you.
 
@@
 
-\noindent Answer...
+\noindent Thank you for making note of that. We have updated the text to be ``Gram matrix".
 
@@
 
-\noindent Answer...
+\noindent Thank you for your comprehensive notes and constructive comments on our paper.
 

### 2017-09-22 ArticleRevision/article/article.tex
Updated the article for Pattern Recognition to be without markings

@@
 In traditional classification, learning algorithms attempt to correctly label unknown samples by finding patterns between training samples and their class label.
-\textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as text categorization \citep{Andrews2002}, image classification and annotation \citep{Herman2008,qi2007}, human action recognition \citep{Yi2016}, and drug activity prediction \citep{Dietterich1997}.
+\textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival \citep{qi2007,cao2017weakly}, human action recognition \citep{Yi2016}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).
 
@@
 Support vector machines represent a set of supervised, linear and nonlinear, classification and regression methods that have theoretical foundations on Vapnik-Chervonenkis (VC) theory~\citep{Huang2006,Schoelkopf2002}.
-SVM models are similar to other machine learning algorithms and techniques, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, which makes them a useful data mining tool for various real-world applications~\citep{chen2016structural}.
+SVM models are similar to other machine learning techniques, but research has shown that they usually outperform them in terms of computational efficiency, scalability, and robustness against outliers~\citep{Kecman2016,Melki2016}, making them a useful tool for various real-world applications~\citep{chen2016structural}.
 
 To address the limitations presented by MIL algorithms, this paper proposes a novel support vector machine formulation with a bag-representative selector, called Multiple-Instance Representative Support Vector Machine (MIRSVM).
-SVMs are known to perform well when data is limited, therefore combining them with a bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without assuming the bags' internal distributions.
+SVMs are known to perform well when data is limited, therefore combining them with a novel bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without assuming the bags' internal distributions.
 The algorithm selects bag-representatives iteratively according to the standard MI assumption, ensuring known information, such as the negative bag labels, are fully utilized during the training process.
@@
 This implies that individual instance labels $y_i$ exist, but are not known (for positive bags) during training.
-Equation~\eqref{eqn:stas} can also be rewritten as Equation~\eqref{eqn:stasmax} for simplicity:
-\begin{equation}
-\centering \label{eqn:stasmax}
-Y_I = \text{argmax}_{\forall i \in I}\,\,\, y_i.
-\end{equation}
+Equation~\eqref{eqn:stas} can also be rewritten as $Y_I = \text{argmax}_{\forall i \in I}\,\,\, y_i$, for simplicity.
 
 In addition to the SMI assumption, alternative MI assumptions have been proposed to date~\citep{Foulds2010}.
-A recent review describing the taxonomy of multi-instance classification was presented by~\citet{Amores2013}.
-The review presents various methods and algorithms used in literature which are categorized based on their approach to handling the MI input space.
-Instance-based classifiers that fall under the \textit{instance-space paradigm}, aim to separate instances in positive bags from those in negative ones.
+A recent review describing the taxonomy of multi-instance classification was presented by \citet{Amores2013}.
+Classifiers that fall under the \textit{instance-space paradigm} aim to separate instances in positive bags from those in negative ones.
 Bag-level classifiers (\textit{bag-space paradigm}) treat each bag as a whole entity, implicitly extracting information from each bag in order to accurately predict their labels~\citep{qiao2017diversified}.
@@
 
-Instance-based methods that follow the SMI assumption attempt to identify desirable instance properties that make a bag positive.
-One traditional method in this category is the Axis-Parallel Rectangle (APR)~\citep{Dietterich1997}, which trains a model that assigns a positive label to an instance if it belongs to an axis-parallel rectangle in feature space, and assigns a negative label otherwise.
-The APR is optimized by maximizing the number of positive bags in the training set containing at least one instance in the APR, while concurrently maximizing the number of negative bags that do not contain any instance in the APR.
-Another similar method is the Diverse Density (DD)~\citep{Maron1998} framework which is maximized for instances in feature space that are near at least one instance in a positive bag and far from all instances in negative bags.
-In the Expectation-Maximization Diverse Density (EM-DD) algorithm,~\citet{Zhang2001} propose a similar framework that iteratively maximizes the DD measure.~\citet{Auer2004} present a boosting approach that uses balls centered around positive bags to solve the MI problem called Multi-Instance Optimal Ball (MIOptimalBall).
-This approach is similar to that of APR and DD, except that~\citet{Auer2004} propose computing optimal balls per positive bags.
-A major challenge affecting these methods is that the distributions of the positive and negative bags affect their performance.
-Methods based on the DD metric~\citep{qi2007,Carbonneau2016,Chen2006,Chen2004} assume the positive instances form a cluster, which may not be the case.
-Alternatively, \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
+Instance-based methods under the SMI assumption attempt to identify desirable instance properties that make a bag positive.
+One traditional method is the Axis-Parallel Rectangle (APR) \citep{Dietterich1997}, which assigns a positive label to an instance if it belongs to an APR.
+The Diverse Density (DD){~\citep{Maron1998}} measure is maximized for instances that are near at least one instance in a positive bag and far from all instances in negative bags.~\citet{Auer2004} present a boosting approach that uses balls centered around positive bags, called Multi-Instance Optimal Ball (MIOptimalBall).
+A major challenge of these methods is that the distributions of positive and negative bags affect their performance~\citep{Chen2006,Chen2004}.
+Alternatively \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
+
+Some methods in literature~\citep{Ray2005,Viola2005}, such as Simple-MI~\citep{Dong2006}, transform the MI dataset to a traditional instance-level dataset.
+This approach was evaluated by~\citet{Bunescu2007} and they proposed mapping each bag to a max-min vector.
+The disadvantage of these approaches is that they assume the labels of all instances within positive bags are positive, when this may not be the case.
 \begin{figure*}
 \centering
+\small
 \begin{tabular}{|c|ccccc|c|}
@@
 
-Some methods in literature~\citep{Ray2005,Viola2005}, such as Simple-MI~\citep{Dong2006}, transform the MI dataset to a traditional instance-level dataset.
-Simple-MI represents each bag with the mean vector of the instances within it.
-This approach was evaluated by~\citet{Bunescu2007} and they proposed mapping each bag to a max-min vector, a concatenation of the features with the highest and lowest values.
-The major disadvantage of these types of approaches is that they assume the distribution the instances in positive bags is positive, when it may not be.
-
 An extension of traditional single-instance $k$-nearest neighbors method (KNN) was proposed by~\citet{Wang2000} to be applied to the bag-level, named CitationKNN.
-This method uses a distance function between bags in order to determine bag similarities.
-Not only are the set of closest bags to a single bag  considered, but also how many bags is the single bag closest to.
-A voting scheme is then used to determine the bag class labels.~\citet{Xu2011} proposed a multi-instance Decision-Based Neural Network (MI-DBNN), a probabilistic variant of the traditional DBNN, which is a neural network with a modular structure~\citep{Herrera2016}.
-
-~\citet{Blockeel2005} introduced the Multi-Instance Tree Inducer (MITI), based on the standard MI assumption, which uses decision trees as a heuristic to solve the MI problem.
-This approach aims to identify whether an instance within a bag is truly positive and eliminate false positives within the same bag.
-The disadvantage of this approach stems from removing instances considered as false positives from partially grown trees without updating the existing tree structure.~\citet{Bjerring2011} then enhanced this approach by creating the method Multi-Instance Rule Induction (MIRI).
-The algorithm aims to eliminate any possibility of a suboptimal split because the tree is discarded and regrown.
+This method uses a distance function between bags in order to determine bag similarities and a voting scheme to determine the bag class labels.~\citet{Xu2011} proposed a multi-instance Decision-Based Neural Network (MI-DBNN), which is a neural network with a modular structure{~\citep{Herrera2016}}.
+
+~\citet{Blockeel2005} introduced the Multi-Instance Tree Inducer (MITI), which uses decision trees as a heuristic to solve the MI problem.
+MITI aims to identify whether an instance within a bag is truly positive and eliminate false positives within the same bag.
+The disadvantage of this approach stems from removing instances considered as false positives from partially grown trees without updating the existing tree structure.~\citet{Bjerring2011} then enhanced this approach by creating the method Multi-Instance Rule Induction (MIRI), which eliminates any possibility of a suboptimal split because the tree is discarded and regrown.
 Other popular methods include MIBoost~\citep{Hall2009}, MIWrapper~\citep{Frank2003}, and Two-Level Classifier (TLC)~\citep{Wang2014}.
 
-For most of the methods described above, implicit or explicit assumptions have been made about the distribution of the data.
+For most of the methods described above, implicit or explicit assumptions have been made about the distribution of the data~\citep{2017-KNOSYS-MIMV}.
 Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}.
-The proposed method, MIRSVM, is a general method that uses support vector machines to design a MIL model without making prior assumptions about the data.
-Classifiers of this type are known to provide better generalization capabilities and performance, as well as sparser models.
+MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data.
+Classifiers of this type are known to provide better generalization capabilities, performance, and sparser models.
 
 \subsection{Support Vector Machines}\label{subsec:svms}
-Most classical learning techniques require knowledge of the data distribution to build accurate models.
-This is a serious restriction because, in most cases, the data distribution is unknown~\citep{Kecman2001}.
+Most classical learning techniques require knowledge of the data distribution to build accurate models, which is a serious restriction because, in most cases, the distribution is unknown~\citep{Kecman2001}.
 SVMs represent learning techniques that have been introduced under the \textit{structural risk minimization} (SRM) framework and VC theory.
@@
 In the context of classification, this problem is approached by searching for the optimal \textit{maximal margin} of separability between classes~\citep{carrasco2015multi,fan2017mreklm}.
-Since most real-world datasets are non-linearly separable, ~\citet{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}:
-\begin{subequations} 
-\label{eq:primalsvm}
-\begin{alignat}{2}
-\min\limits_{\bm w,b,\bm\xi}& {\,\,} \frac{1}{2}||\bm{w}||^2 + \frac{C}{m}\sum_{i=1}^m \xi_i \tag{\ref{eq:primalsvm}} \\ 
-\text{s.t.}& {\,\,} y_i(\langle\bm{w},\bm{x}_i\rangle + b) \geq 1 - \xi_i,\,\, \forall i \in \{1,\ldots,m\}  \\
-{} & {\,\,} \xi_i \geq 0,\,\, \forall i \in \{1,\ldots,m\},
-\end{alignat}
-\end{subequations} 
-where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term, and $C \in \reals$ is the penalty parameter that controls the trade-off between margin maximization and classification error minimization.
-The slack variable $\bm \xi \in \reals^m$ allows for optimizing over sample errors.
+Since most real-world datasets are non-linearly separable, ~\citet{Cortes1995} introduced the \textit{Soft-Margin L$1$-SVM}.
 However, if the training dataset is not linearly separable, the classifier may not have a good generalization capability~\citep{Nocedal2006}.
@@
 \text{s.t.} &\,\,\,\, \sum_{i=1}^m \alpha_iy_i = 0,  \\
-&\,\,\,\, 0 \leq \alpha_i \leq \frac{C}{m},\,\, \forall i \in \{1,\ldots,m\}. 
+&\,\,\,\, 0 \leq \alpha_i \leq \frac{C}{m},\,\, \forall i \in \{1,\ldots,m\}, 
 \end{alignat}
 \end{subequations}
+
+where $C \in \reals$ is the penalty parameter that controls the trade-off between margin maximization and classification error minimization.
 
@@
 It tries to identify the key instance from each positive bag that makes the bag positive by assuming it has the highest margin value~\citep{Herrera2016}.
-Instances from positive bags are selected as bag-representatives, and the algorithm iteratively creates a classifier that separates those representatives from all instances from the negative bags.
-Using bag-representatives from one class and all instances from the other is an example of an approach that combines rules from the SMI assumption and the collective assumption.
-This approach was used in the context of active learning.~\citet{Wang20143106} proposed a multi-criteria decision making system that measures the significance of unlabeled instances and selects the best instance iteratively using MISVM.
-A disadvantage of the approach MISVM takes, stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\citet{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which does not discard the negative instances of the positive bags.
-It rather tries to identify the instances within positive bags that are negative and utilize them in the construction of the negative margin.
+Using bag-representatives from the positive class class and all instances from the other is an example of an approach that combines rules from the SMI assumption and the collective assumption.~\citet{Wang20143106} proposed a multi-criteria decision making system that measures the significance of unlabeled instances and selects the best instance iteratively using MISVM.
+A disadvantage of this approach stems from the assumption that all instances within positive bags are also positive, which is an implicit step in the initialization of MISVM.~\citet{Andrews2002} also proposed a second mixed-integer instance-level approach, named mi-SVM, which tries to identify the instances within positive bags that are negative and utilize them in the construction of the negative margin.
 The main disadvantage of these approaches is that they create an imbalanced class problem that favors the negative class, resulting in a biased classifier.
@@
 
-One of the first bag-level approaches to the multi-instance SVM problem was proposed by \citet{Smola2002}, who defined a bag-level kernel, which determines the similarity between two bags in a higher dimensional space.
-Using such a kernel, the margin can be optimized over bags without any modification to the SVM problem~\citep{Herrera2016}.~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance.
+One of the first bag-level approaches to the multi-instance SVM problem was proposed by \citet{Smola2002}, who defined a bag-level kernel, which determines the similarity between two bags in a higher dimensional space.~\citet{Blaschko2006} propose conformal kernels which manipulate each attribute's dimension based on its importance.
 
@@
 all instances are guaranteed to be negative.
-This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule, $s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n}$.
+This is evident during the representative selection process, by taking the index of the maximum output value within each bag based on the current hyperplane using the following rule:
+\begin{equation}
+\label{eq:SIPrimal}
+\centering
+s_I = \text{argmax}_{i \in I} (\langle \bm w,\, \bm x_i \rangle + b),\, \forall I \in \set{1,\ldots,n},
+\end{equation}
+where $\bm w \in \reals^d$ is a $d$-dimensional weight vector, $b \in \reals$ is a bias term.
 In other words, the most positive instance is chosen from each positive bag and the least negative instance is chosen from each negative bag (instances with the largest output value based on the current hyperplane), pushing the decision boundary  towards the positive bags.
@@
 \end{subequations} 
-where $\bm S_I$ is a set of the bag representatives' indices and $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$.
+where $\bm S_I$ is a set of the bag representatives' indices, $\bm x_{s_I}$ is the instance representative of bag $\mathcal{B}_I$, and the slack variable $\bm \xi \in \reals^m$ allows for optimizing over bag errors.
 Note the variables in MIRSVMs formulation are the similar to those of the traditional SVM, except they are now representing each bag as an instance.
+This is one of the benefits of the MIRSVM formulation, whereby using a bag-representative selector, traditional SVM solvers can be used for new data representations such the multi-instance data.
+
 Solving the optimization problem given in Equation~\eqref{eq:primalmirsvm} using a quadratic programming solver is a computationally expensive task due to the number of constraints, which scales by the number of bags $n$, as well as the calculation of the inner product between two $d$-dimensional vectors in constraint~\eqref{eq:primalmirsvm1}.
@@
 
-The dual can be formed by taking the Lagrangian of~\eqref{eq:primalmirsvm}, given by Equation~\eqref{eqn:svmlagrangian}, where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers.
-\begin{equation}
-\centering \label{eqn:svmlagrangian}
-\resizebox{.9\textwidth}{!}{$
-\begin{aligned}
-\mathcal{L}\left(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}\right) = \frac{1}{2}\sum_{j=1}^d w_j^2  + \frac{C}{n}\sum_I \xi_I - \sum_I{\beta_I \xi_I} - \sum_I{\alpha_I\left(Y_I\left(\sum_{j=1}^d w_j x_{s_Ij} + b\right) -1 + \xi_I\right)}
-\end{aligned}$} 
-\end{equation}
-
-At optimality~\citep{Boyd2004}, $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$ and the following conditions are met:
-\begin{align}
-&\frac{\partial\mathcal{L}}{\partial w_j}: w_j = \sum_I{\alpha_I\,Y_I\, x_{s_I\,j}},\,\forall j \in \{1,\ldots,d\}\label{eqn:optcond1}\\
-&\frac{\partial\mathcal{L}}{\partial b}: \sum_I{\alpha_IY_I} = 0,\label{eqn:optcond2}\\
-&\frac{\partial\mathcal{L}}{\partial\xi_I}: \alpha_I + \beta_I = \frac{C}{n},\,\forall I \in \set{1,\ldots,n}\label{eqn:optcond3} 
-\end{align}
-\newpage
-By substituting Equations~\eqref{eqn:optcond1},~\eqref{eqn:optcond2}, and~\eqref{eqn:optcond3} into the Lagrangian in~\eqref{eqn:svmlagrangian}, the dual MIRSVM formulation becomes the following:
+The dual can be formed by taking the Lagrangian of~{\eqref{eq:primalmirsvm}}, $\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta})$, and substituting the optimality conditions (from $\bigtriangledown_{w,b,\xi}\mathcal{L}(\bm{w},b,\bm{\xi},\bm{\alpha},\bm{\beta}) = 0$), where $\bm \alpha$ and $\bm \beta$ are the non-negative Lagrange multipliers.
+The dual MIRSVM formulation becomes the following:
 \begin{subequations} 
@@
 
-We then kernelize the dual function by replacing the inner product of the samples in feature space with their corresponding kernel values, $\spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right)$.
-The dual function is now written as:
-\begin{subequations} 
-\label{eq:dualmirsvm}
-\begin{alignat}{2}
-\max\limits_{\bm \alpha}& \sum_I \alpha_I - \frac{1}{2}\sum_I \sum_{K\in I} \alpha_I \alpha_K Y_I Y_K  \spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right) \tag{\ref{eq:dualmirsvm}}\\
-\text{s.t.}&  \sum_I{\alpha_IY_I} = 0\,  \\
-{} & 0 \leq \alpha_I \leq \frac{C}{n},\, \forall I \in \set{1,\ldots,n}.
-\end{alignat}
-\end{subequations}
-
-One of the biggest advantages of the dual SVM formulation is the sparseness of the resulting model.
-This is because support vectors, instances that have their corresponding $\alpha_I \neq 0$, are only considered when forming the decision boundary.
+We then kernelize the dual by replacing the inner product of the samples in feature space with their corresponding kernel values, $\spa{K}\left(\bm{x}_{s_I},\bm{x}_{s_K}\right)$.
+One of the biggest advantages of the dual SVM formulation is the sparseness of the resulting model, because support vectors, instances that have their corresponding $\alpha_I \neq 0$, are only considered when forming the decision boundary.
 MIRSVM uses a Gaussian RBF kernel, given by Equation~\eqref{eq:gaussiankernel}, where $\sigma$ is the Gaussian shape parameter.
@@
 \end{tikzpicture}}
-\caption{MIRSVM flow diagram.
-This figure represents a summary of the steps performed by the MIRSVM algorithm.
-The representatives are first randomly initialized and continuously updated according to the current hyper-plane, which is found using a quadratic programming (QP) solver.
+\caption{This figure represents a summary of the steps performed by MIRSVM.
+The representatives are first randomly initialized, then continuously updated according to the current hyper-plane, which is found using a quadratic programming (QP) solver.
 Upon completion, the model is returned along with the optimal bag-representatives.}
@@
 \State $\bm S_{old} \leftarrow \bm S$
-\State $\bm G \leftarrow (\bm Y_S \times \bm Y_S) \bm \cdot \mathcal{K}\left( \bm X_S,\,\bm X_S,\,\sigma\right)$ \Comment{Build Graham matrix}
+\State $\bm G \leftarrow (\bm Y_S \times \bm Y_S) \bm \cdot \mathcal{K}\left( \bm X_S,\,\bm X_S,\,\sigma\right)$ \Comment{Build Gram matrix}
 \State $\bm \alpha \leftarrow \text{ quadprog}\left(\bm G, \bm{-1}^n, \bm Y_S, \bm 0^n, \bm 0^n, \bm C^n\right)$ \Comment{Solve QP Problem}
@@
 \newpage
-This formulation is designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances.
-MISVM allows multiple representatives to be chosen from negative bags and limits positive bag-representatives to be one, while MIRSVM allows for balanced bag-representative selection, where each bag is allowed one.
+The MIRSVM formulation and representative selector are designed to utilize and select representatives from positive and negative bags, unlike MISVM, which only optimizes over representatives from positive bags, while flattening the negative bag instances.
+MISVM allows multiple representatives to be chosen from negative bags and limits the number of positive bag-representatives to be one, while MIRSVM allows for balanced bag-representative selection, where bags of each class are allowed a representative.
 MISVM also uses a wrapper method to initialize the positive bag-representatives by taking the mean vector of the instances within each positive bag.

### 2017-09-22 prototype_code/mirsvm_vs_misvm.m

@@ -53,7 +53,7 @@ O = Gp*alphay + bias;
 O = reshape(O,length(x1),length(x2));
 [~,h] = contour(x1,x2,(O'),[0 0],'k','DisplayName','decision boundary');
 set(h,'linewidth',1.5);
-h = plot(X(S,1),X(S,2),'kx','DisplayName','support vectors');
+h = plot(X(S,1),X(S,2),'kx','DisplayName','support vectors','linewidth',2);
 set(h,'linewidth',1.5);
 [~,h] = contour(x1,x2,(O'),[1 1],'b--','DisplayName','positive margin');
 set(h,'linewidth',1.5);
@@ -63,7 +63,6 @@ axis([minnum maxnum minnum+0.5 maxnum-1]);
 set(gca,'TickLabelInterpreter', 'tex');
 title('MIRSVM Decision Boundary','Interpreter','latex');
 set(gca,'fontsize',11);
-legend('show');
 vars = [1.1 1.1];
 for b=1:bnump
     indB = find(B == b);
@@ -78,6 +77,8 @@ for b=1:bnumn
     meanB = mean([minx; maxx]);
     circle(meanB(1),meanB(2),vars(b),0.01,1,[0.9 0.1 0.1]);
 end
+legend({'instance in positive bag','instance in negative bag','decision boundary','support vectors','positive margin','negative margin'});
+
 
 %% MISVM is here
 [alphay,bias,S,indSV] = MISVM(X,Y,B,C,param,options,Bsizes);
@@ -104,7 +105,7 @@ O = Gp*alphay + bias;
 O = reshape(O,length(x1),length(x2));
 [~,h] = contour(x1,x2,(O'),[0 0],'k','DisplayName','decision boundary');
 set(h,'linewidth',1.5);
-h = plot(Xn(indSV,1),Xn(indSV,2),'kx','DisplayName','support vectors');
+h = plot(Xn(indSV,1),Xn(indSV,2),'kx','DisplayName','support vectors','linewidth',2);
 set(h,'linewidth',1.5);
 [~,h] = contour(x1,x2,(O'),[1 1],'b--','DisplayName','positive margin');
 set(h,'linewidth',1.5);
@@ -114,7 +115,6 @@ axis([minnum maxnum minnum+0.5 maxnum-1]);
 set(gca,'TickLabelInterpreter', 'tex');
 title('MISVM Decision Boundary','Interpreter','latex');
 set(gca,'fontsize',11);
-legend('show');
[…]

### 2017-09-22 prototype_code/plot2D.m

@@ -1,0 +1,18 @@
+function [] = plot2D(X,Y,f)
+%% Plots 2D data with 2 classes in figure f
+figure(f);
+hold on;
+grid on;
+
+indp = (Y==1);
+indn = (Y==-1);
+plot(X(indp,1),X(indp,2),'bo','DisplayName','instance in positive bag');
+plot(X(indn,1),X(indn,2),'ro','DisplayName','instance in negative bag');
+
+xlabel('$x_1$','Interpreter','latex');
+ylabel('$x_2$','Interpreter','latex');
+set(gca,'fontsize',11);
+set(gca,'TickLabelInterpreter', 'latex');
+
+%hold off;
+end

### 2017-09-22 ArticleRevision/article/article.tex
Added a missing comma

@@
 A major challenge of these methods is that the distributions of positive and negative bags affect their performance~\citep{Chen2006,Chen2004}.
-Alternatively \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
+Alternatively, \citet{Fu2011} models the distribution of negative bags with Gaussian kernels, which can prove difficult when the quantity of data is limited.
 

### 2018-02-01 Pattern Recognition R2/article/article.tex
Added paper documents from dropbox

--- 2017-09-22 ArticleRevision/article/article.tex
@@
 The experimental study evaluates and compares the performance of this proposal against $11$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis.
-The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as this proposal's overall superior performance against other multi-instance SVM models.
+The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as MIRSVM's overall superior performance against other multi-instance SVM models, having an average accuracy of $82.6\%$, which is $2.5\%$ better than the best performing state-of-the-art MI classifier.
 \end{abstract}
@@
 \textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival \citep{qi2007,cao2017weakly}, human action recognition \citep{Yi2016}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).
+In the case of drug activity prediction, MIL allows molecules to be represented as related instances contained in a bag rather than single instances with their own labels.
 
@@
 To address the limitations presented by MIL algorithms, this paper proposes a novel support vector machine formulation with a bag-representative selector, called Multiple-Instance Representative Support Vector Machine (MIRSVM).
-SVMs are known to perform well when data is limited, therefore combining them with a novel bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without assuming the bags' internal distributions.
+SVMs are known to perform well when data is limited, therefore combining them with a novel bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without making specific assumptions about the bags' internal distributions.
 The algorithm selects bag-representatives iteratively according to the standard MI assumption, ensuring known information, such as the negative bag labels, are fully utilized during the training process.
@@
 The dual formulation is kernelized with a Gaussian radial basis function, which calculates the distances between bag representatives.
-\newpage
+
 \iitem Devising a unique bag-representative selection method that makes no presumptions about the underlying distributions of the instances within each bag, while maintaining the default MI assumption.
@@
 Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}.
-MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data.
+Our prososed contribution, MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data.
 Classifiers of this type are known to provide better generalization capabilities, performance, and sparser models.
@@
 
-SimpleMI achieves the highest rank and competitive run times because, rather than use the instances in each bag to train a model, it takes the mean value of the instances in a bag and uses that for training.
+SimpleMI achieves the highest rank and competitive run times because, rather than using the instances in each bag to train a model, it takes the mean value of the instances in a bag and uses that for training.
 Even though SimpleMI has fast run-times, its performance over the previous metrics has been shown to be random and not as effective as the bag-level methods.
@@
 The results, according to a variety of performance metrics, were compared and further validated using statistical analysis with non-parametric tests which highlight the advantages of using bag-level based and ensemble learners, such as miGraph, Bagging, and Stacking, while showing the instance-level based learners performed poorly in comparison or were deemed as strongly biased and unstable classifiers.
+This was especially reflected in the meta-ranks comparison, shown in Table~\ref{tab:metarank}, over Accuracy, Precision, Recall, Cohen's Kappa, AUC, and run time, where instance-level learners were ranked last, whereas bag-level and ensemble learners were better in rank, and MIRSVM ranked first.
 Our proposal, MIRSVM, performs statistically better, neither compromising accuracy nor run-time while displaying a robust performance across all of the evaluated datasets.
 
+MIRSVM could be further improved by invesitgating the following approaches.
+Rather than using a QP solver at each iteration of MIRSVM, a different optimal solver could be experimented with.
+Due to the run time implications of using a QP solver, using a different solver might improve MIRSVM's scalability.
+Another area to investigate would be implementing MIRSVM in high-performance distributed environments.
+A third concept to explore would be testing MIRSVM on highly imbalanced multi-instance datasets and observe its performance.
+MIRSVM could also be extended to handle multi-class multi-instance problems by using traditional methods such as one-versus-one, where $c(c - 1)/2$ classifiers are trained for a $c$-class problem, and one-versus-all, where a single classifier is trained per class~\citep{bishop2007pattern}.
+
 \section*{Acknowledgment}
-This research was supported by the Spanish Ministry of Economy and Competitiveness, project TIN2014-55252-P, and by FEDER funds.
+This research was supported by the Spanish Ministry of Economy and Competitiveness, project TIN2017-83445-P and by FEDER funds.
 

### 2018-02-01 Pattern Recognition R2/article_with_markings/article.tex
Added paper documents from dropbox

--- 2018-02-01 Pattern Recognition R2/article/article.tex
@@
 The experimental study evaluates and compares the performance of this proposal against $11$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis.
-The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as MIRSVM's overall superior performance against other multi-instance SVM models, having an average accuracy of $82.6\%$, which is $2.5\%$ better than the best performing state-of-the-art MI classifier.
+The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as MIRSVM's overall superior performance against other multi-instance SVM models{\color{red}, having an average accuracy of $82.6\%$, which is $2.5\%$ better than the best performing state-of-the-art MI classifier.}
 \end{abstract}
@@
 \textit{Multi-instance} (MI) learning is a generalization of \textit{supervised learning} that has been recently been gaining interest because of its applicability to many real-world problems such as webmining and text categorization {\citep{Andrews2002}}, image classification and retreival \citep{qi2007,cao2017weakly}, human action recognition \citep{Yi2016}, medical diagnosis and imaging {\citep{Herrera2016}}, and bioinformatics {\citep{Dietterich1997}} (drug activity prediction and protein identification).
-In the case of drug activity prediction, MIL allows molecules to be represented as related instances contained in a bag rather than single instances with their own labels.
+{\color{red}In the case of drug activity prediction, MIL allows molecules to be represented as related instances contained in a bag rather than single instances with their own labels.}
 
@@
 To address the limitations presented by MIL algorithms, this paper proposes a novel support vector machine formulation with a bag-representative selector, called Multiple-Instance Representative Support Vector Machine (MIRSVM).
-SVMs are known to perform well when data is limited, therefore combining them with a novel bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without making specific assumptions about the bags' internal distributions.
+SVMs are known to perform well when data is limited, therefore combining them with a novel bag-representative selector aims to remedy class imbalance caused by limited positive bag instances, without {\color{red}making specific assumptions about the bags' internal distributions}.
 The algorithm selects bag-representatives iteratively according to the standard MI assumption, ensuring known information, such as the negative bag labels, are fully utilized during the training process.
@@
 Selecting a method that is robust for a problem such as MIL can be difficult when little is known about the nature of the data, especially considering the unknown distribution of the instances within bags~\citep{2015-KAIS,2016-INS-MIARM}.
-Our prososed contribution, MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data.
+{\color{red}Our prososed contribution,} MIRSVM, is an iterative method that uses SVMs to design a MIL model without making prior assumptions about the data.
 Classifiers of this type are known to provide better generalization capabilities, performance, and sparser models.
@@
 
-SimpleMI achieves the highest rank and competitive run times because, rather than using the instances in each bag to train a model, it takes the mean value of the instances in a bag and uses that for training.
+SimpleMI achieves the highest rank and competitive run times because, {\color{red}rather than using the instances} in each bag to train a model, it takes the mean value of the instances in a bag and uses that for training.
 Even though SimpleMI has fast run-times, its performance over the previous metrics has been shown to be random and not as effective as the bag-level methods.
@@
 The results, according to a variety of performance metrics, were compared and further validated using statistical analysis with non-parametric tests which highlight the advantages of using bag-level based and ensemble learners, such as miGraph, Bagging, and Stacking, while showing the instance-level based learners performed poorly in comparison or were deemed as strongly biased and unstable classifiers.
-This was especially reflected in the meta-ranks comparison, shown in Table~\ref{tab:metarank}, over Accuracy, Precision, Recall, Cohen's Kappa, AUC, and run time, where instance-level learners were ranked last, whereas bag-level and ensemble learners were better in rank, and MIRSVM ranked first.
-Our proposal, MIRSVM, performs statistically better, neither compromising accuracy nor run-time while displaying a robust performance across all of the evaluated datasets.
-
-MIRSVM could be further improved by invesitgating the following approaches.
+{\color{red}This was especially reflected in the meta-ranks comparison, shown in Table~\ref{tab:metarank}, over Accuracy, Precision, Recall, Cohen's Kappa, AUC, and run time, where instance-level learners were ranked last, whereas bag-level and ensemble learners were better in rank, and MIRSVM ranked first.} Our proposal, MIRSVM, performs statistically better, neither compromising accuracy nor run-time while displaying a robust performance across all of the evaluated datasets.
+
+{\color{red}MIRSVM could be further improved by invesitgating the following approaches.
 Rather than using a QP solver at each iteration of MIRSVM, a different optimal solver could be experimented with.
@@
 MIRSVM could also be extended to handle multi-class multi-instance problems by using traditional methods such as one-versus-one, where $c(c - 1)/2$ classifiers are trained for a $c$-class problem, and one-versus-all, where a single classifier is trained per class~\citep{bishop2007pattern}.
+}
 

### 2018-02-01 Pattern Recognition R2/letter/letter.tex
Added paper documents from dropbox

\documentclass[a4paper,notitlepage]{article}
\usepackage[colorlinks,linkcolor=blue,citecolor=green,filecolor=magenta,urlcolor=blue]{hyperref}
\usepackage{url}
\setlength{\parskip}{2ex}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={210mm,297mm},
 left=20mm,
 right=20mm,
 top=20mm,
 bottom=20mm,
 }

\begin{document}

\noindent \textbf{\small MANUSCRIPT NUMBER:} PR-D-17-01043R1

\noindent \textbf{\small TITLE:} {\small MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives}

\noindent \textbf{\small AUTHORS:} {\small Gabriella Melki, Alberto Cano, and Sebasti\'{a}n~Ventura}

\bigskip

\noindent Dear Editor and Reviewers,

\noindent We would like to thank you for your kind words concerning our contribution. We have modified the article to reflect the reviewers' suggestions. The following is our explanation of the changes made, as well as how they address the comments raised by the reviewers. The bold text corresponds to the original comments. We are grateful to the reviewers for their constructive comments and suggestions in their revisions. They definitely have helped us improve the quality of the article.

\noindent We hope that the reviewers find the proposed revision of our manuscript satisfactory. We look forward to hearing from you soon.

\section{Reviewer \#2}

\noindent \textbf{\textit{The authors did a great job addressing all the points raised. I have no further comments and would like to recommend the paper for publication. Thank you. }}

\noindent We appreciate the positive feedback given towards this paper.

\section{Reviewer \#3}

\noindent \textbf{\textit{The paper proposes a novel approach tackling multi-instance classification problems where bags or instances are labeled depending on whether they contain at least one positive instance or not. The topic is relevant for different fields of application and the publication is for sure relevant for this journal. The article is very clearly explained, very well written and thoroughly evaluated. The comparisons with other approaches all come with statistical significance tests, which makes the claims solid. I definitely argue for publication.}}

\medskip

\noindent We tried to be as comprehensive as possible with the experiemental environment when testing our method and intend on continuing with this method of experimentation. We thank and appreciate your positive and constructive comment on this.

\noindent \textbf{\textit{Comment 1: It would be beneficial to add a short sentence in the introduction to explain with an example why concretely MIL is beneficial for training / deploying in real applications. The authors cite various fields (e.g. web mining, action recognition) and for at least one of these it would be nice to have a short statement about why MIL is useful for that application. I guess this can be found in the respective cited works, but for the purpose of self containment an example would be nice - e.g.: why is it useful to have a method to train with bags for action recognition problems?}}

\medskip

\noindent Adding an example of why MIL is useful, rather than using traditional learning, would definitely add to the quality of the paper by making it more self contained. We thank the reviewer for pointing this out and have added a sentence to the introduction with an example of how MIL better represents the real-world problem of drug activity prediction, rather than a traditional dataset. Specifically: ``\textit{In the case of drug activity prediction, MIL allows molecules to be represented as related instances contained in a bag rather than single instances with their own labels.}" Another example, for the case of action recognition, individual instances represent some activity data recorded over time, and the task at hand would be to determine whether a specific action of interest is being performed for a majority of the time. In this case, a bag would represent actions performed over time, and is labeled positively (e.g. for action ``drinking from a cup'') if at least one instance in the bag indicates drinking from a cup.

\newpage
\noindent \textbf{\textit{Comment 2: In the abstract (and even more in the conclusions) it is quite usual to have some concrete numbers defining the performance. Like that, someone reading the abstract already can get an idea of how much better this algorithm could get compared to other state-of-the-art approaches.}}

\medskip

\noindent We took your advice on this and added some more specifics on the performance of MIRSVM against the competing algorithms. Since we used $6$ metrics to measure and evaluate performance, we decided to mention the accuracy in the abstract and conclusion, just for the sake of being comprehensive. We hope that in doing this we fulfilled your suggestion.

\noindent \textbf{\textit{Comment 3: The whole approach, along with other related ones, is suitable for problems involving exactly one positive and one negative class. It would be nice if the authors could briefly discuss about ideas (if there are any around) of how to extend such an approach for problems where there are negative bags and positive bags with different dominant classes. I'm thinking here about modelling null class as the negative class and then different (more than one) positive classes. But maybe it's not relevant, it just occurred to my mind while reading the paper.}}

\medskip

\noindent Thank you for the interesting question. The origin and core of MIL stems from a binary classification problem and the standard assumption by Dietterich et al., where bags obtain a negative label if all instances within it are negative, and otherwise the bag is labeled as positive. To the best of our knowledge, we have not encountered a multi-class MIL problem. However, one idea for an extension of MIRSVM for a multi-class application would be to use methods such as one-vs-one (pairwise classifier) or one-vs-all. These ensemble methods are known to be a little expensive in terms of run time but they merit investigation if the multi-class problem existed. We added a short discussion on this in Section 5 and appreciate you bringing our attention to this topic.

\noindent \textbf{\textit{Comment 4: Just a couple small clarifications / grammar issues in the text: 
\begin{itemize}
\item[-] Section 1 (page 2): instead of ``assuming the bags' internal distributions" I'd write ``making specific assumptions about the bags' internal distributions" 
\item[-]  Section 2.2 (page 5): I'd complete the sentence starting with ``MIRSVM, is an iterartive...", writing ``Our prososed contribution, MIRSVM, is an iterative..." 
\item[-]  Section 4.7: ``rather than use the instances" $\rightarrow$ ``rather than using the instances" 
\end{itemize}}}

\medskip

\noindent Thank you for pointing those clarifications and grammar issues. As you have suggested, we modified the text to reflect your suggestions.

\noindent \textbf{\textit{Within (or after) the conclusion, it would be nice to have some kind of outlook - or is it kind of ``problem solved conclusively"? Are there still areas of improvement to be addressed? }}

\medskip

\noindent Thank you for looking ahead. One area to invesitgate would be to use a different SVM solver (instead of a quadratic programming, QP, solver) during the training procedure for the sake of speed. Another would be to investigate distributed implementations of the algorithm. A third idea would be to experiment with highly imbalanced datasets and observe how the algorithm performs. We have included these open ideas in the conclusion. We appreciate you mentioning this.

\end{document}
